---
title: "Supplementary Materials"
output: html_document
date: "2025-09-05"
---

## Appendix

\landscape
\footnotesize

## Table 2

| Performance Measure | Empirical Calculation | MCSE |
|---|---|---|
| **Absolute Criteria** | | |
| Bias | $\bar{B} - \beta$ | $\sqrt{S_B^2/K}$ |
| MSE | $\frac{1}{K}\sum_{k=1}^{K}(B_k - \beta)^2$ | $\sqrt{\frac{1}{K}[S_B^4(k_B - 1) + 4S_B^2 g_B(\bar{B} - \beta) + 4S_B^2(\bar{B} - \beta)^2]}$ |
| RMSE | $\sqrt{\frac{1}{K}\sum_{k=1}^{K}(B_k - \beta)^2}$ | $\sqrt{\frac{K-1}{K}\sum_{j=1}^{K}(\text{RMSE}_{(j)} - \text{RMSE})^2}$ |
| Median Estimate | $\textit{Mdn}(B)$ | — |
| Median Bias | $\textit{Mdn}(B) - \beta$ | — |
| MAD | $\textit{Mdn}(\|B_k - \textit{Mdn}(B)\|)$ | — |
| Median RMSE | $\sqrt{\text{Bias}_{\textit{Mdn}}^2 + \text{MAD}^2}$ | — |
| **Relative Criteria** | | |
| Relative Bias | $(\frac{\bar{B}}{\beta})- 1$ | $\sqrt{S_B^2/(K\beta^2)}$ |
| Percent Relative Bias | $(\frac{\bar{B}}{\beta})- 1\times 100\%$ | — |
| Relative MSE | $\frac{(\bar{B} - \beta)^2 + S_B^2}{\beta^2}$ | $\sqrt{\frac{1}{K\beta^4}[S_B^4(k_B - 1) + 4S_B^2 g_B(\bar{B} - \beta) + 4S_B^2(\bar{B} - \beta)^2]}$ |
| Relative RMSE | $\sqrt{\frac{(\bar{B} - \beta)^2 + S_B^2}{\beta^2}}$ | $\sqrt{\frac{K-1}{K}\sum_{j=1}^{K}(\text{rRMSE}_{(j)} - \text{rRMSE})^2}$ |
| Relative Median Bias | $\frac{\text{Mdn}(B) - \beta}{\beta}$ | — |
| Percent Relative Median Bias | $\frac{\textit{Mdn}(B) - \beta}{\beta} \times 100\%$ | — |
| **Standard Error Assessment** | | |
| Mean SE | $\overline{SE} = \frac{1}{K}\sum_{k=1}^{K}\widehat{SE}_k$ | — |
| SE Ratio | $\overline{SE}/S_B$ | — |
| **Hypothesis Testing** | | |
| Rejection Rate | $r_\alpha = \frac{1}{K}\sum_{k=1}^{K}I(P_k < \alpha)$ | $\sqrt{r_\alpha(1-r_\alpha)/K}$ |
| **Confidence Intervals** | | |
| Coverage | $c_\beta = \frac{1}{K}\sum_{k=1}^{K}I(A_k \leq \beta \leq B_k)$ | $\sqrt{c_\beta(1-c_\beta)/K}$ |
| Average Width | $\bar{W} = \bar{B} - \bar{A}$ | $\sqrt{S_W^2/K}$ |

*Note.* $B$ = parameter estimator; $\beta$ = true parameter value; $K$ = number of replications; $S_B^2$ = sample variance; $k_B$ = standardized kurtosis; $g_B$ = standardized skewness; $I(\cdot)$ = indicator function; $P_k$ = p-value from replication $k$; $\alpha$ = significance level; $A_k$, $B_k$ = CI endpoints; $S_W^2$ = variance of CI widths. MCSE = Monte Carlo Standard Error. Dashes indicate MCSEs not computed for these measures.

\endlandscape
\normalsize

### Complete plots for study 1

```{r complete-plots-study1, echo=FALSE, fig.width=12, fig.height=16, fig.align='center', message=FALSE, warning=FALSE}
# ========= COMPLETE STUDY 1 PLOTS (ALL DATA) =========

study1_data <- prepare_study1_data(results_study_1)

# Bias - all conditions
plot_bias(study1_data$bias, shapes = SHAPES_4, ltys = LTYS_4, 
          title = "Study 1: Bias (All Conditions)")

# Relative Bias - all conditions
plot_bias(study1_data$bias_relative, shapes = SHAPES_4, ltys = LTYS_4,
          title = "Study 1: Relative Bias (All Conditions)", bias_type = "relative")

# RMSE - all conditions
plot_rmse(study1_data$rmse, shapes = SHAPES_4, ltys = LTYS_4,
          title = "Study 1: RMSE (All Conditions)")

# Relative RMSE - all conditions
plot_rmse(study1_data$rmse_relative, shapes = SHAPES_4, ltys = LTYS_4,
          title = "Study 1: Relative RMSE (All Conditions)")

# SE/SD Ratio - all conditions
plot_sesd(study1_data$sesd, shapes = SHAPES_4, ltys = LTYS_4,
          title = "Study 1: SE/SD Ratio (All Conditions)")

# Coverage - all conditions
plot_coverage(study1_data$coverage, shapes = SHAPES_4, ltys = LTYS_4,
              title = "Study 1: Coverage (All Conditions)")

# Type I Error - all conditions
plot_type1(study1_data$type1, greys = GREYS_4,
           title = "Study 1: Type I Error (All Conditions)")

# Power - all conditions
plot_power(study1_data$power, greys = GREYS_4,
           title = "Study 1: Power (All Conditions)")
```

### Complete plots for study 2

#### Normal condition

```{r complete-plots-study2-normal, echo=FALSE, fig.width=12, fig.height=14, fig.align='center', message=FALSE, warning=FALSE}
# ========= COMPLETE STUDY 2 PLOTS - NORMAL DISTRIBUTION =========

study_2_normal_data <- prepare_study2_data(results_study_2$results, "normal")

# Bias - all conditions
plot_bias(study_2_normal_data$bias, shapes = SHAPES_3, ltys = LTYS_3,
          title = "Study 2 (Normal): Bias (All Conditions)")

# Relative Bias - all conditions
plot_bias(study_2_normal_data$bias_relative, shapes = SHAPES_3, ltys = LTYS_3,
          title = "Study 2 (Normal): Relative Bias (All Conditions)", bias_type = "relative")

# RMSE - all conditions
plot_rmse(study_2_normal_data$rmse, shapes = SHAPES_3, ltys = LTYS_3,
          title = "Study 2 (Normal): RMSE (All Conditions)")

# Relative RMSE - all conditions
plot_rmse(study_2_normal_data$rmse_relative, shapes = SHAPES_3, ltys = LTYS_3,
          title = "Study 2 (Normal): Relative RMSE (All Conditions)")

# SE/SD Ratio - all conditions
plot_sesd(study_2_normal_data$sesd, shapes = SHAPES_3, ltys = LTYS_3,
          title = "Study 2 (Normal): SE/SD Ratio (All Conditions)")

# Coverage - all conditions
plot_coverage(study_2_normal_data$coverage, shapes = SHAPES_3, ltys = LTYS_3,
              title = "Study 2 (Normal): Coverage (All Conditions)")

# Type I Error - all conditions
plot_type1(study_2_normal_data$type1, greys = GREYS_3,
           title = "Study 2 (Normal): Type I Error (All Conditions)")

# Power - all conditions
plot_power(study_2_normal_data$power, greys = GREYS_3,
           title = "Study 2 (Normal): Power (All Conditions)")
```

#### Nonnormal condition

```{r complete-plots-study2-nonnormal, echo=FALSE, fig.width=12, fig.height=14, fig.align='center', message=FALSE, warning=FALSE}
# ========= COMPLETE STUDY 2 PLOTS - NONNORMAL DISTRIBUTION =========

study_2_nonnormal_data <- prepare_study2_data(results_study_2$results, "nonnormal")

plot_bias(study_2_nonnormal_data$bias, shapes = SHAPES_3, ltys = LTYS_3,
          title = "Study 2 (Nonnormal): Bias (All Conditions)")

plot_bias(study_2_nonnormal_data$bias_relative, shapes = SHAPES_3, ltys = LTYS_3,
          title = "Study 2 (Nonnormal): Relative Bias (All Conditions)", bias_type = "relative")

plot_rmse(study_2_nonnormal_data$rmse, shapes = SHAPES_3, ltys = LTYS_3,
          title = "Study 2 (Nonnormal): RMSE (All Conditions)")

plot_rmse(study_2_nonnormal_data$rmse_relative, shapes = SHAPES_3, ltys = LTYS_3,
          title = "Study 2 (Nonnormal): Relative RMSE (All Conditions)")

plot_sesd(study_2_nonnormal_data$sesd, shapes = SHAPES_3, ltys = LTYS_3,
          title = "Study 2 (Nonnormal): SE/SD Ratio (All Conditions)")

plot_coverage(study_2_nonnormal_data$coverage, shapes = SHAPES_3, ltys = LTYS_3,
              title = "Study 2 (Nonnormal): Coverage (All Conditions)")

plot_type1(study_2_nonnormal_data$type1, greys = GREYS_3,
           title = "Study 2 (Nonnormal): Type I Error (All Conditions)")

plot_power(study_2_nonnormal_data$power, greys = GREYS_3,
           title = "Study 2 (Nonnormal): Power (All Conditions)")
```

#### Uniform condition

```{r complete-plots-study2-uniform, echo=FALSE, fig.width=12, fig.height=14, fig.align='center', message=FALSE, warning=FALSE}
# ========= COMPLETE STUDY 2 PLOTS - UNIFORM DISTRIBUTION =========

study_2_uniform_data <- prepare_study2_data(results_study_2$results, "uniform")

plot_bias(study_2_uniform_data$bias, shapes = SHAPES_3, ltys = LTYS_3,
          title = "Study 2 (Uniform): Bias (All Conditions)")

plot_bias(study_2_uniform_data$bias_relative, shapes = SHAPES_3, ltys = LTYS_3,
          title = "Study 2 (Uniform): Relative Bias (All Conditions)", bias_type = "relative")

plot_rmse(study_2_uniform_data$rmse, shapes = SHAPES_3, ltys = LTYS_3,
          title = "Study 2 (Uniform): RMSE (All Conditions)")

plot_rmse(study_2_uniform_data$rmse_relative, shapes = SHAPES_3, ltys = LTYS_3,
          title = "Study 2 (Uniform): Relative RMSE (All Conditions)")

plot_sesd(study_2_uniform_data$sesd, shapes = SHAPES_3, ltys = LTYS_3,
          title = "Study 2 (Uniform): SE/SD Ratio (All Conditions)")

plot_coverage(study_2_uniform_data$coverage, shapes = SHAPES_3, ltys = LTYS_3,
              title = "Study 2 (Uniform): Coverage (All Conditions)")

plot_type1(study_2_uniform_data$type1, greys = GREYS_3,
           title = "Study 2 (Uniform): Type I Error (All Conditions)")

plot_power(study_2_uniform_data$power, greys = GREYS_3,
           title = "Study 2 (Uniform): Power (All Conditions)")
```

```{r conv-table, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
library(kableExtra)
# ============================================================================
# STUDY 1: Convergence & Outliers Summary (APA Style - Landscape with longtable)
# ============================================================================
create_apa_convergence_table_study1 <- function(results_df) {
  results_df %>%
    filter(Parameter == "eta1") %>%
    select(
      Condition,
      Method, 
      Model, 
      Distribution, 
      SampleSize, 
      Reliability,
      N_Converged_This_Method,
      Convergence_Rate_This_Method,
      N_After_Global_Convergence,
      N_Outliers_This_Method,
      Outlier_Rate_This_Method,
      N_After_Global_Outlier,
      N_Final
    ) %>%
    mutate(
      Convergence_Rate_This_Method = round(Convergence_Rate_This_Method, 1),
      Outlier_Rate_This_Method = round(Outlier_Rate_This_Method, 1)
    ) %>%
    # Sort: Full model first, then Linear
    arrange(Condition, factor(Model, levels = c("Full", "Linear")), Method)
}

# Create table
conv_table_study1 <- create_apa_convergence_table_study1(results_study_1)

tab_caption_study1 <- "Convergence and Outlier Statistics (Study 1)"
tab_note_study1 <- "N Conv. = number of replications that converged for this method. Conv. Rate = percentage of replications that converged (%). N Global Conv. = sample size after requiring all methods to converge. N Outliers = number of outliers detected for this method. Outlier Rate = percentage of converged cases flagged as outliers (%). N Global Outlier = sample size after global outlier removal across methods. N Final = final sample size after all exclusions."

kableExtra::kbl(
  conv_table_study1,
  booktabs = TRUE,
  longtable = TRUE,
  align = c("l", "l", "l", "l", "r", "r",
            "r", "r", "r",
            "r", "r",
            "r", "r"),
  col.names = c("Condition", "Method", "Model", "Distribution", "N", "Reliability",
                "N Conv.", "Conv. Rate", "N Global Conv.",
                "N Outliers", "Outlier Rate", "N Global Outlier", "N Final"),
  caption = tab_caption_study1,
  linesep = ""
) %>%
  kableExtra::add_header_above(c(
    " " = 6,
    "Convergence" = 3,
    "Outliers" = 2,
    "Final" = 2
  )) %>%
  kableExtra::kable_styling(
    latex_options = c("hold_position", "repeat_header", "scale_down"),
    font_size = 6
  ) %>%
  kableExtra::collapse_rows(columns = 1, valign = "top", latex_hline = "major") %>%
  kableExtra::footnote(
    general = tab_note_study1,
    general_title = "Note.",
    threeparttable = TRUE,
    escape = TRUE
  ) %>%
  kableExtra::landscape()


# ============================================================================
# STUDY 2: Convergence & Outliers Summary (APA Style - Landscape with longtable)
# ============================================================================
create_apa_convergence_table_study2 <- function(results_df, equation = "eta4") {
  param <- ifelse(equation == "eta4", "eta1", "eta4")
  
  results_df$results %>%
    filter(Equation == equation, Parameter == param) %>%
    select(
      Condition,
      Method, 
      Model, 
      Distribution, 
      SampleSize, 
      Reliability,
      N_Converged_This_Method,
      Convergence_Rate_This_Method,
      N_After_Global_Convergence,
      N_Outliers_This_Method,
      Outlier_Rate_This_Method,
      N_After_Global_Outlier,
      N_Final
    ) %>%
    mutate(
      Convergence_Rate_This_Method = round(Convergence_Rate_This_Method, 1),
      Outlier_Rate_This_Method = round(Outlier_Rate_This_Method, 1)
    ) %>%
    # Sort: Full model first, then Linear
    arrange(Condition, factor(Model, levels = c("Full", "Linear")), Method)
}

# ============================================================================
# STUDY 2 - EQUATION ETA4 TABLE
# ============================================================================
conv_table_study2_eta4 <- create_apa_convergence_table_study2(results_study_2, "eta4")

tab_caption_study2_eta4 <- "Convergence and Outlier Statistics for Equation 4 (Study 2)"
tab_note_study2 <- "N Conv. = number of replications that converged for this method. Conv. Rate = percentage of replications that converged (%). N Global Conv. = sample size after requiring all methods to converge. N Outliers = number of outliers detected for this method. Outlier Rate = percentage of converged cases flagged as outliers (%). N Global Outlier = sample size after global outlier removal across methods. N Final = final sample size after all exclusions."

kableExtra::kbl(
  conv_table_study2_eta4,
  booktabs = TRUE,
  longtable = TRUE,
  align = c("l", "l", "l", "l", "r", "r",
            "r", "r", "r",
            "r", "r",
            "r", "r"),
  col.names = c("Condition", "Method", "Model", "Distribution", "N", "Reliability",
                "N Conv.", "Conv. Rate", "N Global Conv.",
                "N Outliers", "Outlier Rate", "N Global Outlier", "N Final"),
  caption = tab_caption_study2_eta4,
  linesep = ""
) %>%
  kableExtra::add_header_above(c(
    " " = 6,
    "Convergence" = 3,
    "Outliers" = 2,
    "Final" = 2
  )) %>%
  kableExtra::kable_styling(
    latex_options = c("hold_position", "repeat_header", "scale_down"),
    font_size = 6
  ) %>%
  kableExtra::collapse_rows(columns = 1, valign = "top", latex_hline = "major") %>%
  kableExtra::footnote(
    general = tab_note_study2,
    general_title = "Note.",
    threeparttable = TRUE,
    escape = TRUE
  ) %>%
  kableExtra::landscape()

# ============================================================================
# STUDY 2 - EQUATION ETA5 TABLE
# ============================================================================
conv_table_study2_eta5 <- create_apa_convergence_table_study2(results_study_2, "eta5")

tab_caption_study2_eta5 <- "Convergence and Outlier Statistics for Equation 5 (Study 2)"

kableExtra::kbl(
  conv_table_study2_eta5,
  booktabs = TRUE,
  longtable = TRUE,
  align = c("l", "l", "l", "l", "r", "r",
            "r", "r", "r",
            "r", "r",
            "r", "r"),
  col.names = c("Condition", "Method", "Model", "Distribution", "N", "Reliability",
                "N Conv.", "Conv. Rate", "N Global Conv.",
                "N Outliers", "Outlier Rate", "N Global Outlier", "N Final"),
  caption = tab_caption_study2_eta5,
  linesep = ""
) %>%
  kableExtra::add_header_above(c(
    " " = 6,
    "Convergence" = 3,
    "Outliers" = 2,
    "Final" = 2
  )) %>%
  kableExtra::kable_styling(
    latex_options = c("hold_position", "repeat_header", "scale_down"),
    font_size = 6
  ) %>%
  kableExtra::collapse_rows(columns = 1, valign = "top", latex_hline = "major") %>%
  kableExtra::footnote(
    general = tab_note_study2,
    general_title = "Note.",
    threeparttable = TRUE,
    escape = TRUE
  ) %>%
  kableExtra::landscape()
```

```{r trial-tables, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
# ============================================================================
# STUDY 1: Results Table (APA Style - Landscape with longtable)
# ============================================================================
create_apa_results_table_study1 <- function(results_df) {
  
  df <- results_df %>%
    select(
      Condition,
      Method,
      Model,
      Distribution,
      SampleSize,
      Reliability,
      Parameter,
      TrueValue,
      MeanEstimate,
      Bias_Mean,
      Bias_Mean_MCSE,
      RelativeBias_Mean,
      RelativeBias_MCSE,
      MedianEstimate,
      Bias_Median,
      MAD,
      Variance,
      Variance_MCSE,
      SD,
      SD_MCSE,
      MSE_Mean,
      MSE_Mean_MCSE,
      RMSE_Mean,
      RMSE_Mean_MCSE,
      RMSE_Median,
      Relative_MSE,
      Relative_MSE_MCSE,
      Relative_RMSE,
      Relative_RMSE_MCSE,
      MeanSE,
      SE_SD_Ratio,
      CoverageRate,
      CoverageRate_MCSE,
      CI_Width,
      CI_Width_MCSE,
      TypeI_Error,
      TypeI_Error_MCSE,
      Power,
      Power_MCSE
    ) %>%
    mutate(
      # Create combined columns with ± MCSE
      `Bias ± MCSE` = sprintf("%.3f ± %.3f", Bias_Mean, Bias_Mean_MCSE),
      `Rel. Bias ± MCSE` = ifelse(TrueValue == 0, "—", 
                                    sprintf("%.3f ± %.3f", RelativeBias_Mean, RelativeBias_MCSE)),
      `Variance ± MCSE` = sprintf("%.4f ± %.4f", Variance, Variance_MCSE),
      `SD ± MCSE` = sprintf("%.4f ± %.4f", SD, SD_MCSE),
      `MSE ± MCSE` = sprintf("%.4f ± %.4f", MSE_Mean, MSE_Mean_MCSE),
      `RMSE ± MCSE` = sprintf("%.4f ± %.4f", RMSE_Mean, RMSE_Mean_MCSE),
      `Rel. MSE ± MCSE` = ifelse(TrueValue == 0, "—",
                                   sprintf("%.4f ± %.4f", Relative_MSE, Relative_MSE_MCSE)),
      `Rel. RMSE ± MCSE` = ifelse(TrueValue == 0, "—",
                                    sprintf("%.4f ± %.4f", Relative_RMSE, Relative_RMSE_MCSE)),
      `Coverage ± MCSE` = sprintf("%.1f ± %.1f", CoverageRate, CoverageRate_MCSE),
      `CI Width ± MCSE` = sprintf("%.4f ± %.4f", CI_Width, CI_Width_MCSE),
      `Type I ± MCSE` = sprintf("%.1f ± %.1f", TypeI_Error, TypeI_Error_MCSE),
      `Power ± MCSE` = sprintf("%.1f ± %.1f", Power, Power_MCSE)
    ) %>%
    select(
      Condition, Method, Model, Distribution, SampleSize, Reliability, Parameter,
      TrueValue, MeanEstimate, `Bias ± MCSE`, `Rel. Bias ± MCSE`,
      MedianEstimate, Bias_Median, MAD,
      `Variance ± MCSE`, `SD ± MCSE`,
      `MSE ± MCSE`, `RMSE ± MCSE`, RMSE_Median,
      `Rel. MSE ± MCSE`, `Rel. RMSE ± MCSE`,
      MeanSE, SE_SD_Ratio,
      `Coverage ± MCSE`, `CI Width ± MCSE`,
      `Type I ± MCSE`, `Power ± MCSE`
    ) %>%
    mutate(
      TrueValue = round(TrueValue, 3),
      MeanEstimate = round(MeanEstimate, 3),
      MedianEstimate = round(MedianEstimate, 3),
      Bias_Median = round(Bias_Median, 3),
      MAD = round(MAD, 4),
      RMSE_Median = round(RMSE_Median, 4),
      MeanSE = round(MeanSE, 4),
      SE_SD_Ratio = round(SE_SD_Ratio, 3)
    ) %>%
    # Sort: Condition, Model (Full first), then Method, then Parameter
    arrange(Condition, factor(Model, levels = c("Full", "Linear")), Method, Parameter)
  
  return(df)
}

# Study 1 results
results_table_study1 <- create_apa_results_table_study1(results_study_1)

tab_caption_results_s1 <- "Parameter Estimation Results (Study 1)"
tab_note_results <- "MCSE = Monte Carlo Standard Error shown as ± value. Coverage, Type I Error, and Power expressed as percentages. — indicates relative measures are undefined when true value = 0."

kableExtra::kbl(
  results_table_study1,
  booktabs = TRUE,
  longtable = TRUE,
  align = c("l", "l", "l", "l", "r", "r", "l",
            rep("r", 19)),
  col.names = c("Cond.", "Method", "Model", "Dist.", "N", "Rel.", "Param.",
                "True", "Mean", "Bias ± MCSE", "Rel. Bias ± MCSE",
                "Median", "Bias (Med)", "MAD",
                "Var. ± MCSE", "SD ± MCSE",
                "MSE ± MCSE", "RMSE ± MCSE", "RMSE (Med)",
                "Rel. MSE ± MCSE", "Rel. RMSE ± MCSE",
                "Mean SE", "SE/SD",
                "Cover. (%) ± MCSE", "CI Width ± MCSE",
                "Type I (%) ± MCSE", "Power (%) ± MCSE"),
  caption = tab_caption_results_s1,
  linesep = ""
) %>%
  kableExtra::add_header_above(c(
    " " = 7,
    "Mean-based" = 4,
    "Median-based" = 3,
    "Variability" = 2,
    "Accuracy" = 3,
    "Relative Accuracy" = 2,
    "Inference" = 5
  )) %>%
  kableExtra::kable_styling(
    latex_options = c("hold_position", "repeat_header", "scale_down"),
    font_size = 4
  ) %>%
  kableExtra::collapse_rows(columns = 1:2, valign = "top", latex_hline = "major") %>%
  kableExtra::footnote(
    general = tab_note_results,
    general_title = "Note.",
    threeparttable = TRUE,
    escape = TRUE
  ) %>%
  kableExtra::landscape()


# ============================================================================
# STUDY 2: Results Table (APA Style - Landscape with longtable)
# ============================================================================
create_apa_results_table_study2 <- function(results_df, equation = "eta4") {
  
  df <- results_df$results %>%
    filter(Equation == equation) %>%
    select(
      Condition,
      Method,
      Model,
      Distribution,
      SampleSize,
      Reliability,
      Parameter,
      TrueValue,
      MeanEstimate,
      Bias_Mean,
      Bias_Mean_MCSE,
      RelativeBias_Mean,
      RelativeBias_MCSE,
      MedianEstimate,
      Bias_Median,
      MAD,
      Variance,
      Variance_MCSE,
      SD,
      SD_MCSE,
      MSE_Mean,
      MSE_Mean_MCSE,
      RMSE_Mean,
      RMSE_Mean_MCSE,
      RMSE_Median,
      Relative_MSE,
      Relative_MSE_MCSE,
      Relative_RMSE,
      Relative_RMSE_MCSE,
      MeanSE,
      SE_SD_Ratio,
      CoverageRate,
      CoverageRate_MCSE,
      CI_Width,
      CI_Width_MCSE,
      TypeI_Error,
      TypeI_Error_MCSE,
      Power,
      Power_MCSE
    ) %>%
    mutate(
      # Create combined columns with ± MCSE
      `Bias ± MCSE` = sprintf("%.3f ± %.3f", Bias_Mean, Bias_Mean_MCSE),
      `Rel. Bias ± MCSE` = ifelse(TrueValue == 0, "—", 
                                    sprintf("%.3f ± %.3f", RelativeBias_Mean, RelativeBias_MCSE)),
      `Variance ± MCSE` = sprintf("%.4f ± %.4f", Variance, Variance_MCSE),
      `SD ± MCSE` = sprintf("%.4f ± %.4f", SD, SD_MCSE),
      `MSE ± MCSE` = sprintf("%.4f ± %.4f", MSE_Mean, MSE_Mean_MCSE),
      `RMSE ± MCSE` = sprintf("%.4f ± %.4f", RMSE_Mean, RMSE_Mean_MCSE),
      `Rel. MSE ± MCSE` = ifelse(TrueValue == 0, "—",
                                   sprintf("%.4f ± %.4f", Relative_MSE, Relative_MSE_MCSE)),
      `Rel. RMSE ± MCSE` = ifelse(TrueValue == 0, "—",
                                    sprintf("%.4f ± %.4f", Relative_RMSE, Relative_RMSE_MCSE)),
      `Coverage ± MCSE` = sprintf("%.1f ± %.1f", CoverageRate, CoverageRate_MCSE),
      `CI Width ± MCSE` = sprintf("%.4f ± %.4f", CI_Width, CI_Width_MCSE),
      `Type I ± MCSE` = sprintf("%.1f ± %.1f", TypeI_Error, TypeI_Error_MCSE),
      `Power ± MCSE` = sprintf("%.1f ± %.1f", Power, Power_MCSE)
    ) %>%
    select(
      Condition, Method, Model, Distribution, SampleSize, Reliability, Parameter,
      TrueValue, MeanEstimate, `Bias ± MCSE`, `Rel. Bias ± MCSE`,
      MedianEstimate, Bias_Median, MAD,
      `Variance ± MCSE`, `SD ± MCSE`,
      `MSE ± MCSE`, `RMSE ± MCSE`, RMSE_Median,
      `Rel. MSE ± MCSE`, `Rel. RMSE ± MCSE`,
      MeanSE, SE_SD_Ratio,
      `Coverage ± MCSE`, `CI Width ± MCSE`,
      `Type I ± MCSE`, `Power ± MCSE`
    ) %>%
    mutate(
      TrueValue = round(TrueValue, 3),
      MeanEstimate = round(MeanEstimate, 3),
      MedianEstimate = round(MedianEstimate, 3),
      Bias_Median = round(Bias_Median, 3),
      MAD = round(MAD, 4),
      RMSE_Median = round(RMSE_Median, 4),
      MeanSE = round(MeanSE, 4),
      SE_SD_Ratio = round(SE_SD_Ratio, 3)
    ) %>%
    # Sort: Condition, Model (Full first), then Method, then Parameter
    arrange(Condition, factor(Model, levels = c("Full", "Linear")), Method, Parameter)
  
  return(df)
}

# ============================================================================
# STUDY 2 - EQUATION ETA4 TABLE
# ============================================================================
results_table_study2_eta4 <- create_apa_results_table_study2(results_study_2, "eta4")

tab_caption_results_s2_eta4 <- "Parameter Estimation Results for Equation 4 (Study 2)"

kableExtra::kbl(
  results_table_study2_eta4,
  booktabs = TRUE,
  longtable = TRUE,
  align = c("l", "l", "l", "l", "r", "r", "l",
            rep("r", 19)),
  col.names = c("Cond.", "Method", "Model", "Dist.", "N", "Rel.", "Param.",
                "True", "Mean", "Bias ± MCSE", "Rel. Bias ± MCSE",
                "Median", "Bias (Med)", "MAD",
                "Var. ± MCSE", "SD ± MCSE",
                "MSE ± MCSE", "RMSE ± MCSE", "RMSE (Med)",
                "Rel. MSE ± MCSE", "Rel. RMSE ± MCSE",
                "Mean SE", "SE/SD",
                "Cover. (%) ± MCSE", "CI Width ± MCSE",
                "Type I (%) ± MCSE", "Power (%) ± MCSE"),
  caption = tab_caption_results_s2_eta4,
  linesep = ""
) %>%
  kableExtra::add_header_above(c(
    " " = 7,
    "Mean-based" = 4,
    "Median-based" = 3,
    "Variability" = 2,
    "Accuracy" = 3,
    "Relative Accuracy" = 2,
    "Inference" = 5
  )) %>%
  kableExtra::kable_styling(
    latex_options = c("hold_position", "repeat_header", "scale_down"),
    font_size = 4
  ) %>%
  kableExtra::collapse_rows(columns = 1:2, valign = "top", latex_hline = "major") %>%
  kableExtra::footnote(
    general = tab_note_results,
    general_title = "Note.",
    threeparttable = TRUE,
    escape = TRUE
  ) %>%
  kableExtra::landscape()

# ============================================================================
# STUDY 2 - EQUATION ETA5 TABLE
# ============================================================================
results_table_study2_eta5 <- create_apa_results_table_study2(results_study_2, "eta5")

tab_caption_results_s2_eta5 <- "Parameter Estimation Results for Equation 5 (Study 2)"

kableExtra::kbl(
  results_table_study2_eta5,
  booktabs = TRUE,
  longtable = TRUE,
  align = c("l", "l", "l", "l", "r", "r", "l",
            rep("r", 19)),
  col.names = c("Cond.", "Method", "Model", "Dist.", "N", "Rel.", "Param.",
                "True", "Mean", "Bias ± MCSE", "Rel. Bias ± MCSE",
                "Median", "Bias (Med)", "MAD",
                "Var. ± MCSE", "SD ± MCSE",
                "MSE ± MCSE", "RMSE ± MCSE", "RMSE (Med)",
                "Rel. MSE ± MCSE", "Rel. RMSE ± MCSE",
                "Mean SE", "SE/SD",
                "Cover. (%) ± MCSE", "CI Width ± MCSE",
                "Type I (%) ± MCSE", "Power (%) ± MCSE"),
  caption = tab_caption_results_s2_eta5,
  linesep = ""
) %>%
  kableExtra::add_header_above(c(
    " " = 7,
    "Mean-based" = 4,
    "Median-based" = 3,
    "Variability" = 2,
    "Accuracy" = 3,
    "Relative Accuracy" = 2,
    "Inference" = 5
  )) %>%
  kableExtra::kable_styling(
    latex_options = c("hold_position", "repeat_header", "scale_down"),
    font_size = 4
  ) %>%
  kableExtra::collapse_rows(columns = 1:2, valign = "top", latex_hline = "major") %>%
  kableExtra::footnote(
    general = tab_note_results,
    general_title = "Note.",
    threeparttable = TRUE,
    escape = TRUE
  ) %>%
  kableExtra::landscape()
```

```{r dist_tables_landscape, echo=FALSE, results='asis', message=FALSE, warning=FALSE, eval=FALSE}
library(dplyr)
library(tidyr)
library(stringr)
library(glue)
library(kableExtra)
library(tools)

# --- formatting helpers ---
fmt_num <- function(x, digits = 3) ifelse(is.na(x), "", formatC(x, digits = digits, format = "f"))
fmt_pm  <- function(value, mcse, digits_value = 3, digits_mcse = 3, scale_mcse = 1) {
  ifelse(is.na(value), "", paste0(fmt_num(value, digits_value), " ± ", fmt_num(mcse * scale_mcse, digits_mcse)))
}
cap_first <- function(x) tools::toTitleCase(tolower(as.character(x)))

METHOD_ORDER <- c("SAM","LMS","QML","DBLCENT")
PARAM_KEPT   <- c("eta1:eta2","eta1:eta1","eta2:eta2")

# ---- Styling to match the convergence/outliers table ----
LATEX_FONT_SIZE <- 6              # same font size
FIRST_COL_WIDTH <- "7em"          # width for Method (first column)
MAX_ROWS_PAGE   <- 40
NOTE_TEXT <- paste(
  "Values are mean ± MCSE where available.",
  "Coverage (%) and Rej. (%) are percentages; MCSEs are scaled accordingly.",
  "% Rel. Bias is blank when the true value is 0."
)

# --- sanitize for LaTeX label ids ---
slugify <- function(x) {
  x |>
    tolower() |>
    gsub("[^a-z0-9]+","-", x = _) |>
    gsub("(^-|-$)", "", x = _)
}

# --- core table builder (Method first) ---
.make_table <- function(dfi, model_type, dist_name, caption_main = "Reported Measures") {
  if (nrow(dfi) == 0) return(NULL)

  # Rejection logic: Type I when true = 0; Power otherwise
  rej_value <- ifelse(dfi$TrueValue == 0, dfi$TypeI_Error, dfi$Power)
  rej_mcse  <- ifelse(dfi$TrueValue == 0, dfi$TypeI_Error_MCSE, dfi$Power_MCSE)

  # Build display data (Method BEFORE Parameter)
  out <- dfi %>%
    transmute(
      Method, Parameter, Reliability, SampleSize,
      `Bias ± MCSE`         = fmt_pm(Bias_Mean, Bias_Mean_MCSE, 3, 3, 1),
      `% Rel. Bias ± MCSE`  = ifelse(TrueValue == 0, "",
                                      fmt_pm(PercentRelativeBias_Mean, RelativeBias_MCSE * 100, 1, 1, 1)),
      `RMSE ± MCSE`         = fmt_pm(RMSE_Mean, RMSE_Mean_MCSE, 4, 4, 1),
      `Rel. RMSE ± MCSE`    = fmt_pm(Relative_RMSE, Relative_RMSE_MCSE, 4, 4, 1),
      `Coverage (%) ± MCSE` = fmt_pm(CoverageRate, CoverageRate_MCSE, 1, 1, 100),
      `SE/SD`               = fmt_num(SE_SD_Ratio, 3),
      `Rej. (%) ± MCSE`     = fmt_pm(rej_value, rej_mcse, 1, 1, 100)
    )

  safe_names <- names(out) |> stringr::str_replace_all("%", "\\\\%")

  # --- caption: main line + italic metadata line right under it ---
  Ns <- sort(unique(dfi$SampleSize))
  N_str <- if (length(Ns) == 1) glue("N = {Ns}") else glue("N = {paste(Ns, collapse = ', ')}")
  caption_meta <- glue("\\textit{{{model_type} model — {cap_first(dist_name)} — {N_str}}}")
  full_caption <- glue("{caption_main}\\\\{caption_meta}")  # LaTeX line break under 'Table X:'

  # label so you can \@ref(tab:...)
  lbl <- glue("tab:{slugify(model_type)}-{slugify(dist_name)}-{if(length(Ns)==1) paste0('n', Ns) else 'multiN'}")

  kb <- kbl(
    out,
    booktabs   = TRUE,
    longtable  = TRUE,
    linesep    = "",
    align      = c("l","l","r","r", rep("r", ncol(out) - 4)),
    col.names  = safe_names,
    escape     = FALSE,
    caption    = full_caption,
    label      = lbl
  ) |>
    kable_styling(
      latex_options = c("hold_position","repeat_header","scale_down"),
      font_size     = LATEX_FONT_SIZE
    ) |>
    # collapse by Method (first column) with no inner lines between blocks
    collapse_rows(columns = 1, valign = "top", latex_hline = "major") |>
    add_header_above(
      c(" " = 4, "Requested Measures ($\\pm$ MCSE where available)" = ncol(out) - 4),
      escape = FALSE
    ) |>
    footnote(
      general = NOTE_TEXT,
      threeparttable = TRUE,
      escape = TRUE
    )

  # Landscape + width for first column (Method)
  kb <- column_spec(kb, 1, width = FIRST_COL_WIDTH)
  kb <- landscape(kb)
  return(kb)
}

# --- orchestrator: one landscape table per distribution (split if too tall) ---
build_tables_by_distribution <- function(df, model_type, dist_name) {
  dfi <- df %>%
    filter(Model == model_type,
           tolower(Distribution) == tolower(dist_name),
           Parameter %in% PARAM_KEPT) %>%
    mutate(
      Method    = factor(toupper(Method), levels = METHOD_ORDER),
      Parameter = factor(Parameter, levels = PARAM_KEPT)
    ) %>%
    arrange(Method, Parameter, Reliability, SampleSize)

  if (nrow(dfi) == 0) return(invisible(NULL))

  if (nrow(dfi) > MAX_ROWS_PAGE && length(unique(dfi$SampleSize)) > 1) {
    # split by N so each table has a single N in its caption meta
    for (s in unique(dfi$SampleSize)) {
      dsub <- dfi %>% filter(SampleSize == s)
      print(.make_table(dsub, model_type, dist_name))
    }
  } else {
    print(.make_table(dfi, model_type, dist_name))
  }
}

# --- driver: generate tables (PDF only) ---
all_dists <- results_with_mcse$Distribution %>% as.character() %>% unique() %>% sort()

for (mdl in c("Full","Linear")) {
  for (dd in all_dists) build_tables_by_distribution(results_with_mcse, mdl, dd)
}

```
