```{r}
#| label: package-versions
#| echo: false

modsem_version <- packageVersion("modsem")
lavaan_version <- packageVersion("lavaan")
covsim_version <- packageVersion("covsim")
vinecop <- packageVersion("rvinecopulib")
doparallel_version <- packageVersion("doParallel")
dorng_version <- packageVersion("doRNG")
ggplot_version <- packageVersion("ggplot2")
library(microbenchmark)
microbenchmark_version <- packageVersion("microbenchmark")
simhelpers_version <- packageVersion("simhelpers")
R_version <- getRversion()
```

# Simulation Design and Performance Evaluation

In this section, we present the simulation design and performance metrics for the two simulation studies. The information presented here follows the suggestions from previous articles that investigated the quality of simulation studies [@siepe_etall_2024; @white_etall_2024; @morris_etall_2019; @pawel_etall_2025].

## Simulation Conditions
```{r}
#| label: benchmark-lms
#| echo: false
#| eval: false

# using the data obtained from data retrieval script that replicates the dataset exactly for condition 1 iteration 1
# plus, analysis.model from sim 2
bench <- microbenchmark(
  lms = modsem::modsem_da(model.syntax = analysis.model, data = data_study1, method = "lms", nodes = 32),
  times = 1
)
(bench); summary(bench, unit = "s")
```

Both simulations used a 2 (sample sizes) × 3 (reliability levels) × 3 (latent predictor distributions) × 2 (measurement error distributions) × 2 (structural disturbance distributions) factorial design, yielding 72 conditions. Simulation 1 evaluated UPI, LMS, QML, and LSAM; Simulation 2 excluded LMS due to computational constraints^[For illustration purposes, with *microbenchmark* [@R-microbenchmark] (version `r microbenchmark_version`) on the same operating system as detailed in Reproducibility and Computational Details, using the dataset for the first replication within the first condition for Simulation 2, it took approximately 29 minutes (1729.536 seconds) to fit a single model with LMS with 32 nodes (see *modsem* documentation for more information about nodes).]. To assess Type I error rates and empirical local power, we tested two specifications: (a) linear model data generation with full model estimation (assessing Type I error), and (b) full nonlinear model for both generation and estimation (assessing power). This yielded 144 conditions per Simulation, each replicated 1,000 times.

Sample size was selected as a design factor because the estimators under comparison rely on fundamentally different estimation frameworks which may exhibit differential sensitivity to sample size due to their distinct asymptotic properties, finite-sample behavior, and number of parameters to be estimated [@kelava_etall_2011; @rosseel_etall_2025; @klein_muthen_2007; @klein_moosbrugger_2000]. Sample sizes of 400 and 1000 represented moderate to large samples. We selected 400 to examine performance below the suggested 500-threshold minimum for complex latent interaction models [@wall_etall_2012; @brandt_etall_2020] while remaining realistic for applied research. The 1000 sample size allowed evaluation of behavior approaching asymptotic properties and aligned with previous simulations (e.g., Cham et al., 2012; Lonati et al., 2024; Wall \& Amemiya, 2003).

As mentioned, the effect of different levels of reliability has not been as extensively investigated in prior simulation studies, yet it is particularly relevant for latent variable models where measurement conditions directly affect estimation [@bollen_1989] and measurement error may be amplified in product terms. Previous simulations typically examined reliability above 0.7 [@brandt_etall_2014; @wall_amemiya_2003; @kelava_etall_2014]; two studies contrasted high versus low reliability [@brandt_etall_2020; @lonati_etall_2024], but in @brandt_etall_2020 the effect of reliability was conditional on structural misspecifications. To extend their findings, we include three reliability levels (0.4, 0.6, 0.8—termed low, moderate, and high)^[It is important to note that some studies report construct-level reliability while others indicator-level, which is the case here.].

Last, the three distributional conditions—normal, right-skewed (i.e., skewness = 2, excess kurtosis = 6), and uniform—address concerns about nonnormality that are both empirically and methodologically motivated. Nonnormal (univariate and multivariate) predictors commonly emerge in psychological research [@micceri_1989; @cain_etall_2017], and nonnormality of latent predictors has been a guiding concern in the methodological development of this literature [@cham_etall_2012; @kelava_etall_2011; @lonati_etall_2024; @schoemann_jorgensen_2021; @klein_moosbrugger_2000; @klein_muthen_2007; @rosseel_etall_2025; @marsh_etall_2012]. The right-skewed condition reflects distributions observed in empirical settings, while the uniform distribution, though less commonly encountered in practice, was included for comparison with previous simulation studies [@lonati_etall_2024; @wall_amemiya_2003; @marsh_etall_2012] and to represent symmetric nonnormality.  With respect to the variation of measurement error and structural disturbance distributions, the assumption of normality for measurement errors may be particularly relevant for the LSAM, given its second-order corrections assumption. Plus, as highlighted, this manipulation was only recently investigated in @lonati_etall_2024 but not for all approaches under comparison here (see p. 4 where the authors give examples of how nonnormality may arise in each of these sources).

## Data Generation

Appendix B describes the complete data generation in detail. We followed a similar procedure as in previous studies [@ng_chan_2020; @cox_kelcey_2021; @rosseel_etall_2025]. In the baseline condition, all stochastic components were normal: exogenous latent predictors, measurement errors, and structural disturbances. Under this baseline, structural parameters, structural residual variances, and measurement error variances were jointly calibrated to achieve $R^2 \approx 0.30$ and reliability $\rho \approx \{0.4, 0.6, 0.8\}$. Individual nonlinear effects each accounted for approximately 1-2% of the total variance in the dependent latent variables, consistent with prior simulation studies [@brandt_etall_2014; @lonati_etall_2024; @marsh_etall_2004] (see Figure 1 for the population models).

For Simulation 1, the dependent latent variable was generated according to the same structural model as in @brandt_etall_2014, which is also similar to @rosseel_etall_2025:
$$
\begin{aligned}
\eta_3 = \beta_{30} + \beta_{31}\eta_1 + \beta_{32}\eta_2 + \beta_{33}(\eta_1\eta_2) + \beta_{34}\eta_1^2 + \beta_{35}\eta_2^2 + \zeta_3
\end{aligned}
$$

\noindent with parameters $\beta_{30} = -0.255$, $\beta_{31} = \beta_{32} = 0.316$, $\beta_{33} = 0.139$, $\beta_{34} = \beta_{35} = 0.101$, and $\text{Var}(\zeta_3) = \psi_{33}$ (see Appendix B). For the linear model comparison, nonlinear terms were omitted (i.e., $\beta_{33} = \beta_{34} = \beta_{35} = 0$).

For Simulation 2, we targeted a more complex model to address the concerns outlined previously. The dependent latent variables were generated as follows:
$$
\begin{aligned}
\eta_4 &= \beta_{40} + \beta_{41}\eta_1 + \beta_{42}\eta_2 + \beta_{43}\eta_3 + \beta_{44}(\eta_1\eta_2) + \beta_{45}(\eta_1\eta_3) + \beta_{46}\eta_1^2 + \beta_{47}\eta_2^2 + \zeta_4 \\
\eta_5 &= \beta_{50} + \beta_{51}\eta_4 + \beta_{52}\eta_1 + \beta_{53}\eta_2 + \beta_{54}\eta_3 + \beta_{55}(\eta_1\eta_4) + \beta_{56}(\eta_2\eta_4) + \beta_{57}\eta_1^2 + \beta_{58}\eta_3^2 + \zeta_5
\end{aligned}
$$

\noindent with parameters $\beta_{40} = -0.215$, $\beta_{50} = -0.160$, $\beta_{41} = \beta_{42} = \beta_{43} = 0.20$, $\beta_{44} = \beta_{45} = 0.11$, $\beta_{46} = \beta_{47} = 0.08$; $\beta_{51} = \beta_{52} = \beta_{53} = \beta_{54} = 0.16$, $\beta_{55} = \beta_{56} = 0.08$, $\beta_{57} = \beta_{58} = 0.06$, and $\text{Var}(\zeta_4) = \psi_{44}$, $\text{Var}(\zeta_5) = \psi_{55}$ (see Appendix B). For the linear model comparison, all interaction and quadratic terms were omitted.

The exogenous latent predictors were generated as normal, right-skewed, or uniform using the Vine-To-Anything (VITA) simulation method with regular vine copulas and specified covariance matrices [@gronneberg_foldnes_2022; @foldnes_gronneberg_2015]. Second, measurement errors were generated as either univariate normal, $\epsilon_j \sim \mathcal{N}(0, \theta_{jj})$, or right-skewed, $\epsilon_j \sim \text{Exp}^*(0, \theta_{jj})$, where $j$ indexes observed indicators^[$\text{Exp}^*(0, \theta_{jj})$ denotes a centered and scaled exponential distribution with mean 0 and variance $\theta_{jj}$, defined as $\sqrt{\theta_{jj}}(X - 1)$ where $X \sim \text{Exp}(1)$. Note that $\text{Exp}(1) \equiv \text{Gamma}(1, 1)$, which is the same base distribution used for the right-skewed exogenous latent predictors.]. Third, structural disturbances were similarly generated as either univariate normal, $\zeta_k \sim \mathcal{N}(0, \psi_{kk})$, or right-skewed, $\zeta_k \sim \text{Exp}^*(0, \psi_{kk})$, where $k$ indexes dependent latent variables.

## Nonconvergence and Outliers

Before analyzing the data, we identified nonconvergent solutions as those where the point estimates, SEs, *p*-values, or confidence interval for the structural parameters of interest were not produced or contained undefined or infinite values. Following @lonati_etall_2024, we excluded the entire replication from the analysis across estimation approaches as nonconvergent solutions signal challenging replications for all methods^[Convergent solutions may still be implausible or incomplete, for example when estimates for other parameters in the model are not obtained, when negative variances occur in $\boldsymbol{\Theta}$ (the measurement error covariance matrix), or when $\boldsymbol{\Psi}$ (the structural disturbance covariance matrix) is not positive semi-definite [@dhaene_rosseel_2023]. We tracked these situations and obtained qualitatively identical results when excluding them from the analysis (results are available on the GitHub repository), with one worthy remark that will be clarified in the Results section.]. We calculated convergence rate as $\text{Convergence}_{rate} = N_{\text{complete}}/N_{\text{total}} \times 100\%$, where $N_{\text{complete}}$ represents successfully converged replications with complete output for that specific approach and $N_{\text{total}}$ represents all attempted replications for the same approach.

Similar to @lonati_etall_2024 again, we identified outliers using the box-plot method applied to replications where all methods successfully converged. For each method-parameter combination, quartiles and interquartile ranges were calculated from this common set of converged replications, and point estimates outside $[Q_1 - 3 \times \text{IQR}, Q_3 + 3 \times \text{IQR}]$ (where $\text{IQR} = Q_3 - Q_1$) were flagged as outliers. Following the same exclusion logic as for convergence failures, we excluded the entire replication from the analysis across all estimation approaches when any method produced an outlier point estimate for the main or nonlinear effects. To complement the possible arbitrary threshold selection, we also computed median-based results before outlier removal [@brandt_etall_2020]. In addition, following @lai_hsiao_2022, we computed trimmed-mean–based estimates as a further robustness check. 

## Performance Measures

Method performance was assessed through multiple metrics following the formulas from the *simhelpers* package [@R-simhelpers] (version `r simhelpers_version`), with the exception of the median-based metrics that were based on @brandt_etall_2020 and the trimmed mean-based metrics that were based on @lai_hsiao_2022. Following the *simhelpers* documentation and references therein, we also quantified the Monte Carlo Standard Errors (MCSE) simulation uncertainty for most of the reported performance measures using the jack-knife technique. Generally speaking, the measures are classified in terms of absolute and relative criteria measures, SE assessment, hypothesis testing, and confidence intervals. In the main text, we only report and discuss the metrics reported in Table 1 for the interaction and quadratic effects. For the more extensive set of measures and estimates, we refer the reader to the GitHub repository. 

## Reproducibility and Computational Details

The simulation was conducted on a Mac Studio with an Apple M4 Max chip (with 14 cores and 36 GB of RAM), running macOS Sequoia 15.5. All analyses were performed in R [@R-base] (version `r R_version`). Parallel processing was implemented through the *doParallel* package (version `r doparallel_version`) [@R-doParallel], with *doRNG* (version `r dorng_version`) [@R-doRNG] to ensure independent and reproducible random number streams. For the UPI with double mean-centering, LMS, and QML approach, the *modsem* package was used [@kjell_etall_2024] (version `r modsem_version`) with robust (sandwich-based) SEs. For the LSAM approach, the *lavaan* package was used [@R-lavaan] (version `r lavaan_version`). In this case, we estimated the latent factors with a single measurement block as opposed to separately to maintain some similarity with the other approaches [@rosseel_loh_2024]. Importantly, apart from the aforementioned, we used the default settings for the functions provided in the packages. For generating data, we used the packages *covsim*  (version `r covsim_version`) [@gronneberg_foldnes_2022] and *rvinecopulib* (version `r vinecop`) [@R-rvinecopulib]. Figures were produced with *ggplot2* (version `r ggplot_version`) [@R-ggplot2]. Finally, this paper was written with *apaquarto* [@R-apaquarto] (see GitHub repository for more information on reproducing the manuscript and analyses).