```{r}
#| label: package-versions
#| echo: false

modsem_version <- packageVersion("modsem")
lavaan_version <- packageVersion("lavaan")
covsim_version <- packageVersion("covsim")
vinecop <- packageVersion("rvinecopulib")
doparallel_version <- packageVersion("doParallel")
dorng_version <- packageVersion("dorng")
ggplot_version <- packageVersion("ggplot2")
microbenchmark_version <- packageVersion("microbenchmark")
R_version <- getRversion()
```

# Simulation Design and Performance Evaluation

In this section, we present the simulation design and performance metrics for the two simulation studies. The information presented here follows the suggestions from previous articles that investigated the quality of simulation studies [@siepe_etall_2024; @white_etall_2024; @morris_etall_2019].

## Simulation Conditions
```{r}
#| label: benchmark-lms
#| echo: false
#| eval: false

#library(microbenchmark)

# using the data obtained from data retrieval script that replicates the dataset exactly for condition 1 iteration 1
# plus, analysis.model from sim 2
bench <- microbenchmark(
  lms = modsem::modsem_da(model.syntax = analysis.model, data = data_study1, method = "lms", nodes = 32),
  times = 1
)
print(bench); summary(bench, unit = "s")
```

Both simulations used a 2 (sample sizes) × 3 (reliability levels) × 3 (latent predictor distributions) factorial design, yielding 18 conditions. Simulation 1 evaluated UPI, LMS, QML, and LSAM; Simulation 2 excluded LMS due to computational constraints^[For illustration purposes, with *microbenchmark* [@R-microbenchmark] (version `r microbenchmark_version`) on the same operating system as below, using the dataset for the first replication within the first condition for Simulation 2, it took approximately 29 minutes (1729.536 seconds) to fit a single model with LMS with 32 nodes (see *modsem* documentation for more information about nodes).]. To assess Type I error rates and empirical local power [@irmer_etall_2024], we tested two specifications: (a) linear model data generation with full model estimation (assessing Type I error), and (b) full nonlinear model for both generation and estimation (assessing power). This yielded 36 total conditions, each replicated 1,000 times.

Sample sizes of 400 and 1000 represented moderate to large samples. We selected 400 to examine performance below the suggested 500-threshold minimum for complex latent interaction models [@wall_etall_2012] while remaining realistic for applied research. The 1000 sample size allowed evaluation of asymptotic properties and aligned with previous simulations. Three reliability levels (0.4, 0.6, 0.8—termed low, medium, and high) covered a broad range of measurement quality. While previous simulations typically examined reliability above 0.7 [@brandt_etall_2014; @lonati_etall_2024; @wall_amemiya_2003; @kelava_etall_2014] or contrasted high versus low (e.g., 0.8 and 0.5 in Brandt et al., 2020), we included 0.4 to assess performance under poor measurement conditions. Last, the three distributional conditions—normal, right-skewed (i.e., skewness = 2, excess kurtosis = 6), and uniform—were based on prior research varying non-normality to different degrees [@brandt_etall_2014; @brandt_etall_2020; @cham_etall_2012; @lonati_etall_2024; @wall_amemiya_2003]. 

## Data Generation

Appendix A describes the complete data generation in detail. We followed a similar procedure as in previous studies [@ng_chan_2020; @cox_kelcey_2021; @rosseel_etall_2025]. First, under full normality, structural residual variances and measurement error variances were set to achieve $R^2 \approx 0.30$ and reliability $\rho \approx \{0.4, 0.6, 0.8\}$. Second, using these fixed variance parameters, data were generated under the three distributional conditions (see Figure 1 for the population models). Correlated predictor latent variables were generated using the Vine-To-Anything (VITA) simulation method with regular vine copulas and specified covariance matrices. This approach improves upon the copula method of @mair_etall_2012 and circumvents the issues associated with other data generation approaches used in previous simulation studies [@gronneberg_foldnes_2022; @foldnes_gronneberg_2015]. Dependent latent variables and observed indicators were then generated with normally distributed disturbances and errors, respectively, isolating non-normality to the predictors.

For Simulation 1, the dependent latent variable was generated according to the same structural model as in @brandt_etall_2014:
$$
\begin{aligned}
\eta_3 = \beta_{30} + \beta_{31}\eta_1 + \beta_{32}\eta_2 + \beta_{33}(\eta_1\eta_2) + \beta_{34}\eta_1^2 + \beta_{35}\eta_2^2 + \zeta
\end{aligned}
$$

\noindent with parameters $\beta_{30} = -0.255$, $\beta_{31} = \beta_{32} = 0.316$, $\beta_{33} = 0.139$, $\beta_{34} = \beta_{35} = 0.101$, and $\zeta \sim \mathcal{N}(0, \psi_{33})$. For the linear model comparison, nonlinear terms were omitted (i.e., $\beta_{33} = \beta_{34} = \beta_{35} = 0$).

For Simulation 2, the dependent latent variables were generated as follows:
$$
\begin{aligned}
\eta_4 &= \beta_{40} + \beta_{41}\eta_1 + \beta_{42}\eta_2 + \beta_{43}\eta_3 + \beta_{44}(\eta_1\eta_2) + \beta_{45}(\eta_1\eta_3) + \beta_{46}\eta_1^2 + \beta_{47}\eta_2^2 + \zeta_4 \\
\eta_5 &= \beta_{50} + \beta_{51}\eta_4 + \beta_{52}\eta_1 + \beta_{53}\eta_2 + \beta_{54}\eta_3 + \beta_{55}(\eta_1\eta_4) + \beta_{56}(\eta_2\eta_4) + \beta_{57}\eta_1^2 + \beta_{58}\eta_3^2 + \zeta_5
\end{aligned}
$$

\noindent with parameters $\beta_{40} = \beta_{50} = 0.1$, $\beta_{41} = \beta_{42} = \beta_{43} = 0.20$, $\beta_{44} = \beta_{45} = 0.11$, $\beta_{46} = \beta_{47} = 0.08$; $\beta_{51} = \beta_{52} = \beta_{53} = \beta_{54} = 0.16$, $\beta_{55} = \beta_{56} = 0.08$, $\beta_{57} = \beta_{58} = 0.06$, and $\zeta_4 \sim \mathcal{N}(0, \psi_{44})$, $\zeta_5 \sim \mathcal{N}(0, \psi_{55})$. For the linear model comparison, all interaction and quadratic terms were omitted.

## Nonconvergence and Outliers

Before analyzing the data, we identified non-convergent solutions as those where estimates for the parameters of interest were not produced. Following @lonati_etall_2024, we excluded the entire iteration from the analysis across estimation approaches as non-convergent solutions signal replications challenging for all methods^[Convergent solutions may still be implausible or incomplete, for example when estimates for other parameters in the model are not obtained. We tracked these via warnings and obtained qualitatively identical results if excluding from the analysis (results are available on the GitHub repository).]. We calculated convergence rate as $\text{Convergence}_{rate} = N_{\text{complete}}/N_{\text{total}} \times 100\%$, where $N_{\text{complete}}$ represents successfully converged replications with complete output for that specific approach and $N_{\text{total}}$ represents all attempted replications for the same approach.

Similar to @lonati_etall_2024 again, we identified outliers using the box-plot method applied to iterations where all methods successfully converged. For each method-parameter combination, quartiles and interquartile ranges were calculated from this common set of converged iterations, and estimates outside $[Q_1 - 3 \times \text{IQR}, Q_3 + 3 \times \text{IQR}]$ (where $\text{IQR} = Q_3 - Q_1$) were flagged as outliers. Following the same exclusion logic as for convergence failures, we excluded the entire iteration from the analysis across all estimation approaches when any method produced an outlier point estimate for the main or nonlinear effects. To complement the possible arbitrary threshold selection, we also computed median-based metrics before outlier removal [@brandt_etall_2020].

## Performance Measures

Method performance was assessed through multiple metrics following the formulas from the *simhelpers* package [@R-simhelpers], with the exception of the median-based metrics that were based on @brandt_etall_2020. Following the *simhelpers* documentation and references therein, we also quantified the Monte Carlo Standard Errors (MCSE) simulation uncertainty for most of the reported performance measures using the jack-knife technique. Generally speaking, the measures are classified in terms of absolute and relative criteria measures, standard error assessment, hypothesis testing, and confidence intervals. In the main text, we only report and discuss the metrics reported in Table 1 for the interaction and quadratic effects. For the complete set of measures, we refer the reader to the online supplemental materials (see Table S1). 

## Reproducibility and Computational Details

The simulation was conducted on a Mac Studio with an Apple M4 Max chip (with 14 cores and 36 GB of RAM), running macOS Sequoia 15.5. All analyses were performed in R [@R-base] (version `r R_version`). Parallel processing was implemented through the *doParalell* package (version `r doparallel_version`) [@R-doParallel], with *doRNG* (version `r dorng_version`) [@R-doRNG] to ensure independent and reproducible random number streams. For the UPI with double mean centering, LMS, and QML approach, the *modsem* package was used [@kjell_etall_2024] (version `r modsem_version`) without robust SEs. For the LSAM approach, the *lavaan* package was used [@R-lavaan] (version `r lavaan_version`). In this case, we estimated the latent factors with a single measurement block as opposed to separately to maintain some similarity with the other approaches [@rosseel_loh_2024]. Importantly, apart from the aforementioned, we used the default settings for the functions provided in the packages^[This is important to acknowledge because there are arguments for the functions used that, in principle, could be manipulated to obtain better results. For instance, one could change the maximum steps for the M-step in the EM algorithm for the LMS. However, this also leads to substantial researcher degrees of freedom and hence were avoided.]. For generating normal, right-skewed, and uniform data we used the packages *covsim*  (version `r covsim_version`) [@gronneberg_foldnes_2022] and *rvinecopulib* (version `r vinecop`) [@R-rvinecopulib]. Figures were produced with *ggplot2* (version `r ggplot_version`) [@R-ggplot2]. Finally, this paper was written with *apaquarto* [@R-apaquarto] (see GitHub repository for more information on reproducing the manuscript and analyses).