---
title: "Evaluating Local Structural-After-Measurement (LSAM) and Traditional Approaches for the Estimation of Complex Nonlinear Effects Among Latent Variables"
shorttitle: "Evaluating LSAM and Traditional SEM Approaches"

author:
  - name: Felipe Fontana Vieira
    corresponding: true
    orcid: 0009-0006-0949-6569
    email: felipe.fontanavieira@ugent.be
    affiliations:
      - name: Ghent University
        department: Department of Data Analysis, Faculty of Psychology and Educational Sciences
        address: Henri Dunantlaan 2
        city: Ghent
        country: Belgium
        postal-code: 9000
        id: UGent
    roles:
      - Conceptualization
      - Methodology
      - Software
      - Investigation
      - Data curation
      - Formal analysis
      - Validation
      - Visualization
      - Writing - original draft
      - Writing - review & editing
  - name: Kjell Solem Slupphaug
    corresponding: false
    orcid: 0009-0005-8324-2834
    affiliations:
      - name: Norwegian University of Science and Technology
        department: Department of Psychology
        city: Trondheim
        country: Norway
    roles:
      - Writing - review & editing
      - Software
  - name: Yves Rosseel
    corresponding: false
    orcid: 0000-0002-4129-4477
    affiliations:
      - ref: UGent
    roles:
      - Conceptualization
      - Methodology
      - Software
      - Supervision
      - Writing - review & editing
      - Funding acquisition

author-note:
  status-changes:
    affiliation-change: ~
    deceased: ~
  disclosures:
    study-registration: "This study was not preregistered."
    data-sharing: "Data, code, and materials for this manuscript can be found at https://github.com/felipelfv/simulation_nonlinear. Ideas and part of the results were previously presented at the conference of the European Association of Methodology 2025." 
    financial-support: "This project was funded by the Special Research Fund (BOF) of Ghent University (BOF/24J/2023/144)."
    
abstract: |
  Various methods exist to include quadratic or interaction terms involving latent variables in structural equation models (SEM). Most use system-wide estimation, where all parameters are estimated simultaneously, and have been investigated in models with few nonlinear effects. Recently, structural-after-measurement (SAM) approaches have been proposed, where estimation proceeds in two stages: measurement model first, then structural model. Rosseel et al. (2025) extended local SAM (LSAM) to handle second-order nonlinear effects among latent variables. In this article, we present a formula for two-step standard errors (SEs) not previously available for LSAM. We also conducted two simulation studies varying latent exogenous predictor distributions (normal, right-skewed, uniform), reliabilities (0.4, 0.6, 0.8), sample sizes (400, 1000), and measurement error and structural disturbance distributions (normal, right-skewed). The first study examined a model with three nonlinear effects. LSAM produced largely unbiased estimates with stable coverage, SEs, and Type I error rates, though power fluctuated and performance was adversely affected under low reliability, particularly with uniform latent exogenous distributions. Larger sample sizes mitigated these issues. Traditional methods (LMS, QML, UPI) showed results consistent with prior literature. The second study, excluding LMS, tested a more complex model with eight nonlinear effects. LSAM maintained adequate performance despite greater complexity, though similar limitations emerged and power decreased under certain conditions. Traditional methods yielded more variable results, with generally poorer performance relative to Simulation 1 and LSAM. Right-skewed measurement errors affected the abovementioned results more than right-skewed structural disturbances, particularly under low and medium reliability.

impact-statement: |
  Interaction effects occur when the relationship between two variables depends on a third variable, and quadratic effects occur when the effect of a variable changes depending on the level of that same variable. Estimating these effects becomes difficult when the variables are not directly observed but instead measured through questionnaires or similar instruments---that is, when they are latent variables. Several methods exist, but they can produce misleading results when assumptions do not hold. This article evaluates the recently proposed local structural-after-measurement (LSAM) and compares it with three established alternatives across conditions that vary data distributions, measurement quality, sample sizes, and model complexity. Practical recommendations for choosing among these methods are provided.

keywords: [nonlinear effects, structural equation modeling, local structural-after-measurement, latent variables]

language:
  title-impact-statement: "Translational Abstract"

word-count: true
floatsintext: true
numbered-lines: false
link-citations: false
mask: false


bibliography: "references.bib"

format:
  apaquarto-pdf:
    documentmode: man
    keep-tex: false
    include-in-header:
      text: |
        \raggedbottom
  #apaquarto-html: default
        
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: setup
#| include: false

library(dplyr) # data wrangling for performance metrics and plots
library(ggplot2) # visualization
library(kableExtra) # appendices
```

{{< include introduction.qmd >}}

{{< include modelsframework.qmd >}}

{{< include present_research.qmd >}}

{{< include design.qmd >}}

{{< include results.qmd >}}

{{< include discussion.qmd >}}

{{< pagebreak >}}

# References

::: {#refs}
:::

{{< pagebreak >}}

\begin{flushleft}
\textbf{Table 1}

\textit{Subset of the Performance Measures for Evaluating Parameter Estimates in the Simulation Studies}
\end{flushleft}
\footnotesize
\begin{longtable}{lll}
\toprule
Performance Measure & Empirical Calculation & MCSE \\
\midrule
\textbf{Absolute Criteria} & & \\
Absolute Bias & $\bar{B} - \beta$ & $\sqrt{S_B^2/K}$ \\
MSE & $\frac{1}{K}\sum_{k=1}^{K}(B_k - \beta)^2$ & $\sqrt{\frac{1}{K}[S_B^4(k_B - 1) + 4S_B^3 g_B(\bar{B} - \beta) + 4S_B^2(\bar{B} - \beta)^2]}$ \\
RMSE & $\sqrt{\frac{1}{K}\sum_{k=1}^{K}(B_k - \beta)^2}$ & $\sqrt{\frac{K-1}{K}\sum_{j=1}^{K}(\text{RMSE}_{(j)} - \text{RMSE})^2}$ \\
\textbf{Relative Criteria} & & \\
Relative Bias & $(\frac{\bar{B}}{\beta})- 1$ & $\sqrt{S_B^2/(K\beta^2)}$ \\
Relative MSE & $\frac{(\bar{B} - \beta)^2 + S_B^2}{\beta^2}$ & $\sqrt{\frac{1}{K\beta^4}[S_B^4(k_B - 1) + 4S_B^3 g_B(\bar{B} - \beta) + 4S_B^2(\bar{B} - \beta)^2]}$ \\
Relative RMSE & $\sqrt{\frac{(\bar{B} - \beta)^2 + S_B^2}{\beta^2}}$ & $\sqrt{\frac{K-1}{K}\sum_{j=1}^{K}(\text{rRMSE}_{(j)} - \text{rRMSE})^2}$ \\
\textbf{Standard Error} & & \\
Mean SE & $\overline{SE} = \frac{1}{K}\sum_{k=1}^{K}\widehat{SE}_k$ & --- \\
SE/SD Ratio & $\overline{SE}/S_B$ & --- \\
\textbf{Hypothesis Testing} & & \\
Rejection Rate & $r_\alpha = \frac{1}{K}\sum_{k=1}^{K}I(P_k < \alpha)$ & $\sqrt{r_\alpha(1-r_\alpha)/K}$ \\
\textbf{Confidence Intervals} & & \\
Coverage & $c_\beta = \frac{1}{K}\sum_{k=1}^{K}I(L_k \leq \beta \leq U_k)$ & $\sqrt{c_\beta(1-c_\beta)/K}$ \\
\bottomrule
\end{longtable}
\begin{flushleft}
\textit{Note}. $B$ = estimator for parameter $\beta$; $K$ = number of replications producing estimates $B_1, ..., B_K$; $\bar{B} = (1/K)\sum_{k=1}^{K}B_k$ = sample mean; $S_B^2 = (1/(K-1))\sum_{k=1}^{K}(B_k - \bar{B})^2$ = sample variance; $S_B = \sqrt{S_B^2}$ = sample standard deviation; $k_B$ = standardized kurtosis; $g_B$ = standardized skewness; $I(\cdot)$ = indicator function; $P_k$ = p-value from replication $k$; $\alpha$ = significance level; $L_k$, $U_k$ = lower and upper CI endpoints; $r_\alpha$ and $c_\beta$ denote rejection rate and coverage, respectively. MCSE = Monte Carlo Standard Error, dashes indicate MCSEs not computed. MSE = Mean Squared Error. RMSE = Root Mean Squared Error.
\end{flushleft}
\normalsize

{{< pagebreak >}}

```{tikz}
#| label: fig-model
#| fig-cap: "Data Generating Model for the Simulation Studies. Top: Model for Simulation 1. Bottom: Model for Simulation 2."
#| apa-note: "*Note*. Residual variances, covariances, and intercepts are not shown for clarity."
#| fig-align: center
#| fig-width: 10
#| fig-height: 16

\tikzset{
  latent/.style  ={circle,draw,minimum size=14mm},
  ind/.style     ={rectangle,draw,minimum height=6mm,minimum width=8mm,align=center},
  derived/.style ={circle,draw,minimum size=14mm},
  every node/.style={font=\small}
}

\begin{tikzpicture}

% FIRST DIAGRAM (Simulation 1)
\node[ind] (y1)  at (0,  0.8) {y$_1$};
\node[ind] (y2)  at (0,  0.0) {y$_2$};
\node[ind] (y3)  at (0, -0.8) {y$_3$};
\node[latent] (eta1) at (2.4, 0.0) {$\eta_1$};

\draw[->] (eta1.west) -- (y1.east);
\draw[->] (eta1.west) -- (y2.east);
\draw[->] (eta1.west) -- (y3.east);

\node[ind] (y4)  at (0, -2.8) {y$_4$};
\node[ind] (y5)  at (0, -3.6) {y$_5$};
\node[ind] (y6)  at (0, -4.4) {y$_6$};
\node[latent] (eta2) at (2.4, -3.6) {$\eta_2$};

\draw[->] (eta2.west) -- (y4.east);
\draw[->] (eta2.west) -- (y5.east);
\draw[->] (eta2.west) -- (y6.east);

\draw[<->,gray!40,bend right=30] (eta1) to (eta2);

\node[latent] (eta3) at (6.6, -1.6) {$\eta_3$};

\draw[->] (eta1) -- node[above] {} (eta3);
\draw[->] (eta2) -- node[above,sloped] {} (eta3);

\node[derived] (eta1sq) at (4.3, -4.2) {$\eta_1^{2}$};
\node[derived] (eta2sq) at (6.6, -4.2) {$\eta_2^{2}$};
\node[derived] (eta12)  at (8.9, -4.2) {$\eta_1\eta_2$};

\draw[->] (eta1sq) -- node[above] {} (eta3);
\draw[->] (eta2sq) -- node[right] {} (eta3);
\draw[->] (eta12)  -- node[above] {} (eta3);

\node[ind] (y7) at (5.6, 0.8) {y$_7$};
\node[ind] (y8) at (6.6, 0.8) {y$_8$};
\node[ind] (y9) at (7.6, 0.8) {y$_9$};

\draw[->] (eta3.north) -- (y7.south);
\draw[->] (eta3.north) -- (y8.south);
\draw[->] (eta3.north) -- (y9.south);

% SECOND DIAGRAM (Simulation 2) 
\node[ind] (y1b)  at (0,  -6.0) {y$_1$};
\node[ind] (y2b)  at (0,  -7.0) {y$_2$};
\node[ind] (y3b)  at (0, -8.0) {y$_3$};
\node[latent] (eta1b) at (2.4, -7.0) {$\eta_1$};

\draw[->] (eta1b.west) -- (y1b.east);
\draw[->] (eta1b.west) -- (y2b.east);
\draw[->] (eta1b.west) -- (y3b.east);

\node[ind] (y4b)  at (0, -10.5) {y$_4$};
\node[ind] (y5b)  at (0, -11.5) {y$_5$};
\node[ind] (y6b)  at (0, -12.5) {y$_6$};
\node[latent] (eta2b) at (2.4, -11.5) {$\eta_2$};

\draw[->] (eta2b.west) -- (y4b.east);
\draw[->] (eta2b.west) -- (y5b.east);
\draw[->] (eta2b.west) -- (y6b.east);

\node[ind] (y7b)  at (0, -15.0) {y$_7$};
\node[ind] (y8b)  at (0, -16.0) {y$_8$};
\node[ind] (y9b)  at (0, -17.0) {y$_9$};
\node[latent] (eta3b) at (2.4, -16.0) {$\eta_3$};

\draw[->] (eta3b.west) -- (y7b.east);
\draw[->] (eta3b.west) -- (y8b.east);
\draw[->] (eta3b.west) -- (y9b.east);

\draw[<->,gray!40,bend right=30] (eta1b) to (eta2b);
\draw[<->,gray!40,bend right=30] (eta1b) to (eta3b);
\draw[<->,gray!40,bend right=30] (eta2b) to (eta3b);

\node[latent] (eta4b) at (5.5, -9.5) {$\eta_4$};

\draw[->] (eta1b) -- (eta4b);
\draw[->] (eta2b) -- (eta4b);
\draw[->] (eta3b) -- (eta4b);

\node[derived] (eta12b)  at (9.0, -7.0) {$\eta_1\eta_2$};
\node[derived] (eta13b)  at (9.0, -8.5) {$\eta_1\eta_3$};
\node[derived] (eta1sqb) at (9.0, -10.0) {$\eta_1^{2}$};
\node[derived] (eta2sqb) at (9.0, -11.5) {$\eta_2^{2}$};

\draw[->] (eta12b)  -- (eta4b);
\draw[->] (eta13b)  -- (eta4b);
\draw[->] (eta1sqb) -- (eta4b);
\draw[->] (eta2sqb) -- (eta4b);

\node[ind] (y10b) at (4.5, -6.0) {y$_{10}$};
\node[ind] (y11b) at (5.5, -6.0) {y$_{11}$};
\node[ind] (y12b) at (6.5, -6.0) {y$_{12}$};

\draw[->] (eta4b.north) -- (y10b.south);
\draw[->] (eta4b.north) -- (y11b.south);
\draw[->] (eta4b.north) -- (y12b.south);

\node[latent] (eta5b) at (5.5, -14.5) {$\eta_5$};

\draw[->] (eta4b) -- (eta5b);
\draw[->] (eta1b) -- (eta5b);
\draw[->] (eta2b) -- (eta5b);
\draw[->] (eta3b) -- (eta5b);

\node[derived] (eta14b)   at (9.0, -13.0) {$\eta_1\eta_4$};
\node[derived] (eta24b)   at (9.0, -14.5) {$\eta_2\eta_4$};
\node[derived] (eta1sq2b) at (9.0, -16.0) {$\eta_1^{2}$};
\node[derived] (eta3sqb)  at (9.0, -17.5) {$\eta_3^{2}$};

\draw[->] (eta14b)   -- (eta5b);
\draw[->] (eta24b)   -- (eta5b);
\draw[->] (eta1sq2b) -- (eta5b);
\draw[->] (eta3sqb)  -- (eta5b);

\node[ind] (y13b) at (4.5, -18.0) {y$_{13}$};
\node[ind] (y14b) at (5.5, -18.0) {y$_{14}$};
\node[ind] (y15b) at (6.5, -18.0) {y$_{15}$};

\draw[->] (eta5b.south) -- (y13b.north);
\draw[->] (eta5b.south) -- (y14b.north);
\draw[->] (eta5b.south) -- (y15b.north);

\end{tikzpicture}
```

```{r}
#| label: fig-bias-sim1
#| fig-cap: "Relative Bias for Simulation 1 With Varying Distributions and Reliability Levels (N = 400)."
#| apa-note: "*Note*. Shaded regions represent acceptable deviations. Vertical bars represent the MCSEs."
#| fig-align: center
#| fig-height: 11
#| fig-width: 9
#| echo: false

p_relative_bias_400_full_study_1
```

```{r}
#| label: fig-rmse-sim1
#| fig-cap: "Relative RMSE for Simulation 1 With Varying Distributions and Reliability Levels (N = 400)."
#| apa-note: "*Note*. Vertical bars represent the MCSEs."
#| fig-align: center
#| fig-height: 11
#| fig-width: 9
#| echo: false

p_relative_rmse_400_full_study_1
```

```{r}
#| label: fig-ratio-sim1
#| fig-cap: "SE/SD Ratio for Simulation 1 With Varying Sample Sizes and Reliability Levels (Right-Skewed and Uniform Conditions)."
#| apa-note: "*Note*. Shaded regions represent acceptable deviations."
#| fig-align: center
#| fig-height: 11
#| fig-width: 9
#| echo: false

p_slope_nonnorm_unif_study_1
```

```{r}
#| label: fig-coverage-sim1
#| fig-cap: "Coverage for Simulation 1 With Varying Distributions, Reliability Levels, and Sample Sizes."
#| apa-note: "*Note*. Shaded regions represent acceptable deviations. Vertical bars represent the MCSEs."
#| fig-align: center
#| fig-height: 11
#| fig-width: 9
#| echo: false

p_cov_nonnorm_unif_study_1
```

```{r}
#| label: fig-type1-sim1
#| fig-cap: "Type I Error Rate for Simulation 1 With Varying Distributions and Reliability Levels (N = 1000)."
#| apa-note: "*Note*. Shaded regions represent acceptable deviations. Error bars represent the MCSEs."
#| fig-align: center
#| fig-height: 11
#| fig-width: 9
#| echo: false

p_t1_1000_study_1
```

```{r}
#| label: fig-bias-sim2
#| fig-cap: "Relative Bias for Simulation 2 With Varying Distributions and Reliability Levels (N = 400)."
#| apa-note: "*Note*. Shaded regions represent acceptable deviations. Vertical bars represent the MCSEs."
#| fig-align: center
#| fig-height: 11
#| fig-width: 9
#| echo: false

p_relative_bias_400_full_all_study_2
```

```{r}
#| label: fig-rmse-sim2
#| fig-cap: "Relative RMSE for Simulation 2 With Varying Distributions and Reliability Levels (N = 400)."
#| apa-note: "*Note*. Vertical bars represent the MCSEs."
#| fig-align: center
#| fig-height: 11
#| fig-width: 9
#| echo: false

p_relative_rmse_400_full_all_study_2
```

```{r}
#| label: fig-seratio-sim2
#| fig-cap: "SE/SD Ratio for Simulation 2 With Varying Distributions and Reliability Levels (N = 400)."
#| apa-note: "*Note*. Shaded regions represent acceptable deviations."
#| fig-align: center
#| fig-height: 11
#| fig-width: 9
#| echo: false

p_sesd_400_full_all_study_2
```

```{r}
#| label: fig-coverage-sim2
#| fig-cap: "Coverage for Simulation 2 With Varying Distributions and Reliability Levels (N = 400)."
#| apa-note: "*Note*. Shaded regions represent acceptable deviations. Vertical bars represent the MCSEs."
#| fig-align: center
#| fig-height: 11
#| fig-width: 9
#| echo: false

p_coverage_400_full_all_study_2
```

```{r}
#| label: fig-type1-sim2
#| fig-cap: "Type I Error Rate for Simulation 2 With Varying Distributions and Reliability Levels (N = 1000)."
#| apa-note: "*Note*. Shaded regions represent acceptable deviations. Error bars represent the MCSEs."
#| fig-align: center
#| fig-height: 11
#| fig-width: 9
#| echo: false

p_t1_1000_all_study_2
```

```{r}
#| label: fig-sens-bias-sim1
#| fig-cap: "Additional Distributional Conditions: Relative Bias for Simulation 1 (N = 400)."
#| apa-note: "*Note*. White dots are the results under normal measurement error and structural disturbance, black dots represent nonnormal. Shaded regions indicate acceptable range. Error bars show MCSE."
#| fig-align: center
#| fig-height: 11
#| fig-width: 9
#| echo: false

p_sens_bias_study1
```

```{r}
#| label: fig-sens-rmse-sim1
#| fig-cap: "Additional Distributional Conditions: Relative RMSE for Simulation 1 (N = 400)."
#| apa-note: "*Note*. White dots are the results under normal measurement error and structural disturbance, black dots represent nonnormal. Shaded regions indicate acceptable range. Error bars show MCSE."
#| fig-align: center
#| fig-height: 11
#| fig-width: 9
#| echo: false

p_sens_rmse_study1
```

```{r}
#| label: fig-sens-sesd-sim1
#| fig-cap: "Additional Distributional Conditions: SE/SD Ratio for Simulation 1 (N = 400)."
#| apa-note: "*Note*. White dots are the results under normal measurement error and structural disturbance, black dots represent nonnormal. Shaded regions indicate acceptable range."
#| fig-align: center
#| fig-height: 11
#| fig-width: 9
#| echo: false

p_sens_sesd_study1
```

```{r}
#| label: fig-sens-coverage-sim1
#| fig-cap: "Additional Distributional Conditions: Coverage for Simulation 1 (N = 1000)."
#| apa-note: "*Note*. White dots are the results under normal measurement error and structural disturbance, black dots represent nonnormal. Shaded regions indicate acceptable range. Error bars show MCSE."
#| fig-align: center
#| fig-height: 11
#| fig-width: 9
#| echo: false

p_sens_coverage_study1
```

{{< include appendix_a.qmd >}}

{{< pagebreak >}}

{{< include appendix_b.qmd >}}

{{< pagebreak >}}

{{< include appendix_c.qmd >}}
