---
title: "Local Structural-After-Measurement (LSAM) and Traditional Approaches for Nonlinear Effects among Latent Variables: A Simulation Study"
shorttitle: "Comparing LSAM and Traditional SEM Approaches"

author:
  - name: Felipe Fontana Vieira
    corresponding: true
    orcid: 0009-0006-0949-6569
    email: felipe.fontanavieira@ugent.be
    affiliations:
      - name: Ghent University
        department: Department of Data Analysis, Faculty of Psychology and Educational Sciences
        address: Henri Dunantlaan 2
        city: Ghent
        country: Belgium
        postal-code: 9000
        id: UGent
    roles:
      - Conceptualization
      - Methodology
      - Software
      - Data curation
      - Formal analysis
      - Visualization
      - Writing - original draft
      - Writing - review & editing
  - name: Yves Rosseel
    corresponding: false
    orcid: 0000-0002-4129-4477
    affiliations:
      - ref: UGent
    roles:
      - Conceptualization
      - Methodology
      - Software
      - Writing - review & editing
      - Funding acquisition
  - name: Kjell Solem Slupphaug
    corresponding: false
    orcid: 0009-0005-8324-2834
    affiliations:
      - name: Norwegian University of Science and Technology
        department: Department of Psychology
        city: Trondheim
        country: Norway
    roles:
      - Writing - review & editing
      - Software

author-note:
  status-changes:
    affiliation-change: ~
    deceased: ~
  disclosures:
    # Example: This study was registered at X (Identifier Y).
    study-registration: "This study was not preregistered."
    # Acknowledge and cite data/materials to be shared.
    data-sharing: "Data, code, and materials for this manuscript can be found at link. Ideas and part of the results were previously presented at the conference of the European Association of Methodology 2025." 
    financial-support: "This project was funded by the Special Research Fund (BOF) of Ghent University (BOF/24J/2023/144)."
    
abstract: |
  Several methods have been proposed to include quadratic or interaction terms involving latent variables in structural equation models. Most of these methods use a system-wide estimation approach, meaning all free parameters are estimated simultaneously. Research has investigated their performance in models featuring primarily a limited number of nonlinear effects. Recently, several structural-after-measurement (SAM) approaches to handle latent quadratic and interaction terms have been proposed in the literature. In a SAM approach, estimation proceeds in two stages: first, parameters related to the measurement model are estimated; second, parameters related to the structural model are estimated. In this article, we present two simulation studies demonstrating that the recently proposed LSAM approach (Rosseel et al., 2025) performs well across a variety of conditions including distributional, reliability, and sample size manipulations. The first simulation study examined a model with three nonlinear effects under varying distributions (normal, right-skewed, uniform), reliabilities (0.4, 0.6, 0.8), and sample sizes (400, 1000). LSAM produced largely unbiased estimates with stable coverage, standard errors, and Type I error rates across most conditions. Performance was adversely affected under low reliability for some metrics, particularly with uniform distributions, though larger sample sizes mitigated these issues. Traditional methods (LMS, QML, UPI) exhibited results largely consistent with prior literature. The second simulation study tested a more complex model with eight nonlinear effects under the same conditions to assess whether performance deteriorates with increased complexity. LSAM maintained adequate performance despite greater model complexity, though similar limitations emerged and empirical power decreased under certain conditions. Traditional methods yielded more variable results, with generally poorer performance relative to LSAM.

keywords: [nonlinear effects, structural equation modeling, local structural-after-measurement, latent variables]

# Document formatting
floatsintext: true
numbered-lines: false
link-citations: false
mask: false
word-count: true

# Bibliography
bibliography: "Phd - Initial Readings.bib"

# Format specification for apaquarto
format:
  apaquarto-pdf:
    documentmode: man
    keep-tex: false
    include-in-header:
      text: |
        \usepackage{pdflscape}
        \raggedbottom
        
# Execution options
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: setup
#| include: false

library(simhelpers)
library(dplyr)
library(ggplot2)
```

{{< include introduction.qmd >}}

{{< include modelsframework.qmd >}}

{{< include design.qmd >}}

{{< include results.qmd >}}

{{< include discussion.qmd >}}

{{< pagebreak >}}

# References

::: {#refs}
:::

{{< pagebreak >}}

\begin{landscape}
\small

\begin{flushleft}
\textbf{Table 1}

\textit{Subset of the performance measures for evaluating parameter estimates in the simulation studies}
\end{flushleft}

\begin{longtable}{lll}
\toprule
Performance Measure & Empirical Calculation & MCSE \\
\midrule
\textbf{Absolute Criteria} & & \\
Absolute Bias & $\bar{B} - \beta$ & $\sqrt{S_B^2/K}$ \\
Mean Squared Error (MSE) & $\frac{1}{K}\sum_{k=1}^{K}(B_k - \beta)^2$ & $\sqrt{\frac{1}{K}[S_B^4(k_B - 1) + 4S_B^2 g_B(\bar{B} - \beta) + 4S_B^2(\bar{B} - \beta)^2]}$ \\
Root Mean Squared Error (RMSE) & $\sqrt{\frac{1}{K}\sum_{k=1}^{K}(B_k - \beta)^2}$ & $\sqrt{\frac{K-1}{K}\sum_{j=1}^{K}(\text{RMSE}_{(j)} - \text{RMSE})^2}$ \\
\textbf{Relative Criteria} & & \\
Relative Bias & $(\frac{\bar{B}}{\beta})- 1$ & $\sqrt{S_B^2/(K\beta^2)}$ \\
Relative MSE & $\frac{(\bar{B} - \beta)^2 + S_B^2}{\beta^2}$ & $\sqrt{\frac{1}{K\beta^4}[S_B^4(k_B - 1) + 4S_B^2 g_B(\bar{B} - \beta) + 4S_B^2(\bar{B} - \beta)^2]}$ \\
Relative RMSE & $\sqrt{\frac{(\bar{B} - \beta)^2 + S_B^2}{\beta^2}}$ & $\sqrt{\frac{K-1}{K}\sum_{j=1}^{K}(\text{rRMSE}_{(j)} - \text{rRMSE})^2}$ \\
\textbf{Standard Error Assessment} & & \\
Mean SE & $\overline{SE} = \frac{1}{K}\sum_{k=1}^{K}\widehat{SE}_k$ & --- \\
SE Ratio & $\overline{SE}/S_B$ & --- \\
\textbf{Hypothesis Testing} & & \\
Rejection Rate & $r_\alpha = \frac{1}{K}\sum_{k=1}^{K}I(P_k < \alpha)$ & $\sqrt{r_\alpha(1-r_\alpha)/K}$ \\
\textbf{Confidence Intervals} & & \\
Coverage & $c_\beta = \frac{1}{K}\sum_{k=1}^{K}I(A_k \leq \beta \leq B_k)$ & $\sqrt{c_\beta(1-c_\beta)/K}$ \\
\bottomrule
\end{longtable}

\begin{flushleft}
\textit{Note}. $B$ = estimator for parameter $\beta$; $K$ = number of replications producing estimates $B_1, ..., B_K$; $\bar{B} = (1/K)\sum_{k=1}^{K}B_k$ = sample mean; $S_B^2 = (1/(K-1))\sum_{k=1}^{K}(B_k - \bar{B})^2$ = sample variance; $S_B = \sqrt{S_B^2}$ = sample standard deviation; $k_B$ = standardized kurtosis; $g_B$ = standardized skewness; $I(\cdot)$ = indicator function; $P_k$ = p-value from replication $k$; $\alpha$ = significance level; $A_k$, $B_k$ = CI endpoints; $r_\alpha$ and $c_\beta$ denote rejection rate and coverage, respectively. MCSE = Monte Carlo Standard Error; dashes indicate MCSEs not computed.
\end{flushleft}

\normalsize
\end{landscape}

{{< pagebreak >}}

```{tikz}
#| label: fig-model
#| fig-cap: "Data Generating Model for the simulation studies. Top: Model for Simulation 1. Bottom: Model for Simulation 2. Residual variances and covariances and intercepts are not shown for clarity."
#| fig-align: center
#| fig-width: 10
#| fig-height: 16

\tikzset{
  latent/.style  ={circle,draw,minimum size=14mm},
  ind/.style     ={rectangle,draw,minimum height=6mm,minimum width=8mm,align=center},
  derived/.style ={circle,draw,minimum size=14mm},
  every node/.style={font=\small}
}

\begin{tikzpicture}

% ============================================================================
% FIRST DIAGRAM (Simulation 1)
% ============================================================================

\node[ind] (y1)  at (0,  0.8) {y$_1$};
\node[ind] (y2)  at (0,  0.0) {y$_2$};
\node[ind] (y3)  at (0, -0.8) {y$_3$};
\node[latent] (eta1) at (2.4, 0.0) {$\eta_1$};

\draw[->] (eta1.west) -- (y1.east);
\draw[->] (eta1.west) -- (y2.east);
\draw[->] (eta1.west) -- (y3.east);

\node[ind] (y4)  at (0, -2.8) {y$_4$};
\node[ind] (y5)  at (0, -3.6) {y$_5$};
\node[ind] (y6)  at (0, -4.4) {y$_6$};
\node[latent] (eta2) at (2.4, -3.6) {$\eta_2$};

\draw[->] (eta2.west) -- (y4.east);
\draw[->] (eta2.west) -- (y5.east);
\draw[->] (eta2.west) -- (y6.east);

% Covariance arrow between eta1 and eta2
\draw[<->,gray!40,bend right=30] (eta1) to (eta2);

\node[latent] (eta3) at (6.6, -1.6) {$\eta_3$};

\draw[->] (eta1) -- node[above] {} (eta3);
\draw[->] (eta2) -- node[above,sloped] {} (eta3);

\node[derived] (eta1sq) at (4.3, -4.2) {$\eta_1^{2}$};
\node[derived] (eta2sq) at (6.6, -4.2) {$\eta_2^{2}$};
\node[derived] (eta12)  at (8.9, -4.2) {$\eta_1\eta_2$};

\draw[->] (eta1sq) -- node[above] {} (eta3);
\draw[->] (eta2sq) -- node[right] {} (eta3);
\draw[->] (eta12)  -- node[above] {} (eta3);

\node[ind] (y7) at (5.6, 0.8) {y$_7$};
\node[ind] (y8) at (6.6, 0.8) {y$_8$};
\node[ind] (y9) at (7.6, 0.8) {y$_9$};

\draw[->] (eta3.north) -- (y7.south);
\draw[->] (eta3.north) -- (y8.south);
\draw[->] (eta3.north) -- (y9.south);

% ============================================================================
% SECOND DIAGRAM (Simulation 2) - Shifted down by 7 units instead of 13
% ============================================================================

\node[ind] (y1b)  at (0,  -6.0) {y$_1$};
\node[ind] (y2b)  at (0,  -7.0) {y$_2$};
\node[ind] (y3b)  at (0, -8.0) {y$_3$};
\node[latent] (eta1b) at (2.4, -7.0) {$\eta_1$};

\draw[->] (eta1b.west) -- (y1b.east);
\draw[->] (eta1b.west) -- (y2b.east);
\draw[->] (eta1b.west) -- (y3b.east);

\node[ind] (y4b)  at (0, -10.5) {y$_4$};
\node[ind] (y5b)  at (0, -11.5) {y$_5$};
\node[ind] (y6b)  at (0, -12.5) {y$_6$};
\node[latent] (eta2b) at (2.4, -11.5) {$\eta_2$};

\draw[->] (eta2b.west) -- (y4b.east);
\draw[->] (eta2b.west) -- (y5b.east);
\draw[->] (eta2b.west) -- (y6b.east);

\node[ind] (y7b)  at (0, -15.0) {y$_7$};
\node[ind] (y8b)  at (0, -16.0) {y$_8$};
\node[ind] (y9b)  at (0, -17.0) {y$_9$};
\node[latent] (eta3b) at (2.4, -16.0) {$\eta_3$};

\draw[->] (eta3b.west) -- (y7b.east);
\draw[->] (eta3b.west) -- (y8b.east);
\draw[->] (eta3b.west) -- (y9b.east);

% Covariance arrows between eta1, eta2, and eta3
\draw[<->,gray!40,bend right=30] (eta1b) to (eta2b);
\draw[<->,gray!40,bend right=30] (eta1b) to (eta3b);
\draw[<->,gray!40,bend right=30] (eta2b) to (eta3b);

\node[latent] (eta4b) at (5.5, -9.5) {$\eta_4$};

\draw[->] (eta1b) -- (eta4b);
\draw[->] (eta2b) -- (eta4b);
\draw[->] (eta3b) -- (eta4b);

\node[derived] (eta12b)  at (9.0, -7.0) {$\eta_1\eta_2$};
\node[derived] (eta13b)  at (9.0, -8.5) {$\eta_1\eta_3$};
\node[derived] (eta1sqb) at (9.0, -10.0) {$\eta_1^{2}$};
\node[derived] (eta2sqb) at (9.0, -11.5) {$\eta_2^{2}$};

\draw[->] (eta12b)  -- (eta4b);
\draw[->] (eta13b)  -- (eta4b);
\draw[->] (eta1sqb) -- (eta4b);
\draw[->] (eta2sqb) -- (eta4b);

\node[ind] (y10b) at (4.5, -6.0) {y$_{10}$};
\node[ind] (y11b) at (5.5, -6.0) {y$_{11}$};
\node[ind] (y12b) at (6.5, -6.0) {y$_{12}$};

\draw[->] (eta4b.north) -- (y10b.south);
\draw[->] (eta4b.north) -- (y11b.south);
\draw[->] (eta4b.north) -- (y12b.south);

\node[latent] (eta5b) at (5.5, -14.5) {$\eta_5$};

\draw[->] (eta4b) -- (eta5b);
\draw[->] (eta1b) -- (eta5b);
\draw[->] (eta2b) -- (eta5b);
\draw[->] (eta3b) -- (eta5b);

\node[derived] (eta14b)   at (9.0, -13.0) {$\eta_1\eta_4$};
\node[derived] (eta24b)   at (9.0, -14.5) {$\eta_2\eta_4$};
\node[derived] (eta1sq2b) at (9.0, -16.0) {$\eta_1^{2}$};
\node[derived] (eta3sqb)  at (9.0, -17.5) {$\eta_3^{2}$};

\draw[->] (eta14b)   -- (eta5b);
\draw[->] (eta24b)   -- (eta5b);
\draw[->] (eta1sq2b) -- (eta5b);
\draw[->] (eta3sqb)  -- (eta5b);

\node[ind] (y13b) at (4.5, -18.0) {y$_{13}$};
\node[ind] (y14b) at (5.5, -18.0) {y$_{14}$};
\node[ind] (y15b) at (6.5, -18.0) {y$_{15}$};

\draw[->] (eta5b.south) -- (y13b.north);
\draw[->] (eta5b.south) -- (y14b.north);
\draw[->] (eta5b.south) -- (y15b.north);

\end{tikzpicture}
```

```{r}
#| label: fig-bias-sim1
#| fig-cap: "Relative bias for Simulation 1 with varying distributions and reliability levels (N = 400)."
#| fig-align: center
#| fig-height: 12
#| fig-width: 9
#| echo: false

p_relative_bias_400_full_study_1
```

```{r}
#| label: fig-rmse-sim1
#| fig-cap: "Relative RMSE for Simulation 1 with varying distributions and reliability levels (N = 400)."
#| fig-align: center
#| fig-height: 12
#| fig-width: 9
#| echo: false

p_relative_rmse_400_full_study_1
```

```{r}
#| label: fig-ratio-sim1
#| fig-cap: "SE/SD Ratio for Simulation 1 with varying sample sizes and reliability levels (Right-skewed and uniform conditions)."
#| fig-align: center
#| fig-height: 12
#| fig-width: 9
#| echo: false

p_slope_nonnorm_unif_study_1
```

```{r}
#| label: fig-coverage-sim1
#| fig-cap: "Coverage for Simulation 1 varying distributions, reliability levels, and sample sizes."
#| fig-align: center
#| fig-height: 12
#| fig-width: 9
#| echo: false

p_cov_nonnorm_unif_study_1
```

```{r}
#| label: fig-type1-sim1
#| fig-cap: "Type I error rate for Simulation 1 varying distributions and reliability levels (N = 1000). MCSE are not shown due to their small magnitude."
#| fig-align: center
#| fig-height: 12
#| fig-width: 9
#| echo: false

p_t1_1000_study_1
```

```{r}
#| label: fig-bias-sim2
#| fig-cap: "Relative bias for Simulation 2 with varying distributions and reliability levels (N = 400)."
#| fig-align: center
#| fig-height: 12
#| fig-width: 9
#| echo: false

p_relative_bias_400_full_all_study_2
```

```{r}
#| label: fig-rmse-sim2
#| fig-cap: "Relative RMSE for Simulation 2 with varying distributions and reliability levels (N = 400)."
#| fig-align: center
#| fig-height: 12
#| fig-width: 9
#| echo: false

p_relative_rmse_400_full_all_study_2
```

```{r}
#| label: fig-seratio-sim2
#| fig-cap: "SE/SD Ratio for Simulation 2 with varying distributions and reliability levels (N = 400)."
#| fig-align: center
#| fig-height: 12
#| fig-width: 9
#| echo: false

p_sesd_400_full_all_study_2
```

```{r}
#| label: fig-coverage-sim2
#| fig-cap: "Coverage for Simulation 2 with varying distributions and reliability levels (N = 400)."
#| fig-align: center
#| fig-height: 12
#| fig-width: 9
#| echo: false

p_coverage_400_full_all_study_2
```

```{r}
#| label: fig-type1-sim2
#| fig-cap: "Type I error rate for Simulation 2 with varying distributions and reliability levels (N = 1000). MCSE are not shown due to their small magnitude."
#| fig-align: center
#| fig-height: 12
#| fig-width: 9
#| echo: false

p_t1_1000_all_study_2
```

{{< include appendix_a.qmd >}}

{{< pagebreak >}}

{{< include appendix_b.qmd >}}