---
title: ''
author: ''
date: ''
output:
  pdf_document: default
  html_document: default
---

```{r packages, echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr); library(ggplot2)

source("../Simulations/Plots.R")
source("../Simulations/Study_1/Results/Results(1).R")
source("../Simulations/Study_2/Results/Results(2).R")
```

# Results for simulation studies 

The results reported are a subset of the findings focused mainly on the cases when the nonlinear effects were present. For the complete figures and results, we refer the reader to the online supplementary materials 1. 

## Results for simulation 1

```{r results-first-sim-study, echo=FALSE, warning=FALSE, message=FALSE}

data_study_1 <- load("../Simulations/Study_1/Data/Results_Study_1_final.RData")

results_study_1 <- CalculatePerformance(
   all_results,
   parameters_of_interest = c("eta1","eta2","eta1:eta2","eta1:eta1","eta2:eta2"),
   remove_outliers = TRUE,
   outlier_threshold = 3,
   alpha = 0.05,
   min_reps = 10,
   exclude_warnings = FALSE,  # TRUE to exclude iterations with warnings
   return_convergence_details = FALSE
)
```

```{r convergence-outliers-first-sim-study, echo=FALSE, results='hide'}
get_convergence_outlier_rate_study_1 <- function(method, dist, n, rel, model = "Full", 
                                                  rate_type = c("convergence", "outlier", "final")) {
  rate_type <- match.arg(rate_type)

  col_map <- c(
    "convergence" = "Convergence_Rate_This_Method",
    "outlier" = "Outlier_Rate_This_Method", 
    "final" = "Percent_Total_Excluded"
  )
  
  col_name <- col_map[rate_type]
  
  # since these rates are the same across parameters, we just pick one (e.g., eta1)
  result <- results_study_1 %>%
    filter(
      Method == toupper(method),
      Distribution == dist,
      SampleSize == n,
      Reliability == rel,
      Model == model,
      Parameter == "eta1"  # rates are identical across parameters
    ) %>%
    pull(!!sym(col_name))
  
  if(length(result) > 0) result[1] else NA
}

# most outliers
#results_study_1 %>%
#  filter(Parameter == "eta1") %>%
#  group_by(Method) %>%
#  arrange(desc(Outlier_Rate_This_Method)) %>%
#  slice_head(n = 2) %>%
#  select(Method, Model, Distribution, SampleSize, Reliability, Outlier_Rate_This_Method)

# worst convergence rates (lowest values) for each method
#results_study_1 %>%
#  filter(Parameter == "eta1") %>%
#  group_by(Method) %>%
#  arrange(Convergence_Rate_This_Method) %>%
#  slice_head(n = 2) %>%
#  select(Method, Model, Distribution, SampleSize, Reliability, Convergence_Rate_This_Method)

```

### Convergence Issues and Outliers  

Convergence problems were generally rare. The main exception was UPI, which showed reduced convergence under conditions of moderate sample size, low reliability, and uniform latent predictors. In this scenario, convergence rates were `r round(get_convergence_outlier_rate_study_1("UPI", "uniform", 400, 0.4, "Full", "convergence"), 2)`% for the full model and `r round(get_convergence_outlier_rate_study_1("UPI", "uniform", 400, 0.4, "Linear", "convergence"), 2)`% for the linear model. By contrast, LMS and QML converged well, with the lowest rates in the same setting being `r round(get_convergence_outlier_rate_study_1("LMS", "uniform", 400, 0.4, "Full", "convergence"), 2)`% and `r round(get_convergence_outlier_rate_study_1("QML", "uniform", 400, 0.4, "Full", "convergence"), 2)`% (full model), and `r round(get_convergence_outlier_rate_study_1("LMS", "uniform", 400, 0.4, "Linear", "convergence"), 2)`% and `r round(get_convergence_outlier_rate_study_1("QML", "uniform", 400, 0.4, "Linear", "convergence"), 2)`% (linear model). LSAM consistently converged, with rates of `r round(get_convergence_outlier_rate_study_1("LSAM", "uniform", 400, 0.4, "Linear", "convergence"), 2)`% across all conditions.  

Outlier rates followed a comparable pattern. The most pronounced rates again occurred under moderate sample size, low reliability, and uniform latent predictors. UPI produced the highest outlier frequencies, reaching `r round(get_convergence_outlier_rate_study_1("UPI", "uniform", 400, 0.4, "Full", "outlier"), 2)`% in the full model and `r round(get_convergence_outlier_rate_study_1("UPI", "uniform", 400, 0.4, "Linear", "outlier"), 2)`% in the linear model. LSAM also yielded some outliers (`r round(get_convergence_outlier_rate_study_1("LSAM", "uniform", 400, 0.4, "Linear", "outlier"), 2)`% for the linear model and `r round(get_convergence_outlier_rate_study_1("LSAM", "uniform", 400, 0.4, "Full", "outlier"), 2)`% for the full model). In contrast, LMS and QML generated virtually none, with their highest rates reaching only `r round(get_convergence_outlier_rate_study_1("LMS", "uniform", 400, 0.4, "Full", "outlier"), 2)`% and `r round(get_convergence_outlier_rate_study_1("QML", "uniform", 400, 0.4, "Full", "outlier"), 2)`% (both full model). Detailed results are provided in Table X (Appendix).  

```{r plots-first-sim-study, echo=FALSE}

plot_study_1_data <- prepare_study1_data(results_study_1)

# BIAS 
study_1_relative_bias <- plot_study_1_data$bias_relative

dat_relative_bias_400_full_study_1 <- study_1_relative_bias %>%
   filter(Model == "Full", SampleSize == "400") %>%
   droplevels()

p_relative_bias_400_full_study_1 <- plot_bias(
   dat_relative_bias_400_full_study_1, 
   shapes = SHAPES_4, 
   ltys = LTYS_4,
   facet_formula = Distribution + Parameter ~ .,  # faceting
   y_breaks = seq(-1, 2, by = 1)         # y-axis
)

# Relative RMSE 
study_1_relative_rmse <- plot_study_1_data$rmse_relative

dat_relative_rmse_400_full_study_1 <- study_1_relative_rmse %>%
  filter(Model == "Full", SampleSize == "400") %>%
  droplevels()

p_relative_rmse_400_full_study_1 <- plot_rmse(
  dat_relative_rmse_400_full_study_1, 
  shapes = SHAPES_4, 
  ltys = LTYS_4,
  facet_formula = Distribution + Parameter ~ .,  # faceting as bias
  #y_breaks = seq(0, 0.30, by = 0.05),            # y-axis for RMSE scale
  #y_limits = c(0, 0.30)                          # optional: set limits
)

# SE/SD RATIO (Nonnormal & Uniform, Full, N=400 & 1000) =========
study_1_sesd <- plot_study_1_data$sesd

dat_sesd_full_nonnorm_unif_study_1 <- study_1_sesd %>%
  filter(Model == "Full", 
         SampleSize %in% c("400", "1000"), 
         Distribution %in% c("Right-skewed", "Uniform")) %>%
  droplevels()

p_slope_full_nonnorm_unif_study_1 <- plot_sesd(
  dat_sesd_full_nonnorm_unif_study_1,
  shapes = SHAPES_4,
  ltys = LTYS_4,
  facet_formula = Distribution + Parameter ~ SampleSize
)

# COVERAGE (Full, N=400 & 1000, all distributions)
study_1_coverage <- plot_study_1_data$coverage
dat_cov_full_400_1000_study_1 <- study_1_coverage %>%
  filter(Model == "Full", SampleSize %in% c("400", "1000")) %>%
  droplevels()

p_cov_full_400_1000_study_1 <- plot_coverage(
  dat_cov_full_400_1000_study_1, 
  shapes = SHAPES_4,
  ltys = LTYS_4,
  facet_formula = Distribution + Parameter ~ SampleSize
)

# TYPE I ERROR (Linear, N=1000 only) 
study_1_type1 <- plot_study_1_data$type1
dat_t1_1000_study_1 <- study_1_type1 %>%
  filter(grepl("N=1000", Condition)) %>%
  droplevels()

p_t1_1000_study_1 <- plot_type1(
  dat_t1_1000_study_1,  
  greys = GREYS_4,
  facet_formula = Distribution + Parameter ~ Condition
)
```

### Relative Bias and RMSE When Nonlinear Effects Were Present

Figures 2 and 3 present relative bias and RMSE values across distributional conditions at moderate sample size (results at high sample size were qualitatively similar). Following @brandt_etall_2014, values exceeding 0.10 (i.e., 10%) indicate bias.  

Under normality, most methods performed stably across reliability levels, with bias primarily occurring for the interaction term at low reliability across all approaches. Under right-skewed distributions, clear differences emerged: LSAM and UPI were unbiased for all nonlinear effects except interactions at low reliability, whereas LMS and QML showed severe negative bias for interactions and positive bias for quadratic effects across all reliabilities. Under a uniform distribution, LSAM remained largely unbiased, and UPI displayed bias for most nonlinear effects only at low reliability. In contrast, LMS and QML produced unbiased interaction estimates but consistently negative bias for quadratic effects.  

For relative RMSE, all approaches were comparable under normality, except at low reliability. Under right-skewed distributions, LSAM had the lowest RMSE values, though differences diminished at high reliability. Under a uniform distribution, LMS and QML showed the lowest RMSE, but performance converged across methods at high reliability.  

### Efficiency and Accuracy of Standard Errors when Nonlinear Effects were present

Figure 4 presents SE/SD ratios for right-skewed and uniform conditions across sample sizes. Following @brandt_etall_2014, ratios below 0.85 (underestimation) or above 1.15 (overestimation) indicate bias.  

Under normality, LSAM was unbiased across all conditions, with only UPI overestimating at low reliability under moderate sample size. For right-skewed distributions, UPI alone showed underestimated ratios, whereas LSAM performed comparably to LMS and QML. In uniform conditions, clearer differences emerged: at low reliability, both LSAM and UPI overestimated SEs for all nonlinear effects, though this bias disappeared at large sample sizes. LMS and QML remained stable and similar across all conditions.

### Coverage for When Nonlinear Effects Were Present

Figure 5 visualizes coverage results. For some approaches and conditions, exact values are displayed when they fell outside the y-axis range. Coverage between 93% and 97% was considered acceptable.  

LSAM exceeded this range across all distributions only at low reliability with moderate sample size, but not at large samples. Under normality with moderate samples and medium reliability, all approaches achieved near-nominal 95% coverage for interaction and quadratic effects. Under right-skewness, LMS and QML showed substantial under-coverage, with UPI also affected though to a lesser degree. Larger sample sizes did not improve coverage, whereas higher reliability reduced under-coverage but did not eliminate it. LSAM performed comparatively well, showing only minor under-coverage for one quadratic effect. Under uniform distributions, LMS and QML showed under-coverage only for quadratic effects.  

### Type I Error Rate

Figure 6 shows Type I error rates across approaches at large sample size. Rates between 2.5% and 7.5% were considered acceptable. Results at moderate sample size were qualitatively similar, although under right-skewness LMS and QML showed somewhat less inflation, albeit still above acceptable levels.  

Under normality, all approaches remained within the acceptable range even at low reliability, though LSAM tended to yield slightly lower values than the others. At medium and high reliability, all methods showed similarly well-controlled error rates. Under right-skewed distributions, LSAM and UPI stayed within acceptable limits, whereas LMS and QML exhibited severe inflation for quadratic effects across all reliabilities. Under uniform distributions, LSAM and UPI generally performed well, with values falling below the acceptable range only at low reliability.  

### Empirical Power

Given the inflated Type I error rates observed for some approaches, power results should be interpreted with caution [@morris_etall_2019]. At large sample size, LSAM reached power levels near or above 80% under medium and high reliability across all distributions for most nonlinear effects. The main exception was under the uniform distribution, where quadratic effects remained underpowered. The other approaches showed broadly similar patterns. Under right-skewness, however, LMS and QML diverged markedly, with extremely low power for the interaction term but high power for quadratic effects.  
### Bias, RMSE, Standard Errors, and Coverage When Nonlinear Effects Were Absent.** Bias results were similar to those when effects were present, but with reduced magnitude. One notable difference emerged under uniform distribution: LMS and QML showed unbiased quadratic estimates but biased interaction estimates, which disappeared at high reliability. RMSE showed no relevant differences except for reduced magnitude. Standard error accuracy was generally similar to the presence condition, with one main difference: UPI showed improved accuracy under normality at low reliability and moderate sample size. Regarding coverage, LMS and QML improved under non-normality but remained below the desirable range for quadratic effects. Under uniform distribution, coverage for quadratic effects substantially improved for both LMS and QML approaches.

## Summary of simulation 1

With the exception of low-reliability conditions, LSAM demonstrated adequate performance across all evaluated metrics. LSAM generally yielded unbiased estimates, whereas QML and LMS showed systematic bias: positive and negative bias for nonlinear effects under right-skewed distributions, and negative bias for quadratic effects under uniform distributions. UPI also produced largely unbiased results, consistent with previous findings. For standard errors, LMS and QML were the most efficient, although LSAM produced comparable results at medium and high reliability across all distributions. Coverage rates remained relatively stable for LSAM, but not for LMS, QML, or UPI. Type I error rates were within the acceptable range for LSAM and UPI under medium and high reliability across distributions, whereas LMS and QML showed marked inflation under right-skewed conditions. Finally, power was generally highest for LMS and QML, though this conclusion should be interpreted cautiously given their inflated Type I error. When Type I error was controlled, all approaches achieved desirable power levels for most effects, with the exception of quadratic effects under the uniform distribution, which remained underpowered.  

## Result for simulation 2

```{r results-second-sim-study, echo=FALSE, warning=FALSE, message=FALSE}

data_study_2 <- load("../Simulations/Study_2/Data/Results_Study_2_final.RData")

results_study_2 <- CalculatePerformance_Study2(
  all_results,
  parameters_of_interest = list(
    eta4 = c("eta1", "eta2", "eta3", "eta1:eta2", "eta1:eta3", "eta1:eta1", "eta2:eta2"),
    eta5 = c("eta4", "eta1", "eta2", "eta3", "eta1:eta4", "eta2:eta4", "eta1:eta1", "eta3:eta3")
  ),
  remove_outliers = TRUE,
  outlier_threshold = 3,
  alpha = 0.05,
  min_reps = 10,
  exclude_warnings = FALSE,
  return_convergence_details = TRUE
)
```

### Convergence Issues and Outliers

```{r convergence-second-sim-study, echo=FALSE, warning=FALSE, results='hide'}

get_convergence_outlier_rate_study_2 <- function(method, dist, n, rel, model = "Full",
                                                  equation = c("eta4", "eta5"),
                                                  rate_type = c("convergence", "outlier", "final")) {
  equation <- match.arg(equation)
  rate_type <- match.arg(rate_type)
  
  col_map <- c(
    "convergence" = "Convergence_Rate_This_Method",
    "outlier" = "Outlier_Rate_This_Method", 
    "final" = "Percent_Total_Excluded"
  )
  
  col_name <- col_map[rate_type]
  
  # needs representative parameter for each equation
  # for eta4: use "eta1" (first predictor)
  # for eta5: use "eta4" (first predictor)
  param_to_use <- ifelse(equation == "eta4", "eta1", "eta4")
  
  result <- results_study_2$results %>%
    filter(
      Method == toupper(method),
      Distribution == dist,
      SampleSize == n,
      Reliability == rel,
      Model == model,
      Equation == equation,
      Parameter == param_to_use
    ) %>%
    pull(!!sym(col_name))
  
  if(length(result) > 0) result[1] else NA
}

# worst outlier rates across both equations
#results_study_2$results %>%
#  filter((Equation == "eta4" & Parameter == "eta1") | 
#         (Equation == "eta5" & Parameter == "eta4")) %>%
#  group_by(Method, Equation) %>%
#  arrange(desc(Outlier_Rate_This_Method)) %>%
#  slice_head(n = 2) %>%
#  select(Method, Equation, Model, Distribution, SampleSize, Reliability, Outlier_Rate_This_Method) %>%
#  arrange(Method, Equation, desc(Outlier_Rate_This_Method))

# Worst convergence rates for each method and equation
#results_study_2$results %>%
#  filter((Equation == "eta4" & Parameter == "eta1") | 
#         (Equation == "eta5" & Parameter == "eta4")) %>%
#  group_by(Method, Equation) %>%
#  arrange(Convergence_Rate_This_Method) %>%
#  slice_head(n = 2) %>%
#  select(Method, Equation, Model, Distribution, SampleSize, Reliability, Convergence_Rate_This_Method) %>%
#  arrange(Method, Equation, Convergence_Rate_This_Method)
```

Convergence issues were more pronounced in this study as expected. The UPI exhibited the poorest convergence performance under conditions with moderate sample size, low reliability, and uniform latent predictors, achieving rates of `r round(get_convergence_outlier_rate_study_2("UPI", "uniform", 400, 0.4, "Full", "eta4", "convergence"), 2)`% with the full population model and `r round(get_convergence_outlier_rate_study_2("UPI", "uniform", 400, 0.4, "Linear", "eta4", "convergence"), 2)`% with the linear population model. These rates were consistent across both structural equations. For the normal and nonnormal conditions, convergence rates were above 95%. The QML showed better but still suboptimal convergence under the same challenging condition, with `r round(get_convergence_outlier_rate_study_2("QML", "uniform", 400, 0.4, "Full", "eta4", "convergence"), 2)`% (full model) and `r round(get_convergence_outlier_rate_study_2("QML", "uniform", 400, 0.4, "Linear", "eta4", "convergence"), 2)`% (linear model). In contrast, LSAM maintained perfect convergence (`r round(get_convergence_outlier_rate_study_2("LSAM", "normal", 400, 0.4, "Full", "eta4", "convergence"), 2)`%) across all conditions.

Outlier patterns revealed substantial differences between methods. The UPI exhibited the highest outlier rates under the same problematic condition as above: `r round(get_convergence_outlier_rate_study_2("UPI", "uniform", 400, 0.4, "Linear", "eta4", "outlier"), 2)`% for the linear model and `r round(get_convergence_outlier_rate_study_2("UPI", "uniform", 400, 0.4, "Full", "eta4", "outlier"), 2)`% for the full model, again with identical rates observed for both structural equations. QML demonstrated considerably lower outlier rates under this condition (`r round(get_convergence_outlier_rate_study_2("QML", "uniform", 400, 0.4, "Linear", "eta4", "outlier"), 2)`% for linear, `r round(get_convergence_outlier_rate_study_2("QML", "uniform", 400, 0.4, "Full", "eta4", "outlier"), 2)`% for full model). Notably, LSAM's highest outlier rate (`r round(get_convergence_outlier_rate_study_2("LSAM", "nonnormal", 400, 0.4, "Linear", "eta4", "outlier"), 2)`%) occurred with non-normal rather than uniform distributions, showing consistent rates across both structural equations.

```{r plots-second-sim-study, echo=FALSE}

study_2_normal_data <- prepare_study2_data(results_study_2$results, "normal")
study_2_nonnormal_data <- prepare_study2_data(results_study_2$results, "nonnormal")
study_2_uniform_data <- prepare_study2_data(results_study_2$results, "uniform")

# RELATIVE BIAS (full model, N=400, all Distributions) 
dat_relative_bias_400_full_all_study_2 <- bind_rows(
  study_2_normal_data$bias_relative %>%
    filter(Model == "Full", SampleSize == "400"),
  study_2_nonnormal_data$bias_relative %>%
    filter(Model == "Full", SampleSize == "400"),
  study_2_uniform_data$bias_relative %>%
    filter(Model == "Full", SampleSize == "400")
) %>%
  droplevels()

p_relative_bias_400_full_all_study_2 <- plot_bias(
  dat_relative_bias_400_full_all_study_2,
  shapes = SHAPES_3,
  ltys = LTYS_3,
  facet_formula = Parameter ~ Distribution,
  y_breaks = seq(-1, 1.5, by = 0.5),
  y_limits = c(-1, 1.5),
  bias_type = "relative"
)

# RELATIVE RMSE (full model, N=400, all Distributions) 
dat_relative_rmse_400_full_all_study_2 <- bind_rows(
  study_2_normal_data$rmse_relative %>%
    filter(Model == "Full", SampleSize == "400"),
  study_2_nonnormal_data$rmse_relative %>%
    filter(Model == "Full", SampleSize == "400"),
  study_2_uniform_data$rmse_relative %>%
    filter(Model == "Full", SampleSize == "400")
) %>%
  droplevels()

p_relative_rmse_400_full_all_study_2 <- plot_bias(
  dat_relative_rmse_400_full_all_study_2,
  shapes = SHAPES_3,
  ltys = LTYS_3,
  facet_formula = Parameter ~ Distribution,
  y_breaks = seq(-0.5, 5, by = 1.5),  
  y_limits = c(-0.5, 5),              
  bias_type = "relative"
)


# SE/SD RATIO (Full model, N=400, All Distributions) 
dat_sesd_400_full_all_study_2 <- bind_rows(
  study_2_normal_data$sesd %>%
    filter(Model == "Full", SampleSize == "400"),
  study_2_nonnormal_data$sesd %>%
    filter(Model == "Full", SampleSize == "400"),
  study_2_uniform_data$sesd %>%
    filter(Model == "Full", SampleSize == "400")
) %>%
  droplevels()

p_sesd_400_full_all_study_2 <- plot_sesd(
  dat_sesd_400_full_all_study_2,
  shapes = SHAPES_3,
  ltys = LTYS_3,
  facet_formula = Parameter ~ Distribution,
  title = ""
)

#  COVERAGE (Full model, N=400, All Distributions)
dat_coverage_400_full_all_study_2 <- bind_rows(
  study_2_normal_data$coverage %>%
    filter(Model == "Full", SampleSize == "400"),
  study_2_nonnormal_data$coverage %>%
    filter(Model == "Full", SampleSize == "400"),
  study_2_uniform_data$coverage %>%
    filter(Model == "Full", SampleSize == "400")
) %>%
  droplevels()

p_coverage_400_full_all_study_2 <- plot_coverage(
  dat_coverage_400_full_all_study_2,
  shapes = SHAPES_3,
  ltys = LTYS_3,
  facet_formula = Parameter ~ Distribution,
  title = ""
)

# TYPE I ERROR (Linear, N=1000, Nonnormal & Uniform)
dat_t1_1000_all_study_2 <- bind_rows(
  study_2_nonnormal_data$type1 %>%
    filter(grepl("N=1000", Condition)),
  study_2_uniform_data$type1 %>%
    filter(grepl("N=1000", Condition))
) %>%
  droplevels()

p_t1_1000_all_study_2 <- plot_type1(
  dat_t1_1000_all_study_2,
  greys = GREYS_3,
  facet_formula = Parameter ~ Distribution + Condition,
  title = ""
)
```

### Relative Bias and RMSE When Nonlinear Effects Were Present 

Figure 7 and 8 show respectively the relative bias and RMSE for all nonlinear effects across distributions with a moderate sample size. As in simulation 1, results under a large sample size were qualitatively similar (e.g., reduced MCSE and bias). Under normality, results were mixed. With low reliability, LSAM showed bias for some nonlinear effects, which improved under a medium reliability. The UPI performed similarly, while QML differed slighly with biased results mainly for the nonlinear effects within the structural model for $\eta_5$ under low reliability. Under non-normality, similar patterns emerged: LSAM showed bias for some effects at low reliability, improving at medium reliability. Notably, QML bias increased substantially compared to normality for most nonlinear effects across all reliabilities. Under uniform distribution, LSAM showed unbiased results for nearly all nonlinear effects even at low reliability. UPI and QML followed this pattern, except QML exhibited bias for all quadratic terms across reliability levels. Relative RMSE was similar across methods under normality and other distributions, with QML generally showing smaller RMSE.

### Efficiency and Accuracy of Standard Errors When Nonlinear Effects Were Present

Figure 9 shows SE/SD ratios for all distributions at a moderate sample size. Results improved with increasing sample size for all approaches. Under normality, the LSAM yielded ratios within acceptable range across all reliability levels, while the QML showed the most efficient ratios. The UPI, however, exhibited ratios below 0.85 for all nonlinear effects at low reliability, improving at medium reliability. Under non-normality, LSAM and QML showed ratios within the desirable range with some exceptions for one or two nonlinear effects. The UPI struggled at low and medium reliabilities, though ratios were just slightly below 0.85 in the latter case. Under uniform distribution, LSAM showed one overestimation at low reliability, while UPI yielded underestimated ratios at low and medium reliabilities. The QML resulted in efficient ratios. 

### Coverage When Nonlinear Effects Were Present

Figure 10 visualizes results for a moderate sample size. For some approaches under specific conditions, we show again the exact values. Large sample size yielded qualitatively similar results. Under normality, LSAM generally produced coverage rates within acceptable deviations, though over-coverage occurred at low reliability for some effects. The QML produced coverage within the desirable range for all nonlinear effects, while UPI exhibited under-coverage at low reliability for most effects. Under non-normality, LSAM showed some fluctuations but generally yielded results within acceptable range, apart from similar over-coverage at low reliability. However, QML and UPI resulted in inadequate coverage that achieved acceptable values only at high reliability. Under uniform distribution, LSAM showed similar performance as in the other distributions, while QML and UPI showed under-coverage mainly for quadratic terms at low and medium reliabilities.

### Type I Error Rate

Figure 11 visualizes results for a large sample size. Under normal conditions, all approaches maintained type I error rates within the nominal 5% level. Under nonnormal conditions, QML produced substantially inflated type I error rates with low and moderate reliability. Under uniform distributions, all methods demonstrated acceptable type I error control.

### Empirical Power

Similarly as in simulation 1, results for empirical power are interpreted only when the type I error control rate was within the nominal rate. In that case, for the normal distribution, power was generally larger for the nonlinear effects within $\eta_4$, where only for a large sample size and high reliability surpassed 80%. For the non-normal condition, slightly similar results were obtained. Interestingly, power was larger for the nonlinear effects within the $\eta_5$ equation compared to the normal case. Last, for the uniform distribution, results yielded low power except for the first two interaction effects within the $\eta_4$.

**Bias and RMSE When Nonlinear Effects Were Absent.** Notable differences included reduced bias under low reliability for normality and unbiased quadratic term results for QML under uniform distribution.

**Efficiency and Accuracy of Standard Errors When Nonlinear Effects Were Not Present.** Results were highly similar, except LSAM showed some overestimation under uniform distribution compared to the full model for some nonlinear effects.

**Coverage When Nonlinear Effects Were Not Present.** Coverage improved for all approaches under normal and uniform conditions. However, QML still showed undercoverage under non-normality.

## Brief discussion of simulation 2

As discussed previously, scalability encompasses several components. The first concerns computational time for estimation. Although this depends heavily on software implementation details (e.g., pure R versus C++ implementations), the LMS clearly demands substantial computational resources, which is the reason for not including it, and hence it is aligned with our expectation. However, one could also argue that this computational cost may be acceptable given the potentially valuable statistical properties that LMS offers when assumptions hold. The second component concerns convergence rates. We observed that this was problematic for the UPI, with the severe issues mainly for the uniform and low reliability condition. For the QML and LSAM, convergence was generally not an issue. Related to this, outlier estimates also increased, though this occurred only for the UPI and LSAM methods. The final aspect concerns performance itself. Contrary to our expectations, the biased results for nonlinear effects in the first structural equation did not substantially influence (e.g., cascade affect) the nonlinear effects in the second structural equation. 