---
title: ""
author: ""
date: ""
output: html_document
---

# Results for simulation studies 

The results reported are a subset of the findings. For the complete figures and results, we refer the reader to the online supplementary materials 1. 

## Result for simulation study 1

```{r results, echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr); library(tidyr); library(purrr); library(stringr); library(kableExtra); library(glue); library(simhelpers)

load("sim_results/run_20250828_1758_36_1000/final_results.RData")

extract_eta3_parameters <- function(table, method_type) {
  if (is.null(table)) return(NULL)
  
  if (method_type == "dblcent") {
    rows <- table[table$lhs == "eta3" & table$op == "~", ]
    params <- if (nrow(rows) == 3) {
      c("eta1", "eta2", "eta1:eta2")
    } else {
      c("eta1", "eta2", "eta1:eta2", "eta1:eta1", "eta2:eta2")
    }
    RESULTS <- list(
      "Estimates"        = setNames(rows$est, params),
      "Standard Errors"  = setNames(rows$se, params),
      "P-values"         = setNames(rows$pvalue, params),
      "CI_lower"         = setNames(rows$ci.lower, params),
      "CI_upper"         = setNames(rows$ci.upper, params)
    )
    
  } else if (method_type == "sam") {
    coefs <- table[table$lhs == "eta3" & table$op == "~", ]
    params <- if (nrow(coefs) == 3) {
      c("eta1", "eta2", "eta1:eta2")
    } else {
      c("eta1", "eta2", "eta1:eta2", "eta1:eta1", "eta2:eta2")
    }
    rows <- table$lhs == "eta3" & table$op == "~" & table$rhs %in% params
    ests     <- setNames(table$est[rows], table$rhs[rows])
    ses      <- setNames(table$se[rows], table$rhs[rows])
    pval     <- setNames(table$pvalue[rows], table$rhs[rows])
    ci_lower <- setNames(table$ci.lower[rows], table$rhs[rows])
    ci_upper <- setNames(table$ci.upper[rows], table$rhs[rows])
    RESULTS <- list(
      "Estimates"        = ests[params],
      "Standard Errors"  = ses[params],
      "P-values"         = pval[params],
      "CI_lower"         = ci_lower[params],
      "CI_upper"         = ci_upper[params]
    )
    
  } else if (method_type %in% c("lms", "qml")) {
    rows <- table[table$lhs == "eta3" & table$op == "~", ]
    if (nrow(rows) == 5) {
      eta1eta1_idx <- which(rows$rhs == "eta1:eta1")
      eta1eta2_idx <- which(rows$rhs == "eta1:eta2")
      idx <- seq_len(nrow(rows))
      if (length(eta1eta1_idx) == 1 && length(eta1eta2_idx) == 1) {
        idx[eta1eta1_idx] <- eta1eta2_idx
        idx[eta1eta2_idx] <- eta1eta1_idx
      }
      RESULTS <- list(
        "Estimates"        = setNames(rows$est[idx], rows$rhs[idx]),
        "Standard Errors"  = setNames(rows$std.error[idx], rows$rhs[idx]),
        "P-values"         = setNames(rows$p.value[idx], rows$rhs[idx]),
        "CI_lower"         = setNames(rows$ci.lower[idx], rows$rhs[idx]),
        "CI_upper"         = setNames(rows$ci.upper[idx], rows$rhs[idx])
      )
    } else {
      RESULTS <- list(
        "Estimates"        = setNames(rows$est, rows$rhs),
        "Standard Errors"  = setNames(rows$std.error, rows$rhs),
        "P-values"         = setNames(rows$p.value, rows$rhs),
        "CI_lower"         = setNames(rows$ci.lower, rows$rhs),
        "CI_upper"         = setNames(rows$ci.upper, rows$rhs)
      )
    }
  }
  RESULTS
}

CalculateBiasAndCoverage <- function(all_results,
                                     parameters_of_interest = c("eta1","eta2","eta1:eta2","eta1:eta1","eta2:eta2"),
                                     remove_outliers = TRUE,
                                     outlier_threshold = 3,  # IQR multiplier for outlier removal
                                     alpha = 0.05,
                                     min_reps = 10,
                                     return_convergence_details = TRUE) {  # New parameter
  options(scipen = 999)
  if (is.null(all_results) || length(all_results) == 0) {
    stop("all_results is NULL or empty. Please load your data first.")
  }
  methods <- c("sam", "lms", "qml", "dblcent")
  results_summary <- dplyr::tibble()
  param_index <- c("eta1"=1, "eta2"=2, "eta1:eta2"=3, "eta1:eta1"=4, "eta2:eta2"=5)
  
  # Initialize convergence details storage
  convergence_details <- list()
  
  for (i in seq_along(all_results)) {
    condition <- all_results[[i]]$condition
    res_list  <- all_results[[i]]$results
    
    # true values (fallbacks)
    true_values <- all_results[[i]]$true_parameters
    if (is.null(true_values)) {
      if (!is.null(condition$Model_Type)) {
        if (condition$Model_Type == "null") {
          true_values <- c(0.316, 0.316, 0, 0, 0)
        } else if (condition$Model_Type == "alternative") {
          true_values <- c(0.316, 0.316, 0.139, 0.101, 0.101)
        }
      } else {
        true_values <- c(0.316, 0.316, 0.139, 0.101, 0.101)
      }
    }
    model_name <- if (!is.null(condition$Model_Type)) {
      ifelse(condition$Model_Type == "null", "Linear", "Full")
    } else "Full"
    distribution <- as.character(condition$Distribution)
    if (is.null(distribution) || distribution == "") distribution <- "normal"
    sample_size <- condition$N
    reliability <- condition$Rel
    
    # ============================================================
    # STEP 1: TRACK CONVERGENCE FOR EACH METHOD SEPARATELY
    # ============================================================
    
    # Get the number of replications
    max_reps <- 0
    for (method in methods) {
      tbls <- res_list[[paste0(method, "_tables")]]
      if (!is.null(tbls)) {
        max_reps <- max(max_reps, length(tbls))
      }
    }
    
    if (max_reps == 0) next
    
    # Track convergence for each method separately
    method_convergence <- list()
    for (method in methods) {
      method_convergence[[method]] <- rep(FALSE, max_reps)  # Initialize all as non-converged
    }
    
    # Check each method's convergence independently
    for (method in methods) {
      tbls <- res_list[[paste0(method, "_tables")]]
      if (is.null(tbls)) {
        # If this method doesn't exist, all remain FALSE
        next
      }
      
      for (rep in seq_len(max_reps)) {
        if (rep > length(tbls) || is.null(tbls[[rep]])) {
          next  # Already FALSE
        }
        
        # Extract parameters for this replication
        extr <- extract_eta3_parameters(tbls[[rep]], method)
        if (is.null(extr)) {
          next  # Already FALSE
        }
        
        # Check if all required parameters are present and complete
        converged <- TRUE
        for (p in parameters_of_interest) {
          if (p %in% names(extr$Estimates)) {
            # Check for NA, NaN, or Inf in any of the statistics
            if (is.na(extr$Estimates[p]) || is.nan(extr$Estimates[p]) || is.infinite(extr$Estimates[p]) ||
                is.na(extr$`Standard Errors`[p]) || is.nan(extr$`Standard Errors`[p]) || is.infinite(extr$`Standard Errors`[p]) ||
                is.na(extr$`P-values`[p]) || is.nan(extr$`P-values`[p]) || is.infinite(extr$`P-values`[p]) ||
                is.na(extr$CI_lower[p]) || is.nan(extr$CI_lower[p]) || is.infinite(extr$CI_lower[p]) ||
                is.na(extr$CI_upper[p]) || is.nan(extr$CI_upper[p]) || is.infinite(extr$CI_upper[p])) {
              converged <- FALSE
              break
            }
          } else {
            # Required parameter is missing
            converged <- FALSE
            break
          }
        }
        method_convergence[[method]][rep] <- converged
      }
    }
    
    # Store convergence details for this condition
    convergence_details[[paste0("Condition_", i)]] <- list(
      condition_info = list(
        Model = model_name,
        Distribution = distribution,
        SampleSize = sample_size,
        Reliability = reliability
      ),
      convergence_matrix = do.call(cbind, method_convergence),
      converged_iterations = lapply(method_convergence, which),  # Which iterations converged for each method
      convergence_counts = sapply(method_convergence, sum),
      convergence_rates = sapply(method_convergence, sum) / max_reps * 100
    )
    colnames(convergence_details[[paste0("Condition_", i)]]$convergence_matrix) <- methods
    
    # Calculate individual method convergence statistics
    method_convergence_counts <- list()
    method_convergence_rates <- list()
    method_outlier_counts <- list()  # NEW: Track outliers by method
    
    for (method in methods) {
      method_convergence_counts[[method]] <- sum(method_convergence[[method]])
      method_convergence_rates[[method]] <- sum(method_convergence[[method]]) / max_reps * 100
      method_outlier_counts[[method]] <- 0  # Initialize
    }
    
    # ============================================================
    # STEP 2: TRACK OUTLIERS FOR EACH METHOD INDEPENDENTLY (BEFORE COMPLETE CASE)
    # ============================================================
    
    if (remove_outliers) {
      for (method in methods) {
        tbls <- res_list[[paste0(method, "_tables")]]
        if (is.null(tbls)) next
        
        # Collect all estimates for this method (only from converged cases)
        all_estimates <- list()
        for (p in parameters_of_interest) {
          all_estimates[[p]] <- numeric()
        }
        
        for (rep in which(method_convergence[[method]])) {
          extr <- extract_eta3_parameters(tbls[[rep]], method)
          if (!is.null(extr)) {
            for (p in names(extr$Estimates)) {
              if (p %in% parameters_of_interest) {
                all_estimates[[p]] <- c(all_estimates[[p]], extr$Estimates[p])
              }
            }
          }
        }
        
        # Count outliers across all parameters for this method
        total_outliers <- 0
        for (p in parameters_of_interest) {
          if (length(all_estimates[[p]]) > 0) {
            q1 <- stats::quantile(all_estimates[[p]], 0.25, na.rm = TRUE)
            q3 <- stats::quantile(all_estimates[[p]], 0.75, na.rm = TRUE)
            iqr <- q3 - q1
            lb <- q1 - outlier_threshold * iqr
            ub <- q3 + outlier_threshold * iqr
            outliers <- sum(all_estimates[[p]] < lb | all_estimates[[p]] > ub, na.rm = TRUE)
            total_outliers <- total_outliers + outliers
          }
        }
        method_outlier_counts[[method]] <- total_outliers
      }
    }
    
    # ============================================================
    # STEP 3: IDENTIFY VALID REPLICATIONS ACROSS ALL METHODS
    # ============================================================
    
    # A replication is valid only if ALL methods converged
    valid_reps <- rep(TRUE, max_reps)
    for (method in methods) {
      valid_reps <- valid_reps & method_convergence[[method]]
    }
    
    # Get indices of valid replications
    valid_rep_indices <- which(valid_reps)
    n_total <- max_reps
    n_valid_complete_case <- length(valid_rep_indices)
    complete_case_convergence_rate <- n_valid_complete_case / n_total * 100
    
    # Add complete case info to convergence details
    convergence_details[[paste0("Condition_", i)]]$complete_case_iterations <- valid_rep_indices
    convergence_details[[paste0("Condition_", i)]]$complete_case_count <- n_valid_complete_case
    convergence_details[[paste0("Condition_", i)]]$complete_case_rate <- complete_case_convergence_rate
    
    if (n_valid_complete_case < min_reps) {
      message(paste("Condition", i, ": Only", n_valid_complete_case, 
                    "valid replications across all methods. Skipping."))
      next
    }
    
    # ============================================================
    # STEP 4: PROCESS EACH METHOD USING ONLY VALID REPLICATIONS
    # ============================================================
    
    for (method in methods) {
      tbls <- res_list[[paste0(method, "_tables")]]
      if (is.null(tbls)) next
      
      # Get convergence stats for this specific method
      n_converged_this_method <- method_convergence_counts[[method]]
      convergence_rate_this_method <- method_convergence_rates[[method]]
      n_outliers_this_method <- method_outlier_counts[[method]]  # NEW
      
      # accumulators by parameter - now only for valid reps
      params <- parameters_of_interest
      ests <- setNames(vector("list", length(params)), params)
      ses  <- setNames(vector("list", length(params)), params)
      pvs  <- setNames(vector("list", length(params)), params)
      los  <- setNames(vector("list", length(params)), params)
      his  <- setNames(vector("list", length(params)), params)
      
      # gather ONLY from valid replications
      for (rep in valid_rep_indices) {
        tab <- tbls[[rep]]
        if (is.null(tab)) next  # This shouldn't happen given our validation
        extr <- extract_eta3_parameters(tab, method)
        if (is.null(extr)) next  # This shouldn't happen given our validation
        
        have <- intersect(names(extr$Estimates), params)
        if (length(have) == 0) next
        for (p in have) {
          ests[[p]] <- c(ests[[p]], unname(extr$Estimates[p]))
          ses [[p]] <- c(ses [[p]], unname(extr$`Standard Errors`[p]))
          pvs [[p]] <- c(pvs [[p]], unname(extr$`P-values`[p]))
          los [[p]] <- c(los [[p]], unname(extr$CI_lower[p]))
          his [[p]] <- c(his [[p]], unname(extr$CI_upper[p]))
        }
      }
      
      # compute summaries per parameter
      for (p_name in params) {
        df <- tibble::tibble(
          est = unlist(ests[[p_name]]),
          se  = unlist(ses [[p_name]]),
          p_val = unlist(pvs [[p_name]]),
          lower_bound = unlist(los [[p_name]]),
          upper_bound = unlist(his [[p_name]])
        )
        if (nrow(df) == 0) next
        
        tv <- true_values[param_index[p_name]]
        
        # All data should already be complete cases now
        dfv <- df
        
        # ============================================================
        # CALCULATE MEDIAN-BASED METRICS BEFORE OUTLIER REMOVAL
        # ============================================================
        median_est <- stats::median(dfv$est)
        bias_median <- median_est - tv
        mad_est <- stats::mad(dfv$est, constant = 1)
        rmse_median <- sqrt(bias_median^2 + mad_est^2)
        
        if (tv != 0) {
          rel_bias_median <- bias_median / tv
          rel_bias_median_pct <- rel_bias_median * 100
        } else {
          rel_bias_median <- NA_real_
          rel_bias_median_pct <- NA_real_
        }
        
        # ============================================================
        # NOW REMOVE OUTLIERS FOR MEAN-BASED METRICS
        # ============================================================
        n_out <- 0
        if (remove_outliers && nrow(dfv) > 0) {
          q1 <- stats::quantile(dfv$est, 0.25, na.rm = TRUE)
          q3 <- stats::quantile(dfv$est, 0.75, na.rm = TRUE)
          iqr <- q3 - q1
          lb <- q1 - outlier_threshold * iqr
          ub <- q3 + outlier_threshold * iqr
          keep <- dfv$est >= lb & dfv$est <= ub
          n_out <- sum(!keep, na.rm = TRUE)
          dfv_clean <- dfv[keep, , drop = FALSE]  # cleaned dataset
        } else {
          dfv_clean <- dfv  # no outlier removal
        }
        
        # check if we still have enough data after outlier removal
        if (nrow(dfv_clean) < min_reps) next
        
        # add true parameter column for simhelpers functions
        dfv_clean$true_param <- tv
        
        # ============================================================
        # CALCULATE ALL MEAN-BASED METRICS USING SIMHELPERS ON CLEANED DATA
        # ============================================================
        
        # ABSOLUTE METRICS (bias, variance, MSE, RMSE) without winsorization 
        abs_metrics <- calc_absolute(
          data = dfv_clean,
          estimates = est, 
          true_param = true_param,
          criteria = c("bias", "variance", "stddev", "mse", "rmse"),
          winz = Inf  # No winsorization, we already removed outliers
        )
        
        # RELATIVE METRICS (only if true value is non-zero)
        if (tv != 0) {
          rel_metrics <- calc_relative(
            data = dfv_clean,
            estimates = est,
            true_param = true_param,
            criteria = c("relative bias", "relative mse", "relative rmse"),
            winz = Inf  # No winsorization
          )
          
          # simhelpers returns E(T)/θ (ratio)
          rel_bias_mean <- rel_metrics$rel_bias - 1
          rel_bias_mean_pct <- rel_bias_mean * 100       # convert to percentage
          rel_bias_mcse <- rel_metrics$rel_bias_mcse     # MCSE for the ratio
          
          rel_mse <- rel_metrics$rel_mse
          rel_rmse <- rel_metrics$rel_rmse
          rel_mse_mcse <- rel_metrics$rel_mse_mcse
          rel_rmse_mcse <- rel_metrics$rel_rmse_mcse
        } else {
          rel_bias_mean <- NA_real_
          rel_bias_mean_pct <- NA_real_
          rel_mse <- NA_real_
          rel_rmse <- NA_real_
          rel_bias_mcse <- NA_real_
          rel_mse_mcse <- NA_real_
          rel_rmse_mcse <- NA_real_
        }
        
        # COVERAGE AND CI WIDTH
        cov_metrics <- calc_coverage(
          data = dfv_clean,
          lower_bound = lower_bound, 
          upper_bound = upper_bound, 
          true_param = true_param,
          criteria = c("coverage", "width"),
          winz = Inf  # No winsorization
        )
        
        # REJECTION RATES (Type I Error / Power)
        rej_metrics <- calc_rejection(
          data = dfv_clean,
          p_values = p_val,
          alpha = alpha
        )
        
        # convert rejection rate to percentage but keep MCSE as proportion
        rejection_rate <- rej_metrics$rej_rate * 100
        rej_mcse <- rej_metrics$rej_rate_mcse  # Keep as proportion
        
        # determine Type I Error vs Power
        if (tv == 0) {
          type_i <- rejection_rate
          power <- NA_real_
          typei_mcse <- rej_mcse  # as proportion
          power_mcse <- NA_real_
        } else {
          type_i <- NA_real_
          power <- rejection_rate
          typei_mcse <- NA_real_
          power_mcse <- rej_mcse  # as proportion
        }
        
        # ============================================================
        # ADDITIONAL METRICS
        # ============================================================
        
        # Mean estimate (on cleaned data)
        mean_est <- mean(dfv_clean$est)
        
        # Standard error metrics (on cleaned data)
        mean_se <- mean(dfv_clean$se)
        se_sd_ratio <- mean_se / abs_metrics$stddev
        
        # ============================================================
        # COMPILE RESULTS
        # ============================================================
        
        results_summary <- dplyr::bind_rows(
          results_summary,
          tibble::tibble(
            Condition = i,
            Method = toupper(method),
            Model = model_name,
            Distribution = distribution,
            SampleSize = sample_size,
            Reliability = reliability,
            Parameter = p_name,
            TrueValue = tv,
            
            # Mean-based metrics from simhelpers (on cleaned data)
            MeanEstimate = mean_est,
            Bias_Mean = abs_metrics$bias,
            RelativeBias_Mean = rel_bias_mean,
            PercentRelativeBias_Mean = rel_bias_mean_pct,
            
            # Median-based metrics (calculated BEFORE outlier removal)
            MedianEstimate = median_est,
            Bias_Median = bias_median,
            RelativeBias_Median = rel_bias_median,
            PercentRelativeBias_Median = rel_bias_median_pct,
            MAD = mad_est,
            
            # Variability and accuracy metrics from simhelpers (on cleaned data)
            Variance = abs_metrics$var,
            SD = abs_metrics$stddev,
            MSE_Mean = abs_metrics$mse,
            RMSE_Mean = abs_metrics$rmse,
            RMSE_Median = rmse_median,  # Based on pre-outlier-removal median
            
            # Relative metrics from simhelpers (on cleaned data)
            Relative_MSE = rel_mse,
            Relative_RMSE = rel_rmse,
            
            # Standard error metrics (on cleaned data)
            MeanSE = mean_se,
            SE_SD_Ratio = se_sd_ratio,
            
            # Coverage and CI metrics from simhelpers (on cleaned data)
            CoverageRate = cov_metrics$coverage * 100,
            CI_Width = cov_metrics$width,
            
            # Testing metrics (on cleaned data)
            RejectionRate = rejection_rate,
            TypeI_Error = type_i,
            Power = power,
            
            # Monte Carlo standard errors (all kept as proportions/raw units)
            Bias_Mean_MCSE = abs_metrics$bias_mcse,
            RelativeBias_MCSE = rel_bias_mcse,
            Variance_MCSE = abs_metrics$var_mcse,
            SD_MCSE = abs_metrics$stddev_mcse,
            MSE_Mean_MCSE = abs_metrics$mse_mcse,
            RMSE_Mean_MCSE = abs_metrics$rmse_mcse,
            Relative_MSE_MCSE = rel_mse_mcse,
            Relative_RMSE_MCSE = rel_rmse_mcse,
            CoverageRate_MCSE = cov_metrics$coverage_mcse,  # Proportion
            CI_Width_MCSE = cov_metrics$width_mcse,
            RejectionRate_MCSE = rej_mcse,  # Proportion
            TypeI_Error_MCSE = typei_mcse,  # Proportion
            Power_MCSE = power_mcse,  # Proportion
            
            # SAMPLE SIZE TRACKING
            N_Total = n_total,
            N_Converged_This_Method = n_converged_this_method,  # How many converged for THIS method
            Convergence_Rate_This_Method = convergence_rate_this_method,  # % converged for THIS method
            N_Used_After_Convergence = n_valid_complete_case,  # What's actually used after complete-case deletion
            Complete_Case_Convergence_Rate = complete_case_convergence_rate,  # % converged for ALL methods
            N_Outliers_Removed = n_out,  # Outliers removed from this method/parameter
            Percent_Outliers_Removed = round(n_out / n_valid_complete_case * 100, 2),  # % of complete cases that were outliers
            N_Final_After_Outliers = nrow(dfv_clean),  # Final N after convergence AND outlier removal
            
            # TOTAL EXCLUSION SUMMARY
            N_Total_Excluded = n_total - nrow(dfv_clean),
            Percent_Total_Excluded = round((n_total - nrow(dfv_clean)) / n_total * 100, 2)
          )
        )
      } # end per-parameter
    } # end per-method
  } # end per-condition
  
  # Return both results and convergence details if requested
  if (return_convergence_details) {
    return(list(
      results = results_summary,
      convergence_details = convergence_details
    ))
  } else {
    return(results_summary)
  }
}

# Run the function with convergence details
results_with_mcse <- CalculateBiasAndCoverage(
  all_results,
  parameters_of_interest = c("eta1","eta2","eta1:eta2","eta1:eta1","eta2:eta2"),
  remove_outliers = TRUE,
  outlier_threshold = 3,
  alpha = 0.05,
  min_reps = 10,
  return_convergence_details = FALSE  
)

```

```{r tables, echo=FALSE, results='asis', message=FALSE, eval=FALSE}

# ---- Landscape APA tables | Method-first | ± MCSE | Rej. = Type I if true=0 else Power ----
# Chunk tip: use results='asis'

library(dplyr)
library(tidyr)
library(stringr)
library(glue)
library(kableExtra)
library(tools)

# ---------- helpers ----------
fmt_num <- function(x, digits = 3) ifelse(is.na(x), "", formatC(x, digits = digits, format = "f"))
fmt_pm  <- function(value, mcse, digits_value = 3, digits_mcse = 3, scale_mcse = 1) {
  ifelse(is.na(value), "", paste0(fmt_num(value, digits_value), " ± ", fmt_num(mcse * scale_mcse, digits_mcse)))
}
cap_first <- function(x) tools::toTitleCase(tolower(as.character(x)))

METHOD_ORDER <- c("SAM","LMS","QML","DBLCENT")
PARAM_ORDER  <- c("eta1","eta2","eta1:eta2","eta1:eta1","eta2:eta2")

# ---------- table builder (Method first) ----------
build_condition_table_landscape <- function(df, N, Rel, Dist, model_type, latex_font_size = 9) {

  dfc <- df %>%
    filter(
      SampleSize == N,
      Reliability == Rel,
      tolower(Distribution) == tolower(Dist),
      Model == model_type
    ) %>%
    mutate(
      Method    = factor(toupper(Method), levels = METHOD_ORDER),
      Parameter = factor(Parameter, levels = PARAM_ORDER)
    ) %>%
    arrange(Method, Parameter)

  if (nrow(dfc) == 0) return(NULL)

  # Rejection logic: Type I when true = 0; Power otherwise
  rej_value <- ifelse(dfc$TrueValue == 0, dfc$TypeI_Error,      dfc$Power)
  rej_mcse  <- ifelse(dfc$TrueValue == 0, dfc$TypeI_Error_MCSE, dfc$Power_MCSE)

  # Use columns that exist in results:
  # - Convergence_Rate_This_Method           (percent for this method alone)
  # - Complete_Case_Convergence_Rate         (percent when ALL methods converge)
  # - N_Used_After_Convergence               (complete-case N before outlier removal)
  # - N_Outliers_Removed                     (per-parameter outliers removed)
  # - N_Final_After_Outliers                 (final N after convergence + outliers)
  conv_rate_method   <- dfc$Convergence_Rate_This_Method
  conv_rate_complete <- dfc$Complete_Case_Convergence_Rate
  n_used_complete    <- dfc$N_Used_After_Convergence
  n_final            <- dfc$N_Final_After_Outliers

  tbl <- dfc %>%
    transmute(
      Method, Parameter,
      `True`                      = fmt_num(TrueValue, 3),
      `Mean`                      = fmt_num(MeanEstimate, 3),

      `Bias ± MCSE`               = fmt_pm(Bias_Mean, Bias_Mean_MCSE, 3, 3, 1),
      `% Rel. Bias ± MCSE`        = ifelse(TrueValue == 0, "",
                                           fmt_pm(PercentRelativeBias_Mean, RelativeBias_MCSE * 100, 1, 1, 1)),

      `Median`                    = fmt_num(MedianEstimate, 3),
      `Bias (median)`             = fmt_num(Bias_Median, 3),
      `MAD`                       = fmt_num(MAD, 4),

      `Variance ± MCSE`           = fmt_pm(Variance, Variance_MCSE, 4, 4, 1),
      `SD ± MCSE`                 = fmt_pm(SD, SD_MCSE, 4, 4, 1),
      `MSE ± MCSE`                = fmt_pm(MSE_Mean, MSE_Mean_MCSE, 4, 4, 1),
      `RMSE ± MCSE`               = fmt_pm(RMSE_Mean, RMSE_Mean_MCSE, 4, 4, 1),
      `RMSE (median)`             = fmt_num(RMSE_Median, 4),
      `Rel. MSE ± MCSE`           = fmt_pm(Relative_MSE, Relative_MSE_MCSE, 4, 4, 1),
      `Rel. RMSE ± MCSE`          = fmt_pm(Relative_RMSE, Relative_RMSE_MCSE, 4, 4, 1),

      `Mean SE`                   = fmt_num(MeanSE, 4),
      `SE/SD`                     = fmt_num(SE_SD_Ratio, 3),

      `Coverage (%) ± MCSE`       = fmt_pm(CoverageRate, CoverageRate_MCSE, 1, 1, 100),
      `CI width ± MCSE`           = fmt_pm(CI_Width, CI_Width_MCSE, 4, 4, 1),
      `Rej. (%) ± MCSE`           = fmt_pm(rej_value, rej_mcse, 1, 1, 100),

      # Sample size tracking (now aligned with available columns)
      `Conv. Rate (method) %`     = fmt_num(conv_rate_method, 1),
      `Conv. Rate (complete) %`   = fmt_num(conv_rate_complete, 1),
      `Outliers`                  = N_Outliers_Removed,
      `N Used (post-conv)`        = n_used_complete,
      `N Used (final)`            = n_final
    )

  caption <- glue(
    "N = {N}, Reliability = {Rel}, Distribution = {cap_first(Dist)}, Model = {model_type}."
  )

  if (knitr::is_latex_output()) {
    kb <- kbl(
      tbl,
      booktabs   = TRUE,
      align      = c("l","l", rep("r", ncol(tbl) - 2)),
      col.names  = names(tbl),
      caption    = caption
    )
    kb <- kable_classic(kb, full_width = FALSE, html_font = "Times New Roman")
    kb <- kable_styling(kb, latex_options = c("hold_position","scale_down"), font_size = latex_font_size)
    kb <- collapse_rows(kb, columns = 1, valign = "top")
    kb <- add_header_above(kb, c(" " = 2, "Metrics (MCSE shown as ±)" = ncol(tbl) - 6, "Sample Sizes" = 4))
    kb <- footnote(
      kb,
      general = paste0(
        "Conv. Rate (method) = % of replications converged for this method alone; ",
        "Conv. Rate (complete) = % where all methods converged (complete-case). ",
        "Outliers = # removed; N Used (post-conv) = complete-case N before outliers; ",
        "N Used (final) = after convergence + outlier removal. ",
        "Rej. is Type I error when true=0, Power otherwise. ",
        "Coverage/Type I/Power are percentages; MCSEs are percentage points. ",
        "Cells blank where relative measures are undefined (true value = 0)."
      ),
      threeparttable = TRUE
    )
    return(kableExtra::landscape(kb))
  } else {
    kb <- kbl(
      tbl,
      booktabs   = TRUE,
      align      = c("l","l", rep("r", ncol(tbl) - 2)),
      col.names  = names(tbl),
      caption    = caption
    )
    kb <- kable_classic(kb, full_width = FALSE, html_font = "Times New Roman")
    kb <- kable_styling(kb, font_size = 14)
    kb <- collapse_rows(kb, columns = 1, valign = "top")
    kb <- add_header_above(kb, c(" " = 2, "Metrics (MCSE shown as ±)" = ncol(tbl) - 6, "Sample Sizes" = 4))
    kb <- footnote(
      kb,
      general = paste0(
        "Conv. Rate (method) = % of replications converged for this method alone; ",
        "Conv. Rate (complete) = % where all methods converged (complete-case). ",
        "Outliers = # removed; N Used (post-conv) = complete-case N before outliers; ",
        "N Used (final) = after convergence + outlier removal. ",
        "Rej. is Type I error when true=0, Power otherwise. ",
        "Coverage/Type I/Power are percentages; MCSEs are percentage points. ",
        "Cells blank where relative measures are undefined (true value = 0)."
      ),
      threeparttable = TRUE
    )
    return(scroll_box(kb, width = "100%", height = "520px"))
  }
}


```

```{r convergence-outliers-summary, echo=FALSE, results='asis'}
# Comprehensive convergence and outlier summary table
create_summary_table <- function(results_with_mcse,
                                core_params = c("eta1","eta2","eta1:eta2")) {
  
  # Filter to core parameters and get worst-case scenario across parameters
  summary_data <- results_with_mcse |>
    dplyr::filter(Parameter %in% core_params) |>
    dplyr::group_by(Condition, Method, Model, Distribution, SampleSize, Reliability) |>
    dplyr::summarise(
      # Take values from first parameter (they should be same across params for convergence columns)
      N_Total = first(N_Total),
      N_Converged_This_Method = first(N_Converged_This_Method),
      Convergence_Rate_This_Method = first(Convergence_Rate_This_Method),
      N_Used_After_Convergence = first(N_Used_After_Convergence),
      
      # For outliers, take the maximum across parameters (worst case)
      N_Outliers_Removed = max(N_Outliers_Removed, na.rm = TRUE),
      Percent_Outliers_Removed = max(Percent_Outliers_Removed, na.rm = TRUE),
      
      # For final N, take the minimum across parameters (most conservative)
      N_Final_After_Outliers = min(N_Final_After_Outliers, na.rm = TRUE),
      
      .groups = "drop"
    ) |>
    dplyr::arrange(Condition, Method)
  
  # Comprehensive table with reorganized structure
  comprehensive_table <- summary_data |>
    dplyr::select(
      Condition,
      Method,
      Model,
      Distribution,
      `Sample Size` = SampleSize,
      Reliability,
      # Convergence section - all convergence-related metrics together
      `N Total` = N_Total,
      `N Converged` = N_Converged_This_Method,
      `Conv. Rate (%)` = Convergence_Rate_This_Method,
      `N Converged Total` = N_Used_After_Convergence,  # This is the complete cases within converged
      # Outliers section - remains as is
      `N Outliers` = N_Outliers_Removed,
      `Outlier Rate (%)` = Percent_Outliers_Removed,
      `N Final` = N_Final_After_Outliers
    ) |>
    dplyr::mutate(
      `Conv. Rate (%)` = round(`Conv. Rate (%)`, 1),
      `Outlier Rate (%)` = round(`Outlier Rate (%)`, 1),
      `Final Rate (%)` = round(100 * `N Final` / `N Total`, 1)
    )
  
  comprehensive_table
}

# Create summary table
summary_table <- create_summary_table(results_with_mcse)

# Helper function to get rates from the summary table
get_rate <- function(metric, method, model, dist, n, rel) {
  # Map the metric names to new column names
  metric_map <- c(
    "ConvergenceRate" = "Conv. Rate (%)",
    "OutlierRate" = "Outlier Rate (%)",
    "FinalRate" = "Final Rate (%)"
  )
  
  # Get mapped metric name, or use as-is if not in map
  col_name <- ifelse(metric %in% names(metric_map), metric_map[metric], metric)
  
  result <- summary_table |>
    dplyr::filter(
      Method == method,
      Model == model,
      Distribution == dist,
      `Sample Size` == n,
      Reliability == rel
    ) |>
    dplyr::pull(!!sym(col_name))
  
  result
}

```

### Convergence Rate and Outliers

We refer the reader to Table 2 for a detailed summary for convergence and outliers. For most approaches there were a few convergence issues. One notable exception was for the DBLCENT under the condition with moderate sample size, low reliability, and uniformly distributed latent predictors. In that case, convergence rates were `r round(get_rate("ConvergenceRate", "DBLCENT", "Full", "uniform", 400, 0.4), 2)`% with the full population model and `r round(get_rate("ConvergenceRate", "DBLCENT", "Linear", "uniform", 400, 0.4), 2)`% with the linear population model. For the SAM, convergence rate was `r round(get_rate("ConvergenceRate", "SAM", "Linear", "uniform", 400, 0.4), 2)`% across all conditions. The remaining approaches, LMS and QML, also showed decent convergence rates, with the lowest value being respectively `r round(get_rate("ConvergenceRate", "LMS", "Linear", "uniform", 400, 0.4), 2)`% and `r round(get_rate("ConvergenceRate", "QML", "Linear", "uniform", 400, 0.4), 2)`% for both cases under the same scenario in which DBLCENT, but now only specifically with the linear population model. 

With respect to outliers, a somewhat similar trend as with convergence rates was observed. The DBLCENT had the highest outlier rate (`r round(get_rate("OutlierRate", "DBLCENT", "Linear", "uniform", 400, 0.4), 2)`%) for the condition with moderate sample size, low reliability, and uniformly distributed latent predictors. Both the LMS and QML also had their highest outlier rates in the same condition, with `r round(get_rate("OutlierRate", "LMS", "Linear", "uniform", 400, 0.4), 2)`% and `r round(get_rate("OutlierRate", "QML", "Linear", "uniform", 400, 0.4), 2)`% respectively. For the SAM, however, the highest outlier rate was observed in the condition with moderate sample size, low reliability, and nonnormally distributed latent predictors (`r round(get_rate("OutlierRate", "SAM", "Linear", "nonnormal", 400, 0.4), 2)`%).

```{r apa-plots, echo=FALSE}
# ---- Shared setup: helpers, themes, palettes ----
library(dplyr)
library(ggplot2)
library(stringr)

# Orderings & labels
METHOD_ORDER <- c("SAM","LMS","QML","DBLCENT")
DIST_LABS    <- c(normal="Normal", nonnormal="Nonnormal", uniform="Uniform")
PARAM_ORDER  <- c("eta1:eta2","eta1:eta1","eta2:eta2")
PARAM_LABS   <- c("eta1:eta2"="beta[3]",
                  "eta1:eta1"="beta[4]",
                  "eta2:eta2"="beta[5]")
# Grayscale palettes
GREYS_METHOD <- c(SAM="grey20", LMS="grey45", QML="grey65", DBLCENT="grey85")
GREYS_PARAM  <- c("eta1:eta2"="grey20", "eta1:eta1"="grey55", "eta2:eta2"="grey85")

# APA-ish theme
theme_apa_bw <- function(base_size = 11) {
  theme_bw(base_size = base_size) +
    theme(
      panel.grid.minor = element_blank(),
      strip.text = element_text(face = "bold"),
      legend.position = "bottom",
      legend.title = element_blank()
    )
}

# Convenience: build a Condition factor "N=..., Rel=..."
make_condition <- function(N, Rel) {
  factor(paste0("N=", N, ", Rel=", Rel),
         levels = c("N=400, Rel=0.4","N=400, Rel=0.6","N=400, Rel=0.8",
                    "N=1000, Rel=0.4","N=1000, Rel=0.6","N=1000, Rel=0.8"))
}

# ---- Data prep for nonlinear parameters only ----
prep_nonlinear <- function(df, model = c("Full","Linear")) {
  model <- match.arg(model)
  df %>%
    filter(Parameter %in% PARAM_ORDER, Model == model) %>%
    mutate(
      Method       = factor(Method, levels = METHOD_ORDER),
      Distribution = factor(Distribution, levels = names(DIST_LABS), labels = DIST_LABS),
      Parameter    = factor(Parameter, levels = PARAM_ORDER, 
                           labels = c("beta[3]", "beta[4]", "beta[5]")),  # Add labels here
      Reliability  = factor(Reliability),
      SampleSize   = factor(SampleSize),
      Condition    = make_condition(SampleSize, Reliability)
    )
}

```

```{r bias, echo=FALSE}
shapes <- c(SAM=16, LMS=17, QML=15, DBLCENT=18)
ltys   <- c(SAM="solid", LMS="dashed", QML="dotdash", DBLCENT="twodash")

# ---------- Bias for all conditions ----------
dat_bias <- bind_rows(
  prep_nonlinear(results_with_mcse, model = "Linear") %>% mutate(Model = "Linear"),
  prep_nonlinear(results_with_mcse, model = "Full")   %>% mutate(Model = "Full")
) %>%
  mutate(Model = factor(Model, levels = c("Linear", "Full"))) %>%
  transmute(Distribution, Parameter, SampleSize, Reliability, Method, Model,
            y = Bias_Mean, yerr = Bias_Mean_MCSE)

get_absolute_bias <- function(method, dist, param, n, rel, model = c("Full","Linear")) {
  model <- match.arg(model)
  dat_bias %>%
    filter(Method == method,
           Distribution == dist,
           Parameter == param,
           SampleSize == n,
           Reliability == rel,
           Model == model) %>%
    select(y)
}

# ---------- Filter to Full model & N = 400 ----------
dat_bias_400_full <- dat_bias %>%
  dplyr::filter(Model == "Full", SampleSize == "400") %>%
  droplevels()

# ---------- Plot: Bias ----------
p_bias_400_full <- ggplot(
  dat_bias_400_full,
  aes(x = Reliability, y = y, shape = Method, linetype = Method, group = Method)
) +
  geom_pointrange(aes(ymin = y - yerr, ymax = y + yerr),
                  position = position_dodge(width = .6), color = "black") +
  geom_line(position = position_dodge(width = .6), color = "black") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  scale_shape_manual(values = shapes) +
  scale_linetype_manual(values = ltys) +
  # All distributions in rows; one column (since Full & N=400 only)
  facet_grid(Distribution + Parameter ~ ., labeller = labeller(Parameter = label_parsed)) +
  labs(x = "Reliability", y = "Bias") +
  # >>> Your requested y-axis ticks <<<
  scale_y_continuous(
    breaks = seq(-0.20, 0.20, by = 0.05),
    #limits = c(-0.15, 0.15)   # remove if you don't want clipping
  ) +
  theme_apa_bw()

#p_bias_400_full

# ---------- Relative Bias for all conditions----------
dat_bias_relative <- bind_rows(
  prep_nonlinear(results_with_mcse, model = "Linear") %>% mutate(Model = "Linear"),
  prep_nonlinear(results_with_mcse, model = "Full")   %>% mutate(Model = "Full")
) %>%
  mutate(Model = factor(Model, levels = c("Linear", "Full"))) %>%
  transmute(Distribution, Parameter, SampleSize, Reliability, Method, Model,
            y = RelativeBias_Mean, yerr = RelativeBias_MCSE) 

get_relative_bias <- function(method, dist, param, n, rel, model = c("Full","Linear")) {
  model <- match.arg(model)
  dat_bias_relative %>%
    filter(Method == method,
           Distribution == dist,
           Parameter == param,
           SampleSize == n,
           Reliability == rel,
           Model == model) %>%
    select(y)
}

# ---------- Filter to Full model & N = 400 ----------
dat_biasrel_400_full <- dat_bias_relative %>%
  dplyr::filter(Model == "Full", SampleSize == "400") %>%
  droplevels()

# ---------- Plot: Relative Bias ----------
# If y is already in percent units (e.g., -10..10), use breaks -10..10 by 5:
p_biasrel_400_full <- ggplot(
  dat_biasrel_400_full,
  aes(x = Reliability, y = y, shape = Method, linetype = Method, group = Method)
) +
  geom_pointrange(aes(ymin = y - yerr, ymax = y + yerr),
                  position = position_dodge(width = .6), color = "black") +
  geom_line(position = position_dodge(width = .6), color = "black") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  scale_shape_manual(values = shapes) +
  scale_linetype_manual(values = ltys) +
  facet_grid(Distribution + Parameter ~ ., labeller = labeller(Parameter = label_parsed)) +
  labs(x = "Reliability", y = "Relative Bias") +
  scale_y_continuous(
    breaks = seq(-2, 2, by = 1),
    limits = c(-2, 2)   # remove if you don't want clipping
  ) +
  theme_apa_bw()

p_biasrel_400_full
```

```{r rmse, echo=FALSE}
## ----- RMSE (no scaling) -----
dat_rmse <- bind_rows(
  prep_nonlinear(results_with_mcse, model = "Linear") %>% mutate(Model = "Linear"),
  prep_nonlinear(results_with_mcse, model = "Full")   %>% mutate(Model = "Full")
) %>%
  mutate(Model = factor(Model, levels = c("Linear", "Full"))) %>%
  transmute(Distribution, Parameter, SampleSize, Reliability, Method, Model,
            y    = RMSE_Mean,
            yerr = RMSE_Mean_MCSE)   # adjust to RMSE_MCSE if that's your column

get_rmse <- function(method, dist, param, n, rel, model = c("Full","Linear")) {
  model <- match.arg(model)
  dat_rmse %>%
    filter(Method == method,
           Distribution == dist,
           Parameter == param,
           SampleSize == n,
           Reliability == rel,
           Model == model) %>%
    select(y)
}

# ---- Filter to Full model & N = 400 ----
dat_rmse_400_full <- dat_rmse %>%
  dplyr::filter(Model == "Full", SampleSize == "400") %>%
  droplevels()

p_rmse_400_full <- ggplot(
  dat_rmse_400_full,
  aes(x = Reliability, y = y, shape = Method, linetype = Method, group = Method)
) +
  geom_pointrange(aes(ymin = y - yerr, ymax = y + yerr),
                  position = position_dodge(width = .6), color = "black") +
  geom_line(position = position_dodge(width = .6), color = "black") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  scale_shape_manual(values = shapes) +
  scale_linetype_manual(values = ltys) +
  facet_grid(Distribution + Parameter ~ ., labeller = labeller(Parameter = label_parsed)) +
  labs(x = "Reliability", y = "RMSE", title = "") +
  theme_apa_bw()

#p_rmse_400_full

## ----- Relative RMSE (no scaling; stays on 0–1 scale) -----
dat_rmse_relative <- bind_rows(
  prep_nonlinear(results_with_mcse, model = "Linear") %>% mutate(Model = "Linear"),
  prep_nonlinear(results_with_mcse, model = "Full")   %>% mutate(Model = "Full")
) %>%
  mutate(Model = factor(Model, levels = c("Linear", "Full"))) %>%
  transmute(Distribution, Parameter, SampleSize, Reliability, Method, Model,
            y    = Relative_RMSE,
            yerr = Relative_RMSE_MCSE)

get_relative_rmse <- function(method, dist, param, n, rel, model = c("Full","Linear")) {
  model <- match.arg(model)
  dat_rmse_relative %>%
    filter(Method == method,
           Distribution == dist,
           Parameter == param,
           SampleSize == n,
           Reliability == rel,
           Model == model) %>%
    select(y)
}

# ---- Filter to Full model & N = 400 ----
dat_rrmse_400_full <- dat_rmse_relative %>%
  dplyr::filter(Model == "Full", SampleSize == "400") %>%
  droplevels()

# ---- Plot: Relative RMSE (0–1 scale) ----
p_rrmse_400_full <- ggplot(
  dat_rrmse_400_full,
  aes(x = Reliability, y = y, shape = Method, linetype = Method, group = Method)
) +
  geom_pointrange(aes(ymin = pmax(y - yerr, 0), ymax = pmin(y + yerr, 1)),
                  position = position_dodge(width = .6), color = "black") +
  geom_line(position = position_dodge(width = .6), color = "black") +
  scale_shape_manual(values = shapes) +
  scale_linetype_manual(values = ltys) +
  facet_grid(Distribution + Parameter ~ .,
             labeller = labeller(Parameter = label_parsed)) +
  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, by = 1)) +
  labs(x = "Reliability", y = "Relative RMSE", title = "") +
  theme_apa_bw()

#p_rrmse_400_full

```

### Bias When Nonlinear Effects Were Present 

Figure 1 presents a visualization of the reported relative bias values across the distributional conditions given a fixed moderate sample size. The results for a high sample size are qualitatively the same. Note that, given the relatively small magnitude of the true effects, relative bias metrics can appear disproportionately large; therefore, we report in the text both absolute and relative bias alongside RMSE and relative RMSE metrics. Figure 2 shows the relative RMSE for the same set of factors.

Under normal distributions, most methods performed well across reliability levels. LSAM showed borderline bias for the interaction effect only at low reliability ($\beta_3$: relative bias = `r round(get_relative_bias("SAM", "Normal", "beta[3]", 400, 0.4, "Full"),3)` (absolute bias = `r round(get_absolute_bias("SAM", "Normal", "beta[3]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("SAM", "Normal", "beta[3]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("SAM", "Normal", "beta[3]", 400, 0.4, "Full"),3)`)), which resolved at medium reliability (relative bias = `r round(get_relative_bias("SAM", "Normal", "beta[3]", 400, 0.6, "Full"),3)` (absolute bias = `r round(get_absolute_bias("SAM", "Normal", "beta[3]", 400, 0.6, "Full"),3)`, RMSE = `r round(get_rmse("SAM", "Normal", "beta[3]", 400, 0.6, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("SAM", "Normal", "beta[3]", 400, 0.6, "Full"),3)`)). LMS and QML remained unbiased across all reliability levels. In contrast, UPI exhibited persistent negative bias for interactions regardless of reliability (relative bias = `r round(get_relative_bias("DBLCENT", "Normal", "beta[3]", 400, 0.4, "Full"),3)` (absolute bias = `r round(get_absolute_bias("DBLCENT", "Normal", "beta[3]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("DBLCENT", "Normal", "beta[3]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("DBLCENT", "Normal", "beta[3]", 400, 0.4, "Full"),3)`) to `r round(get_relative_bias("DBLCENT", "Normal", "beta[3]", 400, 0.6, "Full"),3)` (absolute bias = `r round(get_absolute_bias("DBLCENT", "Normal", "beta[3]", 400, 0.6, "Full"),3)`, RMSE = `r round(get_rmse("DBLCENT", "Normal", "beta[3]", 400, 0.6, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("DBLCENT", "Normal", "beta[3]", 400, 0.6, "Full"),3)`)).

Under nonnormal distributions, substantial method differences emerged. LSAM maintained relatively robust performance despite some bias at low reliability ($\beta_3$: relative bias = `r round(get_relative_bias("SAM", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)` (absolute bias = `r round(get_absolute_bias("SAM", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("SAM", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("SAM", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)`)). LMS and QML exhibited severe bias for interaction effects (relative bias = `r round(get_relative_bias("LMS", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)` (absolute bias = `r round(get_absolute_bias("LMS", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("LMS", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("LMS", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)`) and `r round(get_relative_bias("QML", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)` (absolute bias = `r round(get_absolute_bias("QML", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("QML", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("QML", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)`), respectively, at low reliability), with LMS bias persisting at high reliability (`r round(get_relative_bias("LMS", "Nonnormal", "beta[3]", 400, 0.8, "Full"),3)` (absolute bias = `r round(get_absolute_bias("LMS", "Nonnormal", "beta[3]", 400, 0.8, "Full"),3)`, RMSE = `r round(get_rmse("LMS", "Nonnormal", "beta[3]", 400, 0.8, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("LMS", "Nonnormal", "beta[3]", 400, 0.8, "Full"),3)`)). UPI performed well for both interaction (relative bias = `r round(get_relative_bias("DBLCENT", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)` (absolute bias = `r round(get_absolute_bias("DBLCENT", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("DBLCENT", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("DBLCENT", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)`)) and quadratic effects ($\beta_4$: relative bias = `r round(get_relative_bias("DBLCENT", "Nonnormal", "beta[4]", 400, 0.4, "Full"),3)` (absolute bias = `r round(get_absolute_bias("DBLCENT", "Nonnormal", "beta[4]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("DBLCENT", "Nonnormal", "beta[4]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("DBLCENT", "Nonnormal", "beta[4]", 400, 0.4, "Full"),3)`)).

Under uniform distributions, performance patterns shifted. LSAM remained largely unbiased for interactions (relative bias = `r round(get_relative_bias("SAM", "Uniform", "beta[3]", 400, 0.4, "Full"),3)` (absolute bias = `r round(get_absolute_bias("SAM", "Uniform", "beta[3]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("SAM", "Uniform", "beta[3]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("SAM", "Uniform", "beta[3]", 400, 0.4, "Full"),3)`)) but showed bias for quadratic effects at low reliability ($\beta_4$: relative bias = `r round(get_relative_bias("SAM", "Uniform", "beta[4]", 400, 0.4, "Full"),3)` (absolute bias = `r round(get_absolute_bias("SAM", "Uniform", "beta[4]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("SAM", "Uniform", "beta[4]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("SAM", "Uniform", "beta[4]", 400, 0.4, "Full"),3)`)). LMS and QML achieved unbiased interaction estimation but maintained positive bias for quadratic effects across all reliability levels ($\beta_4$: relative bias = `r round(get_relative_bias("LMS", "Uniform", "beta[4]", 400, 0.4, "Full"),3)` (absolute bias = `r round(get_absolute_bias("LMS", "Uniform", "beta[4]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("LMS", "Uniform", "beta[4]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("LMS", "Uniform", "beta[4]", 400, 0.4, "Full"),3)`) and `r round(get_relative_bias("QML", "Uniform", "beta[4]", 400, 0.4, "Full"),3)` (absolute bias = `r round(get_absolute_bias("QML", "Uniform", "beta[4]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("QML", "Uniform", "beta[4]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("QML", "Uniform", "beta[4]", 400, 0.4, "Full"),3)`) at low reliability). UPI displayed the opposite pattern, with negative bias for interactions ($\beta_3$: relative bias = `r round(get_relative_bias("DBLCENT", "Uniform", "beta[3]", 400, 0.4, "Full"),3)` (absolute bias = `r round(get_absolute_bias("DBLCENT", "Uniform", "beta[3]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("DBLCENT", "Uniform", "beta[3]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("DBLCENT", "Uniform", "beta[3]", 400, 0.4, "Full"),3)`)) but improved quadratic estimation at higher reliability ($\beta_4$: `r round(get_relative_bias("DBLCENT", "Uniform", "beta[4]", 400, 0.8, "Full"),2)` (absolute bias = `r round(get_absolute_bias("DBLCENT", "Uniform", "beta[4]", 400, 0.8, "Full"),3)`, RMSE = `r round(get_rmse("DBLCENT", "Uniform", "beta[4]", 400, 0.8, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("DBLCENT", "Uniform", "beta[4]", 400, 0.8, "Full"),3)`)).

### Bias When Nonlinear Effects Were Not Present

The bias results are somewhat similar when the nonlinear effects were present (full model) and not present (linear model), but in overall terms with decreased magnitude. There are two main differences worth nothing. Under normally distributed latent variables, the bias in this case is smaller than in the case of the full model for all approaches. Moreover, for the uniform condition, the UPI, LMS and QML showed little bias in contrast to before. Hence, the approaches are more homogeneous.

```{r plot-bias, echo=FALSE, fig.cap = "Absolute bias.", fig.align='center', fig.height=12, fig.width=9}
#(p_bias_400_full)
(p_biasrel_400_full)
```

```{r plot-rmse, echo=FALSE, fig.cap = "Root Mean Squared Error.", fig.align='center', fig.height=12, fig.width=9}
#(p_rmse_400_full)
(p_rrmse_400_full)
```

```{r ratio, echo=FALSE}
library(dplyr)
library(ggplot2)

# data for both models
dat_sesd2 <- bind_rows(
  prep_nonlinear(results_with_mcse, model = "Linear") %>% mutate(Model = "Linear"),
  prep_nonlinear(results_with_mcse, model = "Full") %>% mutate(Model = "Full")
) %>%
  mutate(Model = factor(Model, levels = c("Linear", "Full"))) %>%
  transmute(Distribution, Parameter, SampleSize, Reliability, Method, Model,
            ratio = SE_SD_Ratio)

# Update get_ratio function to include model parameter
get_ratio <- function(method, dist, param, n, rel, model = c("Full", "Linear")) {
  model <- match.arg(model)
  dat_sesd2 %>%
    filter(Method == method,
           Distribution == dist,
           Parameter == param,
           SampleSize == n,
           Reliability == rel,
           Model == model) %>%
    pull(ratio)
}

# ----- Filter: Full model, N = 400 & 1000, Nonnormal only -----
dat_sesd2_full_nonnorm <- dat_sesd2 %>%
  dplyr::filter(
    Model == "Full",
    SampleSize %in% c("400", "1000"),
    Distribution == "Nonnormal"
  ) %>%
  droplevels()

# (reuse your shapes / ltys)
shapes <- c(SAM=16, LMS=17, QML=15, DBLCENT=18)
ltys   <- c(SAM="solid", LMS="dashed", QML="dotdash", DBLCENT="twodash")

# ----- Plot -----
p_slope_full_nonnorm <- ggplot(
  dat_sesd2_full_nonnorm,
  aes(x = Reliability, y = ratio, group = Method, shape = Method, linetype = Method)
) +
  geom_hline(yintercept = 1, linetype = "dashed") +
  # clamp to [0.80, 1.60] so everything stays in-frame
  geom_line(aes(y = pmax(pmin(ratio, 1.6), 0.80)),
            color = "black", position = position_dodge(width = 0.0)) +
  geom_point(aes(y = pmax(pmin(ratio, 1.6), 0.80)),
             color = "black", size = 2, position = position_dodge(width = 0.0)) +
  # Labels for values above 1.6
  geom_text(
    data = dat_sesd2_full_nonnorm %>%
      dplyr::filter(ratio > 1.6) %>%
      dplyr::group_by(Distribution, Parameter, SampleSize, Reliability) %>%
      dplyr::arrange(dplyr::desc(ratio)) %>%
      dplyr::mutate(label_y = 1.59 - (dplyr::row_number() - 1) * 0.08),
    aes(label = sprintf("%s: %.2f", Method, ratio), y = label_y),
    size = 1.8, hjust = 0, vjust = 1
  ) +
  # Labels for values below 0.80 (match the clamp)
  geom_text(
    data = dat_sesd2_full_nonnorm %>%
      dplyr::filter(ratio < 0.80) %>%
      dplyr::group_by(Distribution, Parameter, SampleSize, Reliability) %>%
      dplyr::arrange(ratio) %>%
      dplyr::mutate(label_y = 0.81 + (dplyr::row_number() - 1) * 0.08),
    aes(label = sprintf("%s: %.2f", Method, ratio), y = label_y),
    size = 1.8, hjust = 0, vjust = 0
  ) +
  scale_shape_manual(values = shapes) +
  scale_linetype_manual(values = ltys) +
  # Put Distribution back so the "Nonnormal" strip shows
  facet_grid(Distribution + Parameter ~ SampleSize,
             labeller = labeller(Parameter = label_parsed)) +
  # Show ticks at 0.8, 1.0, 1.2, 1.4, 1.6 and fix range
  scale_y_continuous(breaks = seq(0.8, 1.6, by = 0.2), limits = c(0.8, 1.6)) +
  labs(x = "Reliability", y = "SE / SD", title = "") +
  theme_apa_bw()

#p_slope_full_nonnorm
```

### Efficiency and Accuracy of Standard Errors when Nonlinear Effects were present

Figure 3 shows the computed SE/SD ratios under the full models for the nonnormal condition across sample sizes. Note that for some approaches, under specific conditions, the exact values are shown due to large discrepancies between approaches. Following @brandt_etall_2014, we interpret a ratio below 0.90 (underestimated) and above 1.10 (overestimated) as biased. 

In case of the normal condition, only the UPI showed an overestimation in case of low reliability. While for the uniform condition, both the LSAM and UPI showed overestimated SEs in the case of low reliability. The nonnormal distributional condition revealed the most pronounced differences between approaches, with sample size showing strong influence on the efficiency for the LSAM and UPI. Specific to the latter case, at moderate sample size and low reliability, LSAM yielded an overestimation of `r round(get_ratio("SAM", "Nonnormal", "beta[3]", 400, 0.4, "Full"),2)` for $\beta_3$. Similar qualitative results were obtained for the quadratic effects. Increasing to a large sample size substantially improved the performance for the LSAM, meaning the ratios were not biased even under low reliability. The LMS maintained stable performance with a ratio of `r round(get_ratio("LMS", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)` for $\beta_3$, while QML exhibited underestimation at `r round(get_ratio("QML", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)` the same effect. Here also similar qualitative results were observed for the quadratic effects. With an increasing sample size, however, results were not improved for the QML. Moreover, the UPI demonstrated a high amount of overestimation under the condition of low reliability for all nonlinear effects. Similar overestimation also was obtained for all nonlinear effects under moderate reliability, with the exception of $\beta_5$. As in the LSAM, a higher sample size yielded better results, but in this case the UPI still showed overestimation under low reliability.

### Efficiency and Accuracy of Standard Errors When Nonlinear Effects Were Not Present

The linear model specification generally showed improved accuracy compared to the full model, particularly for UPI under nonnormal conditions. However, the relative performance ordering remained consistent, with LMS and QML providing the most efficient standard error estimates, followed by LSAM, and UPI.

```{r coverage, echo=FALSE}
dat_cov <- bind_rows(
  prep_nonlinear(results_with_mcse, model = "Linear") %>% mutate(Model = "Linear"),
  prep_nonlinear(results_with_mcse, model = "Full")   %>% mutate(Model = "Full")
) %>%
  mutate(Model = factor(Model, levels = c("Linear", "Full"))) %>%
  transmute(Distribution, Parameter, SampleSize, Reliability, Method, Model,
            y = CoverageRate, yerr = 100*CoverageRate_MCSE)

get_coverage <- function(method, dist, param, n, rel, model = c("Full", "Linear")) {
  model <- match.arg(model)
  dat_cov %>%
    filter(Method == method,
           Distribution == dist,
           Parameter == param,
           SampleSize == n,
           Reliability == rel,
           Model == model) %>%
    pull(y)
}

# ----- Filter: Full model, N ∈ {400, 1000}, all distributions -----
dat_cov_full_400_1000 <- dat_cov %>%
  dplyr::filter(Model == "Full", SampleSize %in% c("400", "1000")) %>%
  droplevels()

# (reuse your shapes / ltys defined earlier)

# ----- Plot -----
p_cov_full_400_1000 <- ggplot(
  dat_cov_full_400_1000,
  aes(x = Reliability, y = y, shape = Method, linetype = Method, group = Method)
) +
  annotate("rect", xmin = -Inf, xmax = Inf, ymin = 93, ymax = 97,
           fill = "grey93", alpha = .9) +
  geom_pointrange(
    aes(ymin = pmax(y - yerr, 80), ymax = pmin(y + yerr, 100)),
    position = position_dodge(width = .6), color = "black"
  ) +
  geom_line(aes(y = pmax(y, 80)),
            position = position_dodge(width = .6), color = "black") +
  # Labels for values below 80% (use filtered data)
  geom_text(
    data = dat_cov_full_400_1000 %>%
      dplyr::filter(y < 80) %>%
      dplyr::group_by(Distribution, Parameter, SampleSize, Reliability) %>%
      dplyr::arrange(Method) %>%
      dplyr::mutate(label_y = 81 + (dplyr::row_number() - 1) * 2.5),
    aes(label = sprintf("%s: %.0f%%", Method, y), y = label_y),
    size = 1.5, hjust = 0, vjust = 0
  ) +
  geom_hline(yintercept = 95, linetype = "dotted") +
  scale_shape_manual(values = shapes) +
  scale_linetype_manual(values = ltys) +
  # Keep Distribution strips (all distributions), rows = Distribution + Parameter, cols = SampleSize
  facet_grid(Distribution + Parameter ~ SampleSize,
             labeller = labeller(Parameter = label_parsed)) +
  coord_cartesian(ylim = c(80, 100)) +
  labs(x = "Reliability", y = "Coverage (%)", title = "") +
  theme_apa_bw()

#p_cov_full_400_1000
```

### Coverage for When Nonlinear Effects Were Present

Figure 4 contains the visualization of the results reported here. Note that here as well for some approaches, under specific conditions, the exact values are shown. Coverage rates varied substantially across distributional conditions and estimation methods. 

Under normal distributions with moderate sample size and medium reliability, all approaches achieved near-nominal 95% coverage for interaction and quadratic effects. At low reliability, LSAM showed overcoverage (`r round(get_coverage("SAM", "Normal", "beta[3]", 400, 0.4, "Full"),1)`% for $\beta_3$) as well as the UPI (`r round(get_coverage("DBLCENT", "Normal", "beta[3]", 400, 0.4, "Full"),1)`%), while LMS and QML maintained adequate coverage (`r round(get_coverage("LMS", "Normal", "beta[3]", 400, 0.4, "Full"),1)`% and `r round(get_coverage("QML", "Normal", "beta[3]", 400, 0.4, "Full"),1)`%, respectively).

Nonnormal conditions revealed critical results for the distribution analytic approaches. At moderate sample size and low reliability, LMS coverage dropped to `r round(get_coverage("LMS", "Nonnormal", "beta[3]", 400, 0.4, "Full"),1)`% for $\beta_3$ and below 80% for quadratic parameters ($\beta_4$ = `r round(get_coverage("LMS", "Nonnormal", "beta[4]", 400, 0.4, "Full"),1)`%, $\beta_5$ = `r round(get_coverage("LMS", "Nonnormal", "beta[5]", 400, 0.4, "Full"),1)`%). QML demonstrated more severe undercoverage, particularly for quadratic effects ($\beta_4$ = `r round(get_coverage("QML", "Nonnormal", "beta[4]", 400, 0.4, "Full"),1)`%, $\beta_5$ = `r round(get_coverage("QML", "Nonnormal", "beta[5]", 400, 0.4, "Full"),1)`%). SAM maintained robust coverage (`r round(get_coverage("SAM", "Nonnormal", "beta[3]", 400, 0.4, "Full"),1)`%) across all nonnormal conditions. Increasing sample size provided minimal improvement for the LMS and QML.

Under uniform distributions, LSAM exhibited overcoverage (`r round(get_coverage("SAM", "Uniform", "beta[3]", 400, 0.4, "Full"),1)`-`r round(get_coverage("SAM", "Uniform", "beta[5]", 400, 0.4, "Full"),1)`%) across parameters at low reliability, while LMS and QML showed severe undercoverage for quadratic effects (LMS: `r round(get_coverage("LMS", "Uniform", "beta[4]", 400, 0.4, "Full"),1)`-`r round(get_coverage("LMS", "Uniform", "beta[5]", 400, 0.4, "Full"),1)`%; QML: `r round(get_coverage("QML", "Uniform", "beta[4]", 400, 0.4, "Full"),1)`-`r round(get_coverage("QML", "Uniform", "beta[5]", 400, 0.4, "Full"),1)`%). Coverage improved substantially at higher reliability levels, with most methods approaching nominal rates, though quadratic parameters remained problematic for distribution-analytic approaches (LMS: `r round(get_coverage("LMS", "Uniform", "beta[4]", 400, 0.8, "Full"),1)`-`r round(get_coverage("LMS", "Uniform", "beta[5]", 400, 0.8, "Full"),1)`%; QML: `r round(get_coverage("QML", "Uniform", "beta[4]", 400, 0.8, "Full"),1)`-`r round(get_coverage("QML", "Uniform", "beta[5]", 400, 0.8, "Full"),1)`%).

### Coverage When Nonlinear Effects Were Not Present

The linear model specification showed differential effects on coverage performance. Under nonnormal conditions, the linear model often provided better coverage than the full model for UPI, though distribution analytic methods continued to show poor performance. 

```{r plot-ratio, echo=FALSE, fig.cap="SE/SD Ratio.", fig.align='center', fig.height=12, fig.width=8}
(p_slope_full_nonnorm)
```

```{r plot-coverage, echo=FALSE, fig.cap="Coverage.", fig.align='center', fig.height=12, fig.width=8}
(p_cov_full_400_1000)
```

```{r type, echo=FALSE, fig.align='center', fig.height=12, fig.width=9}

# --- TYPE I (grayscale bars, thin dotted line @ 5%, no x-axis labels) ---
dat_t1 <- prep_nonlinear(results_with_mcse, model = "Linear") %>%
  transmute(Distribution, Parameter, Condition, Method,
            y = TypeI_Error)

get_type <- function(method, dist, param, cond) {
  dat_t1 %>%
    filter(Method == method,
           Distribution == dist,
           Parameter == param,
           Condition == cond) %>%
    select(y)
}

# --- TYPE I (grayscale bars, thin dotted line @ 5%), N = 1000 across all reliabilities ---

dat_t1_1000 <- prep_nonlinear(results_with_mcse, model = "Linear") %>%
  dplyr::filter(SampleSize == "1000") %>%   # keep N = 1000 only
  dplyr::transmute(
    Distribution, Parameter, Condition, Method,
    y = TypeI_Error
  ) %>%
  droplevels()  # drop N=400 conditions from facet levels

ymax_t1_1000 <- max(dat_t1_1000$y, na.rm = TRUE) * 1.15  # 15% headroom for labels

p_t1_1000 <- ggplot(dat_t1_1000, aes(x = Method, y = y, fill = Method)) +
  annotate("rect", xmin = -Inf, xmax = Inf, ymin = 3, ymax = 7,
           fill = "grey92", alpha = .9) +
  geom_col(position = position_dodge(width = 0.9), width = 0.75, color = "black") +
  geom_text(aes(label = sprintf("%.1f", y)), vjust = -0.4, size = 3) +
  geom_hline(yintercept = 5, linetype = "dotted", linewidth = 0.3) +
  facet_grid(Distribution + Parameter ~ Condition,
             labeller = labeller(Parameter = label_parsed)) +
  scale_fill_manual(values = GREYS_METHOD) +
  coord_cartesian(ylim = c(0, ymax_t1_1000)) +
  labs(x = NULL, y = "Type I error (%)", title = "") +
  theme_apa_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.title = element_blank())

#p_t1_1000



```

```{r power, echo=FALSE, fig.align='center', fig.height=12, fig.width=9}
# --- POWER (grayscale bars, thin dotted line @ 80%, no x-axis labels) ---
dat_pow <- prep_nonlinear(results_with_mcse, model = "Full") %>%
  transmute(Distribution, Parameter, Condition, Method,
            y = Power)

get_power <- function(method, dist, param, cond) {
  dat_pow %>%
    filter(Method == method,
           Distribution == dist,
           Parameter == param,
           Condition == cond) %>%
    select(y)
}
```

### Type I Error Control

Figure 5 illustrates the type I error rates across approaches under the case of a large sample size. The results under a moderate sample are qualitatively the same.

Type I error rates at large sample size revealed critical differences across methods and distributions. Under normal conditions with low reliability, UPI showed excessive conservativeness (`r round(get_type("DBLCENT", "Normal", "beta[3]", "N=1000, Rel=0.4"),3)`%-`r round(get_type("DBLCENT", "Normal", "beta[5]", "N=1000, Rel=0.4"),3)`%), while the LSAM showed moderately conservative results (`r round(get_type("SAM", "Normal", "beta[3]", "N=1000, Rel=0.4"),2)`%-`r round(get_type("SAM", "Normal", "beta[5]", "N=1000, Rel=0.4"),2)`%). LMS and QML maintained rates closer to the nominal 5% level.

Nonnormal conditions exposed severe Type I error inflation for the distribution analytic methods. At low reliability, LMS showed inflation for quadratic parameters (`r round(get_type("LMS", "Nonnormal", "beta[4]", "N=1000, Rel=0.4"),1)`% for $\beta_4$, `r round(get_type("LMS", "Nonnormal", "beta[5]", "N=1000, Rel=0.4"),1)`% for $\beta_5$), with QML demonstrating similar results (`r round(get_type("QML", "Nonnormal", "beta[4]", "N=1000, Rel=0.4"),1)`%, `r round(get_type("QML", "Nonnormal", "beta[5]", "N=1000, Rel=0.4"),1)`%). This inflation persisted even at high reliability for LMS (`r round(get_type("LMS", "Nonnormal", "beta[4]", "N=1000, Rel=0.8"),1)`%, `r round(get_type("LMS", "Nonnormal", "beta[5]", "N=1000, Rel=0.8"),2)`%). LSAM maintained robust control across all nonnormal conditions (`r round(get_type("SAM", "Nonnormal", "beta[3]", "N=1000, Rel=0.4"),2)`% for $\beta_3$). Under uniform distributions, Type I error patterns resembled normal conditions, with the exception that the SAM and UPI obtained nominal rates.

### Statistical Power

Figure 6 illustrates power across approaches and conditions. Note that one should look at valid power [...]

Power analysis at large sample size (n = 1,000) demonstrated substantial method differences across distributional conditions. Under normal distributions with low reliability, power for the interaction term ($\beta_3$) reached `r round(get_power("SAM", "Normal", "beta[3]", "N=1000, Rel=0.4"),1)`% (SAM), `r round(get_power("LMS", "Normal", "beta[3]", "N=1000, Rel=0.4"),1)`% (LMS), and `r round(get_power("QML", "Normal", "beta[3]", "N=1000, Rel=0.4"),1)`% (QML), while DBLCENT remained severely underpowered at `r round(get_power("DBLCENT", "Normal", "beta[3]", "N=1000, Rel=0.4"),1)`%. At medium reliability, power exceeded 60% for SAM (`r round(get_power("SAM", "Normal", "beta[3]", "N=1000, Rel=0.6"),1)`%), LMS (`r round(get_power("LMS", "Normal", "beta[3]", "N=1000, Rel=0.6"),1)`%), and QML (`r round(get_power("QML", "Normal", "beta[3]", "N=1000, Rel=0.6"),1)`%). High reliability conditions yielded power above 80% for all approaches.

Nonnormal conditions revealed inflated power for quadratic terms in distribution-analytic methods. At low reliability, LMS showed extreme power inflation for quadratic parameters (`r round(get_power("LMS", "Nonnormal", "beta[4]", "N=1000, Rel=0.4"),1)`% for $\beta_4$, `r round(get_power("LMS", "Nonnormal", "beta[5]", "N=1000, Rel=0.4"),1)`% for $\beta_5$), with QML demonstrating similar patterns (`r round(get_power("QML", "Nonnormal", "beta[4]", "N=1000, Rel=0.4"),1)`%, `r round(get_power("QML", "Nonnormal", "beta[5]", "N=1000, Rel=0.4"),1)`%). These inflated values reflected the corresponding Type I error inflation rather than genuine power gains.

Under uniform distributions at high reliability, power for interaction effects reached acceptable levels: `r round(get_power("SAM", "Uniform", "beta[3]", "N=1000, Rel=0.8"),1)`% (SAM), `r round(get_power("LMS", "Uniform", "beta[3]", "N=1000, Rel=0.8"),1)`% (LMS), and `r round(get_power("DBLCENT", "Uniform", "beta[3]", "N=1000, Rel=0.8"),1)`% (DBLCENT). However, quadratic term detection remained challenging, with power ranging from `r round(get_power("DBLCENT", "Uniform", "beta[4]", "N=1000, Rel=0.8"),1)`% to `r round(get_power("SAM", "Uniform", "beta[4]", "N=1000, Rel=0.8"),1)`% for $\beta_4$.

```{r plot-type, echo=FALSE, fig.cap="Type I error rate.", fig.align='center', fig.height=12, fig.width=9}
(p_t1_1000)
```

## Brief discussion of simulation study 1

The results from simulation study 1 are aligned to certain extent with previous simulation studies. With respect to bias for the QML and LMS, the same pattern of positive bias and negative bias for the nonlinear effects was observed as in @brandt_etall_2014 for the nonnormal condition, while the UPI showed unbiased results. For the LSAM, we obtained unbiased results similarly to the 2SMM performance in @brandt_etall_2014.

Moreover, as in @brandt_etall_2020 similar findings were also observed for extremely large biased results in cases of small reliability, despite not manipulating structural misspecifications here. We also observed similar patterns as in @lonati_etall_2024 for the interaction term. Importantly, however, is the contrast between the interaction and quadratic terms, which was not investigated in their case. For instance, the interaction term showing unbiased results under non-normal conditions, but biased results for the quadratic terms under the same condition. The SE/SD ratio results also follow the results reported in @brandt_etall_2014. Last, [comment about the insane power for lms and qml under non-normal: check with yves; power, type I error].

Thus, the SAM approach shows good results overall that are comparable and even outperform the more widely used approaches. However, caution is needed for cases where low reliability may be the case.

## Result for simulation study 2

[...]
