```{r}
#| label: packages
#| echo: false
#| warning: false
#| message: false

source("../Simulations/Plots.R")
source("../Simulations/Study_1/Results/Results(1).R")
source("../Simulations/Study_2/Results/Results(2).R")
```

# Results for Simulation Studies 

The results reported are a subset of the findings which focused mainly on the cases when the nonlinear effects were present. The same interpretation holds for both results. 

## Results for Simulation 1

```{r}
#| label: results-first-sim-study
#| echo: false
#| warning: false
#| message: false

results_study_1 <- readRDS("../Simulations/Study_1/Results/results_study_1.rds")
```

```{r}
#| label: convergence-outliers-first-sim-study
#| echo: false
#| output: false

get_convergence_outlier_rate_study_1 <- function(method, dist, n, rel, model = "Full", 
                                                  rate_type = c("convergence", "outlier", "final")) {
  rate_type <- match.arg(rate_type)

  col_map <- c(
    "convergence" = "Convergence_Rate_This_Method",
    "outlier" = "Outlier_Rate_This_Method", 
    "final" = "Percent_Total_Excluded"
  )
  
  col_name <- col_map[rate_type]
  
  # since these rates are the same across parameters, we just pick one (e.g., eta1)
  result <- results_study_1 %>%
    filter(
      Method == toupper(method),
      Distribution == dist,
      SampleSize == n,
      Reliability == rel,
      Model == model,
      Parameter == "eta1"  # rates are identical across parameters
    ) %>%
    pull(!!sym(col_name))
  
  if(length(result) > 0) result[1] else NA
}

# most outliers
#results_study_1 %>%
#  filter(Parameter == "eta1") %>%
#  group_by(Method) %>%
#  arrange(desc(Outlier_Rate_This_Method)) %>%
#  slice_head(n = 2) %>%
#  select(Method, Model, Distribution, SampleSize, Reliability, Outlier_Rate_This_Method)

# worst convergence rates (lowest values) for each method
#results_study_1 %>%
#  filter(Parameter == "eta1") %>%
#  group_by(Method) %>%
#  arrange(Convergence_Rate_This_Method) %>%
#  slice_head(n = 2) %>%
#  select(Method, Model, Distribution, SampleSize, Reliability, Convergence_Rate_This_Method)
```

### Convergence Issues and Outliers  

Convergence problems were generally rare. The main exception was UPI, which showed reduced convergence under moderate sample size, low reliability, and uniform latent predictors. In this scenario, convergence rates were `r round(get_convergence_outlier_rate_study_1("UPI", "uniform", 400, 0.4, "Full", "convergence"), 2)`% with the full model and `r round(get_convergence_outlier_rate_study_1("UPI", "uniform", 400, 0.4, "Linear", "convergence"), 2)`% with the linear model. LMS and QML converged well in general, with the lowest rates in the same setting being `r round(get_convergence_outlier_rate_study_1("LMS", "uniform", 400, 0.4, "Full", "convergence"), 2)`% and `r round(get_convergence_outlier_rate_study_1("QML", "uniform", 400, 0.4, "Full", "convergence"), 2)`% (full model), and `r round(get_convergence_outlier_rate_study_1("LMS", "uniform", 400, 0.4, "Linear", "convergence"), 2)`% and `r round(get_convergence_outlier_rate_study_1("QML", "uniform", 400, 0.4, "Linear", "convergence"), 2)`% (linear model), respectively. LSAM consistently converged, with rates of `r round(get_convergence_outlier_rate_study_1("LSAM", "uniform", 400, 0.4, "Linear", "convergence"), 2)`% across all conditions.  

Outlier rates followed a comparable pattern. The most pronounced rates again occurred under moderate sample size, low reliability, and uniform latent predictors. UPI produced the highest outlier frequencies, reaching `r round(get_convergence_outlier_rate_study_1("UPI", "uniform", 400, 0.4, "Full", "outlier"), 2)`% with the full model and `r round(get_convergence_outlier_rate_study_1("UPI", "uniform", 400, 0.4, "Linear", "outlier"), 2)`% with the linear model. For the same condition, LSAM also yielded the most outliers (`r round(get_convergence_outlier_rate_study_1("LSAM", "uniform", 400, 0.4, "Linear", "outlier"), 2)`% with the linear model and `r round(get_convergence_outlier_rate_study_1("LSAM", "uniform", 400, 0.4, "Full", "outlier"), 2)`% with the full model). In contrast, LMS and QML generated virtually none, with their highest rates reaching only `r round(get_convergence_outlier_rate_study_1("LMS", "uniform", 400, 0.4, "Full", "outlier"), 2)`% and `r round(get_convergence_outlier_rate_study_1("QML", "uniform", 400, 0.4, "Full", "outlier"), 2)`% (both full model) in the same scenario as the other approaches. Detailed results for convergence and outliers are provided in Appendix C (see Table C1).

```{r}
#| label: plots-first-sim-study
#| echo: false

plot_study_1_data <- prepare_study1_data(results_study_1)

# RELATIVE BIAS 
study_1_relative_bias <- plot_study_1_data$bias_relative
dat_relative_bias_400_full_study_1 <- study_1_relative_bias %>%
   filter(Model == "Full", SampleSize == "400") %>%
   droplevels()

p_relative_bias_400_full_study_1 <- plot_bias(
   dat_relative_bias_400_full_study_1, 
   shapes = SHAPES_4, 
   ltys = LTYS_4,
   bias_type = "relative",  
   facet_formula = Distribution + Parameter ~ .,  
   y_breaks = seq(-1, 1.5, by = 0.5),
   y_limits = c(-1, 1.5)
)

# Relative RMSE 
study_1_relative_rmse <- plot_study_1_data$rmse_relative

dat_relative_rmse_400_full_study_1 <- study_1_relative_rmse %>%
  filter(Model == "Full", SampleSize == "400") %>%
  droplevels()

p_relative_rmse_400_full_study_1 <- plot_rmse(
  dat_relative_rmse_400_full_study_1, 
  shapes = SHAPES_4, 
  ltys = LTYS_4,
  facet_formula = Distribution + Parameter ~ ., 
  #y_breaks = seq(0, 0.30, by = 0.05),           
  #y_limits = c(0, 0.30)                        
)

# SE/SD RATIO (Right-skewed & Uniform, Full, N=400 & 1000)
study_1_sesd <- plot_study_1_data$sesd

dat_sesd_nonnorm_unif_study_1 <- study_1_sesd %>%
  filter(Model == "Full", 
         SampleSize %in% c("400", "1000"), 
         Distribution %in% c("Right-skewed", "Uniform")) %>%
  droplevels()

p_slope_nonnorm_unif_study_1 <- plot_sesd(
  dat_sesd_nonnorm_unif_study_1,
  shapes = SHAPES_4,
  ltys = LTYS_4,
  facet_formula = Distribution + Parameter ~ SampleSize
)

# COVERAGE (Full, N=400 & 1000, all distributions)
study_1_coverage <- plot_study_1_data$coverage

dat_cov_nonnorm_unif_study_1 <- study_1_coverage %>%
  filter(Model == "Full", 
         SampleSize %in% c("400", "1000"),
         Distribution %in% c("Right-skewed", "Uniform")) %>% 
  droplevels()

p_cov_nonnorm_unif_study_1 <- plot_coverage(
  dat_cov_nonnorm_unif_study_1, 
  shapes = SHAPES_4,
  ltys = LTYS_4,
  facet_formula = Distribution + Parameter ~ SampleSize
)

# TYPE I ERROR (Linear, N=1000 only) 
study_1_type1 <- plot_study_1_data$type1

dat_t1_1000_study_1 <- study_1_type1 %>%
  filter(grepl("N=1000", Condition)) %>%
  droplevels()

p_t1_1000_study_1 <- plot_type1(
  dat_t1_1000_study_1,  
  greys = GREYS_4,
  facet_formula = Distribution + Parameter ~ Condition
)
```

### Relative Bias and RMSE When Nonlinear Effects Were Present

Figures 2 and 3 present relative bias and RMSE across distributional conditions at a moderate sample size (N = 400). Following Brandt et al. (2014), values exceeding 0.10 (10%) were considered biased.

Under normal distributions, LSAM showed stable performance across reliability levels for all nonlinear effects. Bias emerged for the interaction term at low reliability for the other approaches, with LMS and QML also biased under medium reliability. At larger sample sizes, LSAM and UPI were unbiased even at low reliability, whereas LMS and QML continued to show bias under low and medium reliability. With right-skewed distributions, LSAM displayed bias for the interaction term only under low reliability, while UPI showed no bias for all nonlinear effects. In contrast, LMS and QML exhibited severe negative bias for interactions and positive bias for quadratic effects across reliability levels. At larger sample sizes, LSAM was unbiased across conditions, but LMS and QML remained biased. Under uniform distributions, LSAM was unbiased at all reliability levels. UPI showed bias for most nonlinear effects at low reliability, whereas LMS and QML produced unbiased interaction estimates but consistent negative bias for quadratic effects. These last patterns remained qualitatively unchanged at larger sample sizes (see Figure S2 in supplemental materials).

For relative RMSE, all methods performed similarly under normality, with minor differences at low reliability where LMS and QML showed the lowest values. Under right-skewed distributions, LSAM yielded the lowest RMSE, although differences diminished at high reliability. For uniform distributions, LMS and QML produced the lowest RMSE, but method performance converged as reliability increased.

### Efficiency and Accuracy of SEs When Nonlinear Effects Were Present

Figure 4 presents SE/SD ratios for right-skewed and uniform conditions across sample sizes. Following Brandt et al. (2014), ratios below 0.90 (underestimation) or above 1.10 (overestimation) indicate bias.

Under normality, LSAM displayed only a negligible overestimation (1.11) for the interaction term at low reliability and moderate sample sizes. In contrast, UPI produced substantial overestimation across all nonlinear effects under the same conditions (see Figure S5 in supplemental materials). For right-skewed distributions, LSAM showed some overestimation (1.12) at low reliability with moderate sample sizes, and slight underestimation for quadratic terms at high reliability. UPI consistently underestimated across reliability levels and sample sizes for all nonlinear effects. Under uniform distributions, LSAM and UPI overestimated SEs for all nonlinear effects at low reliability^[For LSAM, this overestimation arose from a small number of clear outliers in the SEs. Although these values were retained in the analysis, they are identified and displayed in supplemental materials (Figure X).], though this bias was not present with larger samples. UPI additionally showed a negligible underestimation at medium reliability and moderate sample sizes. LMS and QML remained stable across all conditions. 

### Coverage for When Nonlinear Effects Were Present

Figure 5 displays coverage results for right-skewed and uniform conditions across sample sizes, with exact values shown when they fall outside the plotted y-axis range. Coverage between 93% and 97% was considered acceptable. Previous literature simply considered above 90% as an acceptable performance [@cham_etall_2012; @ayturk_etall_2020].

LSAM slightly exceeded this range (98%) only at low reliability with moderate sample sizes, but not at larger samples, across all distributions. Under normality, all approaches otherwise performed within the acceptable range across reliability and sample sizes (see Figure S6 in supplemental materials). For right-skewed distributions, LMS and QML exhibited substantial under-coverage, with UPI also affected, though to a lesser extent. Larger sample sizes did not improve coverage for these methods, while higher reliability reduced—but did not eliminate—the bias. Under uniform distributions, LMS and QML showed under-coverage exclusively for the quadratic effects.

### Type I Error Rate

Figure 6 presents Type I error rates at large sample sizes across distributions, with 2.5–7.5% considered acceptable. Under normality, LSAM and all other approaches remained within the acceptable range, even at low reliability. For right-skewed distributions, LSAM and UPI also stayed within acceptable bounds, whereas LMS and QML showed severe inflation for quadratic effects across all reliability levels. Under uniform distributions, LSAM and UPI generally performed well, with values falling below the acceptable range only at low reliability. In contrast, LMS and QML yielded consistently well-controlled error rates. Results at moderate sample sizes were qualitatively similar, although under right-skewness LMS and QML showed somewhat less inflation, yet still exceeded acceptable levels at low and medium reliabilities (see Figure S7 in supplemental materials).

### Empirical Power

Given the inflated Type I error rates observed for some approaches, power results should be interpreted with caution [@morris_etall_2019]. At large sample size, LSAM reached power levels near or above 80% under medium and high reliability across all distributions for most nonlinear effects. The main exception was under the uniform distribution, where quadratic effects remained underpowered. The other approaches showed broadly similar patterns in the same conditions. Under right-skewness, however, LMS and QML diverged extremely with low power only for the interaction term under medium reliability (see Figure S8 in supplemental materials).  

### Absolute Bias, RMSE, SEs, and Coverage When Nonlinear Effects Were Absent

Bias patterns resembled those observed when nonlinear effects were present, though with reduced magnitude. A notable difference emerged under the uniform distribution: LMS and QML produced unbiased quadratic estimates but biased interaction estimates, which disappeared at high reliability. RMSE results showed no substantive differences beyond reduced magnitude. The accuracy of SEs was generally comparable, with one key exception: UPI demonstrated improved accuracy under normality at low reliability and moderate sample sizes, but performed worse under the uniform distribution at low reliability. Coverage improved somewhat when nonlinear effects were absent. Specifically, LMS and QML showed higher coverage under right-skewed distributions, though still falling below the desirable range for quadratic effects. Under the uniform distribution, however, coverage for quadratic effects improved substantially for both LMS and QML (see Figures S1, S3, S5, and S6 in supplemental materials).

## Summary of Simulation 1

With the exception of low reliability conditions, LSAM demonstrated adequate performance across all evaluated metrics. LSAM generally yielded unbiased estimates, whereas QML and LMS exhibited systematic bias: positive and negative bias for nonlinear effects under right-skewed distributions, and negative bias for quadratic effects under uniform distributions. UPI also produced largely unbiased results. For SEs, LMS and QML were the most efficient, although LSAM achieved comparable accuracy at medium and high reliability across all distributions, particularly with large sample sizes. Coverage rates remained relatively stable for LSAM but not for LMS, QML, or UPI. Type I error rates fell within the acceptable range for LSAM and UPI, except under uniform conditions with low reliability. By contrast, LMS and QML displayed marked inflation under right-skewed distributions. Finally, empirical power was generally highest for LMS and QML, though this finding must be interpreted cautiously given their inflated Type I error. When Type I error was controlled, all approaches achieved desirable power levels for most effects, with the exception of quadratic effects under the uniform distribution, which remained underpowered.

## Result for Simulation 2

```{r}
#| label: results-second-sim-study
#| echo: false
#| warning: false
#| message: false

results_study_2 <- readRDS("../Simulations/Study_2/Results/results_study_2.rds")
```

### Convergence Issues and Outliers

```{r}
#| label: convergence-outliers-second-sim-study
#| echo: false
#| output: false

get_convergence_outlier_rate_study_2 <- function(method, dist, n, rel, model = "Full",
                                                  equation = c("eta4", "eta5"),
                                                  rate_type = c("convergence", "outlier", "final")) {
  equation <- match.arg(equation)
  rate_type <- match.arg(rate_type)
  
  col_map <- c(
    "convergence" = "Convergence_Rate_This_Method",
    "outlier" = "Outlier_Rate_This_Method", 
    "final" = "Percent_Total_Excluded"
  )
  
  col_name <- col_map[rate_type]
  
  # needs representative parameter for each equation
  # for eta4: use "eta1" (first predictor)
  # for eta5: use "eta4" (first predictor)
  param_to_use <- ifelse(equation == "eta4", "eta1", "eta4")
  
  result <- results_study_2 %>%
    filter(
      Method == toupper(method),
      Distribution == dist,
      SampleSize == n,
      Reliability == rel,
      Model == model,
      Equation == equation,
      Parameter == param_to_use
    ) %>%
    pull(!!sym(col_name))
  
  if(length(result) > 0) result[1] else NA
}

# worst outlier rates across both equations
#results_study_2$results %>%
#  filter((Equation == "eta4" & Parameter == "eta1") | 
#         (Equation == "eta5" & Parameter == "eta4")) %>%
#  group_by(Method, Equation) %>%
#  arrange(desc(Outlier_Rate_This_Method)) %>%
#  slice_head(n = 2) %>%
#  select(Method, Equation, Model, Distribution, SampleSize, Reliability, Outlier_Rate_This_Method) %>%
#  arrange(Method, Equation, desc(Outlier_Rate_This_Method))

# Worst convergence rates for each method and equation
#results_study_2$results %>%
#  filter((Equation == "eta4" & Parameter == "eta1") | 
#         (Equation == "eta5" & Parameter == "eta4")) %>%
#  group_by(Method, Equation) %>%
#  arrange(Convergence_Rate_This_Method) %>%
#  slice_head(n = 2) %>%
#  select(Method, Equation, Model, Distribution, SampleSize, Reliability, Convergence_Rate_This_Method) %>%
#  arrange(Method, Equation, Convergence_Rate_This_Method)
```

Convergence problems were most severe for UPI, particularly with a moderate sample, low reliability, and uniform predictors. Rates fell to `r round(get_convergence_outlier_rate_study_2("UPI", "uniform", 400, 0.4, "Full", "eta4", "convergence"), 2)`% with the full model and linear model. QML converged more often under these conditions but still at suboptimal levels (`r round(get_convergence_outlier_rate_study_2("QML", "uniform", 400, 0.4, "Full", "eta4", "convergence"), 2)`% with the full model; `r round(get_convergence_outlier_rate_study_2("QML", "uniform", 400, 0.4, "Linear", "eta4", "convergence"), 2)`% with the linear model). LSAM converged `r round(get_convergence_outlier_rate_study_2("LSAM", "normal", 400, 0.4, "Full", "eta4", "convergence"), 2)`% under all conditions. For normal and right-skewed predictors, all approaches had a convergence rate above 98%, with a few exceptions.

Outlier rates also varied substantially across methods. UPI again performed worst under the condition of uniform predictors with moderate sample size and low reliability, reaching `r round(get_convergence_outlier_rate_study_2("UPI", "uniform", 400, 0.4, "Linear", "eta4", "outlier"), 2)`% with the linear model and `r round(get_convergence_outlier_rate_study_2("UPI", "uniform", 400, 0.4, "Full", "eta4", "outlier"), 2)`% with the full model. QML showed much lower outlier rates overall, with the highest occurring under right-skewed predictors (`r round(get_convergence_outlier_rate_study_2("QML", "nonnormal", 400, 0.4, "Linear", "eta4", "outlier"), 2)`% with the linear model), followed by uniform predictors (`r round(get_convergence_outlier_rate_study_2("QML", "uniform", 400, 0.4, "Full", "eta4", "outlier"), 2)`% with the full model). LSAM’s highest outlier rates also occurred outside normality, with uniform predictors in the full model (`r round(get_convergence_outlier_rate_study_2("LSAM", "uniform", 400, 0.4, "Full", "eta4", "outlier"), 2)`%) and right-skewed predictors in the linear model (`r round(get_convergence_outlier_rate_study_2("LSAM", "nonnormal", 400, 0.4, "Linear", "eta4", "outlier"), 2)`%) (see Table C2 in Appendix C for more information).  

```{r}
#| label: plots-second-sim-study
#| echo: false

study_2_normal_data <- prepare_study2_data(results_study_2, "normal")
study_2_nonnormal_data <- prepare_study2_data(results_study_2, "nonnormal")
study_2_uniform_data <- prepare_study2_data(results_study_2, "uniform")

# RELATIVE BIAS (full model, N=400, all Distributions) 
dat_relative_bias_400_full_all_study_2 <- bind_rows(
  study_2_normal_data$bias_relative %>%
    filter(Model == "Full", SampleSize == "400"),
  study_2_nonnormal_data$bias_relative %>%
    filter(Model == "Full", SampleSize == "400"),
  study_2_uniform_data$bias_relative %>%
    filter(Model == "Full", SampleSize == "400")
) %>%
  droplevels()

p_relative_bias_400_full_all_study_2 <- plot_bias(
  dat_relative_bias_400_full_all_study_2,
  shapes = SHAPES_3,
  ltys = LTYS_3,
  facet_formula = Parameter ~ Distribution,
  y_breaks = seq(-1, 1.5, by = 0.5),
  y_limits = c(-1, 1.5),
  bias_type = "relative"
)

# RELATIVE RMSE (full model, N=400, all Distributions) 
dat_relative_rmse_400_full_all_study_2 <- bind_rows(
  study_2_normal_data$rmse_relative %>%
    filter(Model == "Full", SampleSize == "400"),
  study_2_nonnormal_data$rmse_relative %>%
    filter(Model == "Full", SampleSize == "400"),
  study_2_uniform_data$rmse_relative %>%
    filter(Model == "Full", SampleSize == "400")
) %>%
  droplevels()

p_relative_rmse_400_full_all_study_2 <- plot_rmse(
    dat_relative_rmse_400_full_all_study_2,
    shapes = SHAPES_3,
    ltys = LTYS_3,
    facet_formula = Parameter ~ Distribution,
    y_breaks = seq(0, 5, by = 1),  
    y_limits = c(0, 5.2),              
)


# SE/SD RATIO (Full model, N=400, All Distributions) 
dat_sesd_400_full_all_study_2 <- bind_rows(
  study_2_normal_data$sesd %>%
    filter(Model == "Full", SampleSize == "400"),
  study_2_nonnormal_data$sesd %>%
    filter(Model == "Full", SampleSize == "400"),
  study_2_uniform_data$sesd %>%
    filter(Model == "Full", SampleSize == "400")
) %>%
  droplevels()

p_sesd_400_full_all_study_2 <- plot_sesd(
  dat_sesd_400_full_all_study_2,
  shapes = SHAPES_3,
  ltys = LTYS_3,
  facet_formula = Parameter ~ Distribution,
  title = ""
)

#  COVERAGE (Full model, N=400, All Distributions)
dat_coverage_400_full_all_study_2 <- bind_rows(
  study_2_normal_data$coverage %>%
    filter(Model == "Full", SampleSize == "400"),
  study_2_nonnormal_data$coverage %>%
    filter(Model == "Full", SampleSize == "400"),
  study_2_uniform_data$coverage %>%
    filter(Model == "Full", SampleSize == "400")
) %>%
  droplevels()

p_coverage_400_full_all_study_2 <- plot_coverage(
  dat_coverage_400_full_all_study_2,
  shapes = SHAPES_3,
  ltys = LTYS_3,
  facet_formula = Parameter ~ Distribution,
  title = ""
)

# TYPE I ERROR (Linear, N=1000, Nonnormal & Uniform)
dat_t1_1000_all_study_2 <- bind_rows(
  study_2_nonnormal_data$type1 %>%
    filter(grepl("N=1000", Condition)),
  study_2_uniform_data$type1 %>%
    filter(grepl("N=1000", Condition))
) %>%
  droplevels()

p_t1_1000_all_study_2 <- plot_type1(
  dat_t1_1000_all_study_2,
  greys = GREYS_3,
  facet_formula = Parameter ~ Distribution + Condition,
  title = ""
)
```

### Relative Bias and RMSE When Nonlinear Effects Were Present 

Figures 7 and 8 present relative bias and RMSE for all nonlinear effects across distributions with a moderate sample size. Under normality, results were mixed. At low reliability, LSAM showed bias for some nonlinear effects, which disappeared at medium reliability. UPI and QML also showed bias at low reliability, but only QML continued to exhibit bias at medium reliability. With right-skewed distributions, LSAM was biased for several nonlinear effects at low reliability, though performance improved at medium reliability, where only one effect displayed minor bias. UPI produced unbiased estimates even at low reliability. QML, however, showed substantial bias affecting most nonlinear effects across all reliability levels. Under the uniform distribution, LSAM was nearly unbiased, with only two nonlinear effects biased at low reliability. UPI showed substantial bias for most nonlinear effects at low reliability, which lessened at medium reliability. QML displayed bias for some effects at low reliability, improving with increasing reliability, yet all quadratic terms remained biased across reliability levels. At larger sample sizes, MCSEs were reduced, and both LSAM and UPI no longer showed the biases observed under moderate sample sizes (see Figures S10, S18, and S26 in supplemental materials).

Relative RMSE was comparable across methods under normality. With right-skewed distributions, LSAM and UPI showed the lowest RMSE at low reliability, though all methods converged at medium reliability. Under uniform predictors, QML yielded substantially lower RMSE than LSAM and UPI at low reliability, with convergence again observed at medium reliability (see Figures S12, S20, and S28 in supplemental materials for a large sample size).

### Efficiency and Accuracy of SEs When Nonlinear Effects Were Present

Figure 9 displays SE/SD ratios across distributions at a moderate sample size. Under normal distributions, LSAM and QML produced ratios within the acceptable range across reliability levels, whereas UPI fell below 0.85 for several nonlinear effects at low reliability, improving for most effects at medium reliability. With right-skewed distributions, LSAM ratios were consistently within the desirable range with only negligible deviations, QML ratios were largely acceptable with a few exceptions, and UPI again showed difficulties at low and medium reliability. Under uniform distributions, LSAM overestimated for some effects at low reliability, UPI underestimated ratios for nearly all nonlinear effects at low reliability and for quadratic effects at both low and medium reliability, while QML maintained efficient ratios across all reliabilities. Results generally improved with larger samples, except in a few cases for the UPI approach (see Figures S13, S21, and S29 in supplemental materials).

### Coverage When Nonlinear Effects Were Present

Figure 10 presents coverage results for a moderate sample size, with exact values reported for selected conditions. Under normality, LSAM generally achieved acceptable coverage, with some over-coverage at low reliability. QML maintained coverage within the desirable range across all nonlinear effects, whereas UPI showed under-coverage for most effects at low reliability. With right-skewed distributions, LSAM again produced acceptable coverage, apart from slight over-coverage at low reliability. In contrast, QML and UPI yielded inadequate coverage, reaching acceptable levels only at high reliability for some effects. Under uniform distributions, LSAM showed a similar pattern as in the other conditions, with modest over-coverage at low reliability. For QML and UPI, coverage for interaction terms was inadequate at low reliability but improved at medium reliability, while quadratic terms remained under-covered at both low and medium reliability. Patterns were qualitatively similar at larger sample sizes (see Figures S14, S22, and S30 in supplemental materials).

### Type I Error Rate

Figure 11 presents Type I error rates for a large sample size under right-skewed and uniform distributions. Under normality, all approaches maintained rates within the nominal 5% level (see Figure S15 in the supplemental materials). Under right-skewed conditions, LSAM and UPI demonstrated well-controlled Type I error rates, whereas QML showed substantial inflation for quadratic effects at low and medium reliability. Under uniform distributions, Type I error control was acceptable across methods, with the exception of LSAM, which fell below the nominal level for two quadratic terms at low reliability (see Figures S15, S23, and S31 in supplemental materials for moderate sample size).

### Empirical Power

Under normal distributions, power only exceeded 80% with large samples and high reliability, primarily for the nonlinear effects in the structural equation for $\eta_4$. Results under right-skewed conditions yielded elevated power rates under the same setting. In contrast, under uniform distributions, power remained substantially lower for all nonlinear effects, even with large samples and high reliability, with the exception of the two interaction terms in $\eta_4$ (see Figures S16, S24, and S32 in supplemental materials).

### Absolute Bias, RMSE, SEs, and Coverage When Nonlinear Effects Were Absent

Notable differences emerged across conditions. Under normality, QML showed reduced bias at low reliability for some nonlinear effects. Under right-skewed and uniform distributions, bias for QML was likewise reduced to certain extent. SE/SD ratios were highly similar. Coverage improved for all approaches under normal and uniform conditions. Under non-normality, however, QML continued to exhibit under-coverage mainly with large sample sizes. RMSE remained similar (see Figures S9, S11, S13, S14, S17, S19, S21, S22, S25, S27, S29, and S30 in supplemental materials). 

## Summary of Simulation 2

Across most conditions, LSAM produced largely unbiased estimates, accurate SEs, and acceptable coverage, except under low reliability, where some bias and over-coverage appeared. UPI was hampered by convergence failures and substantial bias under uniform predictors, along with underestimated SEs and under-coverage, particularly under uniform and right-skewed distributions with low or medium reliability. QML was efficient and often yielded accurate SEs, but displayed persistent bias for several nonlinear effects under right-skewed and uniform distributions, inflated Type I error rates under right-skewness, and under-coverage of nonlinear effects—especially quadratic terms—under both right-skewed and uniform predictors, most notably at low and medium reliability. Relative RMSE differences among methods were modest: QML was occasionally more efficient under uniform predictors, LSAM and UPI performed well under right-skewness, and all methods converged reliably at medium reliability. For power, acceptable levels ($\geq 80$%) were attained only under normality with large samples and high reliability, primarily for nonlinear effects in the structural equation for $\eta_4$. Under uniform predictors, power was substantially lower for all nonlinear effects, except the two interaction terms in $\eta_4$.