---
title: ""
author: ""
date: ""
output: html_document
---

# Results for simulation studies 

## Result for simulation study 1

```{r results, echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr); library(tidyr); library(purrr); library(stringr); library(kableExtra); library(glue); library(simhelpers)

load("sim_results/run_20250828_1758_36_1000/final_results.RData")

extract_eta3_parameters <- function(table, method_type) {
  if (is.null(table)) return(NULL)
  
  if (method_type == "dblcent") {
    rows <- table[table$lhs == "eta3" & table$op == "~", ]
    params <- if (nrow(rows) == 3) {
      c("eta1", "eta2", "eta1:eta2")
    } else {
      c("eta1", "eta2", "eta1:eta2", "eta1:eta1", "eta2:eta2")
    }
    RESULTS <- list(
      "Estimates"        = setNames(rows$est, params),
      "Standard Errors"  = setNames(rows$se, params),
      "P-values"         = setNames(rows$pvalue, params),
      "CI_lower"         = setNames(rows$ci.lower, params),
      "CI_upper"         = setNames(rows$ci.upper, params)
    )
    
  } else if (method_type == "sam") {
    coefs <- table[table$lhs == "eta3" & table$op == "~", ]
    params <- if (nrow(coefs) == 3) {
      c("eta1", "eta2", "eta1:eta2")
    } else {
      c("eta1", "eta2", "eta1:eta2", "eta1:eta1", "eta2:eta2")
    }
    rows <- table$lhs == "eta3" & table$op == "~" & table$rhs %in% params
    ests     <- setNames(table$est[rows], table$rhs[rows])
    ses      <- setNames(table$se[rows], table$rhs[rows])
    pval     <- setNames(table$pvalue[rows], table$rhs[rows])
    ci_lower <- setNames(table$ci.lower[rows], table$rhs[rows])
    ci_upper <- setNames(table$ci.upper[rows], table$rhs[rows])
    RESULTS <- list(
      "Estimates"        = ests[params],
      "Standard Errors"  = ses[params],
      "P-values"         = pval[params],
      "CI_lower"         = ci_lower[params],
      "CI_upper"         = ci_upper[params]
    )
    
  } else if (method_type %in% c("lms", "qml")) {
    rows <- table[table$lhs == "eta3" & table$op == "~", ]
    if (nrow(rows) == 5) {
      eta1eta1_idx <- which(rows$rhs == "eta1:eta1")
      eta1eta2_idx <- which(rows$rhs == "eta1:eta2")
      idx <- seq_len(nrow(rows))
      if (length(eta1eta1_idx) == 1 && length(eta1eta2_idx) == 1) {
        idx[eta1eta1_idx] <- eta1eta2_idx
        idx[eta1eta2_idx] <- eta1eta1_idx
      }
      RESULTS <- list(
        "Estimates"        = setNames(rows$est[idx], rows$rhs[idx]),
        "Standard Errors"  = setNames(rows$std.error[idx], rows$rhs[idx]),
        "P-values"         = setNames(rows$p.value[idx], rows$rhs[idx]),
        "CI_lower"         = setNames(rows$ci.lower[idx], rows$rhs[idx]),
        "CI_upper"         = setNames(rows$ci.upper[idx], rows$rhs[idx])
      )
    } else {
      RESULTS <- list(
        "Estimates"        = setNames(rows$est, rows$rhs),
        "Standard Errors"  = setNames(rows$std.error, rows$rhs),
        "P-values"         = setNames(rows$p.value, rows$rhs),
        "CI_lower"         = setNames(rows$ci.lower, rows$rhs),
        "CI_upper"         = setNames(rows$ci.upper, rows$rhs)
      )
    }
  }
  RESULTS
}

CalculateBiasAndCoverage <- function(all_results,
                                     parameters_of_interest = c("eta1","eta2","eta1:eta2","eta1:eta1","eta2:eta2"),
                                     remove_outliers = TRUE,
                                     outlier_threshold = 3,  # IQR multiplier for outlier removal
                                     alpha = 0.05,
                                     min_reps = 10,
                                     return_convergence_details = TRUE) {  # New parameter
  options(scipen = 999)
  if (is.null(all_results) || length(all_results) == 0) {
    stop("all_results is NULL or empty. Please load your data first.")
  }
  methods <- c("sam", "lms", "qml", "dblcent")
  results_summary <- dplyr::tibble()
  param_index <- c("eta1"=1, "eta2"=2, "eta1:eta2"=3, "eta1:eta1"=4, "eta2:eta2"=5)
  
  # Initialize convergence details storage
  convergence_details <- list()
  
  for (i in seq_along(all_results)) {
    condition <- all_results[[i]]$condition
    res_list  <- all_results[[i]]$results
    
    # true values (fallbacks)
    true_values <- all_results[[i]]$true_parameters
    if (is.null(true_values)) {
      if (!is.null(condition$Model_Type)) {
        if (condition$Model_Type == "null") {
          true_values <- c(0.316, 0.316, 0, 0, 0)
        } else if (condition$Model_Type == "alternative") {
          true_values <- c(0.316, 0.316, 0.139, 0.101, 0.101)
        }
      } else {
        true_values <- c(0.316, 0.316, 0.139, 0.101, 0.101)
      }
    }
    model_name <- if (!is.null(condition$Model_Type)) {
      ifelse(condition$Model_Type == "null", "Linear", "Full")
    } else "Full"
    distribution <- as.character(condition$Distribution)
    if (is.null(distribution) || distribution == "") distribution <- "normal"
    sample_size <- condition$N
    reliability <- condition$Rel
    
    # ============================================================
    # STEP 1: TRACK CONVERGENCE FOR EACH METHOD SEPARATELY
    # ============================================================
    
    # Get the number of replications
    max_reps <- 0
    for (method in methods) {
      tbls <- res_list[[paste0(method, "_tables")]]
      if (!is.null(tbls)) {
        max_reps <- max(max_reps, length(tbls))
      }
    }
    
    if (max_reps == 0) next
    
    # Track convergence for each method separately
    method_convergence <- list()
    for (method in methods) {
      method_convergence[[method]] <- rep(FALSE, max_reps)  # Initialize all as non-converged
    }
    
    # Check each method's convergence independently
    for (method in methods) {
      tbls <- res_list[[paste0(method, "_tables")]]
      if (is.null(tbls)) {
        # If this method doesn't exist, all remain FALSE
        next
      }
      
      for (rep in seq_len(max_reps)) {
        if (rep > length(tbls) || is.null(tbls[[rep]])) {
          next  # Already FALSE
        }
        
        # Extract parameters for this replication
        extr <- extract_eta3_parameters(tbls[[rep]], method)
        if (is.null(extr)) {
          next  # Already FALSE
        }
        
        # Check if all required parameters are present and complete
        converged <- TRUE
        for (p in parameters_of_interest) {
          if (p %in% names(extr$Estimates)) {
            # Check for NA, NaN, or Inf in any of the statistics
            if (is.na(extr$Estimates[p]) || is.nan(extr$Estimates[p]) || is.infinite(extr$Estimates[p]) ||
                is.na(extr$`Standard Errors`[p]) || is.nan(extr$`Standard Errors`[p]) || is.infinite(extr$`Standard Errors`[p]) ||
                is.na(extr$`P-values`[p]) || is.nan(extr$`P-values`[p]) || is.infinite(extr$`P-values`[p]) ||
                is.na(extr$CI_lower[p]) || is.nan(extr$CI_lower[p]) || is.infinite(extr$CI_lower[p]) ||
                is.na(extr$CI_upper[p]) || is.nan(extr$CI_upper[p]) || is.infinite(extr$CI_upper[p])) {
              converged <- FALSE
              break
            }
          } else {
            # Required parameter is missing
            converged <- FALSE
            break
          }
        }
        method_convergence[[method]][rep] <- converged
      }
    }
    
    # Store convergence details for this condition
    convergence_details[[paste0("Condition_", i)]] <- list(
      condition_info = list(
        Model = model_name,
        Distribution = distribution,
        SampleSize = sample_size,
        Reliability = reliability
      ),
      convergence_matrix = do.call(cbind, method_convergence),
      converged_iterations = lapply(method_convergence, which),  # Which iterations converged for each method
      convergence_counts = sapply(method_convergence, sum),
      convergence_rates = sapply(method_convergence, sum) / max_reps * 100
    )
    colnames(convergence_details[[paste0("Condition_", i)]]$convergence_matrix) <- methods
    
    # Calculate individual method convergence statistics
    method_convergence_counts <- list()
    method_convergence_rates <- list()
    method_outlier_counts <- list()  # NEW: Track outliers by method
    
    for (method in methods) {
      method_convergence_counts[[method]] <- sum(method_convergence[[method]])
      method_convergence_rates[[method]] <- sum(method_convergence[[method]]) / max_reps * 100
      method_outlier_counts[[method]] <- 0  # Initialize
    }
    
    # ============================================================
    # STEP 2: TRACK OUTLIERS FOR EACH METHOD INDEPENDENTLY (BEFORE COMPLETE CASE)
    # ============================================================
    
    if (remove_outliers) {
      for (method in methods) {
        tbls <- res_list[[paste0(method, "_tables")]]
        if (is.null(tbls)) next
        
        # Collect all estimates for this method (only from converged cases)
        all_estimates <- list()
        for (p in parameters_of_interest) {
          all_estimates[[p]] <- numeric()
        }
        
        for (rep in which(method_convergence[[method]])) {
          extr <- extract_eta3_parameters(tbls[[rep]], method)
          if (!is.null(extr)) {
            for (p in names(extr$Estimates)) {
              if (p %in% parameters_of_interest) {
                all_estimates[[p]] <- c(all_estimates[[p]], extr$Estimates[p])
              }
            }
          }
        }
        
        # Count outliers across all parameters for this method
        total_outliers <- 0
        for (p in parameters_of_interest) {
          if (length(all_estimates[[p]]) > 0) {
            q1 <- stats::quantile(all_estimates[[p]], 0.25, na.rm = TRUE)
            q3 <- stats::quantile(all_estimates[[p]], 0.75, na.rm = TRUE)
            iqr <- q3 - q1
            lb <- q1 - outlier_threshold * iqr
            ub <- q3 + outlier_threshold * iqr
            outliers <- sum(all_estimates[[p]] < lb | all_estimates[[p]] > ub, na.rm = TRUE)
            total_outliers <- total_outliers + outliers
          }
        }
        method_outlier_counts[[method]] <- total_outliers
      }
    }
    
    # ============================================================
    # STEP 3: IDENTIFY VALID REPLICATIONS ACROSS ALL METHODS
    # ============================================================
    
    # A replication is valid only if ALL methods converged
    valid_reps <- rep(TRUE, max_reps)
    for (method in methods) {
      valid_reps <- valid_reps & method_convergence[[method]]
    }
    
    # Get indices of valid replications
    valid_rep_indices <- which(valid_reps)
    n_total <- max_reps
    n_valid_complete_case <- length(valid_rep_indices)
    complete_case_convergence_rate <- n_valid_complete_case / n_total * 100
    
    # Add complete case info to convergence details
    convergence_details[[paste0("Condition_", i)]]$complete_case_iterations <- valid_rep_indices
    convergence_details[[paste0("Condition_", i)]]$complete_case_count <- n_valid_complete_case
    convergence_details[[paste0("Condition_", i)]]$complete_case_rate <- complete_case_convergence_rate
    
    if (n_valid_complete_case < min_reps) {
      message(paste("Condition", i, ": Only", n_valid_complete_case, 
                    "valid replications across all methods. Skipping."))
      next
    }
    
    # ============================================================
    # STEP 4: PROCESS EACH METHOD USING ONLY VALID REPLICATIONS
    # ============================================================
    
    for (method in methods) {
      tbls <- res_list[[paste0(method, "_tables")]]
      if (is.null(tbls)) next
      
      # Get convergence stats for this specific method
      n_converged_this_method <- method_convergence_counts[[method]]
      convergence_rate_this_method <- method_convergence_rates[[method]]
      n_outliers_this_method <- method_outlier_counts[[method]]  # NEW
      
      # accumulators by parameter - now only for valid reps
      params <- parameters_of_interest
      ests <- setNames(vector("list", length(params)), params)
      ses  <- setNames(vector("list", length(params)), params)
      pvs  <- setNames(vector("list", length(params)), params)
      los  <- setNames(vector("list", length(params)), params)
      his  <- setNames(vector("list", length(params)), params)
      
      # gather ONLY from valid replications
      for (rep in valid_rep_indices) {
        tab <- tbls[[rep]]
        if (is.null(tab)) next  # This shouldn't happen given our validation
        extr <- extract_eta3_parameters(tab, method)
        if (is.null(extr)) next  # This shouldn't happen given our validation
        
        have <- intersect(names(extr$Estimates), params)
        if (length(have) == 0) next
        for (p in have) {
          ests[[p]] <- c(ests[[p]], unname(extr$Estimates[p]))
          ses [[p]] <- c(ses [[p]], unname(extr$`Standard Errors`[p]))
          pvs [[p]] <- c(pvs [[p]], unname(extr$`P-values`[p]))
          los [[p]] <- c(los [[p]], unname(extr$CI_lower[p]))
          his [[p]] <- c(his [[p]], unname(extr$CI_upper[p]))
        }
      }
      
      # compute summaries per parameter
      for (p_name in params) {
        df <- tibble::tibble(
          est = unlist(ests[[p_name]]),
          se  = unlist(ses [[p_name]]),
          p_val = unlist(pvs [[p_name]]),
          lower_bound = unlist(los [[p_name]]),
          upper_bound = unlist(his [[p_name]])
        )
        if (nrow(df) == 0) next
        
        tv <- true_values[param_index[p_name]]
        
        # All data should already be complete cases now
        dfv <- df
        
        # ============================================================
        # CALCULATE MEDIAN-BASED METRICS BEFORE OUTLIER REMOVAL
        # ============================================================
        median_est <- stats::median(dfv$est)
        bias_median <- median_est - tv
        mad_est <- stats::mad(dfv$est, constant = 1)
        rmse_median <- sqrt(bias_median^2 + mad_est^2)
        
        if (tv != 0) {
          rel_bias_median <- bias_median / tv
          rel_bias_median_pct <- rel_bias_median * 100
        } else {
          rel_bias_median <- NA_real_
          rel_bias_median_pct <- NA_real_
        }
        
        # ============================================================
        # NOW REMOVE OUTLIERS FOR MEAN-BASED METRICS
        # ============================================================
        n_out <- 0
        if (remove_outliers && nrow(dfv) > 0) {
          q1 <- stats::quantile(dfv$est, 0.25, na.rm = TRUE)
          q3 <- stats::quantile(dfv$est, 0.75, na.rm = TRUE)
          iqr <- q3 - q1
          lb <- q1 - outlier_threshold * iqr
          ub <- q3 + outlier_threshold * iqr
          keep <- dfv$est >= lb & dfv$est <= ub
          n_out <- sum(!keep, na.rm = TRUE)
          dfv_clean <- dfv[keep, , drop = FALSE]  # cleaned dataset
        } else {
          dfv_clean <- dfv  # no outlier removal
        }
        
        # check if we still have enough data after outlier removal
        if (nrow(dfv_clean) < min_reps) next
        
        # add true parameter column for simhelpers functions
        dfv_clean$true_param <- tv
        
        # ============================================================
        # CALCULATE ALL MEAN-BASED METRICS USING SIMHELPERS ON CLEANED DATA
        # ============================================================
        
        # ABSOLUTE METRICS (bias, variance, MSE, RMSE) without winsorization 
        abs_metrics <- calc_absolute(
          data = dfv_clean,
          estimates = est, 
          true_param = true_param,
          criteria = c("bias", "variance", "stddev", "mse", "rmse"),
          winz = Inf  # No winsorization, we already removed outliers
        )
        
        # RELATIVE METRICS (only if true value is non-zero)
        if (tv != 0) {
          rel_metrics <- calc_relative(
            data = dfv_clean,
            estimates = est,
            true_param = true_param,
            criteria = c("relative bias", "relative mse", "relative rmse"),
            winz = Inf  # No winsorization
          )
          
          # simhelpers returns E(T)/θ (ratio)
          rel_bias_mean <- rel_metrics$rel_bias - 1
          rel_bias_mean_pct <- rel_bias_mean * 100       # convert to percentage
          rel_bias_mcse <- rel_metrics$rel_bias_mcse     # MCSE for the ratio
          
          rel_mse <- rel_metrics$rel_mse
          rel_rmse <- rel_metrics$rel_rmse
          rel_mse_mcse <- rel_metrics$rel_mse_mcse
          rel_rmse_mcse <- rel_metrics$rel_rmse_mcse
        } else {
          rel_bias_mean <- NA_real_
          rel_bias_mean_pct <- NA_real_
          rel_mse <- NA_real_
          rel_rmse <- NA_real_
          rel_bias_mcse <- NA_real_
          rel_mse_mcse <- NA_real_
          rel_rmse_mcse <- NA_real_
        }
        
        # COVERAGE AND CI WIDTH
        cov_metrics <- calc_coverage(
          data = dfv_clean,
          lower_bound = lower_bound, 
          upper_bound = upper_bound, 
          true_param = true_param,
          criteria = c("coverage", "width"),
          winz = Inf  # No winsorization
        )
        
        # REJECTION RATES (Type I Error / Power)
        rej_metrics <- calc_rejection(
          data = dfv_clean,
          p_values = p_val,
          alpha = alpha
        )
        
        # convert rejection rate to percentage but keep MCSE as proportion
        rejection_rate <- rej_metrics$rej_rate * 100
        rej_mcse <- rej_metrics$rej_rate_mcse  # Keep as proportion
        
        # determine Type I Error vs Power
        if (tv == 0) {
          type_i <- rejection_rate
          power <- NA_real_
          typei_mcse <- rej_mcse  # as proportion
          power_mcse <- NA_real_
        } else {
          type_i <- NA_real_
          power <- rejection_rate
          typei_mcse <- NA_real_
          power_mcse <- rej_mcse  # as proportion
        }
        
        # ============================================================
        # ADDITIONAL METRICS
        # ============================================================
        
        # Mean estimate (on cleaned data)
        mean_est <- mean(dfv_clean$est)
        
        # Standard error metrics (on cleaned data)
        mean_se <- mean(dfv_clean$se)
        se_sd_ratio <- mean_se / abs_metrics$stddev
        
        # ============================================================
        # COMPILE RESULTS
        # ============================================================
        
        results_summary <- dplyr::bind_rows(
          results_summary,
          tibble::tibble(
            Condition = i,
            Method = toupper(method),
            Model = model_name,
            Distribution = distribution,
            SampleSize = sample_size,
            Reliability = reliability,
            Parameter = p_name,
            TrueValue = tv,
            
            # Mean-based metrics from simhelpers (on cleaned data)
            MeanEstimate = mean_est,
            Bias_Mean = abs_metrics$bias,
            RelativeBias_Mean = rel_bias_mean,
            PercentRelativeBias_Mean = rel_bias_mean_pct,
            
            # Median-based metrics (calculated BEFORE outlier removal)
            MedianEstimate = median_est,
            Bias_Median = bias_median,
            RelativeBias_Median = rel_bias_median,
            PercentRelativeBias_Median = rel_bias_median_pct,
            MAD = mad_est,
            
            # Variability and accuracy metrics from simhelpers (on cleaned data)
            Variance = abs_metrics$var,
            SD = abs_metrics$stddev,
            MSE_Mean = abs_metrics$mse,
            RMSE_Mean = abs_metrics$rmse,
            RMSE_Median = rmse_median,  # Based on pre-outlier-removal median
            
            # Relative metrics from simhelpers (on cleaned data)
            Relative_MSE = rel_mse,
            Relative_RMSE = rel_rmse,
            
            # Standard error metrics (on cleaned data)
            MeanSE = mean_se,
            SE_SD_Ratio = se_sd_ratio,
            
            # Coverage and CI metrics from simhelpers (on cleaned data)
            CoverageRate = cov_metrics$coverage * 100,
            CI_Width = cov_metrics$width,
            
            # Testing metrics (on cleaned data)
            RejectionRate = rejection_rate,
            TypeI_Error = type_i,
            Power = power,
            
            # Monte Carlo standard errors (all kept as proportions/raw units)
            Bias_Mean_MCSE = abs_metrics$bias_mcse,
            RelativeBias_MCSE = rel_bias_mcse,
            Variance_MCSE = abs_metrics$var_mcse,
            SD_MCSE = abs_metrics$stddev_mcse,
            MSE_Mean_MCSE = abs_metrics$mse_mcse,
            RMSE_Mean_MCSE = abs_metrics$rmse_mcse,
            Relative_MSE_MCSE = rel_mse_mcse,
            Relative_RMSE_MCSE = rel_rmse_mcse,
            CoverageRate_MCSE = cov_metrics$coverage_mcse,  # Proportion
            CI_Width_MCSE = cov_metrics$width_mcse,
            RejectionRate_MCSE = rej_mcse,  # Proportion
            TypeI_Error_MCSE = typei_mcse,  # Proportion
            Power_MCSE = power_mcse,  # Proportion
            
            # SAMPLE SIZE TRACKING
            N_Total = n_total,
            N_Converged_This_Method = n_converged_this_method,  # How many converged for THIS method
            Convergence_Rate_This_Method = convergence_rate_this_method,  # % converged for THIS method
            N_Used_After_Convergence = n_valid_complete_case,  # What's actually used after complete-case deletion
            Complete_Case_Convergence_Rate = complete_case_convergence_rate,  # % converged for ALL methods
            N_Outliers_Removed = n_out,  # Outliers removed from this method/parameter
            Percent_Outliers_Removed = round(n_out / n_valid_complete_case * 100, 2),  # % of complete cases that were outliers
            N_Final_After_Outliers = nrow(dfv_clean),  # Final N after convergence AND outlier removal
            
            # TOTAL EXCLUSION SUMMARY
            N_Total_Excluded = n_total - nrow(dfv_clean),
            Percent_Total_Excluded = round((n_total - nrow(dfv_clean)) / n_total * 100, 2)
          )
        )
      } # end per-parameter
    } # end per-method
  } # end per-condition
  
  # Return both results and convergence details if requested
  if (return_convergence_details) {
    return(list(
      results = results_summary,
      convergence_details = convergence_details
    ))
  } else {
    return(results_summary)
  }
}

# Run the function with convergence details
results_with_mcse <- CalculateBiasAndCoverage(
  all_results,
  parameters_of_interest = c("eta1","eta2","eta1:eta2","eta1:eta1","eta2:eta2"),
  remove_outliers = TRUE,
  outlier_threshold = 3,
  alpha = 0.05,
  min_reps = 10,
  return_convergence_details = FALSE  
)

```

```{r tables, echo=FALSE, results='asis', message=FALSE, eval=FALSE}

# ---- Landscape APA tables | Method-first | ± MCSE | Rej. = Type I if true=0 else Power ----
# Chunk tip: use results='asis'

library(dplyr)
library(tidyr)
library(stringr)
library(glue)
library(kableExtra)
library(tools)

# ---------- helpers ----------
fmt_num <- function(x, digits = 3) ifelse(is.na(x), "", formatC(x, digits = digits, format = "f"))
fmt_pm  <- function(value, mcse, digits_value = 3, digits_mcse = 3, scale_mcse = 1) {
  ifelse(is.na(value), "", paste0(fmt_num(value, digits_value), " ± ", fmt_num(mcse * scale_mcse, digits_mcse)))
}
cap_first <- function(x) tools::toTitleCase(tolower(as.character(x)))

METHOD_ORDER <- c("SAM","LMS","QML","DBLCENT")
PARAM_ORDER  <- c("eta1","eta2","eta1:eta2","eta1:eta1","eta2:eta2")

# ---------- table builder (Method first) ----------
build_condition_table_landscape <- function(df, N, Rel, Dist, model_type, latex_font_size = 9) {

  dfc <- df %>%
    filter(
      SampleSize == N,
      Reliability == Rel,
      tolower(Distribution) == tolower(Dist),
      Model == model_type
    ) %>%
    mutate(
      Method    = factor(toupper(Method), levels = METHOD_ORDER),
      Parameter = factor(Parameter, levels = PARAM_ORDER)
    ) %>%
    arrange(Method, Parameter)

  if (nrow(dfc) == 0) return(NULL)

  # Rejection logic: Type I when true = 0; Power otherwise
  rej_value <- ifelse(dfc$TrueValue == 0, dfc$TypeI_Error,      dfc$Power)
  rej_mcse  <- ifelse(dfc$TrueValue == 0, dfc$TypeI_Error_MCSE, dfc$Power_MCSE)

  # Use columns that exist in results:
  # - Convergence_Rate_This_Method           (percent for this method alone)
  # - Complete_Case_Convergence_Rate         (percent when ALL methods converge)
  # - N_Used_After_Convergence               (complete-case N before outlier removal)
  # - N_Outliers_Removed                     (per-parameter outliers removed)
  # - N_Final_After_Outliers                 (final N after convergence + outliers)
  conv_rate_method   <- dfc$Convergence_Rate_This_Method
  conv_rate_complete <- dfc$Complete_Case_Convergence_Rate
  n_used_complete    <- dfc$N_Used_After_Convergence
  n_final            <- dfc$N_Final_After_Outliers

  tbl <- dfc %>%
    transmute(
      Method, Parameter,
      `True`                      = fmt_num(TrueValue, 3),
      `Mean`                      = fmt_num(MeanEstimate, 3),

      `Bias ± MCSE`               = fmt_pm(Bias_Mean, Bias_Mean_MCSE, 3, 3, 1),
      `% Rel. Bias ± MCSE`        = ifelse(TrueValue == 0, "",
                                           fmt_pm(PercentRelativeBias_Mean, RelativeBias_MCSE * 100, 1, 1, 1)),

      `Median`                    = fmt_num(MedianEstimate, 3),
      `Bias (median)`             = fmt_num(Bias_Median, 3),
      `MAD`                       = fmt_num(MAD, 4),

      `Variance ± MCSE`           = fmt_pm(Variance, Variance_MCSE, 4, 4, 1),
      `SD ± MCSE`                 = fmt_pm(SD, SD_MCSE, 4, 4, 1),
      `MSE ± MCSE`                = fmt_pm(MSE_Mean, MSE_Mean_MCSE, 4, 4, 1),
      `RMSE ± MCSE`               = fmt_pm(RMSE_Mean, RMSE_Mean_MCSE, 4, 4, 1),
      `RMSE (median)`             = fmt_num(RMSE_Median, 4),
      `Rel. MSE ± MCSE`           = fmt_pm(Relative_MSE, Relative_MSE_MCSE, 4, 4, 1),
      `Rel. RMSE ± MCSE`          = fmt_pm(Relative_RMSE, Relative_RMSE_MCSE, 4, 4, 1),

      `Mean SE`                   = fmt_num(MeanSE, 4),
      `SE/SD`                     = fmt_num(SE_SD_Ratio, 3),

      `Coverage (%) ± MCSE`       = fmt_pm(CoverageRate, CoverageRate_MCSE, 1, 1, 100),
      `CI width ± MCSE`           = fmt_pm(CI_Width, CI_Width_MCSE, 4, 4, 1),
      `Rej. (%) ± MCSE`           = fmt_pm(rej_value, rej_mcse, 1, 1, 100),

      # Sample size tracking (now aligned with available columns)
      `Conv. Rate (method) %`     = fmt_num(conv_rate_method, 1),
      `Conv. Rate (complete) %`   = fmt_num(conv_rate_complete, 1),
      `Outliers`                  = N_Outliers_Removed,
      `N Used (post-conv)`        = n_used_complete,
      `N Used (final)`            = n_final
    )

  caption <- glue(
    "N = {N}, Reliability = {Rel}, Distribution = {cap_first(Dist)}, Model = {model_type}."
  )

  if (knitr::is_latex_output()) {
    kb <- kbl(
      tbl,
      booktabs   = TRUE,
      align      = c("l","l", rep("r", ncol(tbl) - 2)),
      col.names  = names(tbl),
      caption    = caption
    )
    kb <- kable_classic(kb, full_width = FALSE, html_font = "Times New Roman")
    kb <- kable_styling(kb, latex_options = c("hold_position","scale_down"), font_size = latex_font_size)
    kb <- collapse_rows(kb, columns = 1, valign = "top")
    kb <- add_header_above(kb, c(" " = 2, "Metrics (MCSE shown as ±)" = ncol(tbl) - 6, "Sample Sizes" = 4))
    kb <- footnote(
      kb,
      general = paste0(
        "Conv. Rate (method) = % of replications converged for this method alone; ",
        "Conv. Rate (complete) = % where all methods converged (complete-case). ",
        "Outliers = # removed; N Used (post-conv) = complete-case N before outliers; ",
        "N Used (final) = after convergence + outlier removal. ",
        "Rej. is Type I error when true=0, Power otherwise. ",
        "Coverage/Type I/Power are percentages; MCSEs are percentage points. ",
        "Cells blank where relative measures are undefined (true value = 0)."
      ),
      threeparttable = TRUE
    )
    return(kableExtra::landscape(kb))
  } else {
    kb <- kbl(
      tbl,
      booktabs   = TRUE,
      align      = c("l","l", rep("r", ncol(tbl) - 2)),
      col.names  = names(tbl),
      caption    = caption
    )
    kb <- kable_classic(kb, full_width = FALSE, html_font = "Times New Roman")
    kb <- kable_styling(kb, font_size = 14)
    kb <- collapse_rows(kb, columns = 1, valign = "top")
    kb <- add_header_above(kb, c(" " = 2, "Metrics (MCSE shown as ±)" = ncol(tbl) - 6, "Sample Sizes" = 4))
    kb <- footnote(
      kb,
      general = paste0(
        "Conv. Rate (method) = % of replications converged for this method alone; ",
        "Conv. Rate (complete) = % where all methods converged (complete-case). ",
        "Outliers = # removed; N Used (post-conv) = complete-case N before outliers; ",
        "N Used (final) = after convergence + outlier removal. ",
        "Rej. is Type I error when true=0, Power otherwise. ",
        "Coverage/Type I/Power are percentages; MCSEs are percentage points. ",
        "Cells blank where relative measures are undefined (true value = 0)."
      ),
      threeparttable = TRUE
    )
    return(scroll_box(kb, width = "100%", height = "520px"))
  }
}


```

```{r convergence-outliers-summary, echo=FALSE, results='asis'}
# Comprehensive convergence and outlier summary table
create_summary_table <- function(results_with_mcse,
                                core_params = c("eta1","eta2","eta1:eta2")) {
  
  # Filter to core parameters and get worst-case scenario across parameters
  summary_data <- results_with_mcse |>
    dplyr::filter(Parameter %in% core_params) |>
    dplyr::group_by(Condition, Method, Model, Distribution, SampleSize, Reliability) |>
    dplyr::summarise(
      # Take values from first parameter (they should be same across params for convergence columns)
      N_Total = first(N_Total),
      N_Converged_This_Method = first(N_Converged_This_Method),
      Convergence_Rate_This_Method = first(Convergence_Rate_This_Method),
      N_Used_After_Convergence = first(N_Used_After_Convergence),
      
      # For outliers, take the maximum across parameters (worst case)
      N_Outliers_Removed = max(N_Outliers_Removed, na.rm = TRUE),
      Percent_Outliers_Removed = max(Percent_Outliers_Removed, na.rm = TRUE),
      
      # For final N, take the minimum across parameters (most conservative)
      N_Final_After_Outliers = min(N_Final_After_Outliers, na.rm = TRUE),
      
      .groups = "drop"
    ) |>
    dplyr::arrange(Condition, Method)
  
  # Comprehensive table with reorganized structure
  comprehensive_table <- summary_data |>
    dplyr::select(
      Condition,
      Method,
      Model,
      Distribution,
      `Sample Size` = SampleSize,
      Reliability,
      # Convergence section - all convergence-related metrics together
      `N Total` = N_Total,
      `N Converged` = N_Converged_This_Method,
      `Conv. Rate (%)` = Convergence_Rate_This_Method,
      `N Converged Total` = N_Used_After_Convergence,  # This is the complete cases within converged
      # Outliers section - remains as is
      `N Outliers` = N_Outliers_Removed,
      `Outlier Rate (%)` = Percent_Outliers_Removed,
      `N Final` = N_Final_After_Outliers
    ) |>
    dplyr::mutate(
      `Conv. Rate (%)` = round(`Conv. Rate (%)`, 1),
      `Outlier Rate (%)` = round(`Outlier Rate (%)`, 1),
      `Final Rate (%)` = round(100 * `N Final` / `N Total`, 1)
    )
  
  comprehensive_table
}

# Create summary table
summary_table <- create_summary_table(results_with_mcse)

# Helper function to get rates from the summary table
get_rate <- function(metric, method, model, dist, n, rel) {
  # Map the metric names to new column names
  metric_map <- c(
    "ConvergenceRate" = "Conv. Rate (%)",
    "OutlierRate" = "Outlier Rate (%)",
    "FinalRate" = "Final Rate (%)"
  )
  
  # Get mapped metric name, or use as-is if not in map
  col_name <- ifelse(metric %in% names(metric_map), metric_map[metric], metric)
  
  result <- summary_table |>
    dplyr::filter(
      Method == method,
      Model == model,
      Distribution == dist,
      `Sample Size` == n,
      Reliability == rel
    ) |>
    dplyr::pull(!!sym(col_name))
  
  result
}

```

### Convergence Rate and Outliers

We refer the reader to Table 2 for a detailed summary for convergence and outliers. For most approaches there were a few convergence issues. One notable exception was for the DBLCENT under the condition with moderate sample size, low reliability, and uniformly distributed latent predictors. In that case, convergence rates were `r round(get_rate("ConvergenceRate", "DBLCENT", "Full", "uniform", 400, 0.4), 2)`% with the full population model and `r round(get_rate("ConvergenceRate", "DBLCENT", "Linear", "uniform", 400, 0.4), 2)`% with the linear population model. For the SAM, convergence rate was `r round(get_rate("ConvergenceRate", "SAM", "Linear", "uniform", 400, 0.4), 2)`% across all conditions. The remaining approaches, LMS and QML, also showed decent convergence rates, with the lowest value being respectively `r round(get_rate("ConvergenceRate", "LMS", "Linear", "uniform", 400, 0.4), 2)`% and `r round(get_rate("ConvergenceRate", "QML", "Linear", "uniform", 400, 0.4), 2)`% for both cases under the same scenario in which DBLCENT, but now only specifically with the linear population model. 

With respect to outliers, a somewhat similar trend as with convergence rates was observed. The DBLCENT had the highest outlier rate (`r round(get_rate("OutlierRate", "DBLCENT", "Linear", "uniform", 400, 0.4), 2)`%) for the condition with moderate sample size, low reliability, and uniformly distributed latent predictors. Both the LMS and QML also had their highest outlier rates in the same condition, with `r round(get_rate("OutlierRate", "LMS", "Linear", "uniform", 400, 0.4), 2)`% and `r round(get_rate("OutlierRate", "QML", "Linear", "uniform", 400, 0.4), 2)`% respectively. For the SAM, however, the highest outlier rate was observed in the condition with moderate sample size, low reliability, and nonnormally distributed latent predictors (`r round(get_rate("OutlierRate", "SAM", "Linear", "nonnormal", 400, 0.4), 2)`%).

```{r apa-plots, echo=FALSE}
# ---- Shared setup: helpers, themes, palettes ----
library(dplyr)
library(ggplot2)
library(stringr)

# Orderings & labels
METHOD_ORDER <- c("SAM","LMS","QML","DBLCENT")
DIST_LABS    <- c(normal="Normal", nonnormal="Nonnormal", uniform="Uniform")
PARAM_ORDER  <- c("eta1:eta2","eta1:eta1","eta2:eta2")
PARAM_LABS   <- c("eta1:eta2"="beta[3]",
                  "eta1:eta1"="beta[4]",
                  "eta2:eta2"="beta[5]")
# Grayscale palettes
GREYS_METHOD <- c(SAM="grey20", LMS="grey45", QML="grey65", DBLCENT="grey85")
GREYS_PARAM  <- c("eta1:eta2"="grey20", "eta1:eta1"="grey55", "eta2:eta2"="grey85")

# APA-ish theme
theme_apa_bw <- function(base_size = 11) {
  theme_bw(base_size = base_size) +
    theme(
      panel.grid.minor = element_blank(),
      strip.text = element_text(face = "bold"),
      legend.position = "bottom",
      legend.title = element_blank()
    )
}

# Convenience: build a Condition factor "N=..., Rel=..."
make_condition <- function(N, Rel) {
  factor(paste0("N=", N, ", Rel=", Rel),
         levels = c("N=400, Rel=0.4","N=400, Rel=0.6","N=400, Rel=0.8",
                    "N=1000, Rel=0.4","N=1000, Rel=0.6","N=1000, Rel=0.8"))
}

# ---- Data prep for nonlinear parameters only ----
prep_nonlinear <- function(df, model = c("Full","Linear")) {
  model <- match.arg(model)
  df %>%
    filter(Parameter %in% PARAM_ORDER, Model == model) %>%
    mutate(
      Method       = factor(Method, levels = METHOD_ORDER),
      Distribution = factor(Distribution, levels = names(DIST_LABS), labels = DIST_LABS),
      Parameter    = factor(Parameter, levels = PARAM_ORDER, 
                           labels = c("beta[3]", "beta[4]", "beta[5]")),  # Add labels here
      Reliability  = factor(Reliability),
      SampleSize   = factor(SampleSize),
      Condition    = make_condition(SampleSize, Reliability)
    )
}

```

```{r bias, echo=FALSE}
shapes <- c(SAM=16, LMS=17, QML=15, DBLCENT=18)
ltys   <- c(SAM="solid", LMS="dashed", QML="dotdash", DBLCENT="twodash")

dat_bias <- bind_rows(
  prep_nonlinear(results_with_mcse, model = "Linear") %>% mutate(Model = "Linear"),
  prep_nonlinear(results_with_mcse, model = "Full")   %>% mutate(Model = "Full")
) %>%
  mutate(Model = factor(Model, levels = c("Linear", "Full"))) %>%
  transmute(Distribution, Parameter, SampleSize, Reliability, Method, Model,
            y = Bias_Mean, yerr = Bias_Mean_MCSE)

get_absolute_bias <- function(method, dist, param, n, rel, model = c("Full","Linear")) {
  model <- match.arg(model)
  dat_bias %>%
    filter(Method == method,
           Distribution == dist,
           Parameter == param,
           SampleSize == n,
           Reliability == rel,
           Model == model) %>%
    select(y)
}

p_bias <- ggplot(
  dat_bias,
  aes(x = Reliability, y = y, shape = Method, linetype = Method, group = Method)
) +
  geom_pointrange(aes(ymin = y - yerr, ymax = y + yerr),
                  position = position_dodge(width = .6), color = "black") +
  geom_line(position = position_dodge(width = .6), color = "black") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  scale_shape_manual(values = shapes) +
  scale_linetype_manual(values = ltys) +
  facet_grid(Distribution + Parameter ~ Model + SampleSize,
             labeller = labeller(SampleSize = label_value,
                                 Parameter = label_parsed)) +
  labs(x = "Reliability", y = "Bias", title = "") +
  theme_apa_bw()

dat_bias_relative <- bind_rows(
  prep_nonlinear(results_with_mcse, model = "Linear") %>% mutate(Model = "Linear"),
  prep_nonlinear(results_with_mcse, model = "Full")   %>% mutate(Model = "Full")
) %>%
  mutate(Model = factor(Model, levels = c("Linear", "Full"))) %>%
  transmute(Distribution, Parameter, SampleSize, Reliability, Method, Model,
            y = RelativeBias_Mean, yerr = RelativeBias_MCSE)  # Convert MCSE to percentage

get_bias <- function(method, dist, param, n, rel, model = c("Full","Linear")) {
  model <- match.arg(model)
  dat_bias_relative %>%
    filter(Method == method,
           Distribution == dist,
           Parameter == param,
           SampleSize == n,
           Reliability == rel,
           Model == model) %>%
    select(y)
}
```

```{r rmse, echo=FALSE}
## ----- RMSE (no scaling) -----
dat_rmse <- bind_rows(
  prep_nonlinear(results_with_mcse, model = "Linear") %>% mutate(Model = "Linear"),
  prep_nonlinear(results_with_mcse, model = "Full")   %>% mutate(Model = "Full")
) %>%
  mutate(Model = factor(Model, levels = c("Linear", "Full"))) %>%
  transmute(Distribution, Parameter, SampleSize, Reliability, Method, Model,
            y    = RMSE_Mean,
            yerr = RMSE_Mean_MCSE)   # adjust to RMSE_MCSE if that's your column

p_rmse <- ggplot(
  dat_rmse,
  aes(x = Reliability, y = y, shape = Method, linetype = Method, group = Method)
) +
  geom_pointrange(aes(ymin = y - yerr, ymax = y + yerr),
                  position = position_dodge(width = .6), color = "black") +
  geom_line(position = position_dodge(width = .6), color = "black") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  scale_shape_manual(values = shapes) +
  scale_linetype_manual(values = ltys) +
  facet_grid(Distribution + Parameter ~ Model + SampleSize,
             labeller = labeller(SampleSize = label_value,
                                 Parameter = label_parsed)) +
  labs(x = "Reliability", y = "RMSE", title = "") +
  theme_apa_bw()

get_rmse <- function(method, dist, param, n, rel, model = c("Full","Linear")) {
  model <- match.arg(model)
  dat_rmse %>%
    filter(Method == method,
           Distribution == dist,
           Parameter == param,
           SampleSize == n,
           Reliability == rel,
           Model == model) %>%
    select(y)
}

## ----- Relative RMSE (no scaling; stays on 0–1 scale) -----
dat_rmse_relative <- bind_rows(
  prep_nonlinear(results_with_mcse, model = "Linear") %>% mutate(Model = "Linear"),
  prep_nonlinear(results_with_mcse, model = "Full")   %>% mutate(Model = "Full")
) %>%
  mutate(Model = factor(Model, levels = c("Linear", "Full"))) %>%
  transmute(Distribution, Parameter, SampleSize, Reliability, Method, Model,
            y    = Relative_RMSE,
            yerr = Relative_RMSE_MCSE)

get_relative_rmse <- function(method, dist, param, n, rel, model = c("Full","Linear")) {
  model <- match.arg(model)
  dat_rmse_relative %>%
    filter(Method == method,
           Distribution == dist,
           Parameter == param,
           SampleSize == n,
           Reliability == rel,
           Model == model) %>%
    select(y)
}
```

### Bias When Nonlinear Effects Were Present 

Figure 1 presents a visualization of the reported values. In that case, we show absolute bias rather than relative bias for the linear models (where nonlinear effects are absent), as relative bias would be undefined in these cases. Note that, given the relatively small magnitude of the true effects, relative bias metrics can appear disproportionately large; therefore, we report in the text both absolute and relative bias alongside RMSE and relative RMSE metrics. Figure 2 shows the RMSE.

#### Normal Distribution

Under normal distributional conditions, most estimation approaches demonstrated comparable performance, with SAM, LMS, and QML remaining consistently unbiased across variations in reliability and sample size, regardless of the nonlinear effect. 

The most challenging condition across all approaches occurred at the combination of low reliability and moderate sample size. Notably, the results for the quadratic terms follow similarly that of the interaction effect. In that case, for $\beta_3$, the SAM approach exhibited a relative bias of `r round(get_bias("SAM", "Normal", "beta[3]", 400, 0.4, "Full"),3)` (absolute bias = `r round(get_absolute_bias("SAM", "Normal", "beta[3]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("SAM", "Normal", "beta[3]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("SAM", "Normal", "beta[3]", 400, 0.4, "Full"),3)`). LMS and QML yielded relative biases of `r round(get_bias("LMS", "Normal", "beta[3]", 400, 0.4, "Full"),3)` (absolute bias = `r round(get_absolute_bias("LMS", "Normal", "beta[3]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("LMS", "Normal", "beta[3]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("LMS", "Normal", "beta[3]", 400, 0.4, "Full"),3)`) and `r round(get_bias("QML", "Normal", "beta[3]", 400, 0.4, "Full"),3)` (absolute bias = `r round(get_absolute_bias("QML", "Normal", "beta[3]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("QML", "Normal", "beta[3]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("QML", "Normal", "beta[3]", 400, 0.4, "Full"),3)`), respectively. With medium reliability and moderate sample size, results improved the same aforementioned approaches. Indeed, the SAM demonstrated a relative bias of `r round(get_bias("SAM", "Normal", "beta[3]", 400, 0.6, "Full"),3)` (absolute bias = `r round(get_absolute_bias("SAM", "Normal", "beta[3]", 400, 0.6, "Full"),3)`, RMSE = `r round(get_rmse("SAM", "Normal", "beta[3]", 400, 0.6, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("SAM", "Normal", "beta[3]", 400, 0.6, "Full"),3)`), while the LMS exhibited a relave bias of `r round(get_bias("LMS", "Normal", "beta[3]", 400, 0.6, "Full"),3)` (absolute bias = `r round(get_absolute_bias("LMS", "Normal", "beta[3]", 400, 0.6, "Full"),3)`, RMSE = `r round(get_rmse("LMS", "Normal", "beta[3]", 400, 0.6, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("LMS", "Normal", "beta[3]", 400, 0.6, "Full"),3)`) and QML showed a relative bias of `r round(get_bias("QML", "Normal", "beta[3]", 400, 0.6, "Full"),3)` (absolute bias = `r round(get_absolute_bias("QML", "Normal", "beta[3]", 400, 0.6, "Full"),3)`, RMSE = `r round(get_rmse("QML", "Normal", "beta[3]", 400, 0.6, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("QML", "Normal", "beta[3]", 400, 0.6, "Full"),3)`). At high reliability and moderate sample size, relative bias further decreased. The SAM approach yielded a relative bias of `r round(get_bias("SAM", "Normal", "beta[3]", 400, 0.8, "Full"),3)` (absolute bias = `r round(get_absolute_bias("SAM", "Normal", "beta[3]", 400, 0.8, "Full"),3)`, RMSE = `r round(get_rmse("SAM", "Normal", "beta[3]", 400, 0.8, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("SAM", "Normal", "beta[3]", 400, 0.8, "Full"),3)`), with the LMS showing a similar relative bias of `r round(get_bias("LMS", "Normal", "beta[3]", 400, 0.8, "Full"),3)` (absolute bias = `r round(get_absolute_bias("LMS", "Normal", "beta[3]", 400, 0.8, "Full"),3)`, RMSE = `r round(get_rmse("LMS", "Normal", "beta[3]", 400, 0.8, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("LMS", "Normal", "beta[3]", 400, 0.8, "Full"),3)`) as well as the QML with `r round(get_bias("QML", "Normal", "beta[3]", 400, 0.8, "Full"),3)` (absolute bias = `r round(get_absolute_bias("QML", "Normal", "beta[3]", 400, 0.8, "Full"),3)`, RMSE = `r round(get_rmse("QML", "Normal", "beta[3]", 400, 0.8, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("QML", "Normal", "beta[3]", 400, 0.8, "Full"),3)`). 

On the other hand, the DBLCENT demonstrated different performance patterns across nonlinear effect estimates. For $\beta_3$, at low reliability and moderate sample size, we observed a relative bias of `r round(get_bias("DBLCENT", "Normal", "beta[3]", 400, 0.4, "Full"),3)` (absolute bias = `r round(get_absolute_bias("DBLCENT", "Normal", "beta[3]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("DBLCENT", "Normal", "beta[3]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("DBLCENT", "Normal", "beta[3]", 400, 0.4, "Full"),3)`). At medium reliability and moderate sample size, substantial negative bias persisted with `r round(get_bias("DBLCENT", "Normal", "beta[3]", 400, 0.6, "Full"),3)` (absolute bias = `r round(get_absolute_bias("DBLCENT", "Normal", "beta[3]", 400, 0.6, "Full"),3)`, RMSE = `r round(get_rmse("DBLCENT", "Normal", "beta[3]", 400, 0.6, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("DBLCENT", "Normal", "beta[3]", 400, 0.6, "Full"),3)`). The quadratic terms exhibited contrasting patterns. For $\beta_4$, DBLCENT showed a relative bias of `r round(get_bias("DBLCENT", "Normal", "beta[4]", 400, 0.4, "Full"),3)` at low reliability and moderate sample size (absolute bias = `r round(get_absolute_bias("DBLCENT", "Normal", "beta[4]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("DBLCENT", "Normal", "beta[4]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("DBLCENT", "Normal", "beta[4]", 400, 0.4, "Full"),3)`), improving to `r round(get_bias("DBLCENT", "Normal", "beta[4]", 400, 0.6, "Full"),3)` at medium reliability with the same sample size (absolute bias = `r round(get_absolute_bias("DBLCENT", "Normal", "beta[4]", 400, 0.6, "Full"),3)`, RMSE = `r round(get_rmse("DBLCENT", "Normal", "beta[4]", 400, 0.6, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("DBLCENT", "Normal", "beta[4]", 400, 0.6, "Full"),3)`) and `r round(get_bias("DBLCENT", "Normal", "beta[4]", 400, 0.8, "Full"),3)` at high reliability (absolute bias = `r round(get_absolute_bias("DBLCENT", "Normal", "beta[4]", 400, 0.8, "Full"),3)`, RMSE = `r round(get_rmse("DBLCENT", "Normal", "beta[4]", 400, 0.8, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("DBLCENT", "Normal", "beta[4]", 400, 0.8, "Full"),3)`).

The results improved for all approaches and nonlinear effects with a large sample size. One notable exception is that the bias increases for $\beta_3$ with the DBLCENT under medium reliability. Specifically, the relative bias in that case is `r round(get_bias("DBLCENT", "Normal", "beta[3]", 1000, 0.6, "Full"),3)`.

#### Nonnormal Distribution

Under nonnormal distributional conditions, substantial differences emerged across estimation approaches, with the degree varying depending on the nonlinear effect considered.

For the interaction effect ($\beta_3$), SAM performance struggled at low reliability and moderate sample size, yielding a relative bias of `r round(get_bias("SAM", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)` (absolute bias = `r round(get_absolute_bias("SAM", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("SAM", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("SAM", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)`). At medium reliability and moderate sample size, the relative bias decreased to `r round(get_bias("SAM", "Nonnormal", "beta[3]", 400, 0.6, "Full"),3)` (absolute bias = `r round(get_absolute_bias("SAM", "Nonnormal", "beta[3]", 400, 0.6, "Full"),3)`, RMSE = `r round(get_rmse("SAM", "Nonnormal", "beta[3]", 400, 0.6, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("SAM", "Nonnormal", "beta[3]", 400, 0.6, "Full"),3)`). 

In contrast, LMS and QML exhibited substantial bias across all reliability conditions. At low reliability and moderate sample size, LMS produced a relative bias of `r round(get_bias("LMS", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)` (absolute bias = `r round(get_absolute_bias("LMS", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("LMS", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("LMS", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)`), while QML yielded `r round(get_bias("QML", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)` (absolute bias = `r round(get_absolute_bias("QML", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("QML", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("QML", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)`). At medium reliability and moderate sample size, LMS showed a relative bias of `r round(get_bias("LMS", "Nonnormal", "beta[3]", 400, 0.6, "Full"),3)` (absolute bias = `r round(get_absolute_bias("LMS", "Nonnormal", "beta[3]", 400, 0.6, "Full"),3)`, RMSE = `r round(get_rmse("LMS", "Nonnormal", "beta[3]", 400, 0.6, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("LMS", "Nonnormal", "beta[3]", 400, 0.6, "Full"),3)`) and QML showed a relative bias of `r round(get_bias("QML", "Nonnormal", "beta[3]", 400, 0.6, "Full"),3)` (absolute bias = `r round(get_absolute_bias("QML", "Nonnormal", "beta[3]", 400, 0.6, "Full"),3)`, RMSE = `r round(get_rmse("QML", "Nonnormal", "beta[3]", 400, 0.6, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("QML", "Nonnormal", "beta[3]", 400, 0.6, "Full"),3)`). At high reliability and moderate sample size, substantial bias persisted with the LMS showing `r round(get_bias("LMS", "Nonnormal", "beta[3]", 400, 0.8, "Full"),3)` (absolute bias = `r round(get_absolute_bias("LMS", "Nonnormal", "beta[3]", 400, 0.8, "Full"),3)`, RMSE = `r round(get_rmse("LMS", "Nonnormal", "beta[3]", 400, 0.8, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("LMS", "Nonnormal", "beta[3]", 400, 0.8, "Full"),3)`) and QML showing `r round(get_bias("QML", "Nonnormal", "beta[3]", 400, 0.8, "Full"),3)` (absolute bias = `r round(get_absolute_bias("QML", "Nonnormal", "beta[3]", 400, 0.8, "Full"),3)`, RMSE = `r round(get_rmse("QML", "Nonnormal", "beta[3]", 400, 0.8, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("QML", "Nonnormal", "beta[3]", 400, 0.8, "Full"),3)`).

Notably, quadratic effects demonstrated positive bias under nonnormal conditions, contrasting with the negative bias observed for interaction terms. In fact, both $\beta_4$ and $\beta_5$ showed similar qualitative performance-where the bias is larger for $\beta_4$ than $\beta_5$. For instance, the LMS exhibited a relative bias of `r round(get_bias("LMS", "Nonnormal", "beta[4]", 400, 0.4, "Full"),3)` at low reliability and moderate sample size (absolute bias = `r round(get_absolute_bias("LMS", "Nonnormal", "beta[4]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("LMS", "Nonnormal", "beta[4]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("LMS", "Nonnormal", "beta[4]", 400, 0.4, "Full"),3)`) for $\beta_4$. While for $\beta_5$, we observed a relative bias of `r round(get_bias("LMS", "Nonnormal", "beta[5]", 400, 0.4, "Full"),3)` at low reliability and moderate sample size (absolute bias = `r round(get_absolute_bias("LMS", "Nonnormal", "beta[5]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("LMS", "Nonnormal", "beta[5]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("LMS", "Nonnormal", "beta[5]", 400, 0.4, "Full"),3)`). At high reliability and moderate sample size results improved but the LMS and QML still showed substantial bias. The LMS showed a relative bias of `r round(get_bias("LMS", "Nonnormal", "beta[5]", 400, 0.8, "Full"),3)` for $\beta_5$ (absolute bias = `r round(get_absolute_bias("LMS", "Nonnormal", "beta[5]", 400, 0.8, "Full"),3)`, RMSE = `r round(get_rmse("LMS", "Nonnormal", "beta[5]", 400, 0.8, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("LMS", "Nonnormal", "beta[5]", 400, 0.8, "Full"),3)`) and QML yielded a relative bias of `r round(get_bias("QML", "Nonnormal", "beta[5]", 400, 0.8, "Full"),3)` (absolute bias = `r round(get_absolute_bias("QML", "Nonnormal", "beta[5]", 400, 0.8, "Full"),3)`, RMSE = `r round(get_rmse("QML", "Nonnormal", "beta[5]", 400, 0.8, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("QML", "Nonnormal", "beta[5]", 400, 0.8, "Full"),3)`).

For the DBLCENT, we observe a similar performance for $\beta_3$ as the distribution analytic approaches, albeit with reduced bias at low reliability (`r round(get_bias("DBLCENT", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)`, absolute bias = `r round(get_absolute_bias("DBLCENT", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("DBLCENT", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("DBLCENT", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)`) compared to medium reliability (`r round(get_bias("DBLCENT", "Nonnormal", "beta[3]", 400, 0.6, "Full"),3)`, absolute bias = `r round(get_absolute_bias("DBLCENT", "Nonnormal", "beta[3]", 400, 0.6, "Full"),3)`, RMSE = `r round(get_rmse("DBLCENT", "Nonnormal", "beta[3]", 400, 0.6, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("DBLCENT", "Nonnormal", "beta[3]", 400, 0.6, "Full"),3)`). However, DBLCENT demonstrated negligible bias for quadratic effects across all conditions.

Last, sample size did not substantially influence bias reduction for either LMS or QML (see Figure 1). Hence, the results for a large sample size follow the interpretations from above, despite possible negligible numerical differences. 

#### Uniform Distribution

Under uniform distributional conditions, the performance somewhat improved for all approaches in comparison to the nonnormal scenario. Yet the LMS, QML, and DBLCENT approaches all exhibited bias for specific nonlinear effects. Specifically, only the DBLCENT showed biased results for the interaction effect, while for the quadratic effects all three approaches were biased. The SAM only showed bias under the case of low reliability for the quadratic terms.

At low reliability and moderate sample size, the relative bias under the DBLCENT for the $\beta_3$ equaled `r round(get_bias("DBLCENT", "Uniform", "beta[3]", 400, 0.4, "Full"),3)` (absolute bias = `r round(get_absolute_bias("DBLCENT", "Uniform", "beta[3]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("DBLCENT", "Uniform", "beta[3]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("DBLCENT", "Uniform", "beta[3]", 400, 0.4, "Full"),3)`). This improved to `r round(get_bias("DBLCENT", "Uniform", "beta[3]", 400, 0.8, "Full"),3)` (absolute bias = `r round(get_absolute_bias("DBLCENT", "Uniform", "beta[3]", 400, 0.8, "Full"),3)`, RMSE = `r round(get_rmse("DBLCENT", "Uniform", "beta[3]", 400, 0.8, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("DBLCENT", "Uniform", "beta[3]", 400, 0.8, "Full"),3)`) at high reliability and moderate sample size.

For the quadratic effects, all approaches exhibited bias at low reliability and moderate sample size. For $\beta_4$ ($\eta_1^2$), SAM demonstrated a relative bias of `r round(get_bias("SAM", "Uniform", "beta[4]", 400, 0.4, "Full"),3)` (absolute bias = `r round(get_absolute_bias("SAM", "Uniform", "beta[4]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("SAM", "Uniform", "beta[4]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("SAM", "Uniform", "beta[4]", 400, 0.4, "Full"),3)`), while LMS, QML, and DBLCENT showed relative biases of `r round(get_bias("LMS", "Uniform", "beta[4]", 400, 0.4, "Full"),3)` (absolute bias = `r round(get_absolute_bias("LMS", "Uniform", "beta[4]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("LMS", "Uniform", "beta[4]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("LMS", "Uniform", "beta[4]", 400, 0.4, "Full"),3)`), `r round(get_bias("QML", "Uniform", "beta[4]", 400, 0.4, "Full"),3)` (absolute bias = `r round(get_absolute_bias("QML", "Uniform", "beta[4]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("QML", "Uniform", "beta[4]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("QML", "Uniform", "beta[4]", 400, 0.4, "Full"),3)`), and `r round(get_bias("DBLCENT", "Uniform", "beta[4]", 400, 0.4, "Full"),3)` (absolute bias = `r round(get_absolute_bias("DBLCENT", "Uniform", "beta[4]", 400, 0.4, "Full"),3)`, RMSE = `r round(get_rmse("DBLCENT", "Uniform", "beta[4]", 400, 0.4, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("DBLCENT", "Uniform", "beta[4]", 400, 0.4, "Full"),3)`), respectively. 

At medium reliability and moderate sample size, only the SAM achieved unbiased estimation (`r round(get_bias("SAM", "Uniform", "beta[4]", 400, 0.6, "Full"),2)`, absolute bias = `r round(get_absolute_bias("SAM", "Uniform", "beta[4]", 400, 0.6, "Full"),3)`, RMSE = `r round(get_rmse("SAM", "Uniform", "beta[4]", 400, 0.6, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("SAM", "Uniform", "beta[4]", 400, 0.6, "Full"),3)`), while LMS and QML showed relative biases of `r round(get_bias("LMS", "Uniform", "beta[4]", 400, 0.6, "Full"),2)` (absolute bias = `r round(get_absolute_bias("LMS", "Uniform", "beta[4]", 400, 0.6, "Full"),3)`, RMSE = `r round(get_rmse("LMS", "Uniform", "beta[4]", 400, 0.6, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("LMS", "Uniform", "beta[4]", 400, 0.6, "Full"),3)`) and `r round(get_bias("QML", "Uniform", "beta[4]", 400, 0.6, "Full"),2)` (absolute bias = `r round(get_absolute_bias("QML", "Uniform", "beta[4]", 400, 0.6, "Full"),3)`, RMSE = `r round(get_rmse("QML", "Uniform", "beta[4]", 400, 0.6, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("QML", "Uniform", "beta[4]", 400, 0.6, "Full"),3)`), respectively. 

At high reliability and moderate sample size, both SAM and DBLCENT produced unbiased estimates with relative biases of `r round(get_bias("SAM", "Uniform", "beta[4]", 400, 0.8, "Full"),2)` (absolute bias = `r round(get_absolute_bias("SAM", "Uniform", "beta[4]", 400, 0.8, "Full"),3)`, RMSE = `r round(get_rmse("SAM", "Uniform", "beta[4]", 400, 0.8, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("SAM", "Uniform", "beta[4]", 400, 0.8, "Full"),3)`) and `r round(get_bias("DBLCENT", "Uniform", "beta[4]", 400, 0.8, "Full"),2)` (absolute bias = `r round(get_absolute_bias("DBLCENT", "Uniform", "beta[4]", 400, 0.8, "Full"),3)`, RMSE = `r round(get_rmse("DBLCENT", "Uniform", "beta[4]", 400, 0.8, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("DBLCENT", "Uniform", "beta[4]", 400, 0.8, "Full"),3)`), respectively. LMS and QML remained biased, showing `r round(get_bias("LMS", "Uniform", "beta[4]", 400, 0.8, "Full"),2)` (absolute bias = `r round(get_absolute_bias("LMS", "Uniform", "beta[4]", 400, 0.8, "Full"),3)`, RMSE = `r round(get_rmse("LMS", "Uniform", "beta[4]", 400, 0.8, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("LMS", "Uniform", "beta[4]", 400, 0.8, "Full"),3)`) and `r round(get_bias("QML", "Uniform", "beta[4]", 400, 0.8, "Full"),2)` (absolute bias = `r round(get_absolute_bias("QML", "Uniform", "beta[4]", 400, 0.8, "Full"),3)`, RMSE = `r round(get_rmse("QML", "Uniform", "beta[4]", 400, 0.8, "Full"),3)`, relative RMSE = `r round(get_relative_rmse("QML", "Uniform", "beta[4]", 400, 0.8, "Full"),3)`). The quadratic term $\beta_5$ ($\eta_2^2$) exhibited qualitatively identical patterns.

These patterns largely persisted regardless of sample size increases, with the exception of one case for the DBLCENT. Indeed, for $\beta_5$, this approach performed well across reliability levels in the case of moderate sample size. With a high sample size, however, biased results were obtained. 

### Bias When Nonlinear Effects Were Not Present

As shown in Figure 1, the bias results are somewhat similar when the nonlinear effects were present (full model) and not present (linear model), but overall with decreased magnitude. There are two main differences worth nothing. Under normally distributed latent variables, the bias in this case is smaller than in the case of the full model for all approaches. Moreover, for the uniform condition, the DBLCENT, LMS and QML showed little bias in contrast to before. Hence, the approaches are more homogeneous.

```{r plot-bias, echo=FALSE, fig.cap = "Absolute bias.", fig.align='center', fig.height=11, fig.width=9}
(p_bias)
```

```{r plot-rmse, echo=FALSE, fig.cap = "Root Mean Squared Error.", fig.align='center', fig.height=11, fig.width=9}
(p_rmse)
```

```{r ratio, echo=FALSE}
library(dplyr)
library(ggplot2)

# data for both models
dat_sesd2 <- bind_rows(
  prep_nonlinear(results_with_mcse, model = "Linear") %>% mutate(Model = "Linear"),
  prep_nonlinear(results_with_mcse, model = "Full") %>% mutate(Model = "Full")
) %>%
  mutate(Model = factor(Model, levels = c("Linear", "Full"))) %>%
  transmute(Distribution, Parameter, SampleSize, Reliability, Method, Model,
            ratio = SE_SD_Ratio)

shapes <- c(SAM=16, LMS=17, QML=15, DBLCENT=18)
ltys <- c(SAM="solid", LMS="dashed", QML="dotdash", DBLCENT="twodash")

p_slope <- ggplot(dat_sesd2,
                  aes(x = Reliability, y = ratio, group = Method,
                      shape = Method, linetype = Method)) +
  geom_hline(yintercept = 1, linetype = "dashed") +
  geom_line(aes(y = pmax(pmin(ratio, 1.6), 0.85)), 
            color = "black", position = position_dodge(width = 0.0)) +
  geom_point(aes(y = pmax(pmin(ratio, 1.6), 0.85)),
             color = "black", size = 2, position = position_dodge(width = 0.0)) +
  # Add text labels for values above 1.6
  geom_text(data = filter(dat_sesd2, ratio > 1.6) %>%
              group_by(Distribution, Parameter, Model, SampleSize, Reliability) %>%
              arrange(desc(ratio)) %>%
              mutate(label_y = 1.59 - (row_number() - 1) * 0.8), 
            aes(label = sprintf("%s: %.2f", Method, ratio),
                y = label_y),
            size = 1.5, hjust = 0, vjust = 1) +
  # Add text labels for values below 0.85
  geom_text(data = filter(dat_sesd2, ratio < 0.85) %>%
              group_by(Distribution, Parameter, Model, SampleSize, Reliability) %>%
              arrange(ratio) %>%
              mutate(label_y = 0.86 + (row_number() - 1) * 0.8), 
            aes(label = sprintf("%s: %.2f", Method, ratio),
                y = label_y),
            size = 1.5, hjust = 0, vjust = 0) +
  scale_shape_manual(values = shapes) +
  scale_linetype_manual(values = ltys) +
  facet_grid(Distribution + Parameter ~ Model + SampleSize,
             labeller = labeller(SampleSize = label_value,
                                 Parameter = label_parsed)) +
  coord_cartesian(ylim = c(0.85, 1.6)) +  # Zoom to reasonable range
  labs(x = "Reliability", y = "SE / SD",
       title = "") +
  theme_apa_bw()

# Update get_ratio function to include model parameter
get_ratio <- function(method, dist, param, n, rel, model = c("Full", "Linear")) {
  model <- match.arg(model)
  dat_sesd2 %>%
    filter(Method == method,
           Distribution == dist,
           Parameter == param,
           SampleSize == n,
           Reliability == rel,
           Model == model) %>%
    pull(ratio)
}

```

### Efficiency and Accuracy of Standard Errors when Nonlinear Effects were present

Figure 3 shows the computed SE/SD ratios under both linear and full models. Note that for some approaches, under specific conditions, the exact values are shown due to large discrepancies between approaches. 

#### Normal Distribution

Under normal distributional conditions with the full model specification, LMS and QML maintained near-optimal efficiency across most reliability levels. The SAM showed negligible overestimation in the case of low reliability and moderate sample size, while the same overestimation is observed for the DBLCENT but in this case with a larger magnitude across sample sizes. Given that in the case of a large sample size the performance remains again similar to that of moderate sample sizes, we only report the results for the latter case. 

For the interaction parameter ($\beta_3$) at low reliability and moderate sample size, the LMS achieved a ratio of `r round(get_ratio("LMS", "Normal", "beta[3]", 400, 0.4, "Full"),3)` and QML yielded `r round(get_ratio("QML", "Normal", "beta[3]", 400, 0.4, "Full"),3)`. The SAM approach obtained a ratio of `r round(get_ratio("SAM", "Normal", "beta[3]", 400, 0.4, "Full"),2)`, while DBLCENT showed an overestimation at `r round(get_ratio("DBLCENT", "Normal", "beta[3]", 400, 0.4, "Full"),2)`. At medium reliability and moderate sample size, all methods converged toward unity, with SAM improving to `r round(get_ratio("SAM", "Normal", "beta[3]", 400, 0.6, "Full"),3)`, LMS at `r round(get_ratio("LMS", "Normal", "beta[3]", 400, 0.6, "Full"),3)`, QML at `r round(get_ratio("QML", "Normal", "beta[3]", 400, 0.6, "Full"),3)`, and DBLCENT at `r round(get_ratio("DBLCENT", "Normal", "beta[3]", 400, 0.6, "Full"),2)`. At high reliability and moderate sample size, the methods achieved near-optimal performance, with ratios ranging from `r round(get_ratio("SAM", "Normal", "beta[3]", 400, 0.8, "Full"),3)` (SAM) to `r round(get_ratio("LMS", "Normal", "beta[3]", 400, 0.8, "Full"),3)` (LMS).

The quadratic effects ($\beta_4$ and $\beta_5$) exhibited similar patterns. For $\beta_4$ at low reliability and moderate sample size, ratios were `r round(get_ratio("SAM", "Normal", "beta[4]", 400, 0.4, "Full"),2)` (SAM), `r round(get_ratio("LMS", "Normal", "beta[4]", 400, 0.4, "Full"),3)` (LMS), `r round(get_ratio("QML", "Normal", "beta[4]", 400, 0.4, "Full"),3)` (QML), and `r round(get_ratio("DBLCENT", "Normal", "beta[4]", 400, 0.4, "Full"),2)` (DBLCENT). For $\beta_5$, the corresponding values were `r round(get_ratio("SAM", "Normal", "beta[5]", 400, 0.4, "Full"),2)` (SAM), `r round(get_ratio("LMS", "Normal", "beta[5]", 400, 0.4, "Full"),3)` (LMS), `r round(get_ratio("QML", "Normal", "beta[5]", 400, 0.4, "Full"),3)` (QML), and `r round(get_ratio("DBLCENT", "Normal", "beta[5]", 400, 0.4, "Full"),2)` (DBLCENT). Thus, the DBLCENT consistently showed the largest overestimation of standard errors in low reliability conditions, with ratios exceeding 1.5 for all nonlinear parameters.

#### Nonnormal Distribution

Nonnormal distributional conditions revealed more pronounced differences between approaches. In this case, however, sample size had a larger influence.

SAM's efficiency deteriorated at low reliability and moderated sample size, with the interaction effect ratio increasing to `r round(get_ratio("SAM", "Nonnormal", "beta[3]", 400, 0.4, "Full"),2)`. This pattern was more extreme for $\beta_5$, reaching `r round(get_ratio("SAM", "Nonnormal", "beta[5]", 400, 0.4, "Full"),2)`. LMS maintained a stable performance with a ratio of `r round(get_ratio("LMS", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)` for $\beta_3$, but QML exhibited underestimation at `r round(get_ratio("QML", "Nonnormal", "beta[3]", 400, 0.4, "Full"),3)`. DBLCENT demonstrated severe inefficiency under these conditions, with ratios of `r round(get_ratio("DBLCENT", "Nonnormal", "beta[3]", 400, 0.4, "Full"),2)` ($\beta_3$), `r round(get_ratio("DBLCENT", "Nonnormal", "beta[4]", 400, 0.4, "Full"),2)` ($\beta_4$), and `r round(get_ratio("DBLCENT", "Nonnormal", "beta[5]", 400, 0.4, "Full"),2)` ($\beta_5$).

Increasing to a large sample size substantially improved DBLCENT's performance at low reliability, reducing ratios to `r round(get_ratio("DBLCENT", "Nonnormal", "beta[3]", 1000, 0.4, "Full"),2)` ($\beta_3$), `r round(get_ratio("DBLCENT", "Nonnormal", "beta[4]", 1000, 0.4, "Full"),2)` ($\beta_4$), and `r round(get_ratio("DBLCENT", "Nonnormal", "beta[5]", 1000, 0.4, "Full"),2)` ($\beta_5$), though these values still indicated overestimation. SAM achieved optimal efficiency (`r round(get_ratio("SAM", "Nonnormal", "beta[3]", 1000, 0.4, "Full"),3)` for $\beta_3$), while LMS maintained it as well (`r round(get_ratio("LMS", "Nonnormal", "beta[3]", 1000, 0.4, "Full"),3)`). QML continued to show underestimation, with ratios of `r round(get_ratio("QML", "Nonnormal", "beta[3]", 1000, 0.4, "Full"),3)` ($\beta_3$), `r round(get_ratio("QML", "Nonnormal", "beta[4]", 1000, 0.4, "Full"),3)` ($\beta_4$), and `r round(get_ratio("QML", "Nonnormal", "beta[5]", 1000, 0.4, "Full"),3)` ($\beta_5$).

#### Uniform Distribution

With the exception of the DBLCENT and SAM, the other approaches showed decent results throughout reliability levels and sample sizes. Specifically, the SAM yet again struggled in the case of low reliability and moderate sample size. Again, results are focused only on the case of moderate sample size. 

Indeed, at low reliability and moderate sample size, the SAM showed ratios of `r round(get_ratio("SAM", "Uniform", "beta[3]", 400, 0.4, "Full"),2)` ($\beta_3$), `r round(get_ratio("SAM", "Uniform", "beta[4]", 400, 0.4, "Full"),2)` ($\beta_4$), and `r round(get_ratio("SAM", "Uniform", "beta[5]", 400, 0.4, "Full"),2)` ($\beta_5$). DBLCENT exhibited a ratio of `r round(get_ratio("DBLCENT", "Uniform", "beta[3]", 400, 0.4, "Full"),1)` for the interaction term, and the quadratic terms showed overestimation at `r round(get_ratio("DBLCENT", "Uniform", "beta[4]", 400, 0.4, "Full"),2)` ($\beta_4$) and `r round(get_ratio("DBLCENT", "Uniform", "beta[5]", 400, 0.4, "Full"),2)` ($\beta_5$). LMS and QML maintained reasonable efficiency, with LMS showing ratios of `r round(get_ratio("LMS", "Uniform", "beta[3]", 400, 0.4, "Full"),3)`, `r round(get_ratio("LMS", "Uniform", "beta[4]", 400, 0.4, "Full"),2)`, and `r round(get_ratio("LMS", "Uniform", "beta[5]", 400, 0.4, "Full"),3)`, while QML yielded `r round(get_ratio("QML", "Uniform", "beta[3]", 400, 0.4, "Full"),3)`, `r round(get_ratio("QML", "Uniform", "beta[4]", 400, 0.4, "Full"),2)`, and `r round(get_ratio("QML", "Uniform", "beta[5]", 400, 0.4, "Full"),3)` for $\beta_3$, $\beta_4$, and $\beta_5$ respectively.

At medium reliability and moderate sample size, improvements occurred across all methods, but the most significant were for the DBLCENT approach. SAM achieved ratios of `r round(get_ratio("SAM", "Uniform", "beta[3]", 400, 0.6, "Full"),3)` ($\beta_3$), `r round(get_ratio("SAM", "Uniform", "beta[4]", 400, 0.6, "Full"),3)` ($\beta_4$), and `r round(get_ratio("SAM", "Uniform", "beta[5]", 400, 0.6, "Full"),3)` ($\beta_5$), approaching the efficiency of LMS and QML. DBLCENT improved dramatically to `r round(get_ratio("DBLCENT", "Uniform", "beta[3]", 400, 0.6, "Full"),3)`, `r round(get_ratio("DBLCENT", "Uniform", "beta[4]", 400, 0.6, "Full"),3)`, and `r round(get_ratio("DBLCENT", "Uniform", "beta[5]", 400, 0.6, "Full"),3)` for the respective parameters. At high reliability, all methods demonstrated near-optimal performance, with SAM showing ratios of `r round(get_ratio("SAM", "Uniform", "beta[3]", 400, 0.8, "Full"),2)` ($\beta_3$), `r round(get_ratio("SAM", "Uniform", "beta[4]", 400, 0.8, "Full"),2)` ($\beta_4$), and `r round(get_ratio("SAM", "Uniform", "beta[5]", 400, 0.8, "Full"),3)` ($\beta_5$), while DBLCENT achieved `r round(get_ratio("DBLCENT", "Uniform", "beta[3]", 400, 0.8, "Full"),2)`, `r round(get_ratio("DBLCENT", "Uniform", "beta[4]", 400, 0.8, "Full"),3)`, and `r round(get_ratio("DBLCENT", "Uniform", "beta[5]", 400, 0.8, "Full"),3)`.

### Efficiency and Accuracy of Standard Errors When Nonlinear Effects Were Not Present

The linear model specification generally showed improved accuracy compared to the full model, particularly for DBLCENT under nonnormal conditions. For instance, under nonnormal conditions with medium reliability and moderate sample size, DBLCENT's ratio for $\beta_3$ was `r round(get_ratio("DBLCENT", "Nonnormal", "beta[3]", 400, 0.6, "Linear"),2)` in the linear model compared to `r round(get_ratio("DBLCENT", "Nonnormal", "beta[3]", 400, 0.6, "Full"),2)` in the full model. However, the relative performance ordering remained consistent, with LMS and QML providing the most efficient standard error estimates, followed by SAM, and DBLCENT showing the greatest sensitivity to adverse conditions.

```{r coverage, echo=FALSE}
dat_cov <- bind_rows(
  prep_nonlinear(results_with_mcse, model = "Linear") %>% mutate(Model = "Linear"),
  prep_nonlinear(results_with_mcse, model = "Full")   %>% mutate(Model = "Full")
) %>%
  mutate(Model = factor(Model, levels = c("Linear", "Full"))) %>%
  transmute(Distribution, Parameter, SampleSize, Reliability, Method, Model,
            y = CoverageRate, yerr = 100*CoverageRate_MCSE)

p_cov <- ggplot(
  dat_cov,
  aes(x = Reliability, y = y, shape = Method, linetype = Method, group = Method)
) +
  annotate("rect", xmin = -Inf, xmax = Inf, ymin = 93, ymax = 97,
           fill = "grey93", alpha = .9) +
  geom_pointrange(aes(ymin = pmax(y - yerr, 80), 
                      ymax = pmin(y + yerr, 100)),
                  position = position_dodge(width = .6), color = "black") +
  geom_line(aes(y = pmax(y, 80)), position = position_dodge(width = .6), color = "black") +
  # Add text labels for values below 80% with smart positioning
  geom_text(data = filter(dat_cov, y < 80) %>%
              group_by(Distribution, Parameter, Model, SampleSize, Reliability) %>%
              arrange(Method) %>%
              mutate(label_y = 81 + (row_number() - 1) * 2.5), # Stack labels vertically
            aes(label = sprintf("%s: %.0f%%", Method, y),
                y = label_y),
            size = 1.5, hjust = 0, vjust = 0) +
  geom_hline(yintercept = 95, linetype = "dotted") +
  scale_shape_manual(values = shapes) +
  scale_linetype_manual(values = ltys) +
  facet_grid(Distribution + Parameter ~ Model + SampleSize,
             labeller = labeller(SampleSize = label_value,
                                 Parameter = label_parsed)) +
  coord_cartesian(ylim = c(80, 100)) +
  labs(x = "Reliability", y = "Coverage (%)", title = "") +
  theme_apa_bw()

get_coverage <- function(method, dist, param, n, rel, model = c("Full", "Linear")) {
  model <- match.arg(model)
  dat_cov %>%
    filter(Method == method,
           Distribution == dist,
           Parameter == param,
           SampleSize == n,
           Reliability == rel,
           Model == model) %>%
    pull(y)
}
```

### Coverage for When Nonlinear Effects Were Present

Figure 4 contains the visualization of the results reported here. Note that here as well for some approaches, under specific conditions, the exact values are shown.

#### Normal Distribution

Under normal distributional conditions with the full model, in general, all methods demonstrated adequate coverage levels. Note once more the results are focused on the moderate sample size condition. 

At low reliability and moderate sample size, some approaches had difficulties. For instance, SAM showed some overcoverage for the interaction parameter ($\beta_3$) at `r round(get_coverage("SAM", "Normal", "beta[3]", 400, 0.4, "Full"),1)`%, while LMS and QML achieved `r round(get_coverage("LMS", "Normal", "beta[3]", 400, 0.4, "Full"),1)`% and `r round(get_coverage("QML", "Normal", "beta[3]", 400, 0.4, "Full"),1)`%, respectively. DBLCENT showed also overcoverage at `r round(get_coverage("DBLCENT", "Normal", "beta[3]", 400, 0.4, "Full"),1)`%. For quadratic parameters under these conditions, coverage rates were `r round(get_coverage("SAM", "Normal", "beta[4]", 400, 0.4, "Full"),1)`% (SAM), `r round(get_coverage("LMS", "Normal", "beta[4]", 400, 0.4, "Full"),1)`% (LMS), `r round(get_coverage("QML", "Normal", "beta[4]", 400, 0.4, "Full"),1)`% (QML), and `r round(get_coverage("DBLCENT", "Normal", "beta[4]", 400, 0.4, "Full"),1)`% (DBLCENT) for $\beta_4$, with similar patterns for $\beta_5$. At medium reliability and moderate sample size, coverage converged toward nominal levels. Indeed, SAM achieved `r round(get_coverage("SAM", "Normal", "beta[3]", 400, 0.6, "Full"),1)`% coverage for $\beta_3$, while LMS, QML, and DBLCENT yielded `r round(get_coverage("LMS", "Normal", "beta[3]", 400, 0.6, "Full"),1)`%, `r round(get_coverage("QML", "Normal", "beta[3]", 400, 0.6, "Full"),1)`%, and `r round(get_coverage("DBLCENT", "Normal", "beta[3]", 400, 0.6, "Full"),1)`%, respectively. At high reliability and moderate sample size, all methods maintained near-nominal coverage.

#### Nonnormal Distribution

Nonnormal distributional conditions revealed dramatic coverage failures for distribution analytic methods.

At low reliability and moderate sample size, while SAM maintained a coverage of `r round(get_coverage("SAM", "Nonnormal", "beta[3]", 400, 0.4, "Full"),1)`% for $\beta_3$, LMS coverage dropped to `r round(get_coverage("LMS", "Nonnormal", "beta[3]", 400, 0.4, "Full"),1)`% and QML to `r round(get_coverage("QML", "Nonnormal", "beta[3]", 400, 0.4, "Full"),1)`%. DBLCENT maintained reasonable coverage at `r round(get_coverage("DBLCENT", "Nonnormal", "beta[3]", 400, 0.4, "Full"),1)`%. The coverage degradation was even more severe for quadratic parameters, with LMS achieving only `r round(get_coverage("LMS", "Nonnormal", "beta[4]", 400, 0.4, "Full"),1)`% for $\beta_4$ and `r round(get_coverage("LMS", "Nonnormal", "beta[5]", 400, 0.4, "Full"),1)`% for $\beta_5$. QML showed substantial failure with coverage rates of `r round(get_coverage("QML", "Nonnormal", "beta[4]", 400, 0.4, "Full"),1)`% and `r round(get_coverage("QML", "Nonnormal", "beta[5]", 400, 0.4, "Full"),1)`% for the quadratic terms. At medium reliability and moderate sample size, SAM continued to demonstrate robust performance with `r round(get_coverage("SAM", "Nonnormal", "beta[3]", 400, 0.6, "Full"),1)`% coverage for $\beta_3$. LMS showed modest improvement to `r round(get_coverage("LMS", "Nonnormal", "beta[3]", 400, 0.6, "Full"),1)`%, though quadratic parameters remained problematic at `r round(get_coverage("LMS", "Nonnormal", "beta[4]", 400, 0.6, "Full"),1)`% ($\beta_4$) and `r round(get_coverage("LMS", "Nonnormal", "beta[5]", 400, 0.6, "Full"),1)`% ($\beta_5$). QML coverage was `r round(get_coverage("QML", "Nonnormal", "beta[3]", 400, 0.6, "Full"),1)`% for the interaction term but deteriorated to `r round(get_coverage("QML", "Nonnormal", "beta[4]", 400, 0.6, "Full"),1)`% and `r round(get_coverage("QML", "Nonnormal", "beta[5]", 400, 0.6, "Full"),1)`% for quadratic terms. For high reliability and moderate sample size, coverage results were better for $\beta_3$, but not necessarily for the quadratic effects. 

Increasing to a large sample size at low reliability provided limited improvement for the distribution analytic methods. LMS coverage for $\beta_3$ remained poor at `r round(get_coverage("LMS", "Nonnormal", "beta[3]", 1000, 0.4, "Full"),1)`%, while quadratic parameters showed extreme undercoverage at `r round(get_coverage("LMS", "Nonnormal", "beta[4]", 1000, 0.4, "Full"),1)`% ($\beta_4$) and `r round(get_coverage("LMS", "Nonnormal", "beta[5]", 1000, 0.4, "Full"),1)`% ($\beta_5$). QML demonstrated even worse performance with `r round(get_coverage("QML", "Nonnormal", "beta[3]", 1000, 0.4, "Full"),1)`% coverage for $\beta_3$ and `r round(get_coverage("QML", "Nonnormal", "beta[4]", 1000, 0.4, "Full"),1)`% and `r round(get_coverage("QML", "Nonnormal", "beta[5]", 1000, 0.4, "Full"),1)`% for the quadratic terms. SAM maintained robust coverage at `r round(get_coverage("SAM", "Nonnormal", "beta[3]", 1000, 0.4, "Full"),1)`%, while the DBLCENT achieved an desirable coverage of `r round(get_coverage("DBLCENT", "Nonnormal", "beta[3]", 1000, 0.4, "Full"),1)`%.

#### Uniform Distribution

Under uniform distributional conditions, distinct patterns emerged compared to the previous cases.

At low reliability and moderate sample size, SAM showed overcoverage at `r round(get_coverage("SAM", "Uniform", "beta[3]", 400, 0.4, "Full"),1)`% for $\beta_3$ and `r round(get_coverage("SAM", "Uniform", "beta[4]", 400, 0.4, "Full"),1)`% and `r round(get_coverage("SAM", "Uniform", "beta[5]", 400, 0.4, "Full"),1)`% for the quadratic terms. LMS and QML maintained reasonable coverage for the interaction term (`r round(get_coverage("LMS", "Uniform", "beta[3]", 400, 0.4, "Full"),1)`% and `r round(get_coverage("QML", "Uniform", "beta[3]", 400, 0.4, "Full"),1)`%, respectively) but showed undercoverage for quadratic parameters, with LMS at `r round(get_coverage("LMS", "Uniform", "beta[4]", 400, 0.4, "Full"),1)`% ($\beta_4$) and `r round(get_coverage("LMS", "Uniform", "beta[5]", 400, 0.4, "Full"),1)`% ($\beta_5$), and QML at `r round(get_coverage("QML", "Uniform", "beta[4]", 400, 0.4, "Full"),1)`% and `r round(get_coverage("QML", "Uniform", "beta[5]", 400, 0.4, "Full"),1)`%. DBLCENT demonstrated mixed performance with `r round(get_coverage("DBLCENT", "Uniform", "beta[3]", 400, 0.4, "Full"),1)`% for $\beta_3$, `r round(get_coverage("DBLCENT", "Uniform", "beta[4]", 400, 0.4, "Full"),1)`% for $\beta_4$ and `r round(get_coverage("DBLCENT", "Uniform", "beta[5]", 400, 0.4, "Full"),1)`% for $\beta_5$.

At medium reliability and moderate sample size, substantial improvements occurred. SAM achieved `r round(get_coverage("SAM", "Uniform", "beta[3]", 400, 0.6, "Full"),1)`% coverage for $\beta_3$, with `r round(get_coverage("SAM", "Uniform", "beta[4]", 400, 0.6, "Full"),1)`% and `r round(get_coverage("SAM", "Uniform", "beta[5]", 400, 0.6, "Full"),1)`% for quadratic terms. LMS and QML continued to show undercoverage for quadratic parameters, with LMS at `r round(get_coverage("LMS", "Uniform", "beta[4]", 400, 0.6, "Full"),1)`% ($\beta_4$) and `r round(get_coverage("LMS", "Uniform", "beta[5]", 400, 0.6, "Full"),1)`% ($\beta_5$), while QML achieved `r round(get_coverage("QML", "Uniform", "beta[4]", 400, 0.6, "Full"),1)`% and `r round(get_coverage("QML", "Uniform", "beta[5]", 400, 0.6, "Full"),1)`%. DBLCENT showed improved coverage at `r round(get_coverage("DBLCENT", "Uniform", "beta[3]", 400, 0.6, "Full"),1)`%, `r round(get_coverage("DBLCENT", "Uniform", "beta[4]", 400, 0.6, "Full"),1)`%, and `r round(get_coverage("DBLCENT", "Uniform", "beta[5]", 400, 0.6, "Full"),1)`% for the respective parameters.

At high reliability and moderate sample size, coverage generally improved across all methods. SAM achieved `r round(get_coverage("SAM", "Uniform", "beta[3]", 400, 0.8, "Full"),1)`% for $\beta_3$, while LMS and QML reached `r round(get_coverage("LMS", "Uniform", "beta[3]", 400, 0.8, "Full"),1)`% and `r round(get_coverage("QML", "Uniform", "beta[3]", 400, 0.8, "Full"),1)`%, respectively. The quadratic parameters showed for LMS (`r round(get_coverage("LMS", "Uniform", "beta[4]", 400, 0.8, "Full"),1)`% and `r round(get_coverage("LMS", "Uniform", "beta[5]", 400, 0.8, "Full"),1)`%) and QML (`r round(get_coverage("QML", "Uniform", "beta[4]", 400, 0.8, "Full"),1)`% and `r round(get_coverage("QML", "Uniform", "beta[5]", 400, 0.8, "Full"),1)`%).

With increased sample size at low reliability, the SAM had coverage at `r round(get_coverage("SAM", "Uniform", "beta[3]", 1000, 0.4, "Full"),1)`% for $\beta_3$, while LMS and QML showed severe undercoverage for quadratic parameters at `r round(get_coverage("LMS", "Uniform", "beta[4]", 1000, 0.4, "Full"),1)`% and `r round(get_coverage("LMS", "Uniform", "beta[5]", 1000, 0.4, "Full"),1)`% (LMS), and `r round(get_coverage("QML", "Uniform", "beta[4]", 1000, 0.4, "Full"),1)`% and `r round(get_coverage("QML", "Uniform", "beta[5]", 1000, 0.4, "Full"),1)`% (QML). DBLCENT improved to `r round(get_coverage("DBLCENT", "Uniform", "beta[3]", 1000, 0.4, "Full"),1)`% for the interaction term but maintained inadequate coverage for quadratic parameters.

### Coverage When Nonlinear Effects Were Not Present

The linear model specification showed differential effects on coverage performance. Under nonnormal conditions, the linear model often provided better coverage than the full model for DBLCENT, though distribution analytic methods continued to show poor performance. For instance, at moderate sample size and medium reliability, under nonnormal conditions, DBLCENT achieved `r round(get_coverage("DBLCENT", "Nonnormal", "beta[3]", 400, 0.6, "Linear"),1)`% coverage in the linear model compared to `r round(get_coverage("DBLCENT", "Nonnormal", "beta[3]", 400, 0.6, "Full"),1)`% in the full model.

```{r plot-ratio, echo=FALSE, fig.cap="SE/SD Ratio.", fig.align='center', fig.height=12, fig.width=8}
(p_slope)
```

```{r plot-coverage, echo=FALSE, fig.cap="Coverage.", fig.align='center', fig.height=12, fig.width=8}
(p_cov)
```

```{r type, echo=FALSE, fig.align='center', fig.height=12, fig.width=9}

# --- TYPE I (grayscale bars, thin dotted line @ 5%, no x-axis labels) ---
dat_t1 <- prep_nonlinear(results_with_mcse, model = "Linear") %>%
  transmute(Distribution, Parameter, Condition, Method,
            y = TypeI_Error)

ymax_t1 <- max(dat_t1$y, na.rm = TRUE) * 1.15  # Add 15% headroom for labels

p_t1 <- ggplot(dat_t1, aes(x = Method, y = y, fill = Method)) +
  annotate("rect", xmin = -Inf, xmax = Inf, ymin = 3, ymax = 7,
           fill = "grey92", alpha = .9) +
  geom_col(position = position_dodge(width = 0.9), width = 0.75, color = "black") +
  geom_text(aes(label = sprintf("%.1f", y)), vjust = -0.4, size = 3) +
  geom_hline(yintercept = 5, linetype = "dotted", linewidth = 0.3) +
  facet_grid(Distribution + Parameter ~ Condition,
             labeller = labeller(Parameter = label_parsed)) +
  scale_fill_manual(values = GREYS_METHOD) +
  coord_cartesian(ylim = c(0, ymax_t1)) +
  labs(x = NULL, y = "Type I error (%)",
       title = "") +
  theme_apa_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.title = element_blank())


get_type <- function(method, dist, param, cond) {
  dat_t1 %>%
    filter(Method == method,
           Distribution == dist,
           Parameter == param,
           Condition == cond) %>%
    select(y)
}
```

```{r power, echo=FALSE, fig.align='center', fig.height=12, fig.width=9}
# --- POWER (grayscale bars, thin dotted line @ 80%, no x-axis labels) ---
dat_pow <- prep_nonlinear(results_with_mcse, model = "Full") %>%
  transmute(Distribution, Parameter, Condition, Method,
            y = Power)

# y-axis to go to 110 to accommodate labels at 100%
ymax_pow <- 110  

p_pow <- ggplot(dat_pow, aes(x = Method, y = y, fill = Method)) +
  geom_col(position = position_dodge(width = 0.9), width = 0.75, color = "black") +
  geom_text(aes(label = sprintf("%.0f", y)), vjust = -0.4, size = 3) +
  geom_hline(yintercept = 80, linetype = "dotted", linewidth = 0.3) +
  facet_grid(Distribution + Parameter ~ Condition,
             labeller = labeller(Parameter = label_parsed)) +
  scale_fill_manual(values = GREYS_METHOD) +
  coord_cartesian(ylim = c(0, ymax_pow)) +
  labs(x = NULL, y = "Power (%)",
       title = "") +
  theme_apa_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.title = element_blank())

get_power <- function(method, dist, param, cond) {
  dat_pow %>%
    filter(Method == method,
           Distribution == dist,
           Parameter == param,
           Condition == cond) %>%
    select(y)
}
```

### Type I Error Control

Figure 5 illustrates the type I error rates across approaches and conditions.

#### Normal Distribution

Under normal distributional conditions, SAM and DBLCENT demonstrated the most conservative performances.

At low reliability and moderate sample size, SAM showed Type I error rates of `r round(get_type("SAM", "Normal", "beta[3]", "N=400, Rel=0.4"),2)`% for $\beta_3$, `r round(get_type("SAM", "Normal", "beta[4]", "N=400, Rel=0.4"),2)`% for $\beta_4$, and `r round(get_type("SAM", "Normal", "beta[5]", "N=400, Rel=0.4"),2)`% for $\beta_5$. DBLCENT was even more conservative with rates of `r round(get_type("DBLCENT", "Normal", "beta[3]", "N=400, Rel=0.4"),3)`%, `r round(get_type("DBLCENT", "Normal", "beta[4]", "N=400, Rel=0.4"),2)`%, and `r round(get_type("DBLCENT", "Normal", "beta[5]", "N=400, Rel=0.4"),2)`% for the respective parameters. In contrast, LMS and QML maintained similar rates closer to nominal levels, with LMS showing `r round(get_type("LMS", "Normal", "beta[3]", "N=400, Rel=0.4"),2)`%, `r round(get_type("LMS", "Normal", "beta[4]", "N=400, Rel=0.4"),2)`%, and `r round(get_type("LMS", "Normal", "beta[5]", "N=400, Rel=0.4"),2)`%. At medium reliability and moderate sample size, all methods achieved acceptable Type I error control. DBLCENT showed a coverage of `r round(get_type("DBLCENT", "Normal", "beta[5]", "N=400, Rel=0.6"),2)`%, SAM showed `r round(get_type("SAM", "Normal", "beta[3]", "N=400, Rel=0.6"),2)`%, LMS `r round(get_type("LMS", "Normal", "beta[3]", "N=400, Rel=0.6"),2)`% and QML `r round(get_type("QML", "Normal", "beta[3]", "N=400, Rel=0.6"),2)`%. At high reliability and moderate sample size, all approaches maintained rates within acceptable bounds of the nominal 5% level.

With a large sample size and low reliability, DBLCENT revealed persistent conservativeness, with Type I error rates of `r round(get_type("DBLCENT", "Normal", "beta[3]", "N=1000, Rel=0.4"),3)`% ($\beta_3$), `r round(get_type("DBLCENT", "Normal", "beta[4]", "N=1000, Rel=0.4"),3)`% ($\beta_4$), and `r round(get_type("DBLCENT", "Normal", "beta[5]", "N=1000, Rel=0.4"),3)`% ($\beta_5$). SAM showed improved but still suboptimal rates of `r round(get_type("SAM", "Normal", "beta[3]", "N=1000, Rel=0.4"),2)`%, `r round(get_type("SAM", "Normal", "beta[4]", "N=1000, Rel=0.4"),2)`%, and `r round(get_type("SAM", "Normal", "beta[5]", "N=1000, Rel=0.4"),2)`% for the same respective estimates.

#### Nonnormal Distribution

Nonnormal distributional conditions revealed markedly different patterns.

At low reliability and moderate sample size, for the interaction term ($\beta_3$), SAM and DBLCENT remained conservative (`r round(get_type("SAM", "Nonnormal", "beta[3]", "N=400, Rel=0.4"),2)`% and `r round(get_type("DBLCENT", "Nonnormal", "beta[3]", "N=400, Rel=0.4"),3)`%, respectively), while LMS and QML showed desirable rates of `r round(get_type("LMS", "Nonnormal", "beta[3]", "N=400, Rel=0.4"),2)`% and `r round(get_type("QML", "Nonnormal", "beta[3]", "N=400, Rel=0.4"),2)`%. However, for quadratic parameters, LMS and QML exhibited severe inflation, with LMS showing `r round(get_type("LMS", "Nonnormal", "beta[4]", "N=400, Rel=0.4"),1)`% ($\beta_4$) and `r round(get_type("LMS", "Nonnormal", "beta[5]", "N=400, Rel=0.4"),1)`% ($\beta_5$), while QML reached `r round(get_type("QML", "Nonnormal", "beta[4]", "N=400, Rel=0.4"),1)`% and `r round(get_type("QML", "Nonnormal", "beta[5]", "N=400, Rel=0.4"),1)`%. At medium reliability and moderate sample size, quadratic effects inflation persisted for distribution-analytic methods. LMS showed rates of `r round(get_type("LMS", "Nonnormal", "beta[4]", "N=400, Rel=0.6"),2)`% and `r round(get_type("LMS", "Nonnormal", "beta[5]", "N=400, Rel=0.6"),2)`% for quadratic terms, while QML reached `r round(get_type("QML", "Nonnormal", "beta[4]", "N=400, Rel=0.6"),1)`% and `r round(get_type("QML", "Nonnormal", "beta[5]", "N=400, Rel=0.6"),2)`%.

At low reliability and large sample size, the inflation for quadratic terms worsened dramatically. LMS showed Type I error rates of `r round(get_type("LMS", "Nonnormal", "beta[4]", "N=1000, Rel=0.4"),1)`% ($\beta_4$) and `r round(get_type("LMS", "Nonnormal", "beta[5]", "N=1000, Rel=0.4"),1)`% ($\beta_5$), while QML exhibited `r round(get_type("QML", "Nonnormal", "beta[4]", "N=1000, Rel=0.4"),1)`% and `r round(get_type("QML", "Nonnormal", "beta[5]", "N=1000, Rel=0.4"),1)`%. Notably, SAM performed optimally for the interaction term at `r round(get_type("SAM", "Nonnormal", "beta[3]", "N=1000, Rel=0.4"),2)`%, demonstrating its robustness. Even at high reliability, LMS maintained inflated rates of `r round(get_type("LMS", "Nonnormal", "beta[4]", "N=1000, Rel=0.8"),1)`% and `r round(get_type("LMS", "Nonnormal", "beta[5]", "N=1000, Rel=0.8"),2)`%.

#### Uniform Distribution

Under uniform distributions, Type I error control was generally adequate except for low reliability conditions. Results were similar qualitatively as under normal distributional conditions. Here the main factor affecting the performance was the reliability as there are no major differences observed with increasing sample size, hence only results for the moderate sample size are reported. 

At low reliability and moderate sample size, SAM showed extreme conservativeness for quadratic terms with rates of `r round(get_type("SAM", "Uniform", "beta[4]", "N=400, Rel=0.4"),3)`% ($\beta_4$) and `r round(get_type("SAM", "Uniform", "beta[5]", "N=400, Rel=0.4"),3)`% ($\beta_5$), while DBLCENT showed similar patterns at `r round(get_type("DBLCENT", "Uniform", "beta[4]", "N=400, Rel=0.4"),3)`% and `r round(get_type("DBLCENT", "Uniform", "beta[5]", "N=400, Rel=0.4"),3)`%. With increased reliability, all methods achieved acceptable Type I error control under uniform conditions.

### Statistical Power

Figure 6 illustrates power across approaches and conditions.

#### Normal Distribution

Under normal conditions, power was strongly influenced by both reliability and sample size.

At low reliability and moderate sample size, power was extremely low for all approaches. For the interaction term ($\beta_3$), power was `r round(get_power("LMS", "Normal", "beta[3]", "N=400, Rel=0.4"),1)`% (LMS) and `r round(get_power("QML", "Normal", "beta[3]", "N=400, Rel=0.4"),1)`% (QML), compared to `r round(get_power("SAM", "Normal", "beta[3]", "N=400, Rel=0.4"),1)`% (SAM) and `r round(get_power("DBLCENT", "Normal", "beta[3]", "N=400, Rel=0.4"),1)`% (DBLCENT). This pattern was consistent for quadratic terms, with LMS achieving `r round(get_power("LMS", "Normal", "beta[4]", "N=400, Rel=0.4"),1)`% and `r round(get_power("LMS", "Normal", "beta[5]", "N=400, Rel=0.4"),1)`% for $\beta_4$ and $\beta_5$, while DBLCENT showed severely limited power at `r round(get_power("DBLCENT", "Normal", "beta[4]", "N=400, Rel=0.4"),1)`% and `r round(get_power("DBLCENT", "Normal", "beta[5]", "N=400, Rel=0.4"),1)`%. At medium reliability and moderate sample size, power improved for all methods. SAM achieved `r round(get_power("SAM", "Normal", "beta[3]", "N=400, Rel=0.6"),1)`% for the interaction term ($\beta_3$), comparable to LMS (`r round(get_power("LMS", "Normal", "beta[3]", "N=400, Rel=0.6"),1)`%) and QML (`r round(get_power("QML", "Normal", "beta[3]", "N=400, Rel=0.6"),1)`%). DBLCENT showed a result of `r round(get_power("DBLCENT", "Normal", "beta[3]", "N=400, Rel=0.6"),1)`%.

At low reliability and large sample size, power increased substantially for all methods except the DBLCENT. SAM achieved `r round(get_power("SAM", "Normal", "beta[3]", "N=1000, Rel=0.4"),1)`% for $\beta_3$, while LMS and QML reached `r round(get_power("LMS", "Normal", "beta[3]", "N=1000, Rel=0.4"),1)`% and `r round(get_power("QML", "Normal", "beta[3]", "N=1000, Rel=0.4"),1)`%, respectively. DBLCENT remained severely underpowered at `r round(get_power("DBLCENT", "Normal", "beta[3]", "N=1000, Rel=0.4"),1)`%. At medium reliability and large sample size, power exceeded 60% for all methods except DBLCENT, with SAM, LMS, and QML achieving `r round(get_power("SAM", "Normal", "beta[3]", "N=1000, Rel=0.6"),1)`%, `r round(get_power("LMS", "Normal", "beta[3]", "N=1000, Rel=0.6"),1)`%, and `r round(get_power("QML", "Normal", "beta[3]", "N=1000, Rel=0.6"),1)`%, respectively. At high reliability and large sample size, all approaches showed power above 80%.

#### Nonnormal Distribution

Under nonnormal conditions, power patterns shifted dramatically.

At low reliability and moderate sample size, all methods showed reduced power for the interaction term: SAM (`r round(get_power("SAM", "Nonnormal", "beta[3]", "N=400, Rel=0.4"),1)`%), LMS (`r round(get_power("LMS", "Nonnormal", "beta[3]", "N=400, Rel=0.4"),1)`%), QML (`r round(get_power("QML", "Nonnormal", "beta[3]", "N=400, Rel=0.4"),1)`%), and DBLCENT (`r round(get_power("DBLCENT", "Nonnormal", "beta[3]", "N=400, Rel=0.4"),1)`%). However, for quadratic terms, LMS and QML showed power of `r round(get_power("LMS", "Nonnormal", "beta[4]", "N=400, Rel=0.4"),1)`% and `r round(get_power("QML", "Nonnormal", "beta[4]", "N=400, Rel=0.4"),1)`% for $\beta_4$.

At low reliability and large sample size, power for quadratic terms reached extreme levels for distribution analytic methods: LMS showed `r round(get_power("LMS", "Nonnormal", "beta[4]", "N=1000, Rel=0.4"),1)`% and `r round(get_power("LMS", "Nonnormal", "beta[5]", "N=1000, Rel=0.4"),1)`%, while QML achieved `r round(get_power("QML", "Nonnormal", "beta[4]", "N=1000, Rel=0.4"),1)`% and `r round(get_power("QML", "Nonnormal", "beta[5]", "N=1000, Rel=0.4"),1)`%.

#### Uniform Distribution

Under uniform distributions, power was generally reduced compared to normal conditions.

At low reliability and moderate sample size, SAM showed particularly poor power for quadratic terms at `r round(get_power("SAM", "Uniform", "beta[4]", "N=400, Rel=0.4"),2)`% ($\beta_4$) and `r round(get_power("SAM", "Uniform", "beta[5]", "N=400, Rel=0.4"),2)`% ($\beta_5$), while maintaining `r round(get_power("SAM", "Uniform", "beta[3]", "N=400, Rel=0.4"),1)`% for the interaction term. DBLCENT showed similarly limited power at `r round(get_power("DBLCENT", "Uniform", "beta[4]", "N=400, Rel=0.4"),3)`% and `r round(get_power("DBLCENT", "Uniform", "beta[5]", "N=400, Rel=0.4"),2)`% for quadratic terms.

At high reliability and large sample size, power reached acceptable levels for interaction effects across all methods, with SAM achieving `r round(get_power("SAM", "Uniform", "beta[3]", "N=1000, Rel=0.8"),1)`%, LMS `r round(get_power("LMS", "Uniform", "beta[3]", "N=1000, Rel=0.8"),1)`%, and DBLCENT `r round(get_power("DBLCENT", "Uniform", "beta[3]", "N=1000, Rel=0.8"),1)`%. However, quadratic term detection remained challenging, with power ranging from `r round(get_power("DBLCENT", "Uniform", "beta[4]", "N=1000, Rel=0.8"),1)`% to `r round(get_power("SAM", "Uniform", "beta[4]", "N=1000, Rel=0.8"),1)`% for $\beta_4$.

```{r plot-type, echo=FALSE, fig.cap="Type I error rate.", fig.align='center', fig.height=12, fig.width=9}
(p_t1)
```

```{r plot-power, echo=FALSE, fig.cap="Power.", fig.align='center', fig.height=12, fig.width=9}
(p_pow)
```

## Brief discussion of simulation study 1

The results from simulation study 1 are aligned with previous simulation studies. With respect to bias, the same pattern of positive bias and negative bias for the nonlinear effects was observed as in @brandt_etall_2014. Moreover, as in @brandt_etall_2020 similar findings were also observed for extremely large biased results in cases of small reliability, despite not manipulating structural misspecifications here. We also observed similar patterns as in @lonati_etall_2024 for the interaction term. Importantly, however, is the contrast between the interaction and quadratic terms, which was not investigated in their case. For instance, the interaction term showing unbiased results under non-normal conditions, but biased results for the quadratic terms under the same condition. The SE/SD ratio results also follow the results reported in @brandt_etall_2014. Last, [comment about the insane power for lms and qml under non-normal: check with yves; power, type I error].

Thus, the SAM approach shows good results overall that are comparable and even outperform the more widely used approaches. However, caution is needed for cases where low reliability may be the case.

## Result for simulation study 2

[...]
