```{r}
#| label: packages
#| echo: false
#| warning: false
#| message: false

library(dplyr); library(ggplot2)
source("../Simulations/Plots.R")
source("../Simulations/Study_1/Results/Results(1).R")
source("../Simulations/Study_2/Results/Results(2).R")
```

# Results for the Simulation Studies 

The results reported here focus primarily on conditions where nonlinear effects were present. This section is organized as follows: we first present the main results for Simulation 1 and Simulation 2 under normal measurement errors and structural disturbances, followed by a separate subsection examining how nonnormal measurement errors and structural disturbances affect the results obtained in main analyses (i.e., when measurement errors and structural disturbances were normal).

## Main Results: Simulation 1

```{r}
#| label: results-first-sim-study
#| echo: false
#| warning: false
#| message: false

results_study_1 <- readRDS("../Simulations/Study_1/Results/results_study_1_basic_robust.rds")
```

```{r}
#| label: convergence-outliers-first-sim-study
#| echo: false
#| output: false

get_convergence_outlier_rate_study_1 <- function(method, dist, n, rel, model = "Full",
                                                  rate_type = c("convergence", "outlier", "final")) {
  rate_type <- match.arg(rate_type)

  col_map <- c(
    "convergence" = "Convergence_Rate_This_Method",
    "outlier" = "Outlier_Rate_This_Method",
    "final" = "Percent_Total_Excluded"
  )

  col_name <- col_map[rate_type]

  # since these rates are the same across parameters, we just pick one (e.g., eta1)
  # filter for baseline conditions (normal epsilon and zeta) for main paper results
  result <- results_study_1 %>%
    filter(
      Method == toupper(method),
      Distr_Exo == dist,
      Distr_Epsilon == "normal",
      Distr_Zeta == "normal",
      SampleSize == n,
      Reliability == rel,
      Model == model,
      Parameter == "eta1"  # rates are identical across parameters
    ) %>%
    pull(!!sym(col_name))

  if(length(result) > 0) result[1] else NA
}

# most outliers
#results_study_1 %>%
#  filter(Parameter == "eta1",
#         Distr_Epsilon == "normal",
#         Distr_Zeta == "normal") %>%
#  group_by(Method) %>%
#  arrange(desc(Outlier_Rate_This_Method)) %>%
#  slice_head(n = 2) %>%
#  select(Method, Model, Distr_Exo, SampleSize, Reliability, Outlier_Rate_This_Method)

# worst convergence rates (lowest values) for each method
#results_study_1 %>%
#  filter(Parameter == "eta1",
#         Distr_Epsilon == "normal",
#         Distr_Zeta == "normal") %>%
#  group_by(Method) %>%
#  arrange(Convergence_Rate_This_Method) %>%
#  slice_head(n = 2) %>%
#  select(Method, Model, Distr_Exo, SampleSize, Reliability, Convergence_Rate_This_Method)
```

### Convergence Issues and Outliers  

Convergence problems were generally rare. The main exception was UPI, which showed reduced convergence under moderate sample size, low reliability, and uniform latent predictors. In this scenario, convergence rates were `r round(get_convergence_outlier_rate_study_1("UPI", "uniform", 400, 0.4, "Full", "convergence"), 2)`% with the full model and `r round(get_convergence_outlier_rate_study_1("UPI", "uniform", 400, 0.4, "Linear", "convergence"), 2)`% with the linear model. LMS and QML converged well in general, with the lowest rates in the same setting being `r round(get_convergence_outlier_rate_study_1("LMS", "uniform", 400, 0.4, "Full", "convergence"), 2)`% and `r round(get_convergence_outlier_rate_study_1("QML", "uniform", 400, 0.4, "Full", "convergence"), 2)`% (full model), and `r round(get_convergence_outlier_rate_study_1("LMS", "uniform", 400, 0.4, "Linear", "convergence"), 2)`% and `r round(get_convergence_outlier_rate_study_1("QML", "uniform", 400, 0.4, "Linear", "convergence"), 2)`% (linear model), respectively. LSAM consistently converged, with rates of `r round(get_convergence_outlier_rate_study_1("LSAM", "uniform", 400, 0.4, "Linear", "convergence"), 2)`% across all conditions.

Outlier rates followed a comparable pattern in terms of conditions. The most pronounced rates again occurred under moderate sample size, low reliability, and uniform latent predictors. UPI produced the highest outlier frequencies, reaching `r round(get_convergence_outlier_rate_study_1("UPI", "uniform", 400, 0.4, "Full", "outlier"), 2)`% with the full model and `r round(get_convergence_outlier_rate_study_1("UPI", "uniform", 400, 0.4, "Linear", "outlier"), 2)`% with the linear model. For the same condition, LSAM also yielded the most outliers (`r round(get_convergence_outlier_rate_study_1("LSAM", "uniform", 400, 0.4, "Linear", "outlier"), 2)`% with the linear model and `r round(get_convergence_outlier_rate_study_1("LSAM", "uniform", 400, 0.4, "Full", "outlier"), 2)`% with the full model). In contrast, LMS and QML generated virtually none, with their highest rates reaching only `r round(get_convergence_outlier_rate_study_1("LMS", "uniform", 400, 0.4, "Full", "outlier"), 2)`% and `r round(get_convergence_outlier_rate_study_1("QML", "uniform", 400, 0.4, "Full", "outlier"), 2)`% (both full model) in the same scenario as the other approaches. Detailed results for convergence and outliers are provided in Appendix C (see Table C1).

```{r}
#| label: plots-first-sim-study
#| echo: false

plot_study_1_data <- prepare_study1_data(results_study_1)

# RELATIVE BIAS 
study_1_relative_bias <- plot_study_1_data$bias_relative
dat_relative_bias_400_full_study_1 <- study_1_relative_bias %>%
   filter(Model == "Full", SampleSize == "400") %>%
   droplevels()

p_relative_bias_400_full_study_1 <- plot_bias(
   dat_relative_bias_400_full_study_1, 
   shapes = SHAPES_4, 
   ltys = LTYS_4,
   bias_type = "relative",  
   facet_formula = Distribution + Parameter ~ .,  
   y_breaks = seq(-1, 1.5, by = 0.5),
   y_limits = c(-1, 1.5)
)

# Relative RMSE 
study_1_relative_rmse <- plot_study_1_data$rmse_relative

dat_relative_rmse_400_full_study_1 <- study_1_relative_rmse %>%
  filter(Model == "Full", SampleSize == "400") %>%
  droplevels()

p_relative_rmse_400_full_study_1 <- plot_rmse(
  dat_relative_rmse_400_full_study_1, 
  shapes = SHAPES_4, 
  ltys = LTYS_4,
  facet_formula = Distribution + Parameter ~ ., 
  #y_breaks = seq(0, 0.30, by = 0.05),           
  #y_limits = c(0, 0.30)                        
)

# SE/SD RATIO (Right-skewed & Uniform, Full, N=400 & 1000)
study_1_sesd <- plot_study_1_data$sesd

dat_sesd_nonnorm_unif_study_1 <- study_1_sesd %>%
  filter(Model == "Full", 
         SampleSize %in% c("400", "1000"), 
         Distribution %in% c("Right-skewed", "Uniform")) %>%
  droplevels()

p_slope_nonnorm_unif_study_1 <- plot_sesd(
  dat_sesd_nonnorm_unif_study_1,
  shapes = SHAPES_4,
  ltys = LTYS_4,
  facet_formula = Distribution + Parameter ~ SampleSize
)

# COVERAGE (Full, N=400 & 1000, all distributions)
study_1_coverage <- plot_study_1_data$coverage

dat_cov_nonnorm_unif_study_1 <- study_1_coverage %>%
  filter(Model == "Full", 
         SampleSize %in% c("400", "1000"),
         Distribution %in% c("Right-skewed", "Uniform")) %>% 
  droplevels()

p_cov_nonnorm_unif_study_1 <- plot_coverage(
  dat_cov_nonnorm_unif_study_1, 
  shapes = SHAPES_4,
  ltys = LTYS_4,
  facet_formula = Distribution + Parameter ~ SampleSize
)

# TYPE I ERROR (Linear, N=1000 only) 
study_1_type1 <- plot_study_1_data$type1

dat_t1_1000_study_1 <- study_1_type1 %>%
  filter(grepl("N=1000", Condition)) %>%
  droplevels()

p_t1_1000_study_1 <- plot_type1(
  dat_t1_1000_study_1,  
  greys = GREYS_4,
  facet_formula = Distribution + Parameter ~ Condition
)
```

### Relative Bias and RMSE When Nonlinear Effects Were Present

Figures 2 and 3 present relative bias and RMSE across distributional conditions at a moderate sample size (N = 400). Following @brandt_etall_2014, values exceeding 0.10 (10%) were considered biased. Under normal distributions, LSAM showed stable performance across reliability levels for all nonlinear effects. Bias emerged only for the interaction term at low reliability for the other approaches, with LMS and QML also biased under medium reliability. At larger sample sizes, LSAM and UPI were unbiased even at low reliability, whereas LMS and QML continued to show bias, albeit small, under low and medium reliability. With right-skewed distributions, LSAM displayed bias for the interaction term only under low reliability, while UPI showed no bias for all nonlinear effects. In contrast, LMS and QML exhibited severe negative bias for interactions and positive bias for quadratic effects across reliability levels. At larger sample sizes, LSAM and UPI were unbiased across conditions, but LMS and QML remained biased. Under uniform distributions, LSAM was unbiased at all reliability levels. UPI showed bias for some nonlinear effects at low reliability, whereas LMS and QML produced unbiased interaction estimates but consistent negative bias for quadratic effects throughout reliability levels. These last patterns remained qualitatively unchanged at larger sample sizes (see Figure S1 in supplemental materials).

For relative RMSE, all methods performed similarly under normality, with minor differences at low reliability where LMS and QML showed the lowest values. Under right-skewed distributions, LSAM generally yielded the lowest RMSE, though the advantage was modest and diminished further at high reliability. For uniform distributions, LMS and QML produced substantially lower RMSE, but performance across methods converged as reliability increased (see Figure S4 in supplemental materials for results under a large sample size).

### Efficiency and Accuracy of SEs When Nonlinear Effects Were Present

Figure 4 presents SE/SD ratios for right-skewed and uniform conditions across sample sizes, with exact values shown when they fall outside the y-axis range. Following @brandt_etall_2014, ratios below 0.90 (underestimation) or above 1.10 (overestimation) indicate bias. Under normality, LSAM displayed some small overestimation at low reliability and moderate sample size. In contrast, UPI produced substantial overestimation across all nonlinear effects under the same condition, while LMS and QML yielded extremely accurate ratios (see Figure S5 in online supplemental materials for normal condition). In this case, a large sample size resulted in better results. For right-skewed distributions, LSAM showed overestimation at low reliability with moderate sample sizes. UPI consistently overestimated under low reliability. We also note that in some cases an underestimation is observed for medium reliability. Under uniform distributions, LSAM and UPI yielded an overestimation for all nonlinear effects at low reliability^[For LSAM and UPI, we investigated further this overestimation. Generally speaking, it arose from a small number of clear outliers in the SEs. We retained these values in the analysis, but they are identified and displayed in supplemental materials.]. UPI additionally showed a negligible underestimation at medium reliability and moderate sample sizes. LMS and QML remained stable across basically all nonnormal conditions and reliability levels. Larger sample size improved all results, except for the UPI under the uniform and low reliability condition. Last, we also see a slight underestimation for one quadratic term at high reliability for all approaches in the right-skewed scenario. 

### Coverage for When Nonlinear Effects Were Present

Figure 5 displays coverage results for right-skewed and uniform conditions across sample sizes, also with exact values shown when they fall outside the y-axis range. Coverage between 93% and 97% was considered acceptable. Although, previous literature considered above 90% as an acceptable performance [@cham_etall_2012; @ayturk_etall_2020]. LSAM slightly exceeded this range at low reliability and moderate sample size, but not at larger samples, across all distributions. UPI also showed similar results, but still with some exceeding values with a large sample for some distributions. Under normality, LMS and QML performed within the acceptable range across reliability and sample sizes (see Figure S6 in supplemental materials). For right-skewed distributions, however, LMS and QML exhibited substantial undercoverage. Larger sample sizes did not improve coverage for these methods, while higher reliability reduced—but did not eliminate—the amount of undercoverage. Under uniform distributions, LMS and QML showed undercoverage exclusively for the quadratic effects, with the same remark previously highlighted.

### Type I Error Rate

Figure 6 presents Type I error rates at large sample sizes across distributions, with values between 2.5–7.5% considered acceptable. Under normality, LSAM, LMS, and QML remained mostly within the acceptable range across reliability levels, though UPI fell below this range at low reliability. For right-skewed distributions, LSAM and UPI stayed within acceptable bounds, whereas LMS and QML showed severe inflation for quadratic effects across all reliability levels. Under uniform distributions, LSAM and UPI generally performed well, with values falling below the acceptable range only at low reliability. In contrast, LMS and QML yielded consistently well-controlled error rates under all reliability levels. Results at moderate sample sizes were qualitatively similar, though LMS and QML showed somewhat less inflation under right-skewness. Moreover, at moderate sample sizes, Type I error rates for LSAM and UPI fell below the acceptable range at low reliability across all distributions (see Figure S7 in supplemental materials).

### Empirical Power

Given the inflated Type I error rates and biased results observed for some approaches, power results should be interpreted with caution [@morris_etall_2019]. That said, we restrict our conclusions to only specific conditions. At large sample sizes, LSAM reached power levels near or above 80% under medium and high reliability across all distributions for most nonlinear effects. The main exception was under the uniform distribution, where quadratic effects remained underpowered. The other approaches showed broadly similar patterns in the same conditions. Under right-skewness, however, LMS and QML diverged extremely with low power only for the interaction term under medium reliability (see Figure S8 in supplemental materials).  

### Absolute Bias, RMSE, SEs, and Coverage When Nonlinear Effects Were Absent

Bias patterns resembled those observed when nonlinear effects were present, though with reduced magnitude. A notable difference emerged under the uniform distribution: LMS and QML produced unbiased quadratic estimates. RMSE results showed no substantive differences beyond reduced magnitude. The accuracy of SEs was generally comparable. Coverage improved somewhat when nonlinear effects were absent. Specifically, LMS and QML showed higher coverage under right-skewed distributions, though still falling below the desirable range for quadratic effects. Under the uniform distribution, however, coverage for quadratic effects improved substantially for both LMS and QML (see Figures S1, S3, S5, and S6 in supplemental materials).

### Summary of Simulation 1

With the exception of low reliability conditions, LSAM demonstrated adequate performance across all evaluated metrics. LSAM generally yielded unbiased estimates, whereas QML and LMS exhibited systematic bias: positive and negative bias for nonlinear effects under right-skewed distributions, and negative bias for quadratic effects under uniform distributions. UPI also produced largely unbiased results. For SEs, LMS and QML were the most efficient, although LSAM achieved comparable accuracy at medium and high reliability across all distributions, particularly with large sample sizes. Coverage rates remained relatively stable for LSAM and UPI, but not for LMS and QML. Type I error rates fell within the acceptable range for LSAM and UPI, except under uniform conditions with low reliability. By contrast, LMS and QML displayed marked inflation under right-skewed distributions. Finally, empirical power was generally highest for LMS and QML, though this finding must be interpreted cautiously given their inflated Type I error and biased results. When Type I error was controlled, all approaches achieved desirable power levels for most effects, with the exception of quadratic effects under the uniform distribution, which remained underpowered.

## Main Results: Simulation 2

```{r}
#| label: results-second-sim-study
#| echo: false
#| warning: false
#| message: false

results_study_2 <- readRDS("../Simulations/Study_2/Results/results_study_2_basic_robust.rds")
```

### Convergence Issues and Outliers

```{r}
#| label: convergence-outliers-second-sim-study
#| echo: false
#| output: false

get_convergence_outlier_rate_study_2 <- function(method, dist, n, rel, model = "Full",
                                                  equation = c("eta4", "eta5"),
                                                  rate_type = c("convergence", "outlier", "final")) {
  equation <- match.arg(equation)
  rate_type <- match.arg(rate_type)

  col_map <- c(
    "convergence" = "Convergence_Rate_This_Method",
    "outlier" = "Outlier_Rate_This_Method",
    "final" = "Percent_Total_Excluded"
  )

  col_name <- col_map[rate_type]

  # needs representative parameter for each equation
  # for eta4: use "eta1" (first predictor)
  # for eta5: use "eta4" (first predictor)
  param_to_use <- ifelse(equation == "eta4", "eta1", "eta4")

  # filter for baseline conditions (normal epsilon and zeta) for main paper results
  result <- results_study_2 %>%
    filter(
      Method == toupper(method),
      Distr_Exo == dist,
      Distr_Epsilon == "normal",
      Distr_Zeta == "normal",
      SampleSize == n,
      Reliability == rel,
      Model == model,
      Equation == equation,
      Parameter == param_to_use
    ) %>%
    pull(!!sym(col_name))

  if(length(result) > 0) result[1] else NA
}

# worst outlier rates across both equations
#results_study_2 %>%
#  filter((Equation == "eta4" & Parameter == "eta1") |
#         (Equation == "eta5" & Parameter == "eta4"),
#         Distr_Epsilon == "normal",
#         Distr_Zeta == "normal") %>%
#  group_by(Method, Equation) %>%
#  arrange(desc(Outlier_Rate_This_Method)) %>%
#  slice_head(n = 2) %>%
#  select(Method, Equation, Model, Distr_Exo, SampleSize, Reliability, Outlier_Rate_This_Method) %>%
#  arrange(Method, Equation, desc(Outlier_Rate_This_Method))

# Worst convergence rates for each method and equation
#results_study_2 %>%
#  filter((Equation == "eta4" & Parameter == "eta1") |
#         (Equation == "eta5" & Parameter == "eta4"),
#         Distr_Epsilon == "normal",
#         Distr_Zeta == "normal") %>%
#  group_by(Method, Equation) %>%
#  arrange(Convergence_Rate_This_Method) %>%
#  slice_head(n = 2) %>%
#  select(Method, Equation, Model, Distr_Exo, SampleSize, Reliability, Convergence_Rate_This_Method) %>%
#  arrange(Method, Equation, Convergence_Rate_This_Method)
```

Convergence problems were most severe for UPI, particularly in the worst-case condition of moderate sample size, low reliability, and uniform predictors. Rates fell to `r round(get_convergence_outlier_rate_study_2("UPI", "uniform", 400, 0.4, "Full", "eta4", "convergence"), 2)`% for both full model and linear model. The same condition also produced the lowest convergence rates for QML, which converged more often than UPI but still at suboptimal levels (`r round(get_convergence_outlier_rate_study_2("QML", "uniform", 400, 0.4, "Full", "eta4", "convergence"), 2)`% with the full model; `r round(get_convergence_outlier_rate_study_2("QML", "uniform", 400, 0.4, "Linear", "eta4", "convergence"), 2)`% with the linear model). LSAM converged `r round(get_convergence_outlier_rate_study_2("LSAM", "normal", 400, 0.4, "Full", "eta4", "convergence"), 2)`% under all conditions. For normal and right-skewed predictors, all approaches had a convergence rate above 96%. We note that excluding the implausible solutions leads to virtually no convergence for the UPI approach under low reliability and nonnormal latent distributions.

Outlier rates also varied substantially across methods. UPI again performed worst under the condition of uniform predictors with moderate sample size and low reliability, reaching `r round(get_convergence_outlier_rate_study_2("UPI", "uniform", 400, 0.4, "Linear", "eta4", "outlier"), 2)`% with the linear model and `r round(get_convergence_outlier_rate_study_2("UPI", "uniform", 400, 0.4, "Full", "eta4", "outlier"), 2)`% with the full model. QML showed much lower outlier rates overall, with the highest occurring under uniform predictors: `r round(get_convergence_outlier_rate_study_2("QML", "uniform", 400, 0.4, "Linear", "eta4", "outlier"), 2)`% with the linear model, followed by `r round(get_convergence_outlier_rate_study_2("QML", "uniform", 400, 0.4, "Full", "eta4", "outlier"), 2)`% with the full model. LSAM’s highest outlier rates occurred with right-skewed predictors in the full model (`r round(get_convergence_outlier_rate_study_2("LSAM", "nonnormal", 400, 0.4, "Full", "eta4", "outlier"), 2)`%) and in the linear model (`r round(get_convergence_outlier_rate_study_2("LSAM", "nonnormal", 400, 0.4, "Linear", "eta4", "outlier"), 2)`%). We also note the final sample size for the condition with moderate sample size, low reliability, and uniform distribution is relatively small (see Table C2 in Appendix C).  

```{r}
#| label: plots-second-sim-study
#| echo: false

study_2_normal_data <- prepare_study2_data(results_study_2, "normal")
study_2_nonnormal_data <- prepare_study2_data(results_study_2, "nonnormal")
study_2_uniform_data <- prepare_study2_data(results_study_2, "uniform")

# RELATIVE BIAS (full model, N=400, all Distributions) 
dat_relative_bias_400_full_all_study_2 <- bind_rows(
  study_2_normal_data$bias_relative %>%
    filter(Model == "Full", SampleSize == "400"),
  study_2_nonnormal_data$bias_relative %>%
    filter(Model == "Full", SampleSize == "400"),
  study_2_uniform_data$bias_relative %>%
    filter(Model == "Full", SampleSize == "400")
) %>%
  droplevels()

p_relative_bias_400_full_all_study_2 <- plot_bias(
  dat_relative_bias_400_full_all_study_2,
  shapes = SHAPES_3,
  ltys = LTYS_3,
  facet_formula = Parameter ~ Distribution,
  y_breaks = seq(-1, 1.5, by = 0.5),
  y_limits = c(-1, 1.5),
  bias_type = "relative"
)

# RELATIVE RMSE (full model, N=400, all Distributions) 
dat_relative_rmse_400_full_all_study_2 <- bind_rows(
  study_2_normal_data$rmse_relative %>%
    filter(Model == "Full", SampleSize == "400"),
  study_2_nonnormal_data$rmse_relative %>%
    filter(Model == "Full", SampleSize == "400"),
  study_2_uniform_data$rmse_relative %>%
    filter(Model == "Full", SampleSize == "400")
) %>%
  droplevels()

p_relative_rmse_400_full_all_study_2 <- plot_rmse(
    dat_relative_rmse_400_full_all_study_2,
    shapes = SHAPES_3,
    ltys = LTYS_3,
    facet_formula = Parameter ~ Distribution,
    y_breaks = seq(0, 5, by = 1),  
    y_limits = c(0, 5.2),              
)


# SE/SD RATIO (Full model, N=400, All Distributions) 
dat_sesd_400_full_all_study_2 <- bind_rows(
  study_2_normal_data$sesd %>%
    filter(Model == "Full", SampleSize == "400"),
  study_2_nonnormal_data$sesd %>%
    filter(Model == "Full", SampleSize == "400"),
  study_2_uniform_data$sesd %>%
    filter(Model == "Full", SampleSize == "400")
) %>%
  droplevels()

p_sesd_400_full_all_study_2 <- plot_sesd(
  dat_sesd_400_full_all_study_2,
  shapes = SHAPES_3,
  ltys = LTYS_3,
  facet_formula = Parameter ~ Distribution,
  title = ""
)

#  COVERAGE (Full model, N=400, All Distributions)
dat_coverage_400_full_all_study_2 <- bind_rows(
  study_2_normal_data$coverage %>%
    filter(Model == "Full", SampleSize == "400"),
  study_2_nonnormal_data$coverage %>%
    filter(Model == "Full", SampleSize == "400"),
  study_2_uniform_data$coverage %>%
    filter(Model == "Full", SampleSize == "400")
) %>%
  droplevels()

p_coverage_400_full_all_study_2 <- plot_coverage(
  dat_coverage_400_full_all_study_2,
  shapes = SHAPES_3,
  ltys = LTYS_3,
  facet_formula = Parameter ~ Distribution,
  title = ""
)

# TYPE I ERROR (Linear, N=1000, Nonnormal & Uniform)
dat_t1_1000_all_study_2 <- bind_rows(
  study_2_nonnormal_data$type1 %>%
    filter(grepl("N=1000", Condition)),
  study_2_uniform_data$type1 %>%
    filter(grepl("N=1000", Condition))
) %>%
  droplevels()

p_t1_1000_all_study_2 <- plot_type1(
  dat_t1_1000_all_study_2,
  greys = GREYS_3,
  facet_formula = Parameter ~ Distribution + Condition,
  title = ""
)
```

### Relative Bias and RMSE When Nonlinear Effects Were Present 

Figures 7 and 8 present relative bias and RMSE for all nonlinear effects across distributions with a moderate sample size. Under normality, results were mixed. At low reliability, LSAM showed bias for some nonlinear effects, which largely disappeared at medium reliability. UPI and QML also showed bias at low reliability for some nonlinear effects, but only QML continued to exhibit bias at medium reliability. With right-skewed distributions, LSAM was biased for one nonlinear effect at low reliability. UPI only yielded biased estimates at low reliability. QML, however, showed substantial bias affecting most nonlinear effects across all reliability levels. Under the uniform distribution, LSAM showed some biased results only at low reliability. UPI showed substantial bias for most nonlinear effects at low reliability, which was reduced at medium reliability. QML also displayed bias for some nonlinear effects at low reliability, improving with increasing reliability, yet all quadratic terms remained biased across reliability levels. At larger sample sizes, throughout distributions, both LSAM and UPI no longer resulted in many of the biases observed under low reliability (see Figures S10, S18, and S26 in supplemental materials).

Relative RMSE was comparable across methods under normality and right-skewness. Under uniform predictors, QML yielded substantially lower RMSE than LSAM and UPI at low reliability, with results converging at medium reliability (see Figures S12, S20, and S28 in supplemental materials for a large sample size).

### Efficiency and Accuracy of SEs When Nonlinear Effects Were Present

Figure 9 displays SE/SD ratios across distributions at a moderate sample size, with exact values shown when they fall outside the y-axis range. Under normal distributions, LSAM and QML produced ratios within the acceptable range across reliability levels, whereas UPI overestimated for several nonlinear effects at low reliability. The latter approach improved for most effects at medium reliability. With right-skewed distributions, LSAM and QML ratios were consistently within the desirable range, but UPI ratios were overestimated at low reliability. Under uniform distributions, all approaches yielded overestimated ratios for some nonlinear effects at low reliability. However, the magnitude is the largest for the UPI approach. Results generally improved with larger samples, although the UPI approach remained overestimated for some effects (see Figures S13, S21, and S29 in supplemental materials).

### Coverage When Nonlinear Effects Were Present

Figure 10 presents coverage results for a moderate sample size, also with exact values shown when they fall outside the y-axis range. Under normality, LSAM generally achieved acceptable coverage, with some overcoverage at low reliability. QML maintained coverage within the desirable range across all nonlinear effects, whereas UPI showed overcoverage for most effects at low reliability. With right-skewed distributions, LSAM again produced acceptable coverage, apart from one slight overcoverage at low reliability. In contrast, QML yielded inadequate coverage, reaching acceptable levels only at high reliability for some effects. Under uniform distributions, LSAM and UPI showed a similar pattern as in the other conditions, with overcoverage at low reliability. Note, however, that UPI with a medium reliability resulted in some overcoverage. For QML, coverage for interaction terms was adequate, while quadratic terms remained undercovered at both low and medium reliability. Patterns were qualitatively similar at larger sample sizes (see Figures S14, S22, and S30 in supplemental materials).

### Type I Error Rate

Figure 11 presents Type I error rates for a large sample size under right-skewed and uniform distributions. Under normality, LSAM and QML approaches maintained rates within the nominal 5% level across reliability levels. This was not the case for the UPI approach (see Figure S16 in the supplemental materials). Under right-skewed conditions, LSAM demonstrated well-controlled Type I error rates even at low reliability, whereas QML showed substantial inflation for quadratic effects at low and medium reliability. In this case, the UPI approach results fell below the acceptable range for multiple nonlinear effects. Under uniform distributions, LSAM showed some values below this acceptable range under low reliability for two quadratic terms. This was even more problematic for the UPI with all nonlinear effects, while for the QML the rate was acceptable. A moderate sample size affected negatively LSAM and UPI the most under low reliability across distributions (see Figures S15, S23, and S31 in supplemental materials for moderate sample size).

### Empirical Power

As before, given the inflated Type I error rates and biased results, interpretation is limited. Under normal distributions, power only exceeded 80% with large samples and high reliability, primarily for the nonlinear effects in the structural equation for $\eta_4$. Results under right-skewed conditions yielded elevated power rates under the same setting. In contrast, under uniform distributions, power remained substantially lower for all nonlinear effects, even with large samples and high reliability, with the exception of the two interaction terms in $\eta_4$ (see Figures S16, S24, and S32 in supplemental materials).

### Absolute Bias, RMSE, SEs, and Coverage When Nonlinear Effects Were Absent

The most notable differences emerged across conditions were reduced bias values in the case of the QML approach for certain nonlinear effects were observed throughout distributions. SE/SD ratios were highly similar. Coverage improved for all approaches under normal and uniform conditions. Under nonnormality, however, QML continued to exhibit undercoverage mainly with large sample sizes. RMSE remained similar (see Figures S9, S11, S13, S14, S17, S19, S21, S22, S25, S27, S29, and S30 in supplemental materials). 

### Summary of Simulation 2

With the exception of low reliability conditions, LSAM produced largely unbiased estimates, accurate SEs, and acceptable coverage across distributions. Under low reliability, some bias and overcoverage appeared, but these issues largely diminished at medium reliability and with larger sample sizes. UPI was hampered by convergence failures and substantial bias under uniform predictors at low reliability, along with overestimated SEs across distributions—particularly under uniform and right-skewed conditions with low reliability. These issues improved at medium reliability and with larger samples. QML produced accurate SEs under normal and right-skewed distributions, but displayed persistent bias for most nonlinear effects under right-skewness across all reliability levels, and for quadratic terms under uniform predictors even at medium reliability. This was accompanied by inflated Type I error rates for quadratic effects under right-skewness and undercoverage—especially for quadratic terms—under both right-skewed and uniform predictors. Relative RMSE differences among methods were modest: QML was more efficient under uniform predictors at low reliability, while all methods performed comparably at medium reliability across distributions. For empirical power, acceptable levels ($\geq 80$%) were attained only under normality with large samples and high reliability, primarily for nonlinear effects in the structural equation for $\eta_4$. Under uniform predictors, power was substantially lower for all nonlinear effects, except the two interaction terms in $\eta_4$.

## Computation Time

Computation times per replication are reported in Table S2 in the supplemental materials. We note that these comparisons are contingent on implementation details (e.g., C++ vs. R) and do not necessarily reflect inherent properties of the methods. In Simulation 1, UPI was generally the fastest approach, followed by LSAM. QML was also moderately fast, whereas LMS was substantially slower. In Simulation 2, LSAM became the fastest approach, whereas QML and UPI increased more substantially relative to their Simulation 1 times. Importantly, the distributional conditions affected computation times differently across methods.

## Additional Distributional Conditions: Measurement Error and Structural Disturbance

Results are presented as dumbbell plots comparing normal (main results) to right-skewed conditions for measurement errors and structural disturbance^[A natural concern may be that the right-skewed measurement errors and structural disturbances can lead to additional convergence failures and outliers, thus the effective sample sizes may differ between conditions. To account for this, we computed the MCSE of the difference and a 95% confidence interval around it. This is not reported here but further clarified in the supplemental materials.]. 

```{r}
#| label: sensitivity-plots-study-1
#| echo: false

# Prepare sensitivity dumbbell data for Study 1
dumbbell_study1 <- prepare_sensitivity_dumbbell_data(results_study_1, study = 1, include_low_rel = FALSE)

# Relative Bias (N=400) - Figure 12
p_sens_bias_study1 <- plot_dumbbell(
  dumbbell_study1$bias_relative %>% filter(SampleSize == "400"),
  metric_name = "Relative Bias",
  acceptable_range = c(-0.10, 0.10)
)

# Relative RMSE (N=400) - Figure 13
p_sens_rmse_study1 <- plot_dumbbell(
  dumbbell_study1$rmse_relative %>% filter(SampleSize == "400"),
  metric_name = "Relative RMSE"
)

# SE/SD (N=400) - Figure 14
p_sens_sesd_study1 <- plot_dumbbell(
  dumbbell_study1$sesd %>% filter(SampleSize == "400"),
  metric_name = "SE/SD",
  acceptable_range = c(0.90, 1.10),
  show_errorbars = FALSE
) +
  coord_cartesian(xlim = c(0.70, 1.5))

# Coverage (N=1000) - Figure 15
p_sens_coverage_study1 <- plot_dumbbell(
  dumbbell_study1$coverage %>% filter(SampleSize == "1000"),
  metric_name = "Coverage (%)",
  acceptable_range = c(93, 97)
) +
  coord_cartesian(xlim = c(50, 100))

# Type I Error (N=1000)
p_sens_type1_study1 <- plot_dumbbell(
  dumbbell_study1$type1 %>% filter(SampleSize == "1000"),
  metric_name = "Type I Error (%)",
  acceptable_range = c(3, 7)
)
```

### Simulation 1

Right-skewed measurement errors and structural disturbances had the most negative consequences on convergence and outliers in conditions with low reliability, especially with uniform latent variables — where convergence rates for the UPI approach were extremely low. For this reason, we restrict the comparison here to cases with medium and high reliability. Notably, right-skewed measurement errors were more frequently associated with these issues than structural disturbances (see Table C1).

For the relative bias, focusing on moderate sample sizes, right-skewed measurement error with medium reliability lead to substantial worsening for all approaches, especially in the case with uniform latent predictors. In fact, in this latter scenario, LSAM suffered the most. However, under high reliability, conclusions stay largely in agreement with main results (see Figure 12). Note the direction of the bias is different for interaction and quadratic effects. For relative RMSE, under moderate sample sizes, the largest difference is for the UPI approach with medium reliability and right-skewed measurement error (see Figure 13), where the the values increased. For the SE/SD ratio, results are largely similar, with the most notable difference for the UPI under right-skewed measurement error and medium reliability. In this case, we see an overestimation with right-skewed and uniform latent variables (see Figure 14). All of these results are not different under a large sample size. For coverage, results yielded the most substantial differences under medium reliability. Indeed, with right-skewed measurement error and latent variables, the coverage for LMS and QML actually improved. This is rather unexpected. While for right-skewed measurement error and uniform latent variables, most approaches also yielded lower coverage results except the UPI where this was mild (see Figure 15). Note that a moderate sample size yielded the same conclusions, despite smaller magnitude. Results for Type I error followed the behavior from coverage (see Figures S45, S46, and S47 in supplemental materials).

### Simulation 2

Due to the conclusions being largely the same as in Simulation 1, we do not show any Figures in the manuscript (see supplemental materials). Convergence and outlier issues affected the same conditions as in Simulation 1, though they were more frequent in magnitude. One notable exception is that QML showed substantial convergence issues when latent variables were uniformly distributed, under right-skewed measurement errors and low reliability. We also highlight that the LSAM yielded a high amount of outliers when all random variables manipulated were right-skewed.

For the relative bias, similar trends are observed as in Simulation 1. Right-skewed measurement error with medium reliability lead to substantial worsening for all approaches, primarily under normal and uniform latent predictors. Under high reliability, results remain largely in agreement with the main results (see Figures S51, S52, S53, S69, S70, S71, S69, S70, and S71 in supplemental materials). For the relative RMSE, under moderate sample size and medium reliability, with right-skewed measurement error, we see some increase for LSAM and UPI under right-skewed latent predictors, while under uniform predictors only UPI. Again, results with high reliability remain the same as main results (see Figures S54, S55, S56, S72, S73, S74, S90, S91, and S92 in supplemental materials). For the SE/SD ratio, with normal predictors, varying measurement error and structural disturbance distributions did not lead to results outside the desirable bounds. With right-skewed predictors, some effects fell slightly below the acceptable range, though a large sample size and high reliability improved the results. Under uniform predictors, mainly the UPI approach showed issues (see Figures S57, S58, S59, S75, S76, S77, S93, S94, and S95 in supplemental materials). For coverage, similar patterns as in Simulation 1 are observed (see Figures S60, S61, S62, S78, S79, S80, S93, S94, S95 in supplemental materials). 