---
title: ""
author: ""
date: ""
output: html_document
---

```{r package versions, echo=FALSE}
modsem_version <- packageVersion("modsem")
lavaan_version <- packageVersion("lavaan")
covsim_version <- packageVersion("covsim")
faux_version <- packageVersion("faux")
copula_version <- packageVersion("copula")
doparallel_version <- packageVersion("doParallel")
dorng_version <- packageVersion("dorng")
R_version <- getRversion()
```

# Simulation studies design 

In this section, we present the simulation design for the simulation study 1 and study 2. This includes the simulation conditions, computational information, and the metrics used to evaluate the performance of the approaches under investigation. The information presented here follows the suggestions from previous articles that investigated the quality of simulation studies [@siepe_etall_2024; @white_etall_2024; @morris_etall_2019].

## Reproducibility and Computational details 

The simulation was conducted on a Mac Studio with an Apple M4 Max chip (with 14 cores and 36 GB of RAM), running macOS Sequoia 15.5. All analyses were performed in R [@R-base] (version `r R_version`). Parallel processing was implemented through the *doParalell* package (version `r doparallel_version`) [@R-doParallel], with *doRNG* (version `r dorng_version`) [@R-doRNG] to ensure independent and reproducible random number streams. For the DBLCENT, LMS, and QML approach, the *modsem* package was used [@kjell_etall_2024] (version `r modsem_version`). For the SAM approach, the *lavaan* package was used [@R-lavaan] (version `r lavaan_version`). Importantly, we used the default settings for the functions provided in the packages^[This is important to acknowledge because there are arguments for the functions used that, in principle, could be tweaked to obtain better results. For instance, one could change the maximum steps for the M-step in the EM algorithm for the LMS. However, this also leads to substantial researcher degrees of freedom and hence were avoided.]. Specific to the SAM approach, we estimated the latent factors with three different measurement blocks as opposed to a single one [@rosseel_loh_2024].

All the materials to reproduce this article available on the following GitHub link: https://github.com/felipelfv/Simulation_First_PhD_Article.git. We included a `README` file that contains the step-by-step information required to reproduce the results reported, a `sessionInfo` file, the *renv* lockfile with the information for the relevant packages used [@R-renv], a Dockerfile for system dependencies, and all the estimates obtained for all iterations. Moreover, this paper was written with *papaja* [@R-papaja] in Rmarkdown.

## Simulation study 1

### Simulation Conditions

The simulation design employed a fully crossed factorial design with 2 (sample sizes) × 3 (reliability levels) × 3 (latent predictor distributions) to evaluate the performance of DBLCENT, LMS, QML, and SAM. This factorial design yielded 18 unique experimental conditions^[To examine Type I error rates and power, we implemented two model specifications: (a) data generated under a linear model (no interaction and quadratic terms) but fitted with a full interaction model, and (b) data generated under and fitted with a full interaction model. Thus, resulting in 36 total conditions. The null model conditions allow us to assess Type I error rates, while the full model conditions evaluate parameter recovery and statistical power.], each replicated 1000 times. 

Sample sizes of 400 and 1000 were selected to represent moderate to large samples. While some simulation studies have examined more extensive ranges of sample sizes [@brandt_etall_2014; @cham_etall_2012; @wall_amemiya_2000; @lonati_etall_2024], we focused on 400 and 1000 for specific reasons. We attempted to examine an intermediate sample size not used in the previous simulations (i.e., 250, 350, 500, or 650). Moreover, it allowed us to explore performance just below the 500 threshold that some studies suggest as a minimum for complex latent interaction models (Wall et al., 2012, as cited in Brandt et al., 2020), while still representing a realistic sample size in applied research. In contrast, a sample size equal to 1000 enabled us to evaluate the asymptotic properties of these estimators, while also aligning with previous simulation studies that commonly employed this sample size. Last, although examining additional sample size conditions would provide more information, computational constraints required a more focused selection.

Three reliability levels (0.4, 0.6, and 0.8) were examined, covering a broad range of measurement quality. These will be referred to as low, medium and high reliability, respectively. While previous simulations have typically focused on high reliability conditions (i.e., 0.8 in Brandt et al., 2014; 0.7 and 0.8 in Lonati et al., 2024) or contrasted high versus low reliability (i.e., 0.8 and 0.5 in Brandt et al., 2020), we extended this range by including 0.4 to examine method performance under poor measurement conditions.

The three distributional conditions investigated were: normal, non-normal, and uniform distributions. These choices were based on previous research that also varied the nonnormality to different degrees [@brandt_etall_2014; brandt_etall_2020; @cham_etall_2012; @lonati_etall_2024]. We used the copula method to generate correlated non-normal latent variables due to issues identified with the more commonly used Vale and Maurelli (1983) method [@foldnes_olsson_2016].

### Data Generation

All the population models were first specified to achieve target reliability levels ($\rho \approx 0.4, 0.6, 0.8$) and $R^2 \approx 0.30$ under normally distributed predictor latent variables. The variance parameters derived from these normal-based models were then used unchanged across all distributional conditions, allowing us to isolate the impact of distributional violations on model estimation.

For the structural model, the residual variance $\psi_{33}$ was set such that under normality: $R^2_{\eta_3} = \frac{\text{Var}(\eta_3^*)}{\text{Var}(\eta_3^*) + \psi_{33}} \approx 0.30$, where $\eta_3^*$ represents the deterministic portion of $\eta_3$. Similarly, measurement error variances $\theta_{jj}$ were determined to achieve: $\rho_{x_j} = \frac{\lambda_{j}^2 \cdot \phi_{kk}}{\lambda_{j}^2 \cdot \phi_{kk} + \theta_{jj}} \approx \rho$, where $\lambda_j = 1$ (unit loadings), $\phi_{kk}$ represents the latent variable variance under normality, and $\rho \in \{0.4, 0.6, 0.8\}$.

These fixed variance parameters were then used to generate data under three distributional conditions. The predictor latent variables maintained the covariance structure: $\boldsymbol{\Phi} = \begin{bmatrix} 1 & 0.375 \\ 0.375 & 1 \end{bmatrix}$ across all conditions. Under normal conditions, $(\eta_1, \eta_2)' \sim \mathcal{N}(\mathbf{0}, \boldsymbol{\Phi})$ was generated using the `rIG()` function from the *covsim* package (version `r covsim_version`) [@R-covsim]. For non-normal conditions, the same function generated variables with population skewness $\gamma_1 = 2$ and excess kurtosis $\gamma_2 = 7$, while preserving $\boldsymbol{\Phi}$. The uniform condition employed the *copula* package with a Gumbel–Hougaard copula (dependency parameter $\theta = 2$) to induce dependence between variables with $\mathcal{U}(-2.5, 2.5)$ marginal distributions. Following the approach of @mair_etall_2012 as implemented in @lonati_etall_2024, the copula-generated sample $\mathbf{X}$ was transformed via $\mathbf{Y} = \mathbf{X}\mathbf{S}_x^{-1/2}\boldsymbol{\Sigma}^{1/2}$, where $\mathbf{S}_x$ is the sample covariance matrix of $\mathbf{X}$. 

The dependent latent variable in the case of the full model was generated as:

$$\eta_3 = \beta_0 + \beta_1\eta_1 + \beta_2\eta_2 + \beta_3(\eta_1\eta_2) + \beta_4\eta_1^2 + \beta_5\eta_2^2 + \zeta$$

with parameters $\beta_0 = -0.255$, $\beta_1 = \beta_2 = 0.316$, $\beta_3 = 0.139$, $\beta_4 = \beta_5 = 0.101$. The structural residual $\zeta \sim \mathcal{N}(0, \psi_{33})$ used the same $\psi_{33}$ value derived under normality across all distributional conditions. For the linear model, we simply set $\beta_3 = \beta_4 = \beta_5 = 0$.

For the measurement model, observed indicators were generated through $\mathbf{y} = \boldsymbol{\Lambda}\boldsymbol{\eta} + \boldsymbol{\epsilon}$, where $\boldsymbol{\Lambda}$ contained unit loadings and $\boldsymbol{\epsilon} \sim \mathcal{N}(\mathbf{0}, \boldsymbol{\Theta})$. The diagonal elements of $\boldsymbol{\Theta}$ were the values determined under normality for each reliability condition, applied uniformly across all distributional conditions.

### Nonconvergence and Outliers

Before analyzing the simulation data, we inspected solutions where no estimates were produced. After ensuring that these were caused by a nonconvergent estimator, we excluded the entire iteration from the analysis across approaches. As mentioned in @lonati_etall_2024, a nonconvergent solution signals a replication that could also be challenging for the remaining methods. The convergence rate for each method was calculated as $\text{Convergence}_{rate} = N_{\text{complete}}/N_{\text{total}} \times 100\%$, where $N_{\text{complete}}$ represents successfully converged replications with complete output and $N_{\text{total}}$ represents all attempted replications for that method. 

Following Boomsma (2013), we used the box-plot method to identify outliers in the parameter estimates. Proceeding with one method-parameter combination at a time, we flagged all estimates that were more than three interquartile ranges below the first quartile or above the third quartile as outliers, formally defined as estimates outside the bounds $[Q_1 - 3 \times \text{IQR}, Q_3 + 3 \times \text{IQR}]$, where $Q_1$ and $Q_3$ represent the first and third quartiles and $\text{IQR} = Q_3 - Q_1$. Importantly, to avoid the arguably arbitrary interquartile range chosen, we also computed median estimates, median bias, and median absolute deviation (MAD) on the full set of converged solutions before outlier removal. Therefore, all metrics were calculated after removing non-converged replications, but with median-based robust measures computed before outlier removal and mean-based measures computed after outlier removal. The final effective sample size used for computing mean-based metrics, after excluding both non-converged cases and outliers.

### Performance Measures

Method performance was assessed through multiple metrics following the formulas from the *simhelpers* package [@R-simhelpers], with the exception of the median-based metrics that were based on @brandt_etall_2020. Following the *simhelpers* documentation and references therein, we also quantified the Monte Carlo Standard Errors (MCSE) simulation uncertainty for most of the reported performance measures. Generally speaking, the measures are classified in terms of absolute and relative criteria measures, standard error assessment, rejection rate, hypothesis testing and confidence intervals. In the main text, we only report and discuss the metrics reported in Table 1 for the interaction and quadratic effecs (e.g., $\beta_3$, $\beta_4$, and $\beta_5$). For the complete set of measures and main effects, we refer the reader to the online supplementary materials 1. For clarity purposes, let $B$ denote an estimator for parameter $\beta$, with $K$ valid replications producing estimates $B_1, ..., B_K$ for each simulation condition. The sample mean and variance were calculated as $\bar{B} = (1/K)\sum_{k=1}^{K}B_k$ and $S_B^2 = (1/(K-1))\sum_{k=1}^{K}(B_k - \bar{B})^2$. The standard deviation was calculated as $S_B = \sqrt{S_B^2}$. 

\landscape
\footnotesize

## Table 1

| Performance Measure | Empirical Calculation | MCSE |
|---|---|---|
| **Absolute Criteria** | | |
| Absolute Bias | $\bar{B} - \beta$ | $\sqrt{S_B^2/K}$ |
| MSE | $\frac{1}{K}\sum_{k=1}^{K}(B_k - \beta)^2$ | $\sqrt{\frac{1}{K}[S_B^4(k_B - 1) + 4S_B^2 g_B(\bar{B} - \beta) + 4S_B^2(\bar{B} - \beta)^2]}$ |
| RMSE | $\sqrt{\frac{1}{K}\sum_{k=1}^{K}(B_k - \beta)^2}$ | $\sqrt{\frac{K-1}{K}\sum_{j=1}^{K}(\text{RMSE}_{(j)} - \text{RMSE})^2}$ |
| **Relative Criteria** | | |
| Relative Bias | $(\frac{\bar{B}}{\beta})- 1$ | $\sqrt{S_B^2/(K\beta^2)}$ |
| Relative MSE | $\frac{(\bar{B} - \beta)^2 + S_B^2}{\beta^2}$ | $\sqrt{\frac{1}{K\beta^4}[S_B^4(k_B - 1) + 4S_B^2 g_B(\bar{B} - \beta) + 4S_B^2(\bar{B} - \beta)^2]}$ |
| Relative RMSE | $\sqrt{\frac{(\bar{B} - \beta)^2 + S_B^2}{\beta^2}}$ | $\sqrt{\frac{K-1}{K}\sum_{j=1}^{K}(\text{rRMSE}_{(j)} - \text{rRMSE})^2}$ |
| **Standard Error Assessment** | | |
| Mean SE | $\overline{SE} = \frac{1}{K}\sum_{k=1}^{K}\widehat{SE}_k$ | — |
| SE Ratio | $\overline{SE}/S_B$ | — |
| **Hypothesis Testing** | | |
| Rejection Rate | $r_\alpha = \frac{1}{K}\sum_{k=1}^{K}I(P_k < \alpha)$ | $\sqrt{r_\alpha(1-r_\alpha)/K}$ |
| **Confidence Intervals** | | |
| Coverage | $c_\beta = \frac{1}{K}\sum_{k=1}^{K}I(A_k \leq \beta \leq B_k)$ | $\sqrt{c_\beta(1-c_\beta)/K}$ |

*Note.* $B$ = parameter estimator; $\beta$ = true parameter value; $K$ = number of replications; $S_B^2$ = sample variance; $k_B$ = standardized kurtosis; $g_B$ = standardized skewness; $I(\cdot)$ = indicator function; $P_k$ = p-value from replication $k$; $\alpha$ = significance level; $A_k$, $B_k$ = CI endpoints; $S_W^2$ = variance of CI widths. MCSE = Monte Carlo Standard Error. Dashes indicate MCSEs not computed for these measures.

\endlandscape
\normalsize

### A note on robust estimators and more for the approaches under evaluation

As mentioned in the introduction, the literature has evaluated different strategies for constructing PIs. Additionally, the literature has also proposed slight modifications for other approaches, such as the reliability-corrected single-indicator LMS (Cheung & Lau, 2017; Su et al., 2019, as cited in Lonati et al., 2024), which has shown to be less affected by violations of distributional assumptions. Even differences between Wald z test and likelihood ratio test for hypothesis testing were investigated [@cham_etall_2012]. Notably, however, it is the usage in previous simulation studies of the so-called "robust" corrections to mitigate nonnormality, where these corrections differ in important ways [@savalei_rosseel_2021].

Indeed, some approaches use robust ML estimators such as MLR, which retain the ML estimates but replace normal-theory standard errors and test statistics with Huber–White sandwich standard errors and a Yuan–Bentler corrected chi-square test [@brandt_etall_2014; @brandt_etall_2020; @lonati_etall_2024]. A further variant is the Satorra–Bentler correction, which rescales the chi-square statistic (and, in some implementations, also the standard errors) to improve its performance under nonnormality [@cham_etall_2012]. Despite their widespread use, it is not yet clear whether these robust corrections consistently improve inference across conditions. In fact, sandwich-type standard errors are only asymptotically valid and may remain underestimated in small samples [@lonati_etall_2024]. We therefore relied on standard implementations in our main analyses. In the online supplementary materials 2, we analyzed all approaches with robust standard errors, as well as alternative PI matching strategies and the reliability-corrected single-indicator. The results show no substantial improvements. 

```{r simulation-script, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
library(lavaan)
library(modsem)
library(doParallel)
library(doRNG)
library(covsim)
library(copula)
library(stringr)

# Load required files
load("all_models_with_null.RData")  # Contains calibrated_models, null_models, and all_models
source("Methods(1).R")  # Your modified methods file

# =============================================================================
# SIMULATION PARAMETERS
# =============================================================================

N_REPLICATIONS <- 500
SAMPLE_SIZES <- c(400, 1000)
SEED_START <- 123

# analysis model (for fitting - no fixed values)
analysis.model <- "
eta1 =~ x1 + x2 + x3
eta2 =~ x4 + x5 + x6
eta3 =~ x7 + x8 + x9

eta3 ~ eta1 + eta2 + eta1:eta2 + eta1:eta1 + eta2:eta2
"

# distribution parameters
distributions <- list(
  normal = list(skewness = c(0, 0), excesskurtosis = c(0, 0), distr.exo = "normal.rIG"),
  nonnormal = list(skewness = c(2, 2), excesskurtosis = c(7, 7), distr.exo = "nonnormal.rIG"),
  uniform = list(skewness = c(0, 0), excesskurtosis = c(0, 0), distr.exo = "unif")
)

# =============================================================================
# MAIN SIMULATION
# =============================================================================

dir.create("sim_results", showWarnings = FALSE)
timestamp <- format(Sys.time(), "%Y%m%d_%H%M")
results_dir <- paste0("sim_results/run_", timestamp)
dir.create(results_dir, showWarnings = FALSE)

# conditions
conditions <- expand.grid(
  N = SAMPLE_SIZES,
  Rel = c(0.4, 0.6, 0.8),
  Distribution = names(distributions),
  Model_Type = c("alternative", "null"),  # Add model type
  stringsAsFactors = FALSE
)

# Create model names based on model type and reliability
conditions$model_name <- ifelse(
  conditions$Model_Type == "null",
  paste0("null_normal_rel", gsub("\\.", "", as.character(conditions$Rel))),
  paste0("normal_rel", gsub("\\.", "", as.character(conditions$Rel)))
)

# track actual distribution used for generation
conditions$generation_distribution <- conditions$Distribution

# Parallel setup
n_cores <- detectCores() - 6
cl <- makeCluster(n_cores)
registerDoParallel(cl)
clusterExport(cl, c("GenerateData", "method_analytic", "method_dblcent", "method_sam", 
                    "analysis.model", "all_models", "distributions"))

# run simulation
all_results <- list()
start_time <- Sys.time()

for(cond in 1:nrow(conditions)) {
  cat("\n========================================")
  cat("\nCondition", cond, "of", nrow(conditions))
  cat("\n- Sample size:", conditions$N[cond])
  cat("\n- Target reliability:", conditions$Rel[cond])
  cat("\n- Model type:", conditions$Model_Type[cond])
  cat("\n- Actual distribution:", conditions$Distribution[cond])
  cat("\n- Using model:", conditions$model_name[cond])
  cat("\n========================================\n")
  
  # Get the appropriate model (normal or null)
  population_model <- all_models[[conditions$model_name[cond]]]
  
  if(is.null(population_model)) {
    cat("WARNING: Model", conditions$model_name[cond], "not found. Skipping...\n")
    next
  }
  
  # distribution parameters for data generation
  dist_params <- distributions[[conditions$Distribution[cond]]]
  
  # condition-specific variables to cluster
  clusterExport(cl, c("population_model", "dist_params", "conditions", "cond"), 
                envir = environment())
  
  # MODIFIED: Store full tables instead of extracted parameters
  res <- list(
    lms_tables = vector("list", N_REPLICATIONS),
    qml_tables = vector("list", N_REPLICATIONS),
    dblcent_tables = vector("list", N_REPLICATIONS),
    sam_tables = vector("list", N_REPLICATIONS),
    timing = data.frame(lms = numeric(N_REPLICATIONS), 
                        qml = numeric(N_REPLICATIONS),
                        dblcent = numeric(N_REPLICATIONS), 
                        sam = numeric(N_REPLICATIONS)),
    # track observed R² and reliabilities
    observed_r2 = numeric(N_REPLICATIONS),
    observed_rel = matrix(NA, nrow = N_REPLICATIONS, ncol = 9)
  )
  
  # run replications in parallel
  parallel_results <- foreach(i = 1:N_REPLICATIONS,
                              .packages = c("lavaan", "modsem", "covsim", "copula"),
                              .errorhandling = "pass",
                              .options.RNG = SEED_START + cond * 1000) %dorng% {
                                
                                # generate data using NORMAL-CALIBRATED model with ACTUAL distribution
                                Data <- try(GenerateData(
                                  model = population_model,
                                  N = conditions$N[cond],
                                  skewness = dist_params$skewness,
                                  excesskurtosis = dist_params$excesskurtosis,
                                  distr.exo = dist_params$distr.exo,
                                  distr.epsilon = "normal",
                                  distr.zeta = "normal",
                                  add.eta = FALSE,
                                  return.info = TRUE
                                ), silent = TRUE)
                                
                                if(inherits(Data, "try-error")) return(NULL)
                                
                                # observed metrics
                                observed_metrics <- list(
                                  r2 = attr(Data, "observed_R2")$eta3,
                                  rel = unlist(attr(Data, "observed_reliabilities"))
                                )
                                
                                # remove attributes for methods
                                data_clean <- as.data.frame(Data)
                                attributes(data_clean) <- attributes(data_clean)[c("names", "row.names", "class")]
                                
                                # run all methods and store FULL TABLES
                                results <- list(observed_metrics = observed_metrics)
                                
                                # LMS - returns full parTable
                                t0 <- Sys.time()
                                lms_table <- try(method_analytic(Data = data_clean, 
                                                                 model.fit = analysis.model, 
                                                                 method = "lms"), silent = TRUE)
                                if(!inherits(lms_table, "try-error")) {
                                  results$lms_table <- lms_table
                                  results$lms_timing <- as.numeric(difftime(Sys.time(), t0, units = "secs"))
                                }
                                
                                # QML - returns full parTable
                                t0 <- Sys.time()
                                qml_table <- try(method_analytic(Data = data_clean, 
                                                                 model.fit = analysis.model, 
                                                                 method = "qml"), silent = TRUE)
                                if(!inherits(qml_table, "try-error")) {
                                  results$qml_table <- qml_table
                                  results$qml_timing <- as.numeric(difftime(Sys.time(), t0, units = "secs"))
                                }
                                
                                # UCA - returns full coefParTable
                                t0 <- Sys.time()
                                uca_table <- try(method_dblcent(Data = data_clean, 
                                                                model.fit = analysis.model), silent = TRUE)
                                if(!inherits(uca_table, "try-error")) {
                                  results$dblcent_table <- uca_table
                                  results$dblcent_timing <- as.numeric(difftime(Sys.time(), t0, units = "secs"))
                                }
                                
                                # SAM - returns full parameterEstimates table
                                t0 <- Sys.time()
                                sam_table <- try(method_sam(Data = data_clean, 
                                                            model.fit = analysis.model), silent = TRUE)
                                if(!inherits(sam_table, "try-error")) {
                                  results$sam_table <- sam_table
                                  results$sam_timing <- as.numeric(difftime(Sys.time(), t0, units = "secs"))
                                }
                                
                                results
                              }
  
  # RNG states 
  rng_states_for_condition <- attr(parallel_results, "rng")
  
  # MODIFIED: Store full tables instead of extracting parameters
  for(i in 1:N_REPLICATIONS) {
    if(!is.null(parallel_results[[i]]) && !inherits(parallel_results[[i]], "error")) {
      
      if(!is.null(parallel_results[[i]]$observed_metrics)) {
        res$observed_r2[i] <- parallel_results[[i]]$observed_metrics$r2
        res$observed_rel[i,] <- parallel_results[[i]]$observed_metrics$rel[1:9]
      }
      
      # Store full tables
      if(!is.null(parallel_results[[i]]$lms_table)) {
        res$lms_tables[[i]] <- parallel_results[[i]]$lms_table
        res$timing$lms[i] <- parallel_results[[i]]$lms_timing
      }
      
      if(!is.null(parallel_results[[i]]$qml_table)) {
        res$qml_tables[[i]] <- parallel_results[[i]]$qml_table
        res$timing$qml[i] <- parallel_results[[i]]$qml_timing
      }
      
      if(!is.null(parallel_results[[i]]$dblcent_table)) {
        res$dblcent_tables[[i]] <- parallel_results[[i]]$dblcent_table
        res$timing$dblcent[i] <- parallel_results[[i]]$dblcent_timing
      }
      
      if(!is.null(parallel_results[[i]]$sam_table)) {
        res$sam_tables[[i]] <- parallel_results[[i]]$sam_table
        res$timing$sam[i] <- parallel_results[[i]]$sam_timing
      }
    }
  }
  
  res$rng_states <- rng_states_for_condition
  
  cat("\nObserved metrics across replications:")
  cat("\n- Mean R²:", mean(res$observed_r2, na.rm = TRUE))
  cat("\n- Mean reliabilities:", round(colMeans(res$observed_rel, na.rm = TRUE), 3))
  cat("\n")
  
  all_results[[cond]] <- list(
    condition = conditions[cond, ], 
    results = res,
    true_parameters = if(conditions$Model_Type[cond] == "null") {
      c(0.316, 0.316, 0, 0, 0)  # null model: interaction and quadratic terms are 0
    } else {
      c(0.316, 0.316, 0.139, 0.101, 0.101)  # full model with all effects
    }
  )
  
  # checkpoint
  if(cond %% 5 == 0 || cond == nrow(conditions)) {
    save(all_results, conditions, file = sprintf("%s/checkpoint_%d.RData", results_dir, cond))
  }
  
  gc()
}

stopCluster(cl)

save(all_results, conditions, file = paste0(results_dir, "/final_results.RData"))

total_time <- difftime(Sys.time(), start_time, units = "hours")
cat(sprintf("\n\nSimulation completed in %.2f hours\n", total_time))
```

## Simulation study 2

### Simulation Conditions

[...]

### Data Generation

[...]
