---
title: ""
author: ""
date: ""
output: html_document
---

```{r package versions, echo=FALSE}
modsem_version <- packageVersion("modsem")
lavaan_version <- packageVersion("lavaan")
covsim_version <- packageVersion("covsim")
faux_version <- packageVersion("faux")
copula_version <- packageVersion("copula")
doparallel_version <- packageVersion("doParallel")
dorng_version <- packageVersion("dorng")
R_version <- getRversion()
```

# Simulation Study 1

In this section, we present the simulation design. This includes the simulation conditions, computational information, and the metrics used to evaluate the performance of the different approaches. The information presented here follows the suggestions from previous articles that investigated the quality of simulation studies [@siepe_etall_2024; @white_etall_2024; @morris_etall_2019].

## Reproducibility and Computational details 

The simulation was conducted on a Mac Studio with an Apple M4 Max chip (with 14 cores and 36 GB of RAM), running macOS Sequoia 15.5. All analyses were performed in R [@R-base] (version `r R_version`). Parallel processing was implemented through the *doParalell* package (version `r doparallel_version`) [@R-doParallel], with *doRNG* (version `r dorng_version`) [@R-doRNG] to ensure independent and reproducible random number streams. For the DBLCENT, LMS, and QML approach, the *modsem* package was used [@kjell_etall_2024] (version `r modsem_version`). For the LSAM approach, the *lavaan* package was used [@R-lavaan] (version `r lavaan_version`). Importantly, we used the default settings for the functions provided in the packages^[This is important to acknowledge because there are arguments for the functions used that, in principle, could be tweaked to obtain better results. For instance, one could change the maximum steps for the M-step in the EM algorithm for the LMS. However, this also leads to substantial researcher degrees of freedom and hence were avoided.].

All the materials to reproduce this article available on the following GitHub link: https://github.com/felipelfv/Simulation_First_PhD_Article.git. Specifically, we included a `README` file that contains the step-by-step information required to reproduce the results reported, a `sessionInfo` file, the *renv* lockfile with the information for the relevant packages used [@R-renv], a Dockerfile for system dependencies, and all the estimates obtained for all iterations. Moreover, this paper was written with *papaja* [@R-papaja] in Rmarkdown.

## Simulation Conditions

The simulation design employed a fully crossed factorial design with 2 (sample sizes) × 3 (reliability levels) × 3 (latent predictor distributions) to evaluate the performance of DBLCENT, LMS, QML, and LSAM. This factorial design yielded 18 unique experimental conditions^[To examine Type I error rates and power, we implemented two model specifications: (a) data generated under a null model (no interaction and quadratic terms) but fitted with a full interaction model, and (b) data generated under and fitted with a full interaction model. Thus, resulting in 36 total conditions. The null model conditions allow us to assess Type I error rates, while the full model conditions evaluate parameter recovery and statistical power.], each replicated 1000 times. 

Sample sizes of 400 and 1000 were selected to represent moderate to large samples. While some simulation studies have examined more extensive ranges of sample sizes [@brandt_etall_2024; @cham_etall_2012; @wall_amemyia_2000; @lonati_etall_2024], we focused on 400 and 1000 for specific reasons. We sought to examine an intermediate sample size not used in the previous simulations (which used n = 250, 350, 500, or 650). Moreover, it allows us to explore performance just below the 500 threshold that some studies suggest as a minimum for complex latent interaction models (Wall et al., 2012, as cited in Brandt et al., 2020), while still representing a realistic sample size in applied research. In contrast, n = 1000 enables us to evaluate the asymptotic properties of these estimators, while also aligning with previous simulation studies that commonly employed this sample size. Last, although examining additional sample size conditions would provide more information, computational constraints required a more focused selection.

Three reliability levels (0.4, 0.6, and 0.8) were examined, covering a broad range of measurement quality. While previous simulations have typically focused on high reliability conditions (i.e., 0.8 in @brandt_etall_2014; 0.7 and 0.8 in @lonati_etall_2024) or contrasted high versus low reliability (i.e., 0.8 and 0.5 in @brandt_etall_2020), we extended this range by including 0.4 to examine method performance under poor measurement conditions.

The three distributional conditions investigated were: normal, non-normal, and uniform distributions. In the baseline condition, all latent predictor variables, structural disturbance, and indicator error terms were normal. For the non-normal condition, we generated latent predictors with skewness of 2 and excess kurtosis of 7. These values fall somewhat within the range examined in a previous simulation [@lonati_etall_2024]. The uniform distribution was included following @wall_amemyia_2000 and @lonati_etall_2024. Specifically, this condition is particularly relevant for testing LSAM, as it is expected to perform similarly to 2SMM under this distributional condition initially examined in @wall_amemyia_2000. We used the copula method to generate correlated non-normal latent variables due to issues identified with the more commonly used Vale and Maurelli (1983) method [@foldnes_olsson_2016].

## Data Generation

All the population models were first specified to achieve target reliability levels ($\rho \approx 0.4, 0.6, 0.8$) and $R^2 \approx 0.30$ under normally distributed predictor latent variables. The variance parameters derived from these normal-based models were then used unchanged across all distributional conditions, allowing us to isolate the impact of distributional violations on model estimation.

For the structural model, the residual variance $\psi_{33}$ was set such that under normality: $R^2_{\eta_3} = \frac{\text{Var}(\eta_3^*)}{\text{Var}(\eta_3^*) + \psi_{33}} \approx 0.30$, where $\eta_3^*$ represents the deterministic portion of $\eta_3$. Similarly, measurement error variances $\theta_{jj}$ were determined to achieve: $\rho_{x_j} = \frac{\lambda_{j}^2 \cdot \phi_{kk}}{\lambda_{j}^2 \cdot \phi_{kk} + \theta_{jj}} \approx \rho$, where $\lambda_j = 1$ (unit loadings), $\phi_{kk}$ represents the latent variable variance under normality, and $\rho \in \{0.4, 0.6, 0.8\}$.

These fixed variance parameters were then used to generate data under three distributional conditions. The predictor latent variables maintained the covariance structure: $\boldsymbol{\Phi} = \begin{bmatrix} 1 & 0.375 \\ 0.375 & 1 \end{bmatrix}$ across all conditions. Under normal conditions, $(\eta_1, \eta_2)' \sim \mathcal{N}(\mathbf{0}, \boldsymbol{\Phi})$ was generated using the `rIG()` function from the *covsim* package (version `r covsim_version`) [@R-covsim]. For non-normal conditions, the same function generated variables with population skewness $\gamma_1 = 2$ and excess kurtosis $\gamma_2 = 7$, while preserving $\boldsymbol{\Phi}$. The uniform condition employed the *copula* package (version: `r copula_version`) [@] with a Gumbel copula where marginal distributions were $\text{Uniform}(-2.5, 2.5)$, transformed via $\mathbf{Y} = \mathbf{X} \mathbf{S}_x^{-1/2} \boldsymbol{\Sigma}^{1/2}$ to achieve the target covariance structure.

The dependent latent variable was generated as $\eta_3 = \beta_0 + \beta_1\eta_1 + \beta_2\eta_2 + \beta_3(\eta_1 \times \eta_2) + \beta_4\eta_1^2 + \beta_5\eta_2^2 + \zeta$, with parameters $\beta_0 = -0.255$, $\beta_1 = \beta_2 = 0.316$, $\beta_3 = 0.139$, $\beta_4 = \beta_5 = 0.101$. The structural residual $\zeta \sim \mathcal{N}(0, \psi_{33})$ used the same $\psi_{33}$ value derived under normality across all distributional conditions.

For the measurement model, observed indicators were generated through $\mathbf{y} = \boldsymbol{\Lambda}\boldsymbol{\eta} + \boldsymbol{\epsilon}$, where $\boldsymbol{\Lambda}$ contained unit loadings and $\boldsymbol{\epsilon} \sim \mathcal{N}(\mathbf{0}, \boldsymbol{\Theta})$. The diagonal elements of $\boldsymbol{\Theta}$ were the values determined under normality for each reliability condition, applied uniformly across all distributional conditions.

## Nonconvergence and Outliers

Before analyzing the simulation data, we inspected solutions where no estimates were produced. After ensuring that these were caused by a nonconvergent estimator, we excluded these specific method-replication combinations from analysis. The convergence rate for each method was calculated as $\text{Convergence}_{rate} = N_{\text{complete}}/N_{\text{total}} \times 100\%$, where $N_{\text{complete}}$ represents successfully converged replications with complete output and $N_{\text{total}}$ represents all attempted replications for that method. 

Following Boomsma (2013), we used the box-plot method to identify outliers in the parameter estimates. Proceeding with one method-parameter combination at a time, we flagged all estimates that were more than three interquartile ranges below the first quartile or above the third quartile as outliers, formally defined as estimates outside the bounds $[Q_1 - 3 \times \text{IQR}, Q_3 + 3 \times \text{IQR}]$, where $Q_1$ and $Q_3$ represent the first and third quartiles and $\text{IQR} = Q_3 - Q_1$. Importantly, to avoid the arguably arbitrary interquartile range chosen, we also computed median estimates, median bias, and median absolute deviation (MAD) on the full set of converged solutions before outlier removal. Therefore, all metrics were calculated after removing non-converged replications, but with median-based robust measures computed before outlier removal and mean-based measures computed after outlier removal. The final effective sample size used for computing mean-based metrics, after excluding both non-converged cases and outliers, was calculated as $N_{\text{effective}} = N_{\text{complete}} - N_{\text{outliers}}$.

## Performance Measures

Method performance was assessed through multiple metrics following the formulas from the simhelpers package [@R-simhelpers], with the exception of the median-based metrics. Let $T$ denote an estimator for parameter $\theta$, with $K$ valid replications producing estimates $T_1, ..., T_K$ for each simulation condition. The sample mean and variance were calculated as $\bar{T} = (1/K)\sum_{k=1}^{K}T_k$ and $S_T^2 = (1/(K-1))\sum_{k=1}^{K}(T_k - \bar{T})^2$.

### Absolute Criteria

The mean estimate, $\bar{T} = (1/K)\sum_{k=1}^{K}T_k$, provides the average of the parameter estimates across replications. Bias characterizes whether an estimator tends to lie above or below the true parameter on average, calculated as $\text{Bias} = E[T] - \theta$, empirically estimated as $\bar{T} - \theta$. Variance characterizes the precision of an estimator as the average squared deviation from its mean, empirically estimated as $S_T^2$. The standard deviation, $S_T = \sqrt{S_T^2}$, provides precision in the scale of the estimates. Mean squared error measures accuracy by quantifying how far off an estimator is from the true parameter on average, calculated as $\text{MSE} = E[(T - \theta)^2]$, empirically computed as $(1/K)\sum_{k=1}^{K}(T_k - \theta)^2$. Root mean squared error, $\text{RMSE} = \sqrt{(1/K)\sum_{k=1}^{K}(T_k - \theta)^2}$, expresses accuracy in the scale of the estimates.

Robust alternatives to these mean-based measures included the median estimate, $\text{Median}(T)$, median bias, $\text{Bias}_{\text{median}} = \text{Median}(T) - \theta$, the median absolute deviation, $\text{MAD} = \text{Median}(|T_k - \text{Median}(T)|)$, and median-based RMSE, $\text{RMSE}_{\text{median}} = \sqrt{\text{Bias}_{\text{median}}^2 + \text{MAD}^2}$. These were based on @brandt_etall_2020.

### Relative Criteria

Relative criteria express performance as proportions of the true parameter value, applicable when $\theta \neq 0$. Relative bias was defined as $E[T]/\theta$, empirically estimated as $\bar{T}/\theta$. The relative difference from true parameter, often reported as percent relative bias, was calculated as $(\bar{T} - \theta)/\theta \times 100\%$. Relative MSE was computed as $((\bar{T} - \theta)^2 + S_T^2)/\theta^2$, and relative RMSE as $\sqrt{((\bar{T} - \theta)^2 + S_T^2)/\theta^2}$. 

For robust measures, relative median bias was calculated as $(\text{Median}(T) - \theta)/\theta$, with percent relative median bias as $\text{PRB}_{\text{median}} = \text{RB}_{\text{median}} \times 100\%$.

### Standard Error Assessment

The accuracy of standard error estimation was evaluated through the mean standard error, $\overline{SE} = (1/K)\sum_{k=1}^{K}\widehat{SE}_k$, where $\widehat{SE}_k$ represents the estimated standard error from replication $k$. The standard error ratio, $\text{SE Ratio} = \overline{SE}/S_T$, assesses whether standard errors are accurately estimated, with values close to unity indicating unbiased standard error estimation.

### Hypothesis Testing and Confidence Intervals

Rejection rate captures the proportion of hypothesis tests rejecting the null hypothesis at significance level $\alpha$, calculated as $r_\alpha = (1/K)\sum_{k=1}^{K}I(P_k < \alpha)$, where $P_k$ denotes the p-value from replication $k$ and $I(\cdot)$ is the indicator function. When the true parameter equals the null value ($\theta = 0$), this rejection rate represents the Type I error rate. When the alternative hypothesis is true ($\theta \neq 0$), the rejection rate measures statistical power.

Coverage quantifies the proportion of confidence intervals containing the true parameter. For confidence intervals with nominal level $\beta$, where $A_k$ and $B_k$ denote the lower and upper endpoints from replication $k$, coverage was calculated as $c_\beta = (1/K)\sum_{k=1}^{K}I(A_k \leq \theta \leq B_k)$. The average confidence interval width, $\bar{W} = \bar{B} - \bar{A}$, where $W_k = B_k - A_k$, quantifies the precision of interval estimators.

### Monte Carlo Standard Errors (MCSE)

Following the @R-simhelpers documentation and references therein, MCSE quantified simulation uncertainty. For bias, $\text{MCSE}_{\text{Bias}} = \sqrt{S_T^2/K}$. For variance, $\text{MCSE}_{\text{Var}} = S_T^2\sqrt{(k_T - 1)/K}$, where $k_T = (1/(KS_T^4))\sum_{k=1}^{K}(T_k - \bar{T})^4$ is the standardized kurtosis. For standard deviation, using the jackknife technique with $S_{T(j)}^2 = (1/(K-2))[(K-1)S_T^2 - (K/(K-1))(T_j - \bar{T})^2]$, the MCSE was $\text{MCSE}_{S_T} = \sqrt{((K-1)/K)\sum_{j=1}^{K}(\sqrt{S_{T(j)}^2} - S_T)^2}$. For MSE, $\text{MCSE}_{\text{MSE}} = \sqrt{(1/K)[S_T^4(k_T - 1) + 4S_T^2 g_T(\bar{T} - \theta) + 4S_T^2(\bar{T} - \theta)^2]}$, where $g_T = (1/(KS_T^3))\sum_{k=1}^{K}(T_k - \bar{T})^3$ is the standardized skewness. For RMSE, using the jackknife with $T_{(j)} = (K\bar{T} - T_j)/(K-1)$, $S_{T(j)}^2 = (1/(K-2))[(K-1)S_T^2 - (K/(K-1))(T_j - \bar{T})^2]$, and $\text{RMSE}_{(j)} = \sqrt{(T_{(j)} - \theta)^2 + S_{T(j)}^2}$, the MCSE was $\text{MCSE}_{\text{RMSE}} = \sqrt{((K-1)/K)\sum_{j=1}^{K}(\text{RMSE}_{(j)} - \text{RMSE})^2}$. For relative bias when $\theta \neq 0$, $\text{MCSE}_{\text{RB}} = \sqrt{S_T^2/(K\theta^2)}$. For relative MSE, $\text{MCSE}_{\text{Relative MSE}} = \sqrt{(1/(K\theta^4))[S_T^4(k_T - 1) + 4S_T^2 g_T(\bar{T} - \theta) + 4S_T^2(\bar{T} - \theta)^2]}$. For relative RMSE, using the jackknife with $\text{rRMSE}_{(j)} = \sqrt{((T_{(j)} - \theta)^2 + S_{T(j)}^2)/\theta^2}$, the MCSE was $\text{MCSE}_{\text{Relative RMSE}} = \sqrt{((K-1)/K)\sum_{j=1}^{K}(\text{rRMSE}_{(j)} - \text{rRMSE})^2}$. For variance estimators $V$ estimating $\lambda = \text{Var}(T)$, with $\bar{V} = (1/K)\sum_{k=1}^{K}V_k$ and $S_V^2 = (1/(K-1))\sum_{k=1}^{K}(V_k - \bar{V})^2$, the relative bias $\text{rB} = \bar{V}/S_T^2$ had MCSE computed via jackknife as $\text{MCSE}_{\text{rB}} = \sqrt{((K-1)/K)\sum_{j=1}^{K}(\text{rB}_{(j)} - \text{rB})^2}$, where $\text{rB}_{(j)} = V_{(j)}/S_{T(j)}^2$ with $V_{(j)} = (K\bar{V} - V_j)/(K-1)$. Similarly, relative MSE and RMSE for variance estimators used jackknife MCSEs. For proportions such as coverage and rejection rates, $\text{MCSE}_p = \sqrt{p(1-p)/K}$. For confidence interval width with sample variance $S_W^2$, $\text{MCSE}_{\text{Width}} = \sqrt{S_W^2/K}$.

### Interpretation and Implementation

Relative bias values within ±5% were considered acceptable, those within ±10% moderate, and values exceeding ±10% substantial. Coverage rates between 93% and 97% were deemed acceptable for nominal 95% confidence intervals. Type I error rates between 0.025 and 0.075 were considered acceptable for a nominal $\alpha = 0.05$ level. Standard error ratios between 0.9 and 1.1 indicated adequate standard error estimation. Statistical power of at least 80% was considered desirable for detecting meaningful effects.

The implementation distinguished between robust and non-robust metrics, with median-based measures (median, MAD, median bias) calculated before outlier removal to leverage their natural robustness, while mean-based measures were calculated after removing estimates beyond three interquartile ranges from the quartiles. Only complete cases with successful convergence and all metrics computed were included in the analysis. Conditions with fewer than 10 valid replications after data cleaning were excluded to ensure stable estimates.

These metrics collectively provide a comprehensive assessment of estimator performance, covering point estimation accuracy, uncertainty quantification, and the validity of statistical inference procedures under varying conditions of measurement quality and distributional misspecification.

## A note on robust estimators and different strategies for the approaches under evaluation

As mentioned in the introduction, the literature has evaluated different strategies for constructing PIs. Additionally, the recently proposed reliability-corrected single-indicator LMS has shown to be less affected by violations of distributional assumptions, offering another alternative for handling latent interactions. Moreover, previous simulation studies have also employed various "robust" corrections to handle non-normality, though these take different forms. Some approaches use robust ML estimators like MLR that modify the entire estimation process and produce both different parameter estimates and corrected standard errors. Other approaches apply post-estimation corrections like Huber-White sandwich estimators that only adjust the standard errors while leaving parameter estimates unchanged. The Satorra-Bentler correction, which adjusts both test statistics and standard errors, has also been used.

However, it remains unclear from existing literature whether these robust corrections and alternative PI strategies consistently improve performance across different conditions. In fact, robust standard errors are valid only asymptotically and may still be slightly underestimated in small samples [@]. Given this uncertainty and to maintain clarity, we focused on standard implementations in our main analysis. We conducted supplementary analyses with robust standard errors for the DBLCENT, LMS, and QML approaches, as well as different PI matching strategies, which are available in the supplementary materials for interested readers.

```{r simulation-script, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
library(lavaan)
library(modsem)
library(doParallel)
library(doRNG)
library(covsim)
library(copula)
library(stringr)

# Load required files
load("all_models_with_null.RData")  # Contains calibrated_models, null_models, and all_models
source("Methods(1).R")  # Your modified methods file

# =============================================================================
# SIMULATION PARAMETERS
# =============================================================================

N_REPLICATIONS <- 500
SAMPLE_SIZES <- c(400, 1000)
SEED_START <- 123

# analysis model (for fitting - no fixed values)
analysis.model <- "
eta1 =~ x1 + x2 + x3
eta2 =~ x4 + x5 + x6
eta3 =~ x7 + x8 + x9

eta3 ~ eta1 + eta2 + eta1:eta2 + eta1:eta1 + eta2:eta2
"

# distribution parameters
distributions <- list(
  normal = list(skewness = c(0, 0), excesskurtosis = c(0, 0), distr.exo = "normal.rIG"),
  nonnormal = list(skewness = c(2, 2), excesskurtosis = c(7, 7), distr.exo = "nonnormal.rIG"),
  uniform = list(skewness = c(0, 0), excesskurtosis = c(0, 0), distr.exo = "unif")
)

# =============================================================================
# MAIN SIMULATION
# =============================================================================

dir.create("sim_results", showWarnings = FALSE)
timestamp <- format(Sys.time(), "%Y%m%d_%H%M")
results_dir <- paste0("sim_results/run_", timestamp)
dir.create(results_dir, showWarnings = FALSE)

# conditions
conditions <- expand.grid(
  N = SAMPLE_SIZES,
  Rel = c(0.4, 0.6, 0.8),
  Distribution = names(distributions),
  Model_Type = c("alternative", "null"),  # Add model type
  stringsAsFactors = FALSE
)

# Create model names based on model type and reliability
conditions$model_name <- ifelse(
  conditions$Model_Type == "null",
  paste0("null_normal_rel", gsub("\\.", "", as.character(conditions$Rel))),
  paste0("normal_rel", gsub("\\.", "", as.character(conditions$Rel)))
)

# track actual distribution used for generation
conditions$generation_distribution <- conditions$Distribution

# Parallel setup
n_cores <- detectCores() - 6
cl <- makeCluster(n_cores)
registerDoParallel(cl)
clusterExport(cl, c("GenerateData", "method_analytic", "method_dblcent", "method_sam", 
                    "analysis.model", "all_models", "distributions"))

# run simulation
all_results <- list()
start_time <- Sys.time()

for(cond in 1:nrow(conditions)) {
  cat("\n========================================")
  cat("\nCondition", cond, "of", nrow(conditions))
  cat("\n- Sample size:", conditions$N[cond])
  cat("\n- Target reliability:", conditions$Rel[cond])
  cat("\n- Model type:", conditions$Model_Type[cond])
  cat("\n- Actual distribution:", conditions$Distribution[cond])
  cat("\n- Using model:", conditions$model_name[cond])
  cat("\n========================================\n")
  
  # Get the appropriate model (normal or null)
  population_model <- all_models[[conditions$model_name[cond]]]
  
  if(is.null(population_model)) {
    cat("WARNING: Model", conditions$model_name[cond], "not found. Skipping...\n")
    next
  }
  
  # distribution parameters for data generation
  dist_params <- distributions[[conditions$Distribution[cond]]]
  
  # condition-specific variables to cluster
  clusterExport(cl, c("population_model", "dist_params", "conditions", "cond"), 
                envir = environment())
  
  # MODIFIED: Store full tables instead of extracted parameters
  res <- list(
    lms_tables = vector("list", N_REPLICATIONS),
    qml_tables = vector("list", N_REPLICATIONS),
    dblcent_tables = vector("list", N_REPLICATIONS),
    sam_tables = vector("list", N_REPLICATIONS),
    timing = data.frame(lms = numeric(N_REPLICATIONS), 
                        qml = numeric(N_REPLICATIONS),
                        dblcent = numeric(N_REPLICATIONS), 
                        sam = numeric(N_REPLICATIONS)),
    # track observed R² and reliabilities
    observed_r2 = numeric(N_REPLICATIONS),
    observed_rel = matrix(NA, nrow = N_REPLICATIONS, ncol = 9)
  )
  
  # run replications in parallel
  parallel_results <- foreach(i = 1:N_REPLICATIONS,
                              .packages = c("lavaan", "modsem", "covsim", "copula"),
                              .errorhandling = "pass",
                              .options.RNG = SEED_START + cond * 1000) %dorng% {
                                
                                # generate data using NORMAL-CALIBRATED model with ACTUAL distribution
                                Data <- try(GenerateData(
                                  model = population_model,
                                  N = conditions$N[cond],
                                  skewness = dist_params$skewness,
                                  excesskurtosis = dist_params$excesskurtosis,
                                  distr.exo = dist_params$distr.exo,
                                  distr.epsilon = "normal",
                                  distr.zeta = "normal",
                                  add.eta = FALSE,
                                  return.info = TRUE
                                ), silent = TRUE)
                                
                                if(inherits(Data, "try-error")) return(NULL)
                                
                                # observed metrics
                                observed_metrics <- list(
                                  r2 = attr(Data, "observed_R2")$eta3,
                                  rel = unlist(attr(Data, "observed_reliabilities"))
                                )
                                
                                # remove attributes for methods
                                data_clean <- as.data.frame(Data)
                                attributes(data_clean) <- attributes(data_clean)[c("names", "row.names", "class")]
                                
                                # run all methods and store FULL TABLES
                                results <- list(observed_metrics = observed_metrics)
                                
                                # LMS - returns full parTable
                                t0 <- Sys.time()
                                lms_table <- try(method_analytic(Data = data_clean, 
                                                                 model.fit = analysis.model, 
                                                                 method = "lms"), silent = TRUE)
                                if(!inherits(lms_table, "try-error")) {
                                  results$lms_table <- lms_table
                                  results$lms_timing <- as.numeric(difftime(Sys.time(), t0, units = "secs"))
                                }
                                
                                # QML - returns full parTable
                                t0 <- Sys.time()
                                qml_table <- try(method_analytic(Data = data_clean, 
                                                                 model.fit = analysis.model, 
                                                                 method = "qml"), silent = TRUE)
                                if(!inherits(qml_table, "try-error")) {
                                  results$qml_table <- qml_table
                                  results$qml_timing <- as.numeric(difftime(Sys.time(), t0, units = "secs"))
                                }
                                
                                # UCA - returns full coefParTable
                                t0 <- Sys.time()
                                uca_table <- try(method_dblcent(Data = data_clean, 
                                                                model.fit = analysis.model), silent = TRUE)
                                if(!inherits(uca_table, "try-error")) {
                                  results$dblcent_table <- uca_table
                                  results$dblcent_timing <- as.numeric(difftime(Sys.time(), t0, units = "secs"))
                                }
                                
                                # SAM - returns full parameterEstimates table
                                t0 <- Sys.time()
                                sam_table <- try(method_sam(Data = data_clean, 
                                                            model.fit = analysis.model), silent = TRUE)
                                if(!inherits(sam_table, "try-error")) {
                                  results$sam_table <- sam_table
                                  results$sam_timing <- as.numeric(difftime(Sys.time(), t0, units = "secs"))
                                }
                                
                                results
                              }
  
  # RNG states 
  rng_states_for_condition <- attr(parallel_results, "rng")
  
  # MODIFIED: Store full tables instead of extracting parameters
  for(i in 1:N_REPLICATIONS) {
    if(!is.null(parallel_results[[i]]) && !inherits(parallel_results[[i]], "error")) {
      
      if(!is.null(parallel_results[[i]]$observed_metrics)) {
        res$observed_r2[i] <- parallel_results[[i]]$observed_metrics$r2
        res$observed_rel[i,] <- parallel_results[[i]]$observed_metrics$rel[1:9]
      }
      
      # Store full tables
      if(!is.null(parallel_results[[i]]$lms_table)) {
        res$lms_tables[[i]] <- parallel_results[[i]]$lms_table
        res$timing$lms[i] <- parallel_results[[i]]$lms_timing
      }
      
      if(!is.null(parallel_results[[i]]$qml_table)) {
        res$qml_tables[[i]] <- parallel_results[[i]]$qml_table
        res$timing$qml[i] <- parallel_results[[i]]$qml_timing
      }
      
      if(!is.null(parallel_results[[i]]$dblcent_table)) {
        res$dblcent_tables[[i]] <- parallel_results[[i]]$dblcent_table
        res$timing$dblcent[i] <- parallel_results[[i]]$dblcent_timing
      }
      
      if(!is.null(parallel_results[[i]]$sam_table)) {
        res$sam_tables[[i]] <- parallel_results[[i]]$sam_table
        res$timing$sam[i] <- parallel_results[[i]]$sam_timing
      }
    }
  }
  
  res$rng_states <- rng_states_for_condition
  
  cat("\nObserved metrics across replications:")
  cat("\n- Mean R²:", mean(res$observed_r2, na.rm = TRUE))
  cat("\n- Mean reliabilities:", round(colMeans(res$observed_rel, na.rm = TRUE), 3))
  cat("\n")
  
  all_results[[cond]] <- list(
    condition = conditions[cond, ], 
    results = res,
    true_parameters = if(conditions$Model_Type[cond] == "null") {
      c(0.316, 0.316, 0, 0, 0)  # null model: interaction and quadratic terms are 0
    } else {
      c(0.316, 0.316, 0.139, 0.101, 0.101)  # full model with all effects
    }
  )
  
  # checkpoint
  if(cond %% 5 == 0 || cond == nrow(conditions)) {
    save(all_results, conditions, file = sprintf("%s/checkpoint_%d.RData", results_dir, cond))
  }
  
  gc()
}

stopCluster(cl)

save(all_results, conditions, file = paste0(results_dir, "/final_results.RData"))

total_time <- difftime(Sys.time(), start_time, units = "hours")
cat(sprintf("\n\nSimulation completed in %.2f hours\n", total_time))
```

