---
title             : "Supplemental Materials for Local Structural-After-Measurement (LSAM) and Traditional Approaches for Nonlinear Effects among Latent Variables: A Simulation Study"
shorttitle        : "Comparing LSAM and Traditional SEM Approaches"

figurelist        : yes
tablelist         : yes

header-includes:
  - \raggedbottom
  - \usepackage{pdflscape}
  - \usepackage{longtable} 
  - \usepackage{array}
  - \renewcommand{\thefigure}{S\arabic{figure}}  
  - \renewcommand{\thetable}{S\arabic{table}}   
  - \setcounter{figure}{0}                       
  - \setcounter{table}{0}                   

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
output            : papaja::apa6_pdf

classoption       : "man"

editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include = FALSE}
library(knitr) # for tables
library(ggplot2) # for figures
library(dplyr) # for data wrangling in results
library(simhelpers) # for most performance metrics and MCSE
library(kableExtra)

source("../Simulations/Plots.R")
source("../Simulations/Study_1/Results/Results(1).R")
source("../Simulations/Study_2/Results/Results(2).R")
```

Table S1 includes all the information for the calculation of all performance measures. Tables S2 contains the computation time for the different approaches for simulation 1 and simulation 2. Tables S3-S72 include the numerical results for large part of those metrics. Specifically, for the trimmed mean-based metrics, we did not include them in the tables as interpretation remains the same, but these can be retrieved on the GitHub repository ('results_study_1.rds' and 'results_study_2.rds'). 

Figures S1-S9 are the complete plots for simulation 1. For Simulation 2, we split the plots by distribution. Hence, we show part of the measures under normality, right-skewness, and uniform conditions respectively (Figures S10-S33). 

\landscape
\footnotesize
\begin{flushleft}
\textbf{Table S1}

\textit{Complete performance measures for evaluating parameter estimates in the simulation studies}
\end{flushleft}
| Performance Measure | Empirical Calculation | MCSE |
|---|---|---|
| **Mean-Based Metrics** | | |
| Mean Estimate | $\bar{B} = \frac{1}{K}\sum_{k=1}^{K}B_k$ | — |
| Bias | $\bar{B} - \beta$ | $\sqrt{S_B^2/K}$ |
| Relative Bias | $(\frac{\bar{B}}{\beta})- 1$ | $\sqrt{S_B^2/(K\beta^2)}$ |
| Percent Relative Bias | $(\frac{\bar{B}}{\beta})- 1\times 100\%$ | — |
| MSE | $\frac{1}{K}\sum_{k=1}^{K}(B_k - \beta)^2$ | $\sqrt{\frac{1}{K}[S_B^4(k_B - 1) + 4S_B^2 g_B(\bar{B} - \beta) + 4S_B^2(\bar{B} - \beta)^2]}$ |
| RMSE | $\sqrt{\frac{1}{K}\sum_{k=1}^{K}(B_k - \beta)^2}$ | $\sqrt{\frac{K-1}{K}\sum_{j=1}^{K}(\text{RMSE}_{(j)} - \text{RMSE})^2}$ |
| Relative MSE | $\frac{(\bar{B} - \beta)^2 + S_B^2}{\beta^2}$ | $\sqrt{\frac{1}{K\beta^4}[S_B^4(k_B - 1) + 4S_B^2 g_B(\bar{B} - \beta) + 4S_B^2(\bar{B} - \beta)^2]}$ |
| Relative RMSE | $\sqrt{\frac{(\bar{B} - \beta)^2 + S_B^2}{\beta^2}}$ | $\sqrt{\frac{K-1}{K}\sum_{j=1}^{K}(\text{rRMSE}_{(j)} - \text{rRMSE})^2}$ |
| Mean SE | $\overline{SE} = \frac{1}{K}\sum_{k=1}^{K}\widehat{SE}_k$ | — |
| SE Ratio | $\overline{SE}/S_B$ | — |
| Rejection Rate | $r_\alpha = \frac{1}{K}\sum_{k=1}^{K}I(P_k < \alpha)$ | $\sqrt{r_\alpha(1-r_\alpha)/K}$ |
| Coverage | $c_\beta = \frac{1}{K}\sum_{k=1}^{K}I(A_k \leq \beta \leq B_k)$ | $\sqrt{c_\beta(1-c_\beta)/K}$ |
| Average Width | $\bar{W} = \bar{B} - \bar{A}$ | $\sqrt{S_W^2/K}$ |
| **Median-Based Metrics** | | |
| Median Estimate | $\textit{Mdn}(B)$ | — |
| Median Bias | $\textit{Mdn}(B) - \beta$ | — |
| Relative Median Bias | $\frac{\textit{Mdn}(B) - \beta}{\beta}$ | — |
| Percent Relative Median Bias | $\frac{\textit{Mdn}(B) - \beta}{\beta} \times 100\%$ | — |
| MAD | $\textit{Mdn}(\|B_k - \textit{Mdn}(B)\|)$ | — |
| Median RMSE | $\sqrt{\text{Bias}_{\textit{Mdn}}^2 + \text{MAD}^2}$ | — |
| **Trimmed Mean-Based Metrics** | | |
| Trimmed Mean Estimate | $\bar{B}_{\text{trim}}$ | — |
| Trimmed Bias | $\bar{B}_{\text{trim}} - \beta$ | — |
| Trimmed RMSE | $\sqrt{(\bar{B}_{\text{trim}} - \beta)^2 + \text{MAD}^2}$ | — |
| Trimmed Mean SE | $\overline{SE}_{\text{trim}}$ | — |
| RSB (Robust SE Bias) | $\overline{SE}_{\text{trim}}/\text{MAD} - 1$ | — |
\begin{flushleft}
\textit{Note}. $B$ = parameter estimator; $\beta$ = true parameter value; $K$ = number of replications; $S_B^2$ = sample variance; $k_B$ = standardized kurtosis; $g_B$ = standardized skewness; $I(\cdot)$ = indicator function; $P_k$ = p-value from replication $k$; $\alpha$ = significance level; $A_k$, $B_k$ = CI endpoints; $S_W^2$ = variance of CI widths; $\bar{B}_{\text{trim}}$ = 20\% trimmed mean of estimates; $\overline{SE}_{\text{trim}}$ = 20\% trimmed mean of standard errors; MAD = median absolute deviation with scaling factor 1.4826; RSB = robust relative standard error bias; MCSE = Monte Carlo Standard Error. Dashes indicate MCSEs not computed for these measures.
\end{flushleft}
\endlandscape
\normalsize

\newpage

```{r packages, echo=FALSE, warning=FALSE, message=FALSE}
# technically, this is not ideal/optimal
data_study_1 <- load("../Simulations/Study_1/Data/Data_Study_1_final.RData")
study1_all_results_raw <- all_results  
study1_conditions_raw <- conditions   

data_study_2 <- load("../Simulations/Study_2/Data/Data_Study_2_final.RData")
study2_all_results_raw <- all_results  
study2_conditions_raw <- conditions   

results_study_1 <- readRDS("../Simulations/Study_1/Results/results_study_1.rds")
results_study_2 <- readRDS("../Simulations/Study_2/Results/results_study_2.rds")
```

```{r timing-table, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
# extract timing data from both studies using the _raw variables
# sim 1 timings
study1_timings <- data.frame()
for (i in 1:length(study1_all_results_raw)) {
  if (!is.null(study1_all_results_raw[[i]]$results$timing)) {
    timing <- study1_all_results_raw[[i]]$results$timing
    
    row_data <- data.frame(
      condition_id = i,
      N = study1_conditions_raw$N[i],
      Rel = study1_conditions_raw$Rel[i],
      Distribution = study1_conditions_raw$Distribution[i],
      Model_Type = study1_conditions_raw$Model_Type[i],
      
      S1_lms_mean = mean(timing$lms, na.rm = TRUE),
      S1_lms_median = median(timing$lms, na.rm = TRUE),
      S1_qml_mean = mean(timing$qml, na.rm = TRUE),
      S1_qml_median = median(timing$qml, na.rm = TRUE),
      S1_upi_mean = mean(timing$upi, na.rm = TRUE),
      S1_upi_median = median(timing$upi, na.rm = TRUE),
      S1_lsam_mean = mean(timing$lsam, na.rm = TRUE),
      S1_lsam_median = median(timing$lsam, na.rm = TRUE)
    )
    
    study1_timings <- rbind(study1_timings, row_data)
  }
}

# sim 2 timings
study2_timings <- data.frame()
for (i in 1:length(study2_all_results_raw)) {
  if (!is.null(study2_all_results_raw[[i]]$results$timing)) {
    timing <- study2_all_results_raw[[i]]$results$timing
    
    row_data <- data.frame(
      N = study2_conditions_raw$N[i],
      Rel = study2_conditions_raw$Rel[i],
      Distribution = study2_conditions_raw$Distribution[i],
      Model_Type = study2_conditions_raw$Model_Type[i],
      
      S2_lsam_mean = mean(timing$lsam, na.rm = TRUE),
      S2_lsam_median = median(timing$lsam, na.rm = TRUE),
      S2_qml_mean = mean(timing$qml, na.rm = TRUE),
      S2_qml_median = median(timing$qml, na.rm = TRUE),
      S2_upi_mean = mean(timing$upi, na.rm = TRUE),
      S2_upi_median = median(timing$upi, na.rm = TRUE)
    )
    
    study2_timings <- rbind(study2_timings, row_data)
  }
}

combined_timings <- merge(
  study1_timings,
  study2_timings[, c("N", "Rel", "Distribution", "Model_Type", 
                      "S2_lsam_mean", "S2_lsam_median",
                      "S2_qml_mean", "S2_qml_median", 
                      "S2_upi_mean", "S2_upi_median")],
  by = c("N", "Rel", "Distribution", "Model_Type"),
  all.x = TRUE
)

# reorder columns for better readability
combined_timings <- combined_timings[, c(
  "condition_id", "N", "Rel", "Distribution", "Model_Type",
  # sim 1 methods
  "S1_lms_mean", "S1_lms_median",
  "S1_qml_mean", "S1_qml_median", 
  "S1_upi_mean", "S1_upi_median",
  "S1_lsam_mean", "S1_lsam_median",
  # sim 2 methods
  "S2_lsam_mean", "S2_lsam_median",
  "S2_qml_mean", "S2_qml_median",
  "S2_upi_mean", "S2_upi_median"
)]

timing_cols <- grep("^S[12]_", names(combined_timings))
combined_timings[timing_cols] <- round(combined_timings[timing_cols], 2)

# APA formatted table
apa_timing_table <- combined_timings %>%
  mutate(
    Model = ifelse(Model_Type == "full", "Full", "Linear"),
    Distribution = case_when(
      Distribution == "nonnormal" ~ "right-skewed",
      TRUE ~ Distribution
    ),
    Condition = condition_id
  ) %>%
  arrange(Condition, factor(Model, levels = c("Full", "Linear")), N, Distribution) %>%
  select(
    Condition, Model, Distribution, N, Reliability = Rel,
    # sim 1
    S1_lms_mean, S1_lms_median,
    S1_qml_mean, S1_qml_median,
    S1_upi_mean, S1_upi_median,
    S1_lsam_mean, S1_lsam_median,
    # sim 2
    S2_lsam_mean, S2_lsam_median,
    S2_qml_mean, S2_qml_median,
    S2_upi_mean, S2_upi_median
  )

kableExtra::kbl(
  apa_timing_table,
  booktabs = TRUE,
  longtable = TRUE,
  align = c("l", "l", "l", "r", "r", rep("r", 14)),
  col.names = c(
    "Condition", "Model", "Distribution", "N", "Reliability",
    "Mean", "Mdn", "Mean", "Mdn", "Mean", "Mdn", "Mean", "Mdn",
    "Mean", "Mdn", "Mean", "Mdn", "Mean", "Mdn"
  ),
  caption = "Computation time by approach (in seconds)",
  linesep = "",
  digits = 2
) %>%
  kableExtra::add_header_above(c(
    " " = 5,
    "LMS" = 2,
    "QML" = 2,
    "UPI" = 2,
    "LSAM" = 2,
    "LSAM" = 2,
    "QML" = 2,
    "UPI" = 2
  )) %>%
  kableExtra::add_header_above(c(
    " " = 5,
    "Study 1" = 8,
    "Study 2" = 6
  )) %>%
  kableExtra::kable_styling(
    latex_options = c("hold_position", "repeat_header", "scale_down"),
    font_size = 6,
    position = "left"
  ) %>%
  kableExtra::collapse_rows(columns = 1, valign = "top", latex_hline = "major") %>%
  kableExtra::footnote(
    general = "Values represent mean and median computation times across 1,000 replications.",
    general_title = "Note.",
    threeparttable = TRUE,
    escape = TRUE
  ) %>%
  kableExtra::landscape()
```

```{r plot-outliers, echo=FALSE, warning=FALSE, message=FALSE}
plot_se_simple <- function(extraction_results, condition_number = 13, method = "LSAM", 
                           label_threshold = 5, label_below = NULL) {
  
  # GLOBAL surviving iterations (converged and non-outlier in ALL methods)
  details <- extraction_results$convergence_outliers_details
  cond_key <- paste0("Condition_", condition_number)
  
  surviving_iters <- NULL
  
  if (cond_key %in% names(details)) {
    cond_details <- details[[cond_key]]
    methods_lower <- c("lsam", "lms", "qml", "upi")
    
    # all excluded iterations from ALL methods
    all_excluded <- list()
    for (m in methods_lower) {
      non_conv <- cond_details$non_converged_iterations[[m]]
      outliers <- cond_details$outlier_iterations[[m]]
      all_excluded[[m]] <- unique(c(non_conv, outliers))
    }
    
    # global surviving = not excluded by ANY method
    all_excluded_union <- unique(unlist(all_excluded))
    surviving_iters <- setdiff(1:1000, all_excluded_union)
    
  } else {
    warning("Could not find original iteration IDs, using sequential numbers")
  }
  
  parameters <- c("eta1", "eta2", "eta1:eta2", "eta1:eta1", "eta2:eta2")
  
  # SEs for all parameters
  se_data <- data.frame()
  
  for (param in parameters) {
    key <- paste0(condition_number, "_", method, "_", param)
    
    if (key %in% names(extraction_results$filtered_data)) {
      ses <- extraction_results$filtered_data[[key]]$standard_errors
      
      if (length(ses) > 0) {
        # original iteration IDs if available, otherwise sequential
        if (!is.null(surviving_iters) && length(surviving_iters) == length(ses)) {
          iter_ids <- surviving_iters
        } else {
          iter_ids <- 1:length(ses)
        }
        
        temp_df <- data.frame(
          Iteration = iter_ids,
          Parameter = param,
          SE = ses
        )
        se_data <- rbind(se_data, temp_df)
      }
    }
  }
  
  method_upper <- toupper(method)
  
  if (!is.null(label_below)) {
    points_to_label <- subset(se_data, SE < label_below)
    #subtitle_text <- paste0("Original iteration IDs shown (from 1-1000) | Labels for SE < ", label_below)
  } else {
    points_to_label <- subset(se_data, SE > label_threshold)
    #subtitle_text <- paste0("Original iteration IDs shown (from 1-1000) | Labels for SE > ", label_threshold)
  }
  
  p <- ggplot(se_data, aes(x = Iteration, y = SE)) +
    geom_point(alpha = 0.6, size = 2) +
    geom_text(data = points_to_label,
              aes(label = Iteration), 
              vjust = 0.5, hjust = 1.2, size = 3, fontface = "bold", color = "red") +
    facet_wrap(~ Parameter, scales = "free_y", ncol = 2) +
    theme_minimal() +
    labs(
      #title = paste0("", condition_number, " (", method_upper, ")"),
      #subtitle = subtitle_text,
      x = "",
      y = "SEs"
    ) +
    theme(
      plot.title = element_text(size = 14, face = "bold"),
      strip.text = element_text(face = "bold")
    )
  
  print(p)
  
  se_data
}

# needs results from sim 1
extraction_results <- ExtractConvergenceOutliers(
  all_results = study1_all_results_raw,
  parameters_of_interest = c("eta1","eta2","eta1:eta2","eta1:eta1","eta2:eta2"),
  remove_outliers = TRUE,
  outlier_threshold = 3,
  min_reps = 10,
  exclude_warnings = FALSE
)
```

```{r lsam-outlier-first-sim-study, echo=FALSE, fig.cap="Outliers for the SEs for LSAM in condition 13 ", fig.align='center', fig.height=12, fig.width=9}
# label SEs above 5
se_data <- plot_se_simple(extraction_results, condition_number = 13, method = "LSAM")
```

```{r complete-plots-study1, echo=FALSE, fig.width=12, fig.height=16, fig.align='center', message=FALSE, warning=FALSE}
# COMPLETE STUDY 1 PLOTS (ALL DATA) 
study1_data <- prepare_study1_data(results_study_1)
# COMPLETE STUDY 2 PLOTS - NORMAL DISTRIBUTION 
study_2_normal_data <- prepare_study2_data(results_study_2, "normal")
# COMPLETE STUDY 2 PLOTS - NONNORMAL DISTRIBUTION
study_2_nonnormal_data <- prepare_study2_data(results_study_2, "nonnormal")
# COMPLETE STUDY 2 PLOTS - UNIFORM DISTRIBUTION
study_2_uniform_data <- prepare_study2_data(results_study_2, "uniform")
```

```{r all-bias-first-sim-study, echo=FALSE, fig.cap = "Absolute bias for Simulation 1", fig.align='center', fig.height=12, fig.width=9}
 plot_bias(study1_data$bias, shapes = SHAPES_4, ltys = LTYS_4)
```

```{r all-relbias-first-sim-study, echo=FALSE, fig.cap = "Relative bias for Simulation 1", fig.align='center', fig.height=12, fig.width=9, warning=FALSE}
plot_bias(study1_data$bias_relative, shapes = SHAPES_4, ltys = LTYS_4)
```

```{r all-rmse-first-sim-study, echo=FALSE, fig.cap="RMSE for Simulation 1", fig.align='center', fig.height=12, fig.width=8}
plot_rmse(study1_data$rmse, shapes = SHAPES_4, ltys = LTYS_4)
```

```{r all-relrmse-first-sim-study, echo=FALSE, fig.cap="Relative RMSE for Simulation 1", fig.align='center', fig.height=12, fig.width=8, warning=FALSE}
plot_rmse(study1_data$rmse_relative, shapes = SHAPES_4, ltys = LTYS_4)
```

```{r all-ratio-first-sim-study, echo=FALSE, fig.cap="SE/SD ratio for Simulation 1", fig.align='center', fig.height=12, fig.width=9}
plot_sesd(study1_data$sesd, shapes = SHAPES_4, ltys = LTYS_4)
```

```{r all-coverage-first-sim-study, echo=FALSE, fig.cap="Coverage for Simulation 1", fig.align='center', fig.height=12, fig.width=9}
plot_coverage(study1_data$coverage, shapes = SHAPES_4, ltys = LTYS_4)
```

```{r all-type-first-sim-study, echo=FALSE, fig.cap="Type I error rate for Simulation 1", fig.align='center', fig.height=12, fig.width=9}
plot_type1(study1_data$type1, greys = GREYS_4)
```

```{r all-power-first-sim-study, echo=FALSE, fig.cap="Empirical power for Simulation 1", fig.align='center', fig.height=12, fig.width=9}
plot_power(study1_data$power, greys = GREYS_4)
```

\newpage

```{r normal-bias-second-sim-study, echo=FALSE, fig.cap="Absolute bias for Simulation 2 (Normal)", fig.align='center', fig.height=12, fig.width=9}
plot_bias(study_2_normal_data$bias, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r normal-relbias-second-sim-study, echo=FALSE, fig.cap="Relative bias for Simulation 2 (Normal)", fig.align='center', fig.height=12, fig.width=9, warning=FALSE}
plot_bias(study_2_normal_data$bias_relative, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r normal-rmse-second-sim-study, echo=FALSE, fig.cap="RMSE for Simulation 2 (Normal)", fig.align='center', fig.height=12, fig.width=8}
plot_rmse(study_2_normal_data$rmse, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r normal-relrmse-second-sim-study, echo=FALSE, fig.cap="Relative RMSE for Simulation 2 (Normal)", fig.align='center', fig.height=12, fig.width=8, warning=FALSE}
plot_rmse(study_2_normal_data$rmse_relative, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r normal-ratio-second-sim-study, echo=FALSE, fig.cap="SE/SD ratio for Simulation 2 (Normal)", fig.align='center', fig.height=12, fig.width=9}
plot_sesd(study_2_normal_data$sesd, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r normal-coverage-second-sim-study, echo=FALSE, fig.cap="Coverage for Simulation 2 (Normal)", fig.align='center', fig.height=12, fig.width=9}
plot_coverage(study_2_normal_data$coverage, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r normal-type-second-sim-study, echo=FALSE, fig.cap="Type I error rate for Simulation 2 (Normal)", fig.align='center', fig.height=12, fig.width=9}
plot_type1(study_2_normal_data$type1, greys = GREYS_3)
```

```{r normal-power-second-sim-study, echo=FALSE, fig.cap="Empirical power for Simulation 2 (Normal)", fig.align='center', fig.height=12, fig.width=9}
plot_power(study_2_normal_data$power, greys = GREYS_3)
```

\newpage

```{r nonnormal-bias-second-sim-study, echo=FALSE, fig.cap="Absolute bias for Simulation 2 (Right-skewed)", fig.align='center', fig.height=12, fig.width=9}
plot_bias(study_2_nonnormal_data$bias, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r nonnormal-relbias-second-sim-study, echo=FALSE, fig.cap="Relative bias for Simulation 2 (Right-skewed)", fig.align='center', fig.height=12, fig.width=9, warning=FALSE}
plot_bias(study_2_nonnormal_data$bias_relative, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r nonnormal-rmse-second-sim-study, echo=FALSE, fig.cap="RMSE for Simulation 2 (Right-skewed)", fig.align='center', fig.height=12, fig.width=8}
plot_rmse(study_2_nonnormal_data$rmse, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r nonnormal-relrmse-second-sim-study, echo=FALSE, fig.cap="Relative RMSE for Simulation 2 (Right-skewed)", fig.align='center', fig.height=12, fig.width=8, warning=FALSE}
plot_rmse(study_2_nonnormal_data$rmse_relative, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r nonnormal-ratio-second-sim-study, echo=FALSE, fig.cap="SE/SD ratio for Simulation 2 (Right-skewed)", fig.align='center', fig.height=12, fig.width=9}
plot_sesd(study_2_nonnormal_data$sesd, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r nonnormal-coverage-second-sim-study, echo=FALSE, fig.cap="Coverage for Simulation 2 (Right-skewed)", fig.align='center', fig.height=12, fig.width=9}
plot_coverage(study_2_nonnormal_data$coverage, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r nonnormal-type-second-sim-study, echo=FALSE, fig.cap="Type I error rate for Simulation 2 (Right-skewed)", fig.align='center', fig.height=12, fig.width=9}
plot_type1(study_2_nonnormal_data$type1, greys = GREYS_3)
```

```{r nonnormal-power-second-sim-study, echo=FALSE, fig.cap="Empirical power for Simulation 2 (Right-skewed)", fig.align='center', fig.height=12, fig.width=9}
plot_power(study_2_nonnormal_data$power, greys = GREYS_3)
```
\newpage

```{r uniform-bias-second-sim-study, echo=FALSE, fig.cap="Absolute bias for Simulation 2 (Uniform)", fig.align='center', fig.height=12, fig.width=9}
plot_bias(study_2_uniform_data$bias, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r uniform-relbias-second-sim-study, echo=FALSE, fig.cap="Relative bias for Simulation 2 (Uniform)", fig.align='center', fig.height=12, fig.width=9, warning=FALSE}
plot_bias(study_2_uniform_data$bias_relative, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r uniform-rmse-second-sim-study, echo=FALSE, fig.cap="RMSE for Simulation 2 (Uniform)", fig.align='center', fig.height=12, fig.width=8}
plot_rmse(study_2_uniform_data$rmse, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r uniform-relrmse-second-sim-study, echo=FALSE, fig.cap="Relative RMSE for Simulation 2 (Uniform)", fig.align='center', fig.height=12, fig.width=8, warning=FALSE}
plot_rmse(study_2_uniform_data$rmse_relative, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r uniform-ratio-second-sim-study, echo=FALSE, fig.cap="SE/SD ratio for Simulation 2 (Uniform)", fig.align='center', fig.height=12, fig.width=9}
plot_sesd(study_2_uniform_data$sesd, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r uniform-coverage-second-sim-study, echo=FALSE, fig.cap="Coverage for Simulation 2 (Uniform)", fig.align='center', fig.height=12, fig.width=9}
plot_coverage(study_2_uniform_data$coverage, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r uniform-type-second-sim-study, echo=FALSE, fig.cap="Type I error rate for Simulation 2 (Uniform)", fig.align='center', fig.height=12, fig.width=9}
plot_type1(study_2_uniform_data$type1, greys = GREYS_3)
```

```{r uniform-power-second-sim-study, echo=FALSE, fig.cap="Empirical power for Simulation 2 (Uniform)", fig.align='center', fig.height=12, fig.width=9}
plot_power(study_2_uniform_data$power, greys = GREYS_3)
```

```{r trial-separate, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
# PARAMETER MAPPING FUNCTION
map_parameter_to_beta <- function(param, study = 1, equation = NULL) {
  if (study == 1) {
    beta_map <- c(
      "eta1" = "beta31",
      "eta2" = "beta32",
      "eta1:eta2" = "beta33",
      "eta1:eta1" = "beta34",
      "eta2:eta2" = "beta35"
    )
  } else if (study == 2) {
    if (equation == "eta4") {
      beta_map <- c(
        "eta1" = "beta41",
        "eta2" = "beta42",
        "eta3" = "beta43",
        "eta1:eta2" = "beta44",
        "eta1:eta3" = "beta45",
        "eta1:eta1" = "beta46",
        "eta2:eta2" = "beta47"
      )
    } else if (equation == "eta5") {
      beta_map <- c(
        "eta1" = "beta51",
        "eta2" = "beta52",
        "eta3" = "beta53",
        "eta4" = "beta54",
        "eta1:eta4" = "beta55",
        "eta2:eta4" = "beta56",
        "eta1:eta1" = "beta57",
        "eta3:eta3" = "beta58"
      )
    }
  }
  
  ifelse(param %in% names(beta_map), beta_map[param], param)
}

# SIM 1: results tables separated by condition (keeping Methods together)
create_apa_results_table_study1_by_condition <- function(results_df, condition_filter, model_filter, dist_filter, n_filter, rel_filter) {
  
  df <- results_df %>%
    filter(
      Condition == condition_filter,
      Model == model_filter,
      Distribution == dist_filter,
      SampleSize == n_filter,
      Reliability == rel_filter
    ) %>%
    select(
      Method,
      Parameter,
      TrueValue,
      MeanEstimate,
      Bias_Mean,
      Bias_Mean_MCSE,
      RelativeBias_Mean,
      RelativeBias_MCSE,
      MedianEstimate,
      Bias_Median,
      MAD,
      Variance,
      Variance_MCSE,
      SD,
      SD_MCSE,
      MSE_Mean,
      MSE_Mean_MCSE,
      RMSE_Mean,
      RMSE_Mean_MCSE,
      RMSE_Median,
      Relative_MSE,
      Relative_MSE_MCSE,
      Relative_RMSE,
      Relative_RMSE_MCSE,
      SE_SD_Ratio,
      CoverageRate,
      CoverageRate_MCSE,
      CI_Width,
      CI_Width_MCSE,
      TypeI_Error,
      TypeI_Error_MCSE,
      Power,
      Power_MCSE
    ) %>%
    mutate(
      # map parameter names to beta notation
      Parameter = map_parameter_to_beta(Parameter, study = 1),
      # create combined columns with ± MCSE
      `Bias ± MCSE` = sprintf("%.3f ± %.3f", Bias_Mean, Bias_Mean_MCSE),
      `Rel. Bias ± MCSE` = ifelse(TrueValue == 0, "—", 
                                    sprintf("%.3f ± %.3f", RelativeBias_Mean, RelativeBias_MCSE)),
      `Variance ± MCSE` = sprintf("%.3f ± %.3f", Variance, Variance_MCSE),
      `SD ± MCSE` = sprintf("%.3f ± %.3f", SD, SD_MCSE),
      `MSE ± MCSE` = sprintf("%.3f ± %.3f", MSE_Mean, MSE_Mean_MCSE),
      `RMSE ± MCSE` = sprintf("%.3f ± %.3f", RMSE_Mean, RMSE_Mean_MCSE),
      `Rel. MSE ± MCSE` = ifelse(TrueValue == 0, "—",
                                   sprintf("%.3f ± %.3f", Relative_MSE, Relative_MSE_MCSE)),
      `Rel. RMSE ± MCSE` = ifelse(TrueValue == 0, "—",
                                    sprintf("%.3f ± %.3f", Relative_RMSE, Relative_RMSE_MCSE)),
      `Coverage ± MCSE` = sprintf("%.3f ± %.3f", CoverageRate, CoverageRate_MCSE),
      `CI Width ± MCSE` = sprintf("%.3f ± %.3f", CI_Width, CI_Width_MCSE),
      `Type I ± MCSE` = ifelse(is.na(TypeI_Error), "—", 
                               sprintf("%.3f ± %.3f", TypeI_Error, TypeI_Error_MCSE)),
      `Power ± MCSE` = ifelse(is.na(Power), "—", 
                              sprintf("%.3f ± %.3f", Power, Power_MCSE))
    ) %>%
    select(
      Method, Parameter,
      TrueValue,
      # mean-based columns
      MeanEstimate, `Bias ± MCSE`, `Rel. Bias ± MCSE`,
      `Variance ± MCSE`, `SD ± MCSE`,
      `MSE ± MCSE`, `RMSE ± MCSE`,
      `Rel. MSE ± MCSE`, `Rel. RMSE ± MCSE`,
      # median-based columns
      MedianEstimate, Bias_Median, MAD, RMSE_Median,
      # inference columns
      SE_SD_Ratio,
      `Coverage ± MCSE`, `CI Width ± MCSE`,
      `Type I ± MCSE`, `Power ± MCSE`
    ) %>%
    mutate(
      TrueValue = round(TrueValue, 3),
      MeanEstimate = round(MeanEstimate, 3),
      MedianEstimate = round(MedianEstimate, 3),
      Bias_Median = round(Bias_Median, 3),
      MAD = round(MAD, 4),
      RMSE_Median = round(RMSE_Median, 4),
      SE_SD_Ratio = round(SE_SD_Ratio, 3)
    ) %>%
    arrange(Method, Parameter)
  
  # remove the unnecessary column based on model type
  if(model_filter == "Full") {
    df <- df %>% select(-`Type I ± MCSE`)
  } else {
    df <- df %>% select(-`Power ± MCSE`)
  }
  
  df
}

# unique condition combinations for sim 1 (excluding method)
conditions_study1 <- results_study_1 %>%
  select(Condition, Model, Distribution, SampleSize, Reliability) %>%
  distinct() %>%
  mutate(
    Distribution = case_when(
      Distribution == "nonnormal" ~ "right-skewed",
      TRUE ~ Distribution
    )
  ) %>%
  arrange(Condition, factor(Model, levels = c("Full", "Linear")))

# tables for each condition in sim 1
for(i in 1:nrow(conditions_study1)) {
  condition_data <- conditions_study1[i, ]
  
  # table for this condition (includes all methods)
  condition_table <- create_apa_results_table_study1_by_condition(
    results_study_1,
    condition_data$Condition,
    condition_data$Model,
    ifelse(condition_data$Distribution == "right-skewed", "nonnormal", condition_data$Distribution),
    condition_data$SampleSize,
    condition_data$Reliability
  )
  
  tab_caption <- sprintf(
    "Simulation 1 - Condition %s: %s Model, Distribution = %s, N = %d, Reliability = %.1f",
    condition_data$Condition,
    condition_data$Model,
    condition_data$Distribution,
    condition_data$SampleSize,
    condition_data$Reliability
  )
  
  tab_note <- "MCSE = Monte Carlo Standard Error shown as ± value. Coverage, Type I Error, and Power expressed as percentages. — indicates relative measures are undefined when true value equals 0 and non-existent results for Type I error rate which was evaluated only for nonlinear effects."
  
  cat("\\setlength{\\tabcolsep}{3pt}\n")
  
  print(
    kableExtra::kbl(
      condition_table,
      booktabs = TRUE,
      longtable = TRUE,
      align = c("l", "l", rep("r", if(condition_data$Model == "Full") 17 else 17)),
      col.names = c("Method", "Param.",
                    "True",
                    "Mean", "Bias ± MCSE", "Rel. Bias ± MCSE",
                    "Var. ± MCSE", "SD ± MCSE",
                    "MSE ± MCSE", "RMSE ± MCSE",
                    "Rel. MSE ± MCSE", "Rel. RMSE ± MCSE",
                    "Median", "Bias (Med)", "MAD", "RMSE (Med)",
                    "SE/SD",
                    "Cover. (%) ± MCSE", "CI Width ± MCSE",
                    if(condition_data$Model == "Full") "Power (%) ± MCSE" else "Type I (%) ± MCSE"),
      caption = tab_caption,
      linesep = ""
    ) %>%
      kableExtra::add_header_above(c(
        " " = 3,
        "Mean-based" = 9,
        "Median-based" = 4,
        "Inference" = 4
      )) %>%
      kableExtra::kable_styling(
        latex_options = c("hold_position", "repeat_header"),
        font_size = 3.5
      ) %>%
      kableExtra::collapse_rows(columns = 1, valign = "top", latex_hline = "major") %>%
      kableExtra::footnote(
        general = tab_note,
        general_title = "Note.",
        threeparttable = TRUE,
        escape = TRUE
      ) %>%
      kableExtra::landscape()
  )
  
  cat("\\setlength{\\tabcolsep}{6pt}\n")
  
  cat("\n\\clearpage\n\n")
}


# SIM 2: results tables separated by condition (combining both equations)
create_apa_results_table_study2_by_condition <- function(results_df, condition_filter, model_filter, dist_filter, n_filter, rel_filter) {
  
  # both equations together
  df <- results_df %>%
    filter(
      Condition == condition_filter,
      Model == model_filter,
      Distribution == dist_filter,
      SampleSize == n_filter,
      Reliability == rel_filter
    ) %>%
    select(
      Method,
      Parameter,
      Equation,
      TrueValue,
      MeanEstimate,
      Bias_Mean,
      Bias_Mean_MCSE,
      RelativeBias_Mean,
      RelativeBias_MCSE,
      MedianEstimate,
      Bias_Median,
      MAD,
      Variance,
      Variance_MCSE,
      SD,
      SD_MCSE,
      MSE_Mean,
      MSE_Mean_MCSE,
      RMSE_Mean,
      RMSE_Mean_MCSE,
      RMSE_Median,
      Relative_MSE,
      Relative_MSE_MCSE,
      Relative_RMSE,
      Relative_RMSE_MCSE,
      SE_SD_Ratio,
      CoverageRate,
      CoverageRate_MCSE,
      CI_Width,
      CI_Width_MCSE,
      TypeI_Error,
      TypeI_Error_MCSE,
      Power,
      Power_MCSE
    ) %>%
    mutate(
      Parameter = mapply(map_parameter_to_beta, Parameter, study = 2, equation = Equation)
    ) %>%
    mutate(
      # combined columns with ± MCSE
      `Bias ± MCSE` = sprintf("%.3f ± %.3f", Bias_Mean, Bias_Mean_MCSE),
      `Rel. Bias ± MCSE` = ifelse(TrueValue == 0, "—", 
                                    sprintf("%.3f ± %.3f", RelativeBias_Mean, RelativeBias_MCSE)),
      `Variance ± MCSE` = sprintf("%.3f ± %.3f", Variance, Variance_MCSE),
      `SD ± MCSE` = sprintf("%.3f ± %.3f", SD, SD_MCSE),
      `MSE ± MCSE` = sprintf("%.3f ± %.3f", MSE_Mean, MSE_Mean_MCSE),
      `RMSE ± MCSE` = sprintf("%.3f ± %.3f", RMSE_Mean, RMSE_Mean_MCSE),
      `Rel. MSE ± MCSE` = ifelse(TrueValue == 0, "—",
                                   sprintf("%.3f ± %.3f", Relative_MSE, Relative_MSE_MCSE)),
      `Rel. RMSE ± MCSE` = ifelse(TrueValue == 0, "—",
                                    sprintf("%.3f ± %.3f", Relative_RMSE, Relative_RMSE_MCSE)),
      `Coverage ± MCSE` = sprintf("%.3f ± %.3f", CoverageRate, CoverageRate_MCSE),
      `CI Width ± MCSE` = sprintf("%.3f ± %.3f", CI_Width, CI_Width_MCSE),
      `Type I ± MCSE` = ifelse(is.na(TypeI_Error), "—", 
                               sprintf("%.3f ± %.3f", TypeI_Error, TypeI_Error_MCSE)),
      `Power ± MCSE` = ifelse(is.na(Power), "—", 
                              sprintf("%.3f ± %.3f", Power, Power_MCSE))
    ) %>%
    select(
      Method, Parameter,
      TrueValue,
      # mean-based columns
      MeanEstimate, `Bias ± MCSE`, `Rel. Bias ± MCSE`,
      `Variance ± MCSE`, `SD ± MCSE`,
      `MSE ± MCSE`, `RMSE ± MCSE`,
      `Rel. MSE ± MCSE`, `Rel. RMSE ± MCSE`,
      # median-based columns
      MedianEstimate, Bias_Median, MAD, RMSE_Median,
      # inference columns
      SE_SD_Ratio,
      `Coverage ± MCSE`, `CI Width ± MCSE`,
      `Type I ± MCSE`, `Power ± MCSE`
    ) %>%
    mutate(
      TrueValue = round(TrueValue, 3),
      MeanEstimate = round(MeanEstimate, 3),
      MedianEstimate = round(MedianEstimate, 3),
      Bias_Median = round(Bias_Median, 3),
      MAD = round(MAD, 4),
      RMSE_Median = round(RMSE_Median, 4),
      SE_SD_Ratio = round(SE_SD_Ratio, 3)
    ) %>%
    arrange(Method, Parameter)
  
  if(model_filter == "Full") {
    df <- df %>% select(-`Type I ± MCSE`)
  } else {
    df <- df %>% select(-`Power ± MCSE`)
  }
  
  df
}

# process sim 2 
conditions_study2 <- results_study_2 %>%
  select(Condition, Model, Distribution, SampleSize, Reliability) %>%
  distinct() %>%
  mutate(
    Distribution = case_when(
      Distribution == "nonnormal" ~ "right-skewed",
      TRUE ~ Distribution
    )
  ) %>%
  arrange(Condition, factor(Model, levels = c("Full", "Linear")))

for(i in 1:nrow(conditions_study2)) {
  condition_data <- conditions_study2[i, ]
  
  condition_table <- create_apa_results_table_study2_by_condition(
    results_study_2,
    condition_data$Condition,
    condition_data$Model,
    ifelse(condition_data$Distribution == "right-skewed", "nonnormal", condition_data$Distribution),
    condition_data$SampleSize,
    condition_data$Reliability
  )
  
  tab_caption <- sprintf(
    "Simulation 2 - Condition %s: %s Model, Distribution = %s, N = %d, Reliability = %.1f",
    condition_data$Condition,
    condition_data$Model,
    condition_data$Distribution,
    condition_data$SampleSize,
    condition_data$Reliability
  )
  
  tab_note <- "MCSE = Monte Carlo Standard Error shown as ± value. Coverage, Type I Error, and Power expressed as percentages. — indicates relative measures are undefined when true value equals 0 and non-existent results for Type I error rate which was evaluated only for nonlinear effects."
  
  cat("\\setlength{\\tabcolsep}{3pt}\n")
  
  print(
    kableExtra::kbl(
      condition_table,
      booktabs = TRUE,
      longtable = TRUE,
      align = c("l", "l", rep("r", if(condition_data$Model == "Full") 17 else 17)),
      col.names = c("Method", "Param.",
                    "True",
                    "Mean", "Bias ± MCSE", "Rel. Bias ± MCSE",
                    "Var. ± MCSE", "SD ± MCSE",
                    "MSE ± MCSE", "RMSE ± MCSE",
                    "Rel. MSE ± MCSE", "Rel. RMSE ± MCSE",
                    "Median", "Bias (Med)", "MAD", "RMSE (Med)",
                    "SE/SD",
                    "Cover. (%) ± MCSE", "CI Width ± MCSE",
                    if(condition_data$Model == "Full") "Power (%) ± MCSE" else "Type I (%) ± MCSE"),
      caption = tab_caption,
      linesep = ""
    ) %>%
      kableExtra::add_header_above(c(
        " " = 3,
        "Mean-based" = 9,
        "Median-based" = 4,
        "Inference" = 4
      )) %>%
      kableExtra::kable_styling(
        latex_options = c("hold_position", "repeat_header"),
        font_size = 3.5
      ) %>%
      kableExtra::collapse_rows(columns = 1, valign = "top", latex_hline = "major") %>%
      kableExtra::footnote(
        general = tab_note,
        general_title = "Note.",
        threeparttable = TRUE,
        escape = TRUE
      ) %>%
      kableExtra::landscape()
  )
  
  cat("\\setlength{\\tabcolsep}{6pt}\n")
  
  cat("\n\\clearpage\n\n")
}
```
