---
title: "Tables for Evaluating Local Structural-After-Measurement (LSAM) and Traditional Approaches for the Estimation of Complex Nonlinear Effects Among Latent Variables"
shorttitle: "Tables: Evaluating LSAM and Traditional SEM Approaches"

author:
  - name: Felipe Fontana Vieira
    corresponding: true
    orcid: 0009-0006-0949-6569
    email: felipe.fontanavieira@ugent.be
    affiliations:
      - name: Ghent University
        department: Department of Data Analysis, Faculty of Psychology and Educational Sciences
        address: Henri Dunantlaan 2
        city: Ghent
        country: Belgium
        postal-code: 9000
        id: UGent
  - name: Kjell Solem Slupphaug
    corresponding: false
    orcid: 0009-0005-8324-2834
    affiliations:
      - name: Norwegian University of Science and Technology
        department: Department of Psychology
        city: Trondheim
        country: Norway
  - name: Yves Rosseel
    corresponding: false
    orcid: 0000-0002-4129-4477
    affiliations:
      - ref: UGent

floatsintext: true

format:
  apaquarto-pdf:
    documentmode: man
    keep-tex: false
    toc: true
    toc-depth: 2
    include-in-header:
      text: |
        \raggedbottom
        \usepackage{pdflscape}
        \usepackage{longtable}
        \usepackage{array}
        \renewcommand{\thefigure}{S\arabic{figure}}
        \renewcommand{\thetable}{S\arabic{table}}
        \setcounter{figure}{0}
        \setcounter{table}{0}

execute:
  echo: false
  warning: false
  message: false

editor:
  markdown:
    wrap: sentence
---

```{r}
#| label: setup
#| include: false

library(dplyr)
library(kableExtra)
```

# Performance Measures

\landscape
\footnotesize
\begin{flushleft}
\textbf{Table S1}

\textit{Complete performance measures for evaluating parameter estimates in the simulation studies}
\end{flushleft}
| Performance Measure | Empirical Calculation | MCSE |
|---|---|---|
| **Mean-Based Metrics** | | |
| Absolute Bias | $\bar{B} - \beta$ | $\sqrt{S_B^2/K}$ |
| Relative Bias | $(\frac{\bar{B}}{\beta})- 1$ | $\sqrt{S_B^2/(K\beta^2)}$ |
| Percent Relative Bias | $\left[(\frac{\bar{B}}{\beta})- 1\right]\times 100\%$ | — |
| MSE | $\frac{1}{K}\sum_{k=1}^{K}(B_k - \beta)^2$ | $\sqrt{\frac{1}{K}[S_B^4(k_B - 1) + 4S_B^3 g_B(\bar{B} - \beta) + 4S_B^2(\bar{B} - \beta)^2]}$ |
| RMSE | $\sqrt{\frac{1}{K}\sum_{k=1}^{K}(B_k - \beta)^2}$ | $\sqrt{\frac{K-1}{K}\sum_{j=1}^{K}(\text{RMSE}_{(j)} - \text{RMSE})^2}$ |
| Relative MSE | $\frac{(\bar{B} - \beta)^2 + S_B^2}{\beta^2}$ | $\sqrt{\frac{1}{K\beta^4}[S_B^4(k_B - 1) + 4S_B^3 g_B(\bar{B} - \beta) + 4S_B^2(\bar{B} - \beta)^2]}$ |
| Relative RMSE | $\sqrt{\frac{(\bar{B} - \beta)^2 + S_B^2}{\beta^2}}$ | $\sqrt{\frac{K-1}{K}\sum_{j=1}^{K}(\text{rRMSE}_{(j)} - \text{rRMSE})^2}$ |
| SE/SD Ratio | $\overline{SE}/S_B$ | — |
| Rejection Rate | $r_\alpha = \frac{1}{K}\sum_{k=1}^{K}I(P_k < \alpha)$ | $\sqrt{r_\alpha(1-r_\alpha)/K}$ |
| Coverage | $c_\beta = \frac{1}{K}\sum_{k=1}^{K}I(L_k \leq \beta \leq U_k)$ | $\sqrt{c_\beta(1-c_\beta)/K}$ |
| Average Width | $\bar{W} = \bar{U} - \bar{L}$ | $\sqrt{S_W^2/K}$ |
| **Median-Based Metrics** | | |
| Median Bias | $\textit{Mdn}(B) - \beta$ | — |
| Relative Median Bias | $\frac{\textit{Mdn}(B) - \beta}{\beta}$ | — |
| Percent Relative Median Bias | $\frac{\textit{Mdn}(B) - \beta}{\beta} \times 100\%$ | — |
| MAD | $\textit{Mdn}(\|B_k - \textit{Mdn}(B)\|)$ | — |
| Median RMSE | $\sqrt{\text{Bias}_{\textit{Mdn}}^2 + \text{MAD}^2}$ | — |
\begin{flushleft}
\textit{Note}. $B$ = estimator for parameter $\beta$; $K$ = number of replications producing estimates $B_1, ..., B_K$; $\bar{B} = (1/K)\sum_{k=1}^{K}B_k$ = sample mean; $S_B^2 = (1/(K-1))\sum_{k=1}^{K}(B_k - \bar{B})^2$ = sample variance; $S_B = \sqrt{S_B^2}$ = sample standard deviation; $\overline{SE} = (1/K)\sum_{k=1}^{K}\widehat{SE}_k$ = mean standard error; $k_B$ = standardized kurtosis; $g_B$ = standardized skewness; $I(\cdot)$ = indicator function; $P_k$ = p-value from replication $k$; $\alpha$ = significance level; $L_k$, $U_k$ = lower and upper CI endpoints; $S_W^2$ = variance of CI widths; $r_\alpha$ and $c_\beta$ denote rejection rate and coverage, respectively; $\textit{Mdn}(B)$ = sample median of estimates; MAD = median absolute deviation with scaling factor 1.4826. MCSE = Monte Carlo Standard Error, dashes indicate MCSEs not computed. MSE = Mean Squared Error. RMSE = Root Mean Squared Error.
\end{flushleft}
\endlandscape
\normalsize

\newpage

```{r}
#| label: load-results

results_study_1 <- readRDS("../Simulations/Study_1/Results/results_study_1_basic_robust.rds")
results_study_2 <- readRDS("../Simulations/Study_2/Results/results_study_2_basic_robust.rds")
```

```{r}
#| label: parameter-mapping

# PARAMETER MAPPING FUNCTION
map_parameter_to_beta <- function(param, study = 1, equation = NULL) {
  if (study == 1) {
    beta_map <- c(
      "eta1" = "beta31",
      "eta2" = "beta32",
      "eta1:eta2" = "beta33",
      "eta1:eta1" = "beta34",
      "eta2:eta2" = "beta35"
    )
  } else if (study == 2) {
    if (equation == "eta4") {
      beta_map <- c(
        "eta1" = "beta41",
        "eta2" = "beta42",
        "eta3" = "beta43",
        "eta1:eta2" = "beta44",
        "eta1:eta3" = "beta45",
        "eta1:eta1" = "beta46",
        "eta2:eta2" = "beta47"
      )
    } else if (equation == "eta5") {
      beta_map <- c(
        "eta4" = "beta51",
        "eta1" = "beta52",
        "eta2" = "beta53",
        "eta3" = "beta54",
        "eta1:eta4" = "beta55",
        "eta2:eta4" = "beta56",
        "eta1:eta1" = "beta57",
        "eta3:eta3" = "beta58"
      )
    }
  }

  ifelse(param %in% names(beta_map), beta_map[param], param)
}
```

# Complete Results Tables — Simulation 1

```{r}
#| label: sim1-tables
#| output: asis

# label formatting
label_distr <- function(x) {
  case_when(
    x == "nonnormal" ~ "Right-skewed",
    x == "exp.rate1" ~ "Right-skewed",
    TRUE ~ tools::toTitleCase(as.character(x))
  )
}

create_apa_results_table_study1_by_condition <- function(results_df, condition_filter, model_filter,
                                                          distr_exo_filter, distr_epsilon_filter, distr_zeta_filter,
                                                          n_filter, rel_filter) {

  df <- results_df %>%
    filter(
      Condition == condition_filter,
      Model == model_filter,
      Distr_Exo == distr_exo_filter,
      Distr_Epsilon == distr_epsilon_filter,
      Distr_Zeta == distr_zeta_filter,
      SampleSize == n_filter,
      Reliability == rel_filter
    ) %>%
    select(
      Method, Parameter, TrueValue,
      MeanEstimate, Bias_Mean, Bias_Mean_MCSE,
      RelativeBias_Mean, RelativeBias_MCSE,
      MedianEstimate, Bias_Median, PercentRelativeBias_Median, MAD,
      Variance, Variance_MCSE, SD, SD_MCSE,
      MSE_Mean, MSE_Mean_MCSE, RMSE_Mean, RMSE_Mean_MCSE, RMSE_Median,
      Relative_MSE, Relative_MSE_MCSE, Relative_RMSE, Relative_RMSE_MCSE,
      SE_SD_Ratio, CoverageRate, CoverageRate_MCSE,
      CI_Width, CI_Width_MCSE,
      TypeI_Error, TypeI_Error_MCSE, Power, Power_MCSE
    ) %>%
    mutate(
      Parameter = map_parameter_to_beta(Parameter, study = 1),
      `Bias ± MCSE` = sprintf("%.3f ± %.3f", Bias_Mean, Bias_Mean_MCSE),
      `Rel. Bias ± MCSE` = ifelse(TrueValue == 0, "—",
                                    sprintf("%.3f ± %.3f", RelativeBias_Mean, RelativeBias_MCSE)),
      `Variance ± MCSE` = sprintf("%.3f ± %.3f", Variance, Variance_MCSE),
      `SD ± MCSE` = sprintf("%.3f ± %.3f", SD, SD_MCSE),
      `MSE ± MCSE` = sprintf("%.3f ± %.3f", MSE_Mean, MSE_Mean_MCSE),
      `RMSE ± MCSE` = sprintf("%.3f ± %.3f", RMSE_Mean, RMSE_Mean_MCSE),
      `Rel. MSE ± MCSE` = ifelse(TrueValue == 0, "—",
                                   sprintf("%.3f ± %.3f", Relative_MSE, Relative_MSE_MCSE)),
      `Rel. RMSE ± MCSE` = ifelse(TrueValue == 0, "—",
                                    sprintf("%.3f ± %.3f", Relative_RMSE, Relative_RMSE_MCSE)),
      `% Rel. Bias (Med)` = ifelse(TrueValue == 0, "—",
                                    sprintf("%.2f", PercentRelativeBias_Median)),
      `Coverage ± MCSE` = sprintf("%.3f ± %.3f", CoverageRate, CoverageRate_MCSE),
      `CI Width ± MCSE` = sprintf("%.3f ± %.3f", CI_Width, CI_Width_MCSE),
      `Type I ± MCSE` = ifelse(is.na(TypeI_Error), "—",
                               sprintf("%.3f ± %.3f", TypeI_Error, TypeI_Error_MCSE)),
      `Power ± MCSE` = ifelse(is.na(Power), "—",
                              sprintf("%.3f ± %.3f", Power, Power_MCSE))
    ) %>%
    select(
      Method, Parameter, TrueValue,
      MeanEstimate, `Bias ± MCSE`, `Rel. Bias ± MCSE`,
      `Variance ± MCSE`, `SD ± MCSE`,
      `MSE ± MCSE`, `RMSE ± MCSE`,
      `Rel. MSE ± MCSE`, `Rel. RMSE ± MCSE`,
      MedianEstimate, Bias_Median, `% Rel. Bias (Med)`, MAD, RMSE_Median,
      SE_SD_Ratio, `Coverage ± MCSE`, `CI Width ± MCSE`,
      `Type I ± MCSE`, `Power ± MCSE`
    ) %>%
    mutate(
      TrueValue = round(TrueValue, 3),
      MeanEstimate = round(MeanEstimate, 3),
      MedianEstimate = round(MedianEstimate, 3),
      Bias_Median = round(Bias_Median, 3),
      MAD = round(MAD, 4),
      RMSE_Median = round(RMSE_Median, 4),
      SE_SD_Ratio = round(SE_SD_Ratio, 3)
    ) %>%
    arrange(Method, Parameter)

  if(model_filter == "Full") {
    df <- df %>% select(-`Type I ± MCSE`)
  } else {
    df <- df %>% select(-`Power ± MCSE`)
  }

  df
}

# unique condition combinations for sim 1
conditions_study1 <- results_study_1 %>%
  select(Condition, Model, Distr_Exo, Distr_Epsilon, Distr_Zeta, SampleSize, Reliability) %>%
  distinct() %>%
  arrange(Condition, factor(Model, levels = c("Full", "Linear")))

# tables for each condition in sim 1
for(i in 1:nrow(conditions_study1)) {
  condition_data <- conditions_study1[i, ]

  condition_table <- create_apa_results_table_study1_by_condition(
    results_study_1,
    condition_data$Condition,
    condition_data$Model,
    condition_data$Distr_Exo,
    condition_data$Distr_Epsilon,
    condition_data$Distr_Zeta,
    condition_data$SampleSize,
    condition_data$Reliability
  )

  tab_caption <- sprintf(
    "Simulation 1 - Condition %s: %s Model, Distr = %s, Epsilon = %s, Zeta = %s, N = %d, Reliability = %.1f",
    condition_data$Condition,
    condition_data$Model,
    label_distr(condition_data$Distr_Exo),
    label_distr(condition_data$Distr_Epsilon),
    label_distr(condition_data$Distr_Zeta),
    condition_data$SampleSize,
    condition_data$Reliability
  )

  tab_note <- "MCSE = Monte Carlo Standard Error shown as \\u00b1 value. Coverage, Type I Error, and Power expressed as percentages. \\u2014 indicates relative measures are undefined when true value equals 0 and non-existent results for Type I error rate which was evaluated only for nonlinear effects."

  cat("\\setlength{\\tabcolsep}{3pt}\n")

  print(
    kableExtra::kbl(
      condition_table,
      booktabs = TRUE,
      longtable = TRUE,
      align = c("l", "l", rep("r", 19)),
      col.names = c("Method", "Param.",
                    "True",
                    "Mean", "Bias ± MCSE", "Rel. Bias ± MCSE",
                    "Var. ± MCSE", "SD ± MCSE",
                    "MSE ± MCSE", "RMSE ± MCSE",
                    "Rel. MSE ± MCSE", "Rel. RMSE ± MCSE",
                    "Median", "Bias", "% Rel. Bias", "MAD", "RMSE",
                    "SE/SD",
                    "Cover. (%) ± MCSE", "CI Width ± MCSE",
                    if(condition_data$Model == "Full") "Power (%) ± MCSE" else "Type I (%) ± MCSE"),
      caption = tab_caption,
      linesep = ""
    ) %>%
      kableExtra::add_header_above(c(
        " " = 3,
        "Mean-based" = 9,
        "Median-based" = 5,
        "Inference" = 4
      )) %>%
      kableExtra::kable_styling(
        latex_options = c("hold_position", "repeat_header"),
        font_size = 4.5
      ) %>%
      kableExtra::footnote(
        general = tab_note,
        general_title = "Note.",
        threeparttable = TRUE,
        escape = TRUE
      ) %>%
      kableExtra::landscape()
  )

  cat("\\setlength{\\tabcolsep}{6pt}\n")
  cat("\n\\clearpage\n\n")
}
```

# Complete Results Tables — Simulation 2

```{r}
#| label: sim2-tables
#| output: asis

create_apa_results_table_study2_by_condition <- function(results_df, condition_filter, model_filter,
                                                          distr_exo_filter, distr_epsilon_filter, distr_zeta_filter,
                                                          n_filter, rel_filter) {

  df <- results_df %>%
    filter(
      Condition == condition_filter,
      Model == model_filter,
      Distr_Exo == distr_exo_filter,
      Distr_Epsilon == distr_epsilon_filter,
      Distr_Zeta == distr_zeta_filter,
      SampleSize == n_filter,
      Reliability == rel_filter
    ) %>%
    select(
      Method, Parameter, Equation, TrueValue,
      MeanEstimate, Bias_Mean, Bias_Mean_MCSE,
      RelativeBias_Mean, RelativeBias_MCSE,
      MedianEstimate, Bias_Median, PercentRelativeBias_Median, MAD,
      Variance, Variance_MCSE, SD, SD_MCSE,
      MSE_Mean, MSE_Mean_MCSE, RMSE_Mean, RMSE_Mean_MCSE, RMSE_Median,
      Relative_MSE, Relative_MSE_MCSE, Relative_RMSE, Relative_RMSE_MCSE,
      SE_SD_Ratio, CoverageRate, CoverageRate_MCSE,
      CI_Width, CI_Width_MCSE,
      TypeI_Error, TypeI_Error_MCSE, Power, Power_MCSE
    ) %>%
    mutate(
      Parameter = mapply(map_parameter_to_beta, Parameter, study = 2, equation = Equation)
    ) %>%
    mutate(
      `Bias ± MCSE` = sprintf("%.3f ± %.3f", Bias_Mean, Bias_Mean_MCSE),
      `Rel. Bias ± MCSE` = ifelse(TrueValue == 0, "—",
                                    sprintf("%.3f ± %.3f", RelativeBias_Mean, RelativeBias_MCSE)),
      `Variance ± MCSE` = sprintf("%.3f ± %.3f", Variance, Variance_MCSE),
      `SD ± MCSE` = sprintf("%.3f ± %.3f", SD, SD_MCSE),
      `MSE ± MCSE` = sprintf("%.3f ± %.3f", MSE_Mean, MSE_Mean_MCSE),
      `RMSE ± MCSE` = sprintf("%.3f ± %.3f", RMSE_Mean, RMSE_Mean_MCSE),
      `Rel. MSE ± MCSE` = ifelse(TrueValue == 0, "—",
                                   sprintf("%.3f ± %.3f", Relative_MSE, Relative_MSE_MCSE)),
      `Rel. RMSE ± MCSE` = ifelse(TrueValue == 0, "—",
                                    sprintf("%.3f ± %.3f", Relative_RMSE, Relative_RMSE_MCSE)),
      `% Rel. Bias (Med)` = ifelse(TrueValue == 0, "—",
                                    sprintf("%.2f", PercentRelativeBias_Median)),
      `Coverage ± MCSE` = sprintf("%.3f ± %.3f", CoverageRate, CoverageRate_MCSE),
      `CI Width ± MCSE` = sprintf("%.3f ± %.3f", CI_Width, CI_Width_MCSE),
      `Type I ± MCSE` = ifelse(is.na(TypeI_Error), "—",
                               sprintf("%.3f ± %.3f", TypeI_Error, TypeI_Error_MCSE)),
      `Power ± MCSE` = ifelse(is.na(Power), "—",
                              sprintf("%.3f ± %.3f", Power, Power_MCSE))
    ) %>%
    select(
      Method, Parameter, TrueValue,
      MeanEstimate, `Bias ± MCSE`, `Rel. Bias ± MCSE`,
      `Variance ± MCSE`, `SD ± MCSE`,
      `MSE ± MCSE`, `RMSE ± MCSE`,
      `Rel. MSE ± MCSE`, `Rel. RMSE ± MCSE`,
      MedianEstimate, Bias_Median, `% Rel. Bias (Med)`, MAD, RMSE_Median,
      SE_SD_Ratio, `Coverage ± MCSE`, `CI Width ± MCSE`,
      `Type I ± MCSE`, `Power ± MCSE`
    ) %>%
    mutate(
      TrueValue = round(TrueValue, 3),
      MeanEstimate = round(MeanEstimate, 3),
      MedianEstimate = round(MedianEstimate, 3),
      Bias_Median = round(Bias_Median, 3),
      MAD = round(MAD, 4),
      RMSE_Median = round(RMSE_Median, 4),
      SE_SD_Ratio = round(SE_SD_Ratio, 3)
    ) %>%
    arrange(Method, Parameter)

  if(model_filter == "Full") {
    df <- df %>% select(-`Type I ± MCSE`)
  } else {
    df <- df %>% select(-`Power ± MCSE`)
  }

  df
}

# unique condition combinations for sim 2
conditions_study2 <- results_study_2 %>%
  select(Condition, Model, Distr_Exo, Distr_Epsilon, Distr_Zeta, SampleSize, Reliability) %>%
  distinct() %>%
  arrange(Condition, factor(Model, levels = c("Full", "Linear")))

for(i in 1:nrow(conditions_study2)) {
  condition_data <- conditions_study2[i, ]

  condition_table <- create_apa_results_table_study2_by_condition(
    results_study_2,
    condition_data$Condition,
    condition_data$Model,
    condition_data$Distr_Exo,
    condition_data$Distr_Epsilon,
    condition_data$Distr_Zeta,
    condition_data$SampleSize,
    condition_data$Reliability
  )

  tab_caption <- sprintf(
    "Simulation 2 - Condition %s: %s Model, Distr = %s, Epsilon = %s, Zeta = %s, N = %d, Reliability = %.1f",
    condition_data$Condition,
    condition_data$Model,
    label_distr(condition_data$Distr_Exo),
    label_distr(condition_data$Distr_Epsilon),
    label_distr(condition_data$Distr_Zeta),
    condition_data$SampleSize,
    condition_data$Reliability
  )

  tab_note <- "MCSE = Monte Carlo Standard Error shown as \\u00b1 value. Coverage, Type I Error, and Power expressed as percentages. \\u2014 indicates relative measures are undefined when true value equals 0 and non-existent results for Type I error rate which was evaluated only for nonlinear effects."

  cat("\\setlength{\\tabcolsep}{3pt}\n")

  print(
    kableExtra::kbl(
      condition_table,
      booktabs = TRUE,
      longtable = TRUE,
      align = c("l", "l", rep("r", 19)),
      col.names = c("Method", "Param.",
                    "True",
                    "Mean", "Bias ± MCSE", "Rel. Bias ± MCSE",
                    "Var. ± MCSE", "SD ± MCSE",
                    "MSE ± MCSE", "RMSE ± MCSE",
                    "Rel. MSE ± MCSE", "Rel. RMSE ± MCSE",
                    "Median", "Bias", "% Rel. Bias", "MAD", "RMSE",
                    "SE/SD",
                    "Cover. (%) ± MCSE", "CI Width ± MCSE",
                    if(condition_data$Model == "Full") "Power (%) ± MCSE" else "Type I (%) ± MCSE"),
      caption = tab_caption,
      linesep = ""
    ) %>%
      kableExtra::add_header_above(c(
        " " = 3,
        "Mean-based" = 9,
        "Median-based" = 5,
        "Inference" = 4
      )) %>%
      kableExtra::kable_styling(
        latex_options = c("hold_position", "repeat_header"),
        font_size = 4.5
      ) %>%
      kableExtra::footnote(
        general = tab_note,
        general_title = "Note.",
        threeparttable = TRUE,
        escape = TRUE
      ) %>%
      kableExtra::landscape()
  )

  cat("\\setlength{\\tabcolsep}{6pt}\n")
  cat("\n\\clearpage\n\n")
}
```

# Additional Distributional Conditions: Differences from Baseline

```{r}
#| label: setup-diff-plots
#| include: false

library(ggplot2)
source("../Simulations/Plots.R")
```

```{r}
#| label: prepare-diff-data-s1

dumbbell_s1 <- prepare_sensitivity_dumbbell_data(results_study_1, study = 1, include_low_rel = FALSE)
diff_s1 <- compute_all_sensitivity_differences(dumbbell_s1)
```

```{r}
#| label: fig-diff-s1-relbias-eps
#| fig-cap: "Additional Distributional Conditions Difference: Relative Bias for Simulation 1 (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s1 %>% filter(Metric == "Relative Bias", Error_Condition == "Epsilon"), metric_name = "Relative Bias", greys = GREYS_4)
```

```{r}
#| label: fig-diff-s1-relbias-zeta
#| fig-cap: "Additional Distributional Conditions Difference: Relative Bias for Simulation 1 (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s1 %>% filter(Metric == "Relative Bias", Error_Condition == "Zeta"), metric_name = "Relative Bias", greys = GREYS_4)
```

```{r}
#| label: fig-diff-s1-relbias-both
#| fig-cap: "Additional Distributional Conditions Difference: Relative Bias for Simulation 1 (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s1 %>% filter(Metric == "Relative Bias", Error_Condition == "Epsilon & Zeta"), metric_name = "Relative Bias", greys = GREYS_4)
```

```{r}
#| label: fig-diff-s1-relrmse-eps
#| fig-cap: "Additional Distributional Conditions Difference: Relative RMSE for Simulation 1 (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s1 %>% filter(Metric == "Relative RMSE", Error_Condition == "Epsilon"), metric_name = "Relative RMSE", greys = GREYS_4)
```

```{r}
#| label: fig-diff-s1-relrmse-zeta
#| fig-cap: "Additional Distributional Conditions Difference: Relative RMSE for Simulation 1 (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s1 %>% filter(Metric == "Relative RMSE", Error_Condition == "Zeta"), metric_name = "Relative RMSE", greys = GREYS_4)
```

```{r}
#| label: fig-diff-s1-relrmse-both
#| fig-cap: "Additional Distributional Conditions Difference: Relative RMSE for Simulation 1 (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s1 %>% filter(Metric == "Relative RMSE", Error_Condition == "Epsilon & Zeta"), metric_name = "Relative RMSE", greys = GREYS_4)
```

```{r}
#| label: fig-diff-s1-coverage-eps
#| fig-cap: "Additional Distributional Conditions Difference: Coverage Rate for Simulation 1 (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s1 %>% filter(Metric == "Coverage Rate", Error_Condition == "Epsilon"), metric_name = "Coverage Rate", greys = GREYS_4)
```

```{r}
#| label: fig-diff-s1-coverage-zeta
#| fig-cap: "Additional Distributional Conditions Difference: Coverage Rate for Simulation 1 (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s1 %>% filter(Metric == "Coverage Rate", Error_Condition == "Zeta"), metric_name = "Coverage Rate", greys = GREYS_4)
```

```{r}
#| label: fig-diff-s1-coverage-both
#| fig-cap: "Additional Distributional Conditions Difference: Coverage Rate for Simulation 1 (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s1 %>% filter(Metric == "Coverage Rate", Error_Condition == "Epsilon & Zeta"), metric_name = "Coverage Rate", greys = GREYS_4)
```

```{r}
#| label: fig-diff-s1-sesd-eps
#| fig-cap: "Additional Distributional Conditions Difference: SE/SD Ratio for Simulation 1 (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s1 %>% filter(Metric == "SE/SD Ratio", Error_Condition == "Epsilon"), metric_name = "SE/SD Ratio", greys = GREYS_4)
```

```{r}
#| label: fig-diff-s1-sesd-zeta
#| fig-cap: "Additional Distributional Conditions Difference: SE/SD Ratio for Simulation 1 (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s1 %>% filter(Metric == "SE/SD Ratio", Error_Condition == "Zeta"), metric_name = "SE/SD Ratio", greys = GREYS_4)
```

```{r}
#| label: fig-diff-s1-sesd-both
#| fig-cap: "Additional Distributional Conditions Difference: SE/SD Ratio for Simulation 1 (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s1 %>% filter(Metric == "SE/SD Ratio", Error_Condition == "Epsilon & Zeta"), metric_name = "SE/SD Ratio", greys = GREYS_4)
```

```{r}
#| label: fig-diff-s1-power-eps
#| fig-cap: "Additional Distributional Conditions Difference: Power for Simulation 1 (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s1 %>% filter(Metric == "Power", Error_Condition == "Epsilon"), metric_name = "Power", greys = GREYS_4)
```

```{r}
#| label: fig-diff-s1-power-zeta
#| fig-cap: "Additional Distributional Conditions Difference: Power for Simulation 1 (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s1 %>% filter(Metric == "Power", Error_Condition == "Zeta"), metric_name = "Power", greys = GREYS_4)
```

```{r}
#| label: fig-diff-s1-power-both
#| fig-cap: "Additional Distributional Conditions Difference: Power for Simulation 1 (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s1 %>% filter(Metric == "Power", Error_Condition == "Epsilon & Zeta"), metric_name = "Power", greys = GREYS_4)
```

```{r}
#| label: fig-diff-s1-type1-eps
#| fig-cap: "Additional Distributional Conditions Difference: Type I Error for Simulation 1 (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s1 %>% filter(Metric == "Type I Error", Error_Condition == "Epsilon"), metric_name = "Type I Error", greys = GREYS_4)
```

```{r}
#| label: fig-diff-s1-type1-zeta
#| fig-cap: "Additional Distributional Conditions Difference: Type I Error for Simulation 1 (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s1 %>% filter(Metric == "Type I Error", Error_Condition == "Zeta"), metric_name = "Type I Error", greys = GREYS_4)
```

```{r}
#| label: fig-diff-s1-type1-both
#| fig-cap: "Additional Distributional Conditions Difference: Type I Error for Simulation 1 (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s1 %>% filter(Metric == "Type I Error", Error_Condition == "Epsilon & Zeta"), metric_name = "Type I Error", greys = GREYS_4)
```

\clearpage

```{r}
#| label: prepare-diff-data-s2-normal

dumbbell_s2_normal <- prepare_sensitivity_dumbbell_data(results_study_2, study = 2, include_low_rel = FALSE, distribution = "normal")
diff_s2_normal <- compute_all_sensitivity_differences(dumbbell_s2_normal)
```

```{r}
#| label: fig-diff-s2-normal-relbias-eps
#| fig-cap: "Additional Distributional Conditions Difference: Relative Bias for Simulation 2 -- Normal (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_normal %>% filter(Metric == "Relative Bias", Error_Condition == "Epsilon"), metric_name = "Relative Bias", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-normal-relbias-zeta
#| fig-cap: "Additional Distributional Conditions Difference: Relative Bias for Simulation 2 -- Normal (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_normal %>% filter(Metric == "Relative Bias", Error_Condition == "Zeta"), metric_name = "Relative Bias", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-normal-relbias-both
#| fig-cap: "Additional Distributional Conditions Difference: Relative Bias for Simulation 2 -- Normal (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_normal %>% filter(Metric == "Relative Bias", Error_Condition == "Epsilon & Zeta"), metric_name = "Relative Bias", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-normal-relrmse-eps
#| fig-cap: "Additional Distributional Conditions Difference: Relative RMSE for Simulation 2 -- Normal (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_normal %>% filter(Metric == "Relative RMSE", Error_Condition == "Epsilon"), metric_name = "Relative RMSE", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-normal-relrmse-zeta
#| fig-cap: "Additional Distributional Conditions Difference: Relative RMSE for Simulation 2 -- Normal (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_normal %>% filter(Metric == "Relative RMSE", Error_Condition == "Zeta"), metric_name = "Relative RMSE", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-normal-relrmse-both
#| fig-cap: "Additional Distributional Conditions Difference: Relative RMSE for Simulation 2 -- Normal (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_normal %>% filter(Metric == "Relative RMSE", Error_Condition == "Epsilon & Zeta"), metric_name = "Relative RMSE", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-normal-coverage-eps
#| fig-cap: "Additional Distributional Conditions Difference: Coverage Rate for Simulation 2 -- Normal (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_normal %>% filter(Metric == "Coverage Rate", Error_Condition == "Epsilon"), metric_name = "Coverage Rate", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-normal-coverage-zeta
#| fig-cap: "Additional Distributional Conditions Difference: Coverage Rate for Simulation 2 -- Normal (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_normal %>% filter(Metric == "Coverage Rate", Error_Condition == "Zeta"), metric_name = "Coverage Rate", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-normal-coverage-both
#| fig-cap: "Additional Distributional Conditions Difference: Coverage Rate for Simulation 2 -- Normal (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_normal %>% filter(Metric == "Coverage Rate", Error_Condition == "Epsilon & Zeta"), metric_name = "Coverage Rate", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-normal-sesd-eps
#| fig-cap: "Additional Distributional Conditions Difference: SE/SD Ratio for Simulation 2 -- Normal (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_normal %>% filter(Metric == "SE/SD Ratio", Error_Condition == "Epsilon"), metric_name = "SE/SD Ratio", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-normal-sesd-zeta
#| fig-cap: "Additional Distributional Conditions Difference: SE/SD Ratio for Simulation 2 -- Normal (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_normal %>% filter(Metric == "SE/SD Ratio", Error_Condition == "Zeta"), metric_name = "SE/SD Ratio", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-normal-sesd-both
#| fig-cap: "Additional Distributional Conditions Difference: SE/SD Ratio for Simulation 2 -- Normal (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_normal %>% filter(Metric == "SE/SD Ratio", Error_Condition == "Epsilon & Zeta"), metric_name = "SE/SD Ratio", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-normal-power-eps
#| fig-cap: "Additional Distributional Conditions Difference: Power for Simulation 2 -- Normal (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_normal %>% filter(Metric == "Power", Error_Condition == "Epsilon"), metric_name = "Power", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-normal-power-zeta
#| fig-cap: "Additional Distributional Conditions Difference: Power for Simulation 2 -- Normal (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_normal %>% filter(Metric == "Power", Error_Condition == "Zeta"), metric_name = "Power", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-normal-power-both
#| fig-cap: "Additional Distributional Conditions Difference: Power for Simulation 2 -- Normal (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_normal %>% filter(Metric == "Power", Error_Condition == "Epsilon & Zeta"), metric_name = "Power", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-normal-type1-eps
#| fig-cap: "Additional Distributional Conditions Difference: Type I Error for Simulation 2 -- Normal (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_normal %>% filter(Metric == "Type I Error", Error_Condition == "Epsilon"), metric_name = "Type I Error", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-normal-type1-zeta
#| fig-cap: "Additional Distributional Conditions Difference: Type I Error for Simulation 2 -- Normal (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_normal %>% filter(Metric == "Type I Error", Error_Condition == "Zeta"), metric_name = "Type I Error", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-normal-type1-both
#| fig-cap: "Additional Distributional Conditions Difference: Type I Error for Simulation 2 -- Normal (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_normal %>% filter(Metric == "Type I Error", Error_Condition == "Epsilon & Zeta"), metric_name = "Type I Error", greys = GREYS_3)
```

\clearpage

```{r}
#| label: prepare-diff-data-s2-nonnormal

dumbbell_s2_nonnormal <- prepare_sensitivity_dumbbell_data(results_study_2, study = 2, include_low_rel = FALSE, distribution = "nonnormal")
diff_s2_nonnormal <- compute_all_sensitivity_differences(dumbbell_s2_nonnormal)
```

```{r}
#| label: fig-diff-s2-nonnormal-relbias-eps
#| fig-cap: "Additional Distributional Conditions Difference: Relative Bias for Simulation 2 -- Right-skewed (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_nonnormal %>% filter(Metric == "Relative Bias", Error_Condition == "Epsilon"), metric_name = "Relative Bias", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-nonnormal-relbias-zeta
#| fig-cap: "Additional Distributional Conditions Difference: Relative Bias for Simulation 2 -- Right-skewed (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_nonnormal %>% filter(Metric == "Relative Bias", Error_Condition == "Zeta"), metric_name = "Relative Bias", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-nonnormal-relbias-both
#| fig-cap: "Additional Distributional Conditions Difference: Relative Bias for Simulation 2 -- Right-skewed (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_nonnormal %>% filter(Metric == "Relative Bias", Error_Condition == "Epsilon & Zeta"), metric_name = "Relative Bias", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-nonnormal-relrmse-eps
#| fig-cap: "Additional Distributional Conditions Difference: Relative RMSE for Simulation 2 -- Right-skewed (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_nonnormal %>% filter(Metric == "Relative RMSE", Error_Condition == "Epsilon"), metric_name = "Relative RMSE", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-nonnormal-relrmse-zeta
#| fig-cap: "Additional Distributional Conditions Difference: Relative RMSE for Simulation 2 -- Right-skewed (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_nonnormal %>% filter(Metric == "Relative RMSE", Error_Condition == "Zeta"), metric_name = "Relative RMSE", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-nonnormal-relrmse-both
#| fig-cap: "Additional Distributional Conditions Difference: Relative RMSE for Simulation 2 -- Right-skewed (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_nonnormal %>% filter(Metric == "Relative RMSE", Error_Condition == "Epsilon & Zeta"), metric_name = "Relative RMSE", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-nonnormal-coverage-eps
#| fig-cap: "Additional Distributional Conditions Difference: Coverage Rate for Simulation 2 -- Right-skewed (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_nonnormal %>% filter(Metric == "Coverage Rate", Error_Condition == "Epsilon"), metric_name = "Coverage Rate", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-nonnormal-coverage-zeta
#| fig-cap: "Additional Distributional Conditions Difference: Coverage Rate for Simulation 2 -- Right-skewed (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_nonnormal %>% filter(Metric == "Coverage Rate", Error_Condition == "Zeta"), metric_name = "Coverage Rate", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-nonnormal-coverage-both
#| fig-cap: "Additional Distributional Conditions Difference: Coverage Rate for Simulation 2 -- Right-skewed (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_nonnormal %>% filter(Metric == "Coverage Rate", Error_Condition == "Epsilon & Zeta"), metric_name = "Coverage Rate", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-nonnormal-sesd-eps
#| fig-cap: "Additional Distributional Conditions Difference: SE/SD Ratio for Simulation 2 -- Right-skewed (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_nonnormal %>% filter(Metric == "SE/SD Ratio", Error_Condition == "Epsilon"), metric_name = "SE/SD Ratio", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-nonnormal-sesd-zeta
#| fig-cap: "Additional Distributional Conditions Difference: SE/SD Ratio for Simulation 2 -- Right-skewed (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_nonnormal %>% filter(Metric == "SE/SD Ratio", Error_Condition == "Zeta"), metric_name = "SE/SD Ratio", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-nonnormal-sesd-both
#| fig-cap: "Additional Distributional Conditions Difference: SE/SD Ratio for Simulation 2 -- Right-skewed (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_nonnormal %>% filter(Metric == "SE/SD Ratio", Error_Condition == "Epsilon & Zeta"), metric_name = "SE/SD Ratio", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-nonnormal-power-eps
#| fig-cap: "Additional Distributional Conditions Difference: Power for Simulation 2 -- Right-skewed (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_nonnormal %>% filter(Metric == "Power", Error_Condition == "Epsilon"), metric_name = "Power", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-nonnormal-power-zeta
#| fig-cap: "Additional Distributional Conditions Difference: Power for Simulation 2 -- Right-skewed (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_nonnormal %>% filter(Metric == "Power", Error_Condition == "Zeta"), metric_name = "Power", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-nonnormal-power-both
#| fig-cap: "Additional Distributional Conditions Difference: Power for Simulation 2 -- Right-skewed (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_nonnormal %>% filter(Metric == "Power", Error_Condition == "Epsilon & Zeta"), metric_name = "Power", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-nonnormal-type1-eps
#| fig-cap: "Additional Distributional Conditions Difference: Type I Error for Simulation 2 -- Right-skewed (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_nonnormal %>% filter(Metric == "Type I Error", Error_Condition == "Epsilon"), metric_name = "Type I Error", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-nonnormal-type1-zeta
#| fig-cap: "Additional Distributional Conditions Difference: Type I Error for Simulation 2 -- Right-skewed (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_nonnormal %>% filter(Metric == "Type I Error", Error_Condition == "Zeta"), metric_name = "Type I Error", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-nonnormal-type1-both
#| fig-cap: "Additional Distributional Conditions Difference: Type I Error for Simulation 2 -- Right-skewed (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_nonnormal %>% filter(Metric == "Type I Error", Error_Condition == "Epsilon & Zeta"), metric_name = "Type I Error", greys = GREYS_3)
```

\clearpage

```{r}
#| label: prepare-diff-data-s2-uniform

dumbbell_s2_uniform <- prepare_sensitivity_dumbbell_data(results_study_2, study = 2, include_low_rel = FALSE, distribution = "uniform")
diff_s2_uniform <- compute_all_sensitivity_differences(dumbbell_s2_uniform)
```

```{r}
#| label: fig-diff-s2-uniform-relbias-eps
#| fig-cap: "Additional Distributional Conditions Difference: Relative Bias for Simulation 2 -- Uniform (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_uniform %>% filter(Metric == "Relative Bias", Error_Condition == "Epsilon"), metric_name = "Relative Bias", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-uniform-relbias-zeta
#| fig-cap: "Additional Distributional Conditions Difference: Relative Bias for Simulation 2 -- Uniform (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_uniform %>% filter(Metric == "Relative Bias", Error_Condition == "Zeta"), metric_name = "Relative Bias", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-uniform-relbias-both
#| fig-cap: "Additional Distributional Conditions Difference: Relative Bias for Simulation 2 -- Uniform (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_uniform %>% filter(Metric == "Relative Bias", Error_Condition == "Epsilon & Zeta"), metric_name = "Relative Bias", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-uniform-relrmse-eps
#| fig-cap: "Additional Distributional Conditions Difference: Relative RMSE for Simulation 2 -- Uniform (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_uniform %>% filter(Metric == "Relative RMSE", Error_Condition == "Epsilon"), metric_name = "Relative RMSE", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-uniform-relrmse-zeta
#| fig-cap: "Additional Distributional Conditions Difference: Relative RMSE for Simulation 2 -- Uniform (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_uniform %>% filter(Metric == "Relative RMSE", Error_Condition == "Zeta"), metric_name = "Relative RMSE", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-uniform-relrmse-both
#| fig-cap: "Additional Distributional Conditions Difference: Relative RMSE for Simulation 2 -- Uniform (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_uniform %>% filter(Metric == "Relative RMSE", Error_Condition == "Epsilon & Zeta"), metric_name = "Relative RMSE", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-uniform-coverage-eps
#| fig-cap: "Additional Distributional Conditions Difference: Coverage Rate for Simulation 2 -- Uniform (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_uniform %>% filter(Metric == "Coverage Rate", Error_Condition == "Epsilon"), metric_name = "Coverage Rate", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-uniform-coverage-zeta
#| fig-cap: "Additional Distributional Conditions Difference: Coverage Rate for Simulation 2 -- Uniform (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_uniform %>% filter(Metric == "Coverage Rate", Error_Condition == "Zeta"), metric_name = "Coverage Rate", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-uniform-coverage-both
#| fig-cap: "Additional Distributional Conditions Difference: Coverage Rate for Simulation 2 -- Uniform (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_uniform %>% filter(Metric == "Coverage Rate", Error_Condition == "Epsilon & Zeta"), metric_name = "Coverage Rate", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-uniform-sesd-eps
#| fig-cap: "Additional Distributional Conditions Difference: SE/SD Ratio for Simulation 2 -- Uniform (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_uniform %>% filter(Metric == "SE/SD Ratio", Error_Condition == "Epsilon"), metric_name = "SE/SD Ratio", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-uniform-sesd-zeta
#| fig-cap: "Additional Distributional Conditions Difference: SE/SD Ratio for Simulation 2 -- Uniform (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_uniform %>% filter(Metric == "SE/SD Ratio", Error_Condition == "Zeta"), metric_name = "SE/SD Ratio", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-uniform-sesd-both
#| fig-cap: "Additional Distributional Conditions Difference: SE/SD Ratio for Simulation 2 -- Uniform (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_uniform %>% filter(Metric == "SE/SD Ratio", Error_Condition == "Epsilon & Zeta"), metric_name = "SE/SD Ratio", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-uniform-power-eps
#| fig-cap: "Additional Distributional Conditions Difference: Power for Simulation 2 -- Uniform (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_uniform %>% filter(Metric == "Power", Error_Condition == "Epsilon"), metric_name = "Power", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-uniform-power-zeta
#| fig-cap: "Additional Distributional Conditions Difference: Power for Simulation 2 -- Uniform (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_uniform %>% filter(Metric == "Power", Error_Condition == "Zeta"), metric_name = "Power", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-uniform-power-both
#| fig-cap: "Additional Distributional Conditions Difference: Power for Simulation 2 -- Uniform (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_uniform %>% filter(Metric == "Power", Error_Condition == "Epsilon & Zeta"), metric_name = "Power", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-uniform-type1-eps
#| fig-cap: "Additional Distributional Conditions Difference: Type I Error for Simulation 2 -- Uniform (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_uniform %>% filter(Metric == "Type I Error", Error_Condition == "Epsilon"), metric_name = "Type I Error", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-uniform-type1-zeta
#| fig-cap: "Additional Distributional Conditions Difference: Type I Error for Simulation 2 -- Uniform (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_uniform %>% filter(Metric == "Type I Error", Error_Condition == "Zeta"), metric_name = "Type I Error", greys = GREYS_3)
```

```{r}
#| label: fig-diff-s2-uniform-type1-both
#| fig-cap: "Additional Distributional Conditions Difference: Type I Error for Simulation 2 -- Uniform (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_sensitivity_difference(diff_s2_uniform %>% filter(Metric == "Type I Error", Error_Condition == "Epsilon & Zeta"), metric_name = "Type I Error", greys = GREYS_3)
```
