---
title: "Supplemental Materials for Evaluating Local Structural-After-Measurement (LSAM) and Traditional Approaches for the Estimation of Complex Nonlinear Effects Among Latent Variables"
shorttitle: "Supplemental Materials: Evaluating LSAM and Traditional SEM Approaches"

author:
  - name: Felipe Fontana Vieira
    corresponding: true
    orcid: 0009-0006-0949-6569
    email: felipe.fontanavieira@ugent.be
    affiliations:
      - name: Ghent University
        department: Department of Data Analysis, Faculty of Psychology and Educational Sciences
        address: Henri Dunantlaan 2
        city: Ghent
        country: Belgium
        postal-code: 9000
        id: UGent
  - name: Kjell Solem Slupphaug
    corresponding: false
    orcid: 0009-0005-8324-2834
    affiliations:
      - name: Norwegian University of Science and Technology
        department: Department of Psychology
        city: Trondheim
        country: Norway
  - name: Yves Rosseel
    corresponding: false
    orcid: 0000-0002-4129-4477
    affiliations:
      - ref: UGent

floatsintext: true

format:
  apaquarto-pdf:
    documentmode: man
    keep-tex: false
    toc: false
    toc-depth: 2
    include-in-header:
      text: |
        \raggedbottom
        \usepackage{morefloats}
        \usepackage{pdflscape}
        \usepackage{longtable}
        \usepackage{array}
        \renewcommand{\thefigure}{S\arabic{figure}}
        \renewcommand{\thetable}{S\arabic{table}}
        \setcounter{figure}{0}
        \setcounter{table}{0}

execute:
  echo: false
  warning: false
  message: false

editor:
  markdown:
    wrap: sentence
---

This document contains the online supplemental materials mentioned throughout the manuscript. The table of contents in the next page shows all the separate sections. For the reader interested in the performance measures and tables with those results, see GitHub repository (see `Tables.qmd`); otherwise this file would be very large.

\newpage
\tableofcontents
\newpage

```{r}
#| label: setup
#| include: false

library(dplyr)
library(ggplot2)
library(kableExtra)

source("../Simulations/Plots.R")
```

# Computation Time and R² Values

```{r}
#| label: load-data

data_study_1 <- load("../Simulations/Study_1/Data/Data_Study_1_robustse_final.RData")
study1_all_results_raw <- all_results
study1_conditions_raw <- conditions

data_study_2 <- load("../Simulations/Study_2/Data/Data_Study_2_robustse_final.RData")
study2_all_results_raw <- all_results
study2_conditions_raw <- conditions
```

\setcounter{table}{1}

```{r}
#| label: timing-table
#| output: asis

# extract timing data from both studies using the _raw variables
# sim 1 timings
study1_timings <- data.frame()
for (i in 1:length(study1_all_results_raw)) {
  if (!is.null(study1_all_results_raw[[i]]$results$timing)) {
    timing <- study1_all_results_raw[[i]]$results$timing

    row_data <- data.frame(
      condition_id = i,
      N = study1_conditions_raw$N[i],
      Rel = study1_conditions_raw$Rel[i],
      Distr_Exo = study1_conditions_raw$Distr_Exo[i],
      Distr_Epsilon = study1_conditions_raw$Distr_Epsilon[i],
      Distr_Zeta = study1_conditions_raw$Distr_Zeta[i],
      Model_Type = study1_conditions_raw$Model_Type[i],

      S1_lms_mean = mean(timing$lms, na.rm = TRUE),
      S1_lms_median = median(timing$lms, na.rm = TRUE),
      S1_qml_mean = mean(timing$qml, na.rm = TRUE),
      S1_qml_median = median(timing$qml, na.rm = TRUE),
      S1_upi_mean = mean(timing$upi, na.rm = TRUE),
      S1_upi_median = median(timing$upi, na.rm = TRUE),
      S1_lsam_mean = mean(timing$lsam, na.rm = TRUE),
      S1_lsam_median = median(timing$lsam, na.rm = TRUE)
    )

    study1_timings <- rbind(study1_timings, row_data)
  }
}

# sim 2 timings
study2_timings <- data.frame()
for (i in 1:length(study2_all_results_raw)) {
  if (!is.null(study2_all_results_raw[[i]]$results$timing)) {
    timing <- study2_all_results_raw[[i]]$results$timing

    row_data <- data.frame(
      N = study2_conditions_raw$N[i],
      Rel = study2_conditions_raw$Rel[i],
      Distr_Exo = study2_conditions_raw$Distr_Exo[i],
      Distr_Epsilon = study2_conditions_raw$Distr_Epsilon[i],
      Distr_Zeta = study2_conditions_raw$Distr_Zeta[i],
      Model_Type = study2_conditions_raw$Model_Type[i],

      S2_lsam_mean = mean(timing$lsam, na.rm = TRUE),
      S2_lsam_median = median(timing$lsam, na.rm = TRUE),
      S2_qml_mean = mean(timing$qml, na.rm = TRUE),
      S2_qml_median = median(timing$qml, na.rm = TRUE),
      S2_upi_mean = mean(timing$upi, na.rm = TRUE),
      S2_upi_median = median(timing$upi, na.rm = TRUE)
    )

    study2_timings <- rbind(study2_timings, row_data)
  }
}

combined_timings <- merge(
  study1_timings,
  study2_timings[, c("N", "Rel", "Distr_Exo", "Distr_Epsilon", "Distr_Zeta", "Model_Type",
                      "S2_lsam_mean", "S2_lsam_median",
                      "S2_qml_mean", "S2_qml_median",
                      "S2_upi_mean", "S2_upi_median")],
  by = c("N", "Rel", "Distr_Exo", "Distr_Epsilon", "Distr_Zeta", "Model_Type"),
  all.x = TRUE
)

# reorder columns for better readability
combined_timings <- combined_timings[, c(
  "condition_id", "N", "Rel", "Distr_Exo", "Distr_Epsilon", "Distr_Zeta", "Model_Type",
  # sim 1 methods
  "S1_lms_mean", "S1_lms_median",
  "S1_qml_mean", "S1_qml_median",
  "S1_upi_mean", "S1_upi_median",
  "S1_lsam_mean", "S1_lsam_median",
  # sim 2 methods
  "S2_lsam_mean", "S2_lsam_median",
  "S2_qml_mean", "S2_qml_median",
  "S2_upi_mean", "S2_upi_median"
)]

timing_cols <- grep("^S[12]_", names(combined_timings))
combined_timings[timing_cols] <- round(combined_timings[timing_cols], 2)

# label formatting
label_distr <- function(x) {
  case_when(
    x == "nonnormal" ~ "Right-skewed",
    x == "exp.rate1" ~ "Right-skewed",
    TRUE ~ tools::toTitleCase(as.character(x))
  )
}

# APA formatted table
apa_timing_table <- combined_timings %>%
  mutate(
    Model = ifelse(Model_Type == "full", "Full", "Linear"),
    Distr_Exo = label_distr(Distr_Exo),
    Distr_Epsilon = label_distr(Distr_Epsilon),
    Distr_Zeta = label_distr(Distr_Zeta),
    Condition = condition_id
  ) %>%
  arrange(Condition) %>%
  select(
    Condition, Model, N, Reliability = Rel,
    Distr_Exo, Distr_Epsilon, Distr_Zeta,
    # sim 1
    S1_lms_mean, S1_lms_median,
    S1_qml_mean, S1_qml_median,
    S1_upi_mean, S1_upi_median,
    S1_lsam_mean, S1_lsam_median,
    # sim 2
    S2_lsam_mean, S2_lsam_median,
    S2_qml_mean, S2_qml_median,
    S2_upi_mean, S2_upi_median
  )

kableExtra::kbl(
  apa_timing_table,
  booktabs = TRUE,
  longtable = TRUE,
  align = c("l", "l", "r", "r", "l", "l", "l", rep("r", 14)),
  col.names = c(
    "Cond.", "Model", "N", "Rel.",
    "Distr.", "Epsilon", "Zeta",
    "Mean", "Mdn", "Mean", "Mdn", "Mean", "Mdn", "Mean", "Mdn",
    "Mean", "Mdn", "Mean", "Mdn", "Mean", "Mdn"
  ),
  caption = "Computation time by approach (in seconds)",
  linesep = "",
  digits = 2
) %>%
  kableExtra::add_header_above(c(
    " " = 4,
    "Distribution" = 3,
    "LMS" = 2,
    "QML" = 2,
    "UPI" = 2,
    "LSAM" = 2,
    "LSAM" = 2,
    "QML" = 2,
    "UPI" = 2
  )) %>%
  kableExtra::add_header_above(c(
    " " = 7,
    "Simulation 1" = 8,
    "Simulation 2" = 6
  )) %>%
  kableExtra::kable_styling(
    latex_options = c("hold_position", "repeat_header", "scale_down"),
    font_size = 6,
    position = "left"
  ) %>%
  kableExtra::footnote(
    general = "Each entry is the mean or median time (in seconds) to complete a single iteration, computed over 1,000 iterations per condition. For example, in the first condition LMS took 12.26 seconds for one iteration on average.",
    general_title = "Note.",
    threeparttable = TRUE,
    escape = TRUE
  ) %>%
  kableExtra::landscape()
```

```{r}
#| label: r2-table
#| output: asis

# Filter to baseline (all normal) conditions only
baseline_idx_s1 <- which(
  study1_conditions_raw$Distr_Exo == "normal" &
  study1_conditions_raw$Distr_Epsilon == "normal" &
  study1_conditions_raw$Distr_Zeta == "normal" &
  study1_conditions_raw$Model_Type == "full"
)

# Study 1: observed_r2 is numeric(1000) for eta3
r2_study1 <- data.frame()
for (i in baseline_idx_s1) {
  r2_vals <- study1_all_results_raw[[i]]$results$observed_r2
  r2_vals <- r2_vals[!is.na(r2_vals)]

  row_data <- data.frame(
    N = study1_conditions_raw$N[i],
    Rel = study1_conditions_raw$Rel[i],
    Model_Type = study1_conditions_raw$Model_Type[i],
    R2_eta3_mean = mean(r2_vals),
    R2_eta3_mcse = sd(r2_vals) / sqrt(length(r2_vals))
  )
  r2_study1 <- rbind(r2_study1, row_data)
}

# Filter to baseline (all normal) conditions for Study 2
baseline_idx_s2 <- which(
  study2_conditions_raw$Distr_Exo == "normal" &
  study2_conditions_raw$Distr_Epsilon == "normal" &
  study2_conditions_raw$Distr_Zeta == "normal" &
  study2_conditions_raw$Model_Type == "full"
)

# Study 2: observed_r2 is matrix(1000, 2) for eta4 and eta5
r2_study2 <- data.frame()
for (i in baseline_idx_s2) {
  r2_mat <- study2_all_results_raw[[i]]$results$observed_r2
  r2_eta4 <- r2_mat[!is.na(r2_mat[, 1]), 1]
  r2_eta5 <- r2_mat[!is.na(r2_mat[, 2]), 2]

  row_data <- data.frame(
    N = study2_conditions_raw$N[i],
    Rel = study2_conditions_raw$Rel[i],
    Model_Type = study2_conditions_raw$Model_Type[i],
    R2_eta4_mean = mean(r2_eta4),
    R2_eta4_mcse = sd(r2_eta4) / sqrt(length(r2_eta4)),
    R2_eta5_mean = mean(r2_eta5),
    R2_eta5_mcse = sd(r2_eta5) / sqrt(length(r2_eta5))
  )
  r2_study2 <- rbind(r2_study2, row_data)
}

# combine
r2_combined <- merge(
  r2_study1,
  r2_study2,
  by = c("N", "Rel", "Model_Type"),
  all.x = TRUE
)

apa_r2_table <- r2_combined %>%
  mutate(
    across(starts_with("R2_"), ~ round(.x, 3))
  ) %>%
  arrange(N, Rel) %>%
  select(
    N, Reliability = Rel,
    R2_eta3_mean, R2_eta3_mcse,
    R2_eta4_mean, R2_eta4_mcse,
    R2_eta5_mean, R2_eta5_mcse
  )

kableExtra::kbl(
  apa_r2_table,
  booktabs = TRUE,
  align = c("r", "r", rep("r", 6)),
  col.names = c(
    "N", "Rel.",
    "Mean", "MCSE", "Mean", "MCSE", "Mean", "MCSE"
  ),
  caption = "Average achieved $R^2$ values under normal baseline conditions",
  linesep = "",
  digits = 3
) %>%
  kableExtra::add_header_above(c(
    " " = 2,
    "$\\\\eta_3$ (Simulation 1)" = 2,
    "$\\\\eta_4$ (Simulation 2)" = 2,
    "$\\\\eta_5$ (Simulation 2)" = 2
  ), escape = FALSE) %>%
  kableExtra::kable_styling(
    latex_options = c("hold_position"),
    font_size = 8,
    position = "left"
  ) %>%
  kableExtra::footnote(
    general = "Mean = average observed $R^2$ across 1,000 iterations; MCSE = Monte Carlo standard error, computed as $SD/\\\\sqrt{K}$, where $SD$ is the standard deviation of the observed $R^2$ values and $K$ = 1,000 iterations. Only baseline conditions (all distributions normal, full model) are shown.",
    general_title = "Note.",
    threeparttable = TRUE,
    escape = FALSE
  )
```

```{r}
#| label: load-results

results_study_1 <- readRDS("../Simulations/Study_1/Results/results_study_1_basic_robust.rds")
results_study_2 <- readRDS("../Simulations/Study_2/Results/results_study_2_basic_robust.rds")
```

```{r}
#| label: prepare-plot-data

study1_data <- prepare_study1_data(results_study_1)
study_2_normal_data <- prepare_study2_data(results_study_2, "normal")
study_2_nonnormal_data <- prepare_study2_data(results_study_2, "nonnormal")
study_2_uniform_data <- prepare_study2_data(results_study_2, "uniform")
```

\clearpage

# Plots — Simulation 1

```{r}
#| label: fig-bias-sim1
#| fig-cap: "Absolute Bias for Simulation 1"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_bias(study1_data$bias, shapes = SHAPES_4, ltys = LTYS_4)
```

```{r}
#| label: fig-relbias-sim1
#| fig-cap: "Relative Bias for Simulation 1"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_bias(study1_data$bias_relative, shapes = SHAPES_4, ltys = LTYS_4)
```

```{r}
#| label: fig-rmse-sim1
#| fig-cap: "RMSE for Simulation 1"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_rmse(study1_data$rmse, shapes = SHAPES_4, ltys = LTYS_4)
```

```{r}
#| label: fig-relrmse-sim1
#| fig-cap: "Relative RMSE for Simulation 1"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_rmse(study1_data$rmse_relative, shapes = SHAPES_4, ltys = LTYS_4)
```

```{r}
#| label: fig-sesd-sim1
#| fig-cap: "SE/SD Ratio for Simulation 1"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_sesd(study1_data$sesd, shapes = SHAPES_4, ltys = LTYS_4)
```

```{r}
#| label: fig-coverage-sim1
#| fig-cap: "Coverage for Simulation 1"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_coverage(study1_data$coverage, shapes = SHAPES_4, ltys = LTYS_4)
```

```{r}
#| label: fig-type1-sim1
#| fig-cap: "Type I Error Rate for Simulation 1"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_type1(study1_data$type1, greys = GREYS_4)
```

```{r}
#| label: fig-power-sim1
#| fig-cap: "Empirical Power for Simulation 1"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_power(study1_data$power, greys = GREYS_4)
```

\clearpage

# Plots — Simulation 2

## Normal

```{r}
#| label: fig-bias-sim2-normal
#| fig-cap: "Absolute Bias for Simulation 2 (Normal)"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_bias(study_2_normal_data$bias, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r}
#| label: fig-relbias-sim2-normal
#| fig-cap: "Relative Bias for Simulation 2 (Normal)"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_bias(study_2_normal_data$bias_relative, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r}
#| label: fig-rmse-sim2-normal
#| fig-cap: "RMSE for Simulation 2 (Normal)"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_rmse(study_2_normal_data$rmse, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r}
#| label: fig-relrmse-sim2-normal
#| fig-cap: "Relative RMSE for Simulation 2 (Normal)"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_rmse(study_2_normal_data$rmse_relative, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r}
#| label: fig-sesd-sim2-normal
#| fig-cap: "SE/SD Ratio for Simulation 2 (Normal)"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_sesd(study_2_normal_data$sesd, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r}
#| label: fig-coverage-sim2-normal
#| fig-cap: "Coverage for Simulation 2 (Normal)"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_coverage(study_2_normal_data$coverage, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r}
#| label: fig-type1-sim2-normal
#| fig-cap: "Type I Error Rate for Simulation 2 (Normal)"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_type1(study_2_normal_data$type1, greys = GREYS_3)
```

```{r}
#| label: fig-power-sim2-normal
#| fig-cap: "Empirical Power for Simulation 2 (Normal)"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_power(study_2_normal_data$power, greys = GREYS_3)
```

\clearpage

## Right-Skewed

```{r}
#| label: fig-bias-sim2-nonnormal
#| fig-cap: "Absolute Bias for Simulation 2 (Right-skewed)"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_bias(study_2_nonnormal_data$bias, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r}
#| label: fig-relbias-sim2-nonnormal
#| fig-cap: "Relative Bias for Simulation 2 (Right-skewed)"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_bias(study_2_nonnormal_data$bias_relative, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r}
#| label: fig-rmse-sim2-nonnormal
#| fig-cap: "RMSE for Simulation 2 (Right-skewed)"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_rmse(study_2_nonnormal_data$rmse, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r}
#| label: fig-relrmse-sim2-nonnormal
#| fig-cap: "Relative RMSE for Simulation 2 (Right-skewed)"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_rmse(study_2_nonnormal_data$rmse_relative, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r}
#| label: fig-sesd-sim2-nonnormal
#| fig-cap: "SE/SD Ratio for Simulation 2 (Right-skewed)"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_sesd(study_2_nonnormal_data$sesd, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r}
#| label: fig-coverage-sim2-nonnormal
#| fig-cap: "Coverage for Simulation 2 (Right-skewed)"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_coverage(study_2_nonnormal_data$coverage, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r}
#| label: fig-type1-sim2-nonnormal
#| fig-cap: "Type I Error Rate for Simulation 2 (Right-skewed)"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_type1(study_2_nonnormal_data$type1, greys = GREYS_3)
```

```{r}
#| label: fig-power-sim2-nonnormal
#| fig-cap: "Empirical Power for Simulation 2 (Right-skewed)"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_power(study_2_nonnormal_data$power, greys = GREYS_3)
```

\clearpage

## Uniform

```{r}
#| label: fig-bias-sim2-uniform
#| fig-cap: "Absolute Bias for Simulation 2 (Uniform)"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_bias(study_2_uniform_data$bias, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r}
#| label: fig-relbias-sim2-uniform
#| fig-cap: "Relative Bias for Simulation 2 (Uniform)"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_bias(study_2_uniform_data$bias_relative, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r}
#| label: fig-rmse-sim2-uniform
#| fig-cap: "RMSE for Simulation 2 (Uniform)"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_rmse(study_2_uniform_data$rmse, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r}
#| label: fig-relrmse-sim2-uniform
#| fig-cap: "Relative RMSE for Simulation 2 (Uniform)"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_rmse(study_2_uniform_data$rmse_relative, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r}
#| label: fig-sesd-sim2-uniform
#| fig-cap: "SE/SD Ratio for Simulation 2 (Uniform)"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_sesd(study_2_uniform_data$sesd, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r}
#| label: fig-coverage-sim2-uniform
#| fig-cap: "Coverage for Simulation 2 (Uniform)"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_coverage(study_2_uniform_data$coverage, shapes = SHAPES_3, ltys = LTYS_3)
```

```{r}
#| label: fig-type1-sim2-uniform
#| fig-cap: "Type I Error Rate for Simulation 2 (Uniform)"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_type1(study_2_uniform_data$type1, greys = GREYS_3)
```

```{r}
#| label: fig-power-sim2-uniform
#| fig-cap: "Empirical Power for Simulation 2 (Uniform)"
#| fig-align: center
#| fig-height: 9
#| fig-width: 7

plot_power(study_2_uniform_data$power, greys = GREYS_3)
```

\clearpage

# Additional Distributional Conditions Plots — Simulation 1

```{r}
#| label: prepare-dumbbell-data

dumbbell_study1 <- prepare_sensitivity_dumbbell_data(results_study_1, study = 1, include_low_rel = FALSE)
```

```{r}
#| label: fig-db-s1-relbias-eps
#| fig-cap: "Additional Distributional Conditions: Relative Bias for Simulation 1 (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study1$bias_relative %>% filter(Error_Condition == "Epsilon"), metric_name = "Relative Bias") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s1-relbias-zeta
#| fig-cap: "Additional Distributional Conditions: Relative Bias for Simulation 1 (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study1$bias_relative %>% filter(Error_Condition == "Zeta"), metric_name = "Relative Bias") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s1-relbias-both
#| fig-cap: "Additional Distributional Conditions: Relative Bias for Simulation 1 (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study1$bias_relative %>% filter(Error_Condition == "Epsilon & Zeta"), metric_name = "Relative Bias") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s1-relrmse-eps
#| fig-cap: "Additional Distributional Conditions: Relative RMSE for Simulation 1 (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study1$rmse_relative %>% filter(Error_Condition == "Epsilon"), metric_name = "Relative RMSE") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s1-relrmse-zeta
#| fig-cap: "Additional Distributional Conditions: Relative RMSE for Simulation 1 (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study1$rmse_relative %>% filter(Error_Condition == "Zeta"), metric_name = "Relative RMSE") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s1-relrmse-both
#| fig-cap: "Additional Distributional Conditions: Relative RMSE for Simulation 1 (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study1$rmse_relative %>% filter(Error_Condition == "Epsilon & Zeta"), metric_name = "Relative RMSE") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s1-sesd-eps
#| fig-cap: "Additional Distributional Conditions: SE/SD Ratio for Simulation 1 (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study1$sesd %>% filter(Error_Condition == "Epsilon"), metric_name = "SE/SD Ratio") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s1-sesd-zeta
#| fig-cap: "Additional Distributional Conditions: SE/SD Ratio for Simulation 1 (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study1$sesd %>% filter(Error_Condition == "Zeta"), metric_name = "SE/SD Ratio") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s1-sesd-both
#| fig-cap: "Additional Distributional Conditions: SE/SD Ratio for Simulation 1 (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study1$sesd %>% filter(Error_Condition == "Epsilon & Zeta"), metric_name = "SE/SD Ratio") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s1-coverage-eps
#| fig-cap: "Additional Distributional Conditions: Coverage for Simulation 1 (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study1$coverage %>% filter(Error_Condition == "Epsilon"), metric_name = "Coverage (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s1-coverage-zeta
#| fig-cap: "Additional Distributional Conditions: Coverage for Simulation 1 (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study1$coverage %>% filter(Error_Condition == "Zeta"), metric_name = "Coverage (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s1-coverage-both
#| fig-cap: "Additional Distributional Conditions: Coverage for Simulation 1 (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study1$coverage %>% filter(Error_Condition == "Epsilon & Zeta"), metric_name = "Coverage (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s1-type1-eps
#| fig-cap: "Additional Distributional Conditions: Type I Error for Simulation 1 (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study1$type1 %>% filter(Error_Condition == "Epsilon"), metric_name = "Type I Error (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s1-type1-zeta
#| fig-cap: "Additional Distributional Conditions: Type I Error for Simulation 1 (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study1$type1 %>% filter(Error_Condition == "Zeta"), metric_name = "Type I Error (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s1-type1-both
#| fig-cap: "Additional Distributional Conditions: Type I Error for Simulation 1 (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study1$type1 %>% filter(Error_Condition == "Epsilon & Zeta"), metric_name = "Type I Error (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s1-power-eps
#| fig-cap: "Additional Distributional Conditions: Power for Simulation 1 (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study1$power %>% filter(Error_Condition == "Epsilon"), metric_name = "Power (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s1-power-zeta
#| fig-cap: "Additional Distributional Conditions: Power for Simulation 1 (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study1$power %>% filter(Error_Condition == "Zeta"), metric_name = "Power (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s1-power-both
#| fig-cap: "Additional Distributional Conditions: Power for Simulation 1 (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study1$power %>% filter(Error_Condition == "Epsilon & Zeta"), metric_name = "Power (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

\clearpage

# Additional Distributional Conditions Plots — Simulation 2

\clearpage

```{r}
#| label: prepare-dumbbell-data-s2-normal

dumbbell_study2_normal <- prepare_sensitivity_dumbbell_data(results_study_2, study = 2, include_low_rel = FALSE, distribution = "normal")
```

```{r}
#| label: fig-db-s2-normal-relbias-eps
#| fig-cap: "Additional Distributional Conditions: Relative Bias for Simulation 2 — Normal (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_normal$bias_relative %>% filter(Error_Condition == "Epsilon"), metric_name = "Relative Bias") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-normal-relbias-zeta
#| fig-cap: "Additional Distributional Conditions: Relative Bias for Simulation 2 — Normal (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_normal$bias_relative %>% filter(Error_Condition == "Zeta"), metric_name = "Relative Bias") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-normal-relbias-both
#| fig-cap: "Additional Distributional Conditions: Relative Bias for Simulation 2 — Normal (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_normal$bias_relative %>% filter(Error_Condition == "Epsilon & Zeta"), metric_name = "Relative Bias") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-normal-relrmse-eps
#| fig-cap: "Additional Distributional Conditions: Relative RMSE for Simulation 2 — Normal (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_normal$rmse_relative %>% filter(Error_Condition == "Epsilon"), metric_name = "Relative RMSE") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-normal-relrmse-zeta
#| fig-cap: "Additional Distributional Conditions: Relative RMSE for Simulation 2 — Normal (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_normal$rmse_relative %>% filter(Error_Condition == "Zeta"), metric_name = "Relative RMSE") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-normal-relrmse-both
#| fig-cap: "Additional Distributional Conditions: Relative RMSE for Simulation 2 — Normal (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_normal$rmse_relative %>% filter(Error_Condition == "Epsilon & Zeta"), metric_name = "Relative RMSE") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-normal-sesd-eps
#| fig-cap: "Additional Distributional Conditions: SE/SD Ratio for Simulation 2 — Normal (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_normal$sesd %>% filter(Error_Condition == "Epsilon"), metric_name = "SE/SD Ratio") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-normal-sesd-zeta
#| fig-cap: "Additional Distributional Conditions: SE/SD Ratio for Simulation 2 — Normal (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_normal$sesd %>% filter(Error_Condition == "Zeta"), metric_name = "SE/SD Ratio") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-normal-sesd-both
#| fig-cap: "Additional Distributional Conditions: SE/SD Ratio for Simulation 2 — Normal (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_normal$sesd %>% filter(Error_Condition == "Epsilon & Zeta"), metric_name = "SE/SD Ratio") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-normal-coverage-eps
#| fig-cap: "Additional Distributional Conditions: Coverage for Simulation 2 — Normal (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_normal$coverage %>% filter(Error_Condition == "Epsilon"), metric_name = "Coverage (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-normal-coverage-zeta
#| fig-cap: "Additional Distributional Conditions: Coverage for Simulation 2 — Normal (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_normal$coverage %>% filter(Error_Condition == "Zeta"), metric_name = "Coverage (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-normal-coverage-both
#| fig-cap: "Additional Distributional Conditions: Coverage for Simulation 2 — Normal (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_normal$coverage %>% filter(Error_Condition == "Epsilon & Zeta"), metric_name = "Coverage (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-normal-type1-eps
#| fig-cap: "Additional Distributional Conditions: Type I Error for Simulation 2 — Normal (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_normal$type1 %>% filter(Error_Condition == "Epsilon"), metric_name = "Type I Error (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-normal-type1-zeta
#| fig-cap: "Additional Distributional Conditions: Type I Error for Simulation 2 — Normal (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_normal$type1 %>% filter(Error_Condition == "Zeta"), metric_name = "Type I Error (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-normal-type1-both
#| fig-cap: "Additional Distributional Conditions: Type I Error for Simulation 2 — Normal (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_normal$type1 %>% filter(Error_Condition == "Epsilon & Zeta"), metric_name = "Type I Error (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-normal-power-eps
#| fig-cap: "Additional Distributional Conditions: Power for Simulation 2 — Normal (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_normal$power %>% filter(Error_Condition == "Epsilon"), metric_name = "Power (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-normal-power-zeta
#| fig-cap: "Additional Distributional Conditions: Power for Simulation 2 — Normal (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_normal$power %>% filter(Error_Condition == "Zeta"), metric_name = "Power (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-normal-power-both
#| fig-cap: "Additional Distributional Conditions: Power for Simulation 2 — Normal (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_normal$power %>% filter(Error_Condition == "Epsilon & Zeta"), metric_name = "Power (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

\clearpage

```{r}
#| label: prepare-dumbbell-data-s2-nonnormal

dumbbell_study2_nonnormal <- prepare_sensitivity_dumbbell_data(results_study_2, study = 2, include_low_rel = FALSE, distribution = "nonnormal")
```

```{r}
#| label: fig-db-s2-nonnormal-relbias-eps
#| fig-cap: "Additional Distributional Conditions: Relative Bias for Simulation 2 — Right-skewed (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_nonnormal$bias_relative %>% filter(Error_Condition == "Epsilon"), metric_name = "Relative Bias") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-nonnormal-relbias-zeta
#| fig-cap: "Additional Distributional Conditions: Relative Bias for Simulation 2 — Right-skewed (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_nonnormal$bias_relative %>% filter(Error_Condition == "Zeta"), metric_name = "Relative Bias") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-nonnormal-relbias-both
#| fig-cap: "Additional Distributional Conditions: Relative Bias for Simulation 2 — Right-skewed (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_nonnormal$bias_relative %>% filter(Error_Condition == "Epsilon & Zeta"), metric_name = "Relative Bias") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-nonnormal-relrmse-eps
#| fig-cap: "Additional Distributional Conditions: Relative RMSE for Simulation 2 — Right-skewed (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_nonnormal$rmse_relative %>% filter(Error_Condition == "Epsilon"), metric_name = "Relative RMSE") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-nonnormal-relrmse-zeta
#| fig-cap: "Additional Distributional Conditions: Relative RMSE for Simulation 2 — Right-skewed (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_nonnormal$rmse_relative %>% filter(Error_Condition == "Zeta"), metric_name = "Relative RMSE") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-nonnormal-relrmse-both
#| fig-cap: "Additional Distributional Conditions: Relative RMSE for Simulation 2 — Right-skewed (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_nonnormal$rmse_relative %>% filter(Error_Condition == "Epsilon & Zeta"), metric_name = "Relative RMSE") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-nonnormal-sesd-eps
#| fig-cap: "Additional Distributional Conditions: SE/SD Ratio for Simulation 2 — Right-skewed (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_nonnormal$sesd %>% filter(Error_Condition == "Epsilon"), metric_name = "SE/SD Ratio") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-nonnormal-sesd-zeta
#| fig-cap: "Additional Distributional Conditions: SE/SD Ratio for Simulation 2 — Right-skewed (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_nonnormal$sesd %>% filter(Error_Condition == "Zeta"), metric_name = "SE/SD Ratio") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-nonnormal-sesd-both
#| fig-cap: "Additional Distributional Conditions: SE/SD Ratio for Simulation 2 — Right-skewed (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_nonnormal$sesd %>% filter(Error_Condition == "Epsilon & Zeta"), metric_name = "SE/SD Ratio") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-nonnormal-coverage-eps
#| fig-cap: "Additional Distributional Conditions: Coverage for Simulation 2 — Right-skewed (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_nonnormal$coverage %>% filter(Error_Condition == "Epsilon"), metric_name = "Coverage (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-nonnormal-coverage-zeta
#| fig-cap: "Additional Distributional Conditions: Coverage for Simulation 2 — Right-skewed (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_nonnormal$coverage %>% filter(Error_Condition == "Zeta"), metric_name = "Coverage (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-nonnormal-coverage-both
#| fig-cap: "Additional Distributional Conditions: Coverage for Simulation 2 — Right-skewed (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_nonnormal$coverage %>% filter(Error_Condition == "Epsilon & Zeta"), metric_name = "Coverage (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-nonnormal-type1-eps
#| fig-cap: "Additional Distributional Conditions: Type I Error for Simulation 2 — Right-skewed (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_nonnormal$type1 %>% filter(Error_Condition == "Epsilon"), metric_name = "Type I Error (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-nonnormal-type1-zeta
#| fig-cap: "Additional Distributional Conditions: Type I Error for Simulation 2 — Right-skewed (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_nonnormal$type1 %>% filter(Error_Condition == "Zeta"), metric_name = "Type I Error (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-nonnormal-type1-both
#| fig-cap: "Additional Distributional Conditions: Type I Error for Simulation 2 — Right-skewed (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_nonnormal$type1 %>% filter(Error_Condition == "Epsilon & Zeta"), metric_name = "Type I Error (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-nonnormal-power-eps
#| fig-cap: "Additional Distributional Conditions: Power for Simulation 2 — Right-skewed (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_nonnormal$power %>% filter(Error_Condition == "Epsilon"), metric_name = "Power (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-nonnormal-power-zeta
#| fig-cap: "Additional Distributional Conditions: Power for Simulation 2 — Right-skewed (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_nonnormal$power %>% filter(Error_Condition == "Zeta"), metric_name = "Power (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-nonnormal-power-both
#| fig-cap: "Additional Distributional Conditions: Power for Simulation 2 — Right-skewed (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_nonnormal$power %>% filter(Error_Condition == "Epsilon & Zeta"), metric_name = "Power (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

\clearpage

```{r}
#| label: prepare-dumbbell-data-s2-uniform

dumbbell_study2_uniform <- prepare_sensitivity_dumbbell_data(results_study_2, study = 2, include_low_rel = FALSE, distribution = "uniform")
```

```{r}
#| label: fig-db-s2-uniform-relbias-eps
#| fig-cap: "Additional Distributional Conditions: Relative Bias for Simulation 2 — Uniform (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_uniform$bias_relative %>% filter(Error_Condition == "Epsilon"), metric_name = "Relative Bias") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-uniform-relbias-zeta
#| fig-cap: "Additional Distributional Conditions: Relative Bias for Simulation 2 — Uniform (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_uniform$bias_relative %>% filter(Error_Condition == "Zeta"), metric_name = "Relative Bias") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-uniform-relbias-both
#| fig-cap: "Additional Distributional Conditions: Relative Bias for Simulation 2 — Uniform (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_uniform$bias_relative %>% filter(Error_Condition == "Epsilon & Zeta"), metric_name = "Relative Bias") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-uniform-relrmse-eps
#| fig-cap: "Additional Distributional Conditions: Relative RMSE for Simulation 2 — Uniform (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_uniform$rmse_relative %>% filter(Error_Condition == "Epsilon"), metric_name = "Relative RMSE") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-uniform-relrmse-zeta
#| fig-cap: "Additional Distributional Conditions: Relative RMSE for Simulation 2 — Uniform (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_uniform$rmse_relative %>% filter(Error_Condition == "Zeta"), metric_name = "Relative RMSE") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-uniform-relrmse-both
#| fig-cap: "Additional Distributional Conditions: Relative RMSE for Simulation 2 — Uniform (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_uniform$rmse_relative %>% filter(Error_Condition == "Epsilon & Zeta"), metric_name = "Relative RMSE") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-uniform-sesd-eps
#| fig-cap: "Additional Distributional Conditions: SE/SD Ratio for Simulation 2 — Uniform (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_uniform$sesd %>% filter(Error_Condition == "Epsilon"), metric_name = "SE/SD Ratio") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-uniform-sesd-zeta
#| fig-cap: "Additional Distributional Conditions: SE/SD Ratio for Simulation 2 — Uniform (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_uniform$sesd %>% filter(Error_Condition == "Zeta"), metric_name = "SE/SD Ratio") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-uniform-sesd-both
#| fig-cap: "Additional Distributional Conditions: SE/SD Ratio for Simulation 2 — Uniform (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_uniform$sesd %>% filter(Error_Condition == "Epsilon & Zeta"), metric_name = "SE/SD Ratio") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-uniform-coverage-eps
#| fig-cap: "Additional Distributional Conditions: Coverage for Simulation 2 — Uniform (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_uniform$coverage %>% filter(Error_Condition == "Epsilon"), metric_name = "Coverage (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-uniform-coverage-zeta
#| fig-cap: "Additional Distributional Conditions: Coverage for Simulation 2 — Uniform (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_uniform$coverage %>% filter(Error_Condition == "Zeta"), metric_name = "Coverage (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-uniform-coverage-both
#| fig-cap: "Additional Distributional Conditions: Coverage for Simulation 2 — Uniform (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_uniform$coverage %>% filter(Error_Condition == "Epsilon & Zeta"), metric_name = "Coverage (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-uniform-type1-eps
#| fig-cap: "Additional Distributional Conditions: Type I Error for Simulation 2 — Uniform (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_uniform$type1 %>% filter(Error_Condition == "Epsilon"), metric_name = "Type I Error (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-uniform-type1-zeta
#| fig-cap: "Additional Distributional Conditions: Type I Error for Simulation 2 — Uniform (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_uniform$type1 %>% filter(Error_Condition == "Zeta"), metric_name = "Type I Error (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-uniform-type1-both
#| fig-cap: "Additional Distributional Conditions: Type I Error for Simulation 2 — Uniform (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_uniform$type1 %>% filter(Error_Condition == "Epsilon & Zeta"), metric_name = "Type I Error (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-uniform-power-eps
#| fig-cap: "Additional Distributional Conditions: Power for Simulation 2 — Uniform (Epsilon)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_uniform$power %>% filter(Error_Condition == "Epsilon"), metric_name = "Power (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-uniform-power-zeta
#| fig-cap: "Additional Distributional Conditions: Power for Simulation 2 — Uniform (Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_uniform$power %>% filter(Error_Condition == "Zeta"), metric_name = "Power (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```

```{r}
#| label: fig-db-s2-uniform-power-both
#| fig-cap: "Additional Distributional Conditions: Power for Simulation 2 — Uniform (Epsilon & Zeta)"
#| fig-height: 14
#| fig-width: 12

plot_dumbbell(dumbbell_study2_uniform$power %>% filter(Error_Condition == "Epsilon & Zeta"), metric_name = "Power (%)") +
  facet_grid(Distribution + Parameter ~ SampleSize + Reliability,
             labeller = labeller(Parameter = label_parsed))
```
